---
title: "Spatial CRT Simulation - Heterogeneous Incidence"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output: html_document
---

### Preliminaries

* Design extension to project 1 "Spatial Cluster Randomized Trials - Sampling Design with Spillover Effects & Spatial Dependence" that incorporates heterogeneous incidence of the primary outcome.
* Consider multiple potential design strategies (Null Scenario, Intervention-High Incidence, Block stratification among high/low incidence) to address optimal strategy for study design with heterogeneous outcome incidence
* Understand which design achieves best estimation efficiency (minimal error) -> Sampling strategies when there is spillover, spatial dependence, and heterogeneous incidence of the outcome.
* How can we "best" design a study with known historical data on outcome incidences

```{r, message=FALSE, warning=FALSE}
# --- Load Libraries ---
library(tidyverse)
library(sf)
library(patchwork)
library(grid)
```

### Study Region Setup

```{r}

```

### Outcome Incidence Assignment

```{r}

```

