---
title: "9/30 Simulation 10 by 10"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output: html_document
---

```{r, message=FALSE, warning=FALSE}
### Data generation for simulation in 10x10 grids ###
# load packages
library(raster) # geographic data analysis and modeling, raster grids
library(sf) # spatial objects
library(spdep) # neighborhood structures & spatial dependencies
library(MASS) # g-inverse, stat functions
library(mnormt) # MVN distribution functions
```

```{r}
### generate data ###
# X by X raster grid
cnt <- 2
r <- raster(xmn = 0, xmx = cnt, ymn = 0, ymx = cnt, nrow = cnt, ncol = cnt)

# assign values to every raster cell
r$value <- 1:ncell(r)

# convert raster to polygons
r.sp <- rasterToPolygons(r)

# obtain center coordinates of each polygon
r.center <- coordinates(r.sp)

# convert raster to df (add x & y coordinates)
r.data <- as.data.frame(r)
r.data <- data.frame(r.data,x = r.center[,1],y = r.center[,2])

# convert polygons to simple feature object & set attribute-geometry relationship "constant"
r.sf <- st_as_sf(r.sp)
st_agr(r.sf) = "constant"
```

- section creates a X by X spatial grid with `raster` package, converts it to polygons, and extracts the coordinates of the center of each cell. data is then stored in the data frame.

- `sf` package is used for handling spatial objects. The spatial feature object `r.sf` is created from the polygons.

```{r}
### neighborhood structure ###
# spatial neighborhood structure
nb <- nblag(poly2nb(r.sf), 2)

# created identity matrix & neighborhood weight matrices
nb0 <- diag(nrow(r.sf)) # identity matrix
nb1 <- nb2mat(nb[[1]], style="B") # 1st order neighborhood

# Conditional handling of second-order neighbors
if (cnt >= 3) {
  nb <- nblag(poly2nb(r.sf), 2)  # Expand to second-order neighbors for cnt >= 3
  nb2 <- nb2mat(nb[[2]], style = "B", zero.policy = TRUE)  # Second-order neighborhood matrix
  print(nb2)
} else {
  print(nb1)
}
```

- `poly2nb` defines neighbors based on the adjacency of polygons. `nblag` generates neighbor lists for up to two lags (1st and 2nd order)

- `nb2mat` function creates weight matrices (`nb1` and `nb2`) for the neighborhood structure, used in the simulation to model spatial dependence.

- `nb0` is an identity matrix used for base calculations.

```{r}
### Simulation Setting ###
# parameters
n <- nrow(r.data) # number of observations
N_rep <- 500 # simulation repetitions
sim.sigma.vec <- c(sqrt(0.01), sqrt(0.05), sqrt(0.1), sqrt(0.2)) # list of simulation variances
beta0.vec <- c(-0.5, 0, 0.5) #  list of intercepts
beta1.vec <- c(0.5, 1) # list of slopes
rho <- 0.1 # spatial autocorrelation parameter
omega <- nb1 # 1st order neighborhood matrix as spatial weight
I.tot <- diag(n) # ID matrix (I)

# simulation iteration counter (start at 0)
set.cnt <- 0

# for loops: outer loops of parameter combos (variance/intercept/slope)
for(sim.sigma in sim.sigma.vec) {
  for(beta0 in beta0.vec) {
    for(beta1 in beta1.vec) {
      # increment simulation counter (+1)
      set.cnt <- set.cnt + 1 
      # spatial dependence covariance matrix
      covar.mat <- (sim.sigma ^ 2) * ginv(I.tot - rho * omega)
      # matrices to store covariates (x) & responses (y)
      y.data <- x.data <- matrix(0, n, N_rep)
      
      # loop over every simulation repetition
      for(i in 1:N_rep){
        covariate <- rnorm(n = n, mean = 0, sd = 1) # random covariates (length n)
        epsilon <- rmnorm(n = 1, mean = rep(0, n), varcov = covar.mat) # Spatially correlated error term
        response <- beta0 + beta1 * covariate + epsilon # simulated response (outcome value)
        
        x.data[,i] <- covariate # save covariate
        y.data[,i] <- response # save response
      }
      
      # # call mixture function on one of sim datasets
      # X.in <- x.data[,1]  # Covariates from first simulation
      # Y.in <- y.data[,1]  # Response from first simulation
      # W <- nb2mat(nb[[1]], style = "B")  # Neighborhood matrix
      # 
      # mixture_results <- Mixture(X.in, Y.in, W)
      # 
      # # Print or store results
      # print(mixture_results)
      
      # assign column names to x,y data; combine into dataframe
      colnames(x.data) <- paste0("sim_x", c(1:N_rep))
      colnames(y.data) <- paste0("sim_y", c(1:N_rep))
      sim_data <- cbind(r.data, x.data, y.data)
      
      # save simulation data to csv file
      write.csv(sim_data,paste0("sim_data", set.cnt, ".csv"), row.names = F) 
    } 
  } 
}
```

- run simulation for generating spatial data with multiple repetitions (500) and parameter combos (variance/intercept/slope)

- for each repetition, a random covariate is generated, and the response variable is calculated based on a linear model with spatially correlated errors (epsilon)

- save data in a CSV file with unique IDs for each set of parameters (variance/intercept/slope)

```{r}
## Mixture estimating equations
Mixture <- function(X.in, Y.in, Sp.mat.ori, max.iter = 30){
  X_0 <- X.in * pi / sqrt(3) # Omega_0
  X.in <- as.matrix(X.in) # convert to matrix
  Y.in <- as.matrix(Y.in) # convert to matrix
  W <- as.matrix(Sp.mat.ori) # spatial weights matrix
  
  # obtain initial values w/ spatial autoregressive model
  spreg.1 <- spatialreg::spautolm(Y.in ~ as.matrix(X.in[, -1]) , listw = mat2listw(W), family = "CAR", method="eigen")
  rho.0 <- spreg.1$lambda
  Beta.0 <- as.matrix(spreg.1$fit$coefficients)
  sigma.0 <- sqrt(spreg.1$fit$s2)
  
  # Newton-Raphson iteration for estimating equations
  Beta.old <- Beta.0
  sigma.old <- sigma.0
  rho.old <- rho.0
  iter <- 0
  
  repeat{
    iter <- iter + 1
    
    # Equation (2.7) for updating Beta (no zero-inflation)
    Q1 <- function(x) {
      B <- as.matrix(x)
      Q1 <- sigma.old^(-2) * t(X.in) %*% (Y.in - X.in %*% B)
      as.numeric(Q1)
    }
    
    # Update Beta using multiroot
    Beta.new <- as.matrix(multiroot(Q1, start = Beta.old, atol = 1e-4)$root)
    
    # Equation (2.8) - updating sigma
    sigma.new <- as.vector(sqrt(t(Y.in - X.in %*% Beta.new) %*% (Y.in - X.in %*% Beta.new) / n))
    
    # Equation (2.9) - updating rho
    Q3 <- function(x) {
      Q3 <- sum(eigen(W)$values / (1 - x * eigen(W)$values)) -
        sigma.new^(-2) * t(Y.in - X.in %*% Beta.new) %*% W %*% (Y.in - X.in %*% Beta.new)
      as.numeric(Q3)
    }
    
    VQ3 <- Vectorize(Q3)
    rho.new.test <- uniroot.all(f = VQ3, c(1 / min(eigen(W)$values), 1 / max(eigen(W)$values)))
    rho.new.pos <- rho.new.test[rho.new.test > 0]
    rho.new <- rho.new.pos[which.min(abs(rho.new.pos - rho.old))]
    if (length(rho.new) == 0) rho.new <- 0
    
    # Update values for next iteration
    Beta.old <- Beta.new
    sigma.old <- sigma.new
    rho.old <- rho.new
    
    if (iter >= max.iter) break
  }
  
  # Sandwich estimator
  Sigma.beta.mod <- (sigma.new^2) * ginv(t(X.in) %*% X.in)
  AV <- diag(Sigma.beta.mod)
  
  list(coef = Beta.new, 
       sd = sqrt(AV), 
       sigma = sigma.new, 
       rho = rho.new, 
       iter = iter, 
       covbetahat = Sigma.beta.mod)
}
```

- mixture estimating equation function: estimates SAR model parameters (beta/sigma/rho) with N-R iterative method

- iteratively updates parameters and uses the sandwich estimator to compute the standard errors of the coefficient estimates

```{r}
# # Example to call the Mixture function on one set of simulated data
# # Assume you have generated x.data and y.data (covariates and responses) as shown earlier
# 
# # Select one simulated dataset (e.g., the first repetition)
# X.in <- x.data[, 1]  # Covariate from the first simulation
# Y.in <- y.data[, 1]  # Response from the first simulation
# 
# # W is the spatial weight matrix (neighborhood structure)
# W <- nb2mat(nb[[1]], style = "B")  # First order neighbor matrix
# 
# # Call the Mixture function
# mixture_results <- Mixture(X.in, Y.in, W, max.iter = 30)
# 
# # Print the results
# print(mixture_results)
```

```{r}
# Example call to Mixture() using simulated data
# Select the first replication of covariates and responses
X.in <- x.data[, 1] # Covariate from the first simulation
Y.in <- y.data[, 1] # Response from the first simulation

# Call the Mixture function using the neighborhood matrix nb1 or nb2 (if available)
if (cnt >= 3) {
  mixture_results <- Mixture(X.in, Y.in, nb2, max.iter = 30)
} else {
  mixture_results <- Mixture(X.in, Y.in, nb1, max.iter = 30)
}

# Display the results from the Mixture function
print(mixture_results)
```

