---
title: "Incidence-Guided Treatment Assignment Designs for Spatial Cluster Randomized Trials"
subtitle: "Comprehensive Simulation Study Report"
author: "Andrew Walther"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    theme: cosmo
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    latex-engine: xelatex
    keep-tex: false
    fig-pos: "htbp"
    fig-height: 4
    fig-width: 6.5
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{float}
        \usepackage{amsmath}
        \usepackage{amssymb}
        \usepackage{geometry}
        \usepackage{xcolor}
        \usepackage{mdframed}
        \geometry{margin=1in}
        \floatplacement{figure}{htbp}
        \floatplacement{table}{H}
        \definecolor{boxbg}{RGB}{240,248,255}
        \definecolor{boxframe}{RGB}{70,130,180}
bibliography: ../section_drafts/references.bib
---

```{r setup}
#| include: false
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.pos = "htbp"
)
```

```{r load-packages}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)
```

```{r resolve-paths}
#| include: false
# This report lives in paper/report/; code modules are in ../../code/
script_dir <- normalizePath(file.path(
  dirname(knitr::current_input(dir = TRUE)), "..", "..", "code"
), mustWork = FALSE)
results_dir <- normalizePath(file.path(
  dirname(knitr::current_input(dir = TRUE)), "..", "..", "results"
), mustWork = FALSE)
```

```{r source-modules}
#| include: false
# Source 08_design_recommendations.R (transitively sources 06 -> 01-03)
# Must temporarily set working directory to code/ so internal path resolution works
orig_wd <- getwd()
setwd(script_dir)
source(file.path(script_dir, "08_design_recommendations.R"))
setwd(orig_wd)
```

```{r load-results}
#| include: false
mle_results <- tryCatch(
  load_latest_results(results_dir, estimation_mode = "MLE_combined"),
  error = function(e) {
    message("MLE combined results not found: ", e$message)
    NULL
  }
)
mle_avail <- !is.null(mle_results) && nrow(mle_results) > 0
mle_cfgs  <- if (mle_avail) split_by_incidence_config(mle_results) else list()
cfg_names <- names(mle_cfgs)
```

```{r global-summaries}
#| include: false
if (mle_avail) {
  # Design IDs and names from data
  active_design_ids <- sort(unique(as.integer(
    gsub("Design ", "", mle_results$Design)
  )))
  n_designs <- length(active_design_ids)

  # Scenario counts
  n_scenarios_total <- nrow(mle_results)
  n_scenarios_per_config <- n_scenarios_total / length(mle_cfgs)

  # Parameter levels
  rho_levels   <- sort(unique(mle_results$Rho))
  gamma_levels <- sort(unique(mle_results$Gamma))
  spill_levels <- sort(unique(mle_results$Spillover_Type))
  nb_levels    <- sort(unique(mle_results$Neighbor_Type))
  n_params_per_design <- n_scenarios_per_config / n_designs

  # Overall summary statistics
  mle_summary <- mle_results %>%
    summarise(
      N_scenarios   = n(),
      Bias_min      = round(min(Bias, na.rm = TRUE), 3),
      Bias_max      = round(max(Bias, na.rm = TRUE), 3),
      Bias_mean     = round(mean(Bias, na.rm = TRUE), 3),
      MSE_min       = round(min(MSE, na.rm = TRUE), 3),
      MSE_max       = round(max(MSE, na.rm = TRUE), 3),
      MSE_mean      = round(mean(MSE, na.rm = TRUE), 3),
      Cov_min       = round(min(Coverage, na.rm = TRUE), 2),
      Cov_max       = round(max(Coverage, na.rm = TRUE), 2),
      Cov_mean      = round(mean(Coverage, na.rm = TRUE), 2),
      Fail_mean     = round(mean(Fail_Rate, na.rm = TRUE), 4)
    )

  # Per-design summary
  mle_by_design <- mle_results %>%
    group_by(Design) %>%
    summarise(
      Mean_Bias     = round(mean(Bias, na.rm = TRUE), 3),
      Median_MSE    = round(median(MSE, na.rm = TRUE), 3),
      Mean_MSE      = round(mean(MSE, na.rm = TRUE), 3),
      Mean_Coverage = round(mean(Coverage, na.rm = TRUE), 3),
      Fail_Rate     = round(mean(Fail_Rate, na.rm = TRUE), 4),
      .groups       = "drop"
    ) %>%
    arrange(Mean_MSE)

  # Ranked summary per config
  all_ranked_list <- lapply(seq_along(mle_cfgs), function(i) {
    r <- rank_designs_by_group(mle_cfgs[[i]], character(0))
    r$Inc_Config <- cfg_names[i]
    r
  })
  all_ranked <- bind_rows(all_ranked_list)

  # Best and worst per config
  best_per_config <- all_ranked %>%
    filter(Rank == 1) %>%
    select(Inc_Config, Design, Avg_MSE, Avg_Coverage)
  worst_per_config <- all_ranked %>%
    filter(Rank == n_designs) %>%
    select(Inc_Config, Design, Avg_MSE, Avg_Coverage)

  # Modal best and worst
  modal_best       <- names(sort(table(best_per_config$Design), decreasing = TRUE))[1]
  modal_best_short <- short_design_name(modal_best)
  n_configs_modal_best_wins <- sum(best_per_config$Design == modal_best)
  worst_design       <- names(sort(table(worst_per_config$Design), decreasing = TRUE))[1]
  worst_design_short <- short_design_name(worst_design)

  # Overall rankings
  overall_all <- rank_designs_by_group(mle_results, character(0))
  best_overall       <- overall_all %>% filter(Rank == 1)
  worst_overall      <- overall_all %>% filter(Rank == max(Rank))
  overall_mse_ratio  <- round(worst_overall$Avg_MSE[1] / best_overall$Avg_MSE[1], 1)
  best_overall_short  <- short_design_name(best_overall$Design[1])
  worst_overall_short <- short_design_name(worst_overall$Design[1])

  # MSE ratio range across configs
  mse_ratio_per_config <- all_ranked %>%
    group_by(Inc_Config) %>%
    summarise(
      best_mse  = Avg_MSE[Rank == 1],
      worst_mse = Avg_MSE[Rank == max(Rank)],
      ratio     = round(worst_mse / best_mse, 1),
      .groups   = "drop"
    )
  mse_ratio_range <- paste0(
    min(mse_ratio_per_config$ratio), "--", max(mse_ratio_per_config$ratio)
  )

  # Worst design coverage range
  worst_cov_vals <- worst_per_config$Avg_Coverage
  worst_cov_range <- paste0(
    round(min(worst_cov_vals), 2), "--", round(max(worst_cov_vals), 2)
  )

  # Spillover analysis
  spill_rankings <- lapply(cfg_names, function(cn) {
    cfg <- mle_cfgs[[cn]]
    r <- rank_designs_by_group(cfg, "Spillover_Type")
    r$Inc_Config <- cn
    r
  })
  spill_all <- bind_rows(spill_rankings)

  best_under_control_only <- spill_all %>%
    filter(Spillover_Type == "control_only", Rank == 1) %>%
    count(Design) %>% arrange(desc(n)) %>% slice(1) %>% pull(Design)
  best_under_control_only_short <- short_design_name(best_under_control_only)

  best_under_both <- spill_all %>%
    filter(Spillover_Type == "both", Rank == 1) %>%
    count(Design) %>% arrange(desc(n)) %>% slice(1) %>% pull(Design)
  best_under_both_short <- short_design_name(best_under_both)

  # Runner-up margin
  runner_up_margins <- all_ranked %>%
    group_by(Inc_Config) %>%
    summarise(
      best_mse   = Avg_MSE[Rank == 1],
      second_mse = Avg_MSE[Rank == 2],
      pct_margin = round((second_mse - best_mse) / best_mse * 100, 1),
      .groups    = "drop"
    )

  # Gamma sensitivity
  gamma_eta_vals <- sapply(cfg_names, function(cn) {
    d_data <- mle_cfgs[[cn]] %>% filter(Design == modal_best)
    gm    <- mean(d_data$MSE, na.rm = TRUE)
    ss_tot <- sum((d_data$MSE - gm)^2, na.rm = TRUE)
    if (ss_tot == 0) return(0)
    gs <- d_data %>%
      group_by(Gamma) %>%
      summarise(gm2 = mean(MSE, na.rm = TRUE), gn = n(), .groups = "drop")
    ss_b <- sum(gs$gn * (gs$gm2 - gm)^2)
    ss_b / ss_tot
  })
  max_gamma_eta <- round(max(gamma_eta_vals), 3)

  # Leading design coverage range
  other_designs_cov <- all_ranked %>%
    filter(Design != worst_design) %>%
    pull(Avg_Coverage)
  leading_cov_lo <- round(min(other_designs_cov), 2)
  leading_cov_hi <- round(max(other_designs_cov), 2)

  # Derived narrative values
  best_design       <- mle_by_design$Design[1]
  worst_design_name <- mle_by_design$Design[nrow(mle_by_design)]
  best_mse          <- mle_by_design$Mean_MSE[1]
  worst_mse         <- mle_by_design$Mean_MSE[nrow(mle_by_design)]
  best_coverage     <- mle_by_design$Mean_Coverage[1]
  worst_coverage    <- mle_by_design$Mean_Coverage[nrow(mle_by_design)]
  overall_cov_mean  <- round(mean(mle_results$Coverage, na.rm = TRUE), 2)
}
```

# Introduction

This report provides a comprehensive reference for the simulation study evaluating **`r if (mle_avail) n_designs` treatment assignment designs** for Spatial Cluster Randomized Trials (CRTs) when outcome incidence is heterogeneous and spatially structured.

> *Given known historical incidence data exhibiting spatial heterogeneity, which treatment assignment strategy minimizes estimation error for the direct intervention effect $\hat{\tau}$ across a range of spatial dependence and spillover configurations?*

**Application context:** Sudden Unexpected Death (SUD) in North Carolina counties. The Poisson incidence mode uses an SUD base rate of 35 per 100,000, consistent with county-level analyses.

The study uses Maximum Likelihood Estimation via a spatial autoregressive model (MLE) as the primary estimator, evaluated across `r if (mle_avail) format(n_scenarios_total, big.mark = ",")` parameter scenarios. Three analytical questions structure the results:

- **Q1:** Which design performs best within each incidence generation mode?
- **Q2:** How do design rankings change as individual parameters vary?
- **Q3:** Which design wins for specific parameter combinations?

---

# Study Region and Spatial Structure {#sec-spatial}

The study region is a regular square lattice grid:

$$\mathcal{G} = \{s_1, s_2, \ldots, s_N\}$$

where each cluster $s_i$ is located at integer coordinates $(x_i, y_i)$ on a $G \times G$ grid, so $N = G^2$. In this study, $G = 10$ and $N = 100$.

## Spatial Contiguity

Two contiguity definitions are considered:

- **Rook contiguity**: clusters sharing an edge (4-connected).
$$\mathcal{N}_R(s_i) = \{s_j : |x_i - x_j| + |y_i - y_j| = 1\}$$

- **Queen contiguity**: clusters sharing an edge or vertex (8-connected).
$$\mathcal{N}_Q(s_i) = \{s_j : \max(|x_i - x_j|, |y_i - y_j|) = 1\}$$

## Spatial Weight Matrix

Let $\mathbf{A}$ denote the binary adjacency matrix where $A_{ij} = \mathbf{1}[s_j \in \mathcal{N}(s_i)]$. The row-standardized spatial weight matrix is:

$$W_{ij} = \frac{A_{ij}}{\sum_{k=1}^{N} A_{ik}}, \quad i \neq j; \quad W_{ii} = 0$$

This ensures $\sum_j W_{ij} = 1$ for each row, so spatial lags represent neighborhood averages. We construct $\mathbf{W}_R$ (rook) and $\mathbf{W}_Q$ (queen) weight matrices.

---

# Outcome Data Generating Process {#sec-dgp}

## Spatial Durbin Model (SDM)

The outcome vector $\mathbf{Y} = (Y_1, \ldots, Y_N)^\top$ is generated from the Spatial Durbin Model:

$$\mathbf{Y} = (\mathbf{I}_N - \rho\mathbf{W})^{-1}\left[\tau\mathbf{Z} + \gamma \cdot \text{Spill}(\mathbf{Z}) + \beta\mathbf{X} + \boldsymbol{\varepsilon}\right]$$

where:

| Symbol | Description | Role |
|:---:|:---|:---|
| $\mathbf{Y}$ | $N \times 1$ outcome vector | Response |
| $\rho$ | Spatial autocorrelation parameter | Controls global spatial dependence in $\mathbf{Y}$ |
| $\mathbf{W}$ | $N \times N$ row-standardized weight matrix | Spatial structure (rook or queen) |
| $\tau$ | Direct treatment effect | **Estimand of interest** |
| $\mathbf{Z}$ | $N \times 1$ binary treatment vector | $Z_i \in \{0, 1\}$ |
| $\gamma$ | Spillover effect magnitude | Indirect effect via treated neighbors |
| $\text{Spill}(\mathbf{Z})$ | $N \times 1$ spillover term | See below |
| $\beta$ | Effect of baseline incidence on outcome | Covariate coefficient |
| $\mathbf{X}$ | $N \times 1$ baseline incidence vector | $X_i \in [0, 1]$ |
| $\boldsymbol{\varepsilon}$ | $N \times 1$ error vector | $\varepsilon_i \overset{\text{iid}}{\sim} N(0, \sigma^2)$ |

The spatial multiplier $(\mathbf{I}_N - \rho\mathbf{W})^{-1}$ induces global spatial dependence.

**Stationarity condition:** $|\rho| < 1 / \lambda_{\max}(\mathbf{W})$. For row-standardized $\mathbf{W}$, $\lambda_{\max} = 1$, so $|\rho| < 1$.

## Spillover Construction

$$\text{Spill}_i = \frac{\sum_{j \in \mathcal{N}(i)} Z_j}{|\mathcal{N}(i)|} = (\mathbf{W}\mathbf{Z})_i$$

Two spillover types are considered:

1. **Control-only spillover**: $\text{Spill}_i^{(\text{ctrl})} = \gamma \cdot (\mathbf{W}\mathbf{Z})_i \cdot (1 - Z_i)$
2. **Bidirectional spillover**: $\text{Spill}_i^{(\text{both})} = \gamma \cdot (\mathbf{W}\mathbf{Z})_i$

---

# Incidence Generation Modes {#sec-incidence}

The baseline incidence vector $\mathbf{X}$ represents prior observed outcome rates. Three generation modes are considered, all producing values in $[0, 1]$.

## Mode 1: Independent and Identically Distributed (iid)

$$X_i \overset{\text{iid}}{\sim} \text{Uniform}(0, 1), \quad i = 1, \ldots, N$$

No spatial structure; serves as the baseline. One config ($\rho_X$ = N/A).

## Mode 2: Spatially Correlated (SAR Filter)

$$\mathbf{X}^* = (\mathbf{I}_N - \rho_X \mathbf{W})^{-1}\mathbf{u}, \quad \mathbf{u} \sim N(\mathbf{0}, \mathbf{I}_N)$$

$$X_i = \Phi(X_i^*)$$

where $\Phi(\cdot)$ is the standard normal CDF. Two configs: $\rho_X \in \{0.20, 0.50\}$.

## Mode 3: Poisson Count-Based

1. Spatially correlated log-rates: $\log \boldsymbol{\lambda}^* = \mu_0 \cdot \mathbf{1} + (\mathbf{I}_N - \rho_X \mathbf{W})^{-1}\mathbf{u}$
2. Poisson counts: $C_i \sim \text{Poisson}(\lambda_i^* \cdot P_i)$ where $P_i = 1{,}000$
3. Observed rates: $R_i = C_i / P_i$
4. Rank-normalized: $X_i = (\text{rank}(R_i) - 0.5) / N$

Base rate $\mu_0 = \log(35/100{,}000)$ for SUD. Two configs: $\rho_X \in \{0.20, 0.50\}$.

**Critical design invariant:** Incidence is generated **once per (mode, $\rho_X$) configuration** and held fixed across all ($\rho$, $\gamma$, nb_type) scenarios.

## Incidence Spatial Patterns

```{r incidence-heatmaps}
#| fig-cap: "Incidence spatial patterns across generation modes. Color represents incidence (darker = higher burden). Spatial and Poisson modes show visible spatial clustering absent from iid."
#| fig-height: 6
print(plot_incidence_heatmaps(grid_dim = 10))
```

```{r incidence-distributions}
#| fig-cap: "Marginal distribution of incidence values by mode, pooled across 50 resamples. All modes are marginally Uniform on [0,1]; spatial structure manifests in spatial covariance, not the marginal."
#| fig-height: 5
print(plot_incidence_distributions(grid_dim = 10, n_resamples = 50))
```

---

# Treatment Assignment Designs {#sec-designs}

Eight designs are evaluated. Each produces a binary treatment vector $\mathbf{Z} \in \{0, 1\}^N$.

```{r design-table}
#| results: asis
source(file.path(script_dir, "03_designs.R"))

all_names  <- get_design_names()
design_meta <- data.frame(
  ID            = active_design_ids,
  Name          = unname(all_names[as.character(active_design_ids)]),
  Deterministic = ifelse(
    sapply(active_design_ids, is_design_deterministic), "Yes", "No"
  )
)

knitr::kable(
  design_meta,
  col.names = c("ID", "Name", "Deterministic?"),
  caption   = paste0(
    nrow(design_meta),
    " treatment assignment strategies evaluated in this simulation"
  )
)
```

## Design 1: Checkerboard (Strict Spatial Stratification)

$$Z_i = (x_i + y_i) \mod 2$$

Treatment in an alternating checkerboard pattern. **Deterministic**, exactly 50% treated.

## Design 2: High Incidence Focus

$$Z_i = \mathbf{1}[X_i > \text{median}(\mathbf{X})]$$

Treatment assigned to above-median incidence clusters. **Deterministic** given $\mathbf{X}$.

## Design 3: Saturation Quadrants

Grid partitioned into four spatial quadrants. Saturation levels $\{0.20, 0.40, 0.60, 0.80\}$ randomly assigned to quadrants. Within each quadrant, clusters randomly selected at the assigned rate.

## Design 4: Isolation Buffer

Sequential treatment assignment: randomly select an available cluster, assign treatment, remove it and its neighbors from the available set. Treated clusters are never adjacent.

## Design 5: 2x2 Blocking

Grid partitioned into non-overlapping $2 \times 2$ blocks. Within each block, exactly 2 of 4 clusters randomly assigned to treatment.

## Design 6: Balanced Quartiles

Clusters stratified by incidence quartile. Within each stratum, approximately half randomly assigned to treatment.

## Design 7: Balanced Halves

Clusters stratified into two groups by median baseline incidence. Within each half, approximately half randomly assigned to treatment. A 2-stratum analog of Design 6.

## Design 8: Incidence-Guided Saturation Quadrants

Grid partitioned into four spatial quadrants (same as Design 3). Quadrants ranked by average baseline incidence and **deterministically** assigned saturation levels:

| Rank (by $\bar{X}_{Q_k}$) | Saturation $p_k$ |
|:---:|:---:|
| 1 (highest) | 0.80 |
| 2 | 0.60 |
| 3 | 0.40 |
| 4 (lowest) | 0.20 |

Within each quadrant, clusters randomly selected at the assigned rate. Unlike Design 3, the saturation-to-quadrant mapping is guided by incidence data rather than random.

---

# Estimation Methods {#sec-estimation}

## Difference in Means (DIM)

The naive estimator:
$$\hat{\tau}_{\text{DIM}} = \bar{Y}_1 - \bar{Y}_0$$

DIM is biased for $\tau$ when spillover ($\gamma \neq 0$) or spatial dependence ($\rho \neq 0$) is present.

## Maximum Likelihood Estimation (MLE)

The spatial autoregressive model is estimated via maximum likelihood using `spatialreg::lagsarlm()`:

$$Y_i = \rho \sum_j W_{ij} Y_j + \tau Z_i + \gamma \cdot \text{Spill}_i + \beta X_i + \varepsilon_i$$

MLE simultaneously estimates $\rho$ and regression coefficients. The true spillover covariate $\text{Spill}(\mathbf{Z})$ is included as an **oracle regressor**. Confidence intervals for $\tau$ use the asymptotic covariance matrix.

**MLE is the primary estimator throughout this report.** DIM serves only as a naive baseline.

---

# Simulation Design {#sec-simulation}

## Parameter Grid

```{r param-table}
#| results: asis
if (mle_avail) {
  param_df <- data.frame(
    Parameter = c(
      "Incidence mode",
      "rho_X (incidence spatial autocorr.)",
      "nb_type (contiguity)",
      "rho (outcome spatial autocorr.)",
      "gamma (spillover magnitude)",
      "spill_type",
      "design_id",
      "TOTAL"
    ),
    Values = c(
      paste(sort(unique(mle_results$Incidence_Mode)), collapse = ", "),
      "N/A (iid); 0.20, 0.50 (spatial, poisson)",
      paste(nb_levels, collapse = ", "),
      paste(rho_levels, collapse = ", "),
      paste(gamma_levels, collapse = ", "),
      paste(spill_levels, collapse = ", "),
      paste(active_design_ids, collapse = ", "),
      ""
    ),
    Levels = c(
      paste0(length(mle_cfgs), " configs (1 iid + 2 spatial + 2 poisson)"),
      "---",
      as.character(length(nb_levels)),
      as.character(length(rho_levels)),
      as.character(length(gamma_levels)),
      as.character(length(spill_levels)),
      as.character(n_designs),
      format(n_scenarios_total, big.mark = ",")
    )
  )

  knitr::kable(
    param_df,
    caption = paste0(
      "Simulation parameter grid (",
      format(n_scenarios_total, big.mark = ","),
      " total scenarios)"
    )
  )
}
```

## Resampling Structure

| Mode | Design resamples ($R_d$) | Outcome resamples ($R_o$) | Iterations / scenario |
|------|:---:|:---:|:---:|
| MLE | 25 | 10 | 250 |

## Per-Scenario Reproducibility

Each scenario uses a deterministic seed:
$$\text{seed}_s = \texttt{digest::digest2int}(\texttt{paste}(\text{inc\_mode}, \rho_X, \text{nb\_type}, \rho, \gamma, \text{spill\_type}, d_{\text{id}}, \text{sep}=\text{"|}"))$$

This ensures results are reproducible and order-independent.

---

# Evaluation Metrics {#sec-metrics}

For each scenario, let $\hat{\tau}_1, \ldots, \hat{\tau}_K$ denote the $K$ estimates of $\tau$ (excluding convergence failures).

- **Bias**: $\text{Bias} = \bar{\hat{\tau}} - \tau$
- **Standard Deviation**: $\text{SD} = \sqrt{\frac{1}{K-1}\sum_{k=1}^{K} \left(\hat{\tau}_k - \bar{\hat{\tau}}\right)^2}$
- **Mean Squared Error**: $\text{MSE} = \text{Bias}^2 + \text{SD}^2$ — **primary ranking criterion**
- **Coverage Probability**: $\text{Coverage} = \frac{1}{K}\sum_{k=1}^{K} \mathbf{1}\left[\tau \in \left(\hat{\tau}_{k,L},\ \hat{\tau}_{k,U}\right)\right]$
- **Convergence Failure Rate**: Proportion of iterations where MLE failed to converge

---

# Results: Overall Performance {#sec-results-overall}

## Overall Summary

```{r mle-overall-table}
#| results: asis
if (mle_avail) {
  mle_stats_disp <- data.frame(
    Metric = c("Bias", "MSE", "Coverage", "Fail Rate"),
    Min    = c(mle_summary$Bias_min, mle_summary$MSE_min,  mle_summary$Cov_min,  NA),
    Mean   = c(mle_summary$Bias_mean, mle_summary$MSE_mean, mle_summary$Cov_mean, mle_summary$Fail_mean),
    Max    = c(mle_summary$Bias_max, mle_summary$MSE_max,  mle_summary$Cov_max,  NA)
  )
  knitr::kable(
    mle_stats_disp,
    digits  = 3,
    na      = "\u2014",
    caption = paste0(
      "MLE: Summary statistics across all ",
      format(n_scenarios_total, big.mark = ","),
      " scenarios"
    )
  )
}
```

## Design Comparison by MSE

```{r mle-design-summary}
#| results: asis
if (mle_avail) {
  knitr::kable(
    mle_by_design,
    col.names = c("Design", "Mean Bias", "Median MSE", "Mean MSE",
                  "Mean Coverage", "Fail Rate"),
    digits    = c(0, 3, 3, 3, 3, 4),
    caption   = "MLE: Design performance averaged across all scenarios and incidence modes"
  )
}
```

## MSE by Design and Neighbor Type

```{r mle-mse-boxplot}
#| fig-cap: "MLE: Distribution of MSE by design, faceted by spatial contiguity structure."
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  print(plot_mse_by_neighbor(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (mle_avail && length(mle_cfgs) > 0) {
  print(plot_mse_by_neighbor(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

## Coverage by Design

```{r mle-coverage}
#| fig-cap: "MLE: Coverage probability distribution by design. Red dashed line = nominal 95% target."
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  print(plot_coverage_by_design(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (mle_avail && length(mle_cfgs) > 0) {
  print(plot_coverage_by_design(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

## Bias-Variance Decomposition

```{r mle-biasvar}
#| fig-cap: "MLE: Bias-squared (dark) and variance (light) components of MSE per design for iid Uniform incidence."
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  print(plot_bias_variance(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (mle_avail && length(mle_cfgs) > 0) {
  print(plot_bias_variance(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

---

# Results: Design Rankings by Incidence Mode (Q1) {#sec-q1}

## Cross-Config MSE Rankings

```{r q1-mse-plot}
#| eval: !expr mle_avail
#| fig-cap: "Average MSE per design for each incidence configuration. Bars sorted left-to-right (lowest = best). Rank labels above bars."
#| fig-height: 5.0
print(plot_incidence_rankings(mle_results) +
  theme(text        = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        strip.text  = element_text(size = 9, face = "bold")))
```

## Cross-Config Coverage Rankings

```{r q1-cov-plot}
#| eval: !expr mle_avail
#| fig-cap: "Average 95% CI coverage probability per design for each incidence configuration. Red dashed line = nominal 0.95."
#| fig-height: 5.0
print(plot_incidence_coverage(mle_results) +
  theme(text        = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        strip.text  = element_text(size = 9, face = "bold")))
```

## Detailed Rankings by Incidence Config

```{r q1-detail-table}
#| eval: !expr mle_avail
#| results: asis
for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  r <- rank_designs_by_group(cfg, character(0)) %>%
    mutate(
      Design       = short_design_name(Design),
      Avg_MSE      = round(Avg_MSE, 4),
      Avg_Coverage = round(Avg_Coverage, 3),
      Avg_Bias     = round(Avg_Bias, 4)
    ) %>%
    select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias)

  cap_safe_nm <- gsub("_", " ", cfg_nm)
  tbl_out <- kable(r, booktabs = TRUE, linesep = "", align = "rlrrr",
        col.names = c("Rank", "Design", "Avg MSE", "Avg Coverage", "Avg Bias"),
        caption = sprintf("MLE design rankings for %s", cap_safe_nm)) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
    row_spec(1, bold = TRUE)
  print(tbl_out)
  cat("\n")
}
```

---

# Results: Parameter Sensitivity (Q2) {#sec-q2}

## Effect of Outcome Spatial Autocorrelation (Rho)

```{r q2-rho-trajectories}
#| eval: !expr mle_avail
#| fig-cap: "Design rank trajectories across Rho for each incidence config. Rank 1 = best. Flat lines indicate robust designs; crossing lines reveal rank reversals."
#| fig-height: 8.0
p_list <- lapply(seq_along(mle_cfgs), function(i) {
  plot_rank_trajectories(mle_cfgs[[i]], "Rho", cfg_names[i],
                         point_size = 2.5, line_size = 0.9, label_size = 2.0) +
    theme(legend.position = if (i == length(mle_cfgs)) "right" else "none",
          plot.title    = element_text(size = 9),
          axis.text     = element_text(size = 8),
          axis.title    = element_text(size = 9),
          legend.text   = element_text(size = 8))
})
gridExtra::grid.arrange(grobs = p_list, ncol = 1)
```

## Effect of Spillover Magnitude (Gamma)

```{r q2-gamma-trajectories}
#| eval: !expr mle_avail
#| fig-cap: "Design rank trajectories across Gamma. Gamma has minimal effect on design rankings under MLE: all trajectory lines are nearly flat."
#| fig-height: 8.0
p_list2 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_rank_trajectories(mle_cfgs[[i]], "Gamma", cfg_names[i],
                         point_size = 2.5, line_size = 0.9, label_size = 2.0) +
    theme(legend.position = if (i == length(mle_cfgs)) "right" else "none",
          plot.title    = element_text(size = 9),
          axis.text     = element_text(size = 8),
          axis.title    = element_text(size = 9),
          legend.text   = element_text(size = 8))
})
gridExtra::grid.arrange(grobs = p_list2, ncol = 1)
```

## Sensitivity Analysis (Eta-squared)

```{r mle-sensitivity}
#| results: asis
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  invisible(capture.output(
    sens_tbl <- table_sensitivity(mle_cfgs[["iid Uniform"]], "iid Uniform")
  ))
  knitr::kable(
    as.data.frame(sens_tbl),
    digits  = 4,
    caption = "MLE: Eta-squared (proportion of MSE variance explained) by parameter, for iid Uniform incidence."
  )
}
```

## MSE Per Design Across Gamma

```{r mle-rho-effect}
#| fig-cap: "Per-design MSE line plots across gamma levels, for iid Uniform incidence."
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  print(plot_mse_per_design(mle_cfgs[["iid Uniform"]], "iid Uniform"))
}
```

## Marginal Ranking Tables

```{r q2-marginal-tables}
#| eval: !expr mle_avail
#| results: asis
params_to_show <- c("Rho", "Gamma", "Spillover_Type")

for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  overall_order <- rank_designs_by_group(cfg, character(0)) %>%
    arrange(Rank) %>% pull(Design)

  cap_safe_nm <- gsub("_", " ", cfg_nm)
  cat(sprintf("\n### %s\n\n", cfg_nm))

  for (param in params_to_show) {
    ranked <- rank_designs_by_group(cfg, param) %>%
      mutate(cell = sprintf("%.4f (#%d)", Avg_MSE, Rank)) %>%
      select(Design, all_of(param), cell) %>%
      pivot_wider(names_from = all_of(param), values_from = cell,
                  names_prefix = paste0(param, "=")) %>%
      mutate(Design = factor(Design, levels = overall_order)) %>%
      arrange(Design) %>%
      mutate(Design = short_design_name(as.character(Design)))

    param_label <- switch(param,
      "Rho"            = "Rho (outcome spatial autocorrelation)",
      "Gamma"          = "Gamma (spillover magnitude)",
      "Spillover_Type" = "Spillover Type",
      param)

    tbl_out <- kable(ranked, booktabs = TRUE, linesep = "",
          caption = sprintf(
            "%s | Marginal rankings by %s.", cap_safe_nm, param_label)) %>%
      kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                    font_size = 8) %>%
      row_spec(1, bold = TRUE)
    print(tbl_out)
    cat("\n")
  }
}
```

---

# Results: Best Design by Parameter Combination (Q3) {#sec-q3}

## Rho x Gamma Best-Design Maps

```{r q3-heatmaps}
#| eval: !expr mle_avail
#| fig-cap: "Best design heatmap: Rho vs. Gamma for each incidence config. Each tile shows which design achieves the lowest average MSE."
#| fig-height: 8.0
p_list3 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_best_design_heatmap(mle_cfgs[[i]], "Rho", "Gamma", cfg_names[i],
                           text_size = 3, text_color = "white",
                           compact_labels = TRUE) +
    labs(title = cfg_names[i], subtitle = NULL) +
    theme(plot.title  = element_text(size = 9, face = "bold"),
          axis.text   = element_text(size = 8),
          axis.title  = element_text(size = 9),
          legend.position = "none")
})
gridExtra::grid.arrange(grobs = p_list3, ncol = 2)
```

## Rho x Spillover Type Best-Design Maps

```{r q3-heatmaps-spill}
#| eval: !expr mle_avail
#| fig-cap: "Best design heatmap: Rho vs. Spillover Type for each incidence config. Reveals the key spillover-type interaction."
#| fig-height: 7.5
p_list4 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_best_design_heatmap(mle_cfgs[[i]], "Rho", "Spillover_Type", cfg_names[i],
                           text_size = 3, text_color = "white",
                           compact_labels = TRUE) +
    labs(title = cfg_names[i], subtitle = NULL) +
    theme(plot.title  = element_text(size = 9, face = "bold"),
          axis.text   = element_text(size = 8),
          axis.title  = element_text(size = 9),
          legend.position = "none")
})
gridExtra::grid.arrange(grobs = p_list4, ncol = 2)
```

---

# Per-Config Narrative Findings {#sec-commentary}

```{r per-config-commentary}
#| eval: !expr mle_avail
#| results: asis
for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]

  overall <- rank_designs_by_group(cfg, character(0))
  best_row   <- overall %>% filter(Rank == 1)
  worst_row  <- overall %>% filter(Rank == max(Rank))
  second_row <- overall %>% filter(Rank == 2)

  best_name   <- short_design_name(best_row$Design[1])
  worst_name  <- short_design_name(worst_row$Design[1])
  second_name <- short_design_name(second_row$Design[1])

  # Pairwise dominance
  scenario_ids <- c("Neighbor_Type", "Rho", "Gamma", "Spillover_Type")
  wide <- cfg %>%
    select(all_of(c(scenario_ids, "Design", "MSE"))) %>%
    pivot_wider(names_from = Design, values_from = MSE, id_cols = all_of(scenario_ids))
  dom_vs_second <- round(mean(wide[[best_row$Design[1]]] < wide[[second_row$Design[1]]], na.rm=TRUE)*100, 1)

  # Rank stability
  rho_ranks   <- rank_designs_by_group(cfg, "Rho")   %>% filter(Design == best_row$Design[1])
  gamma_ranks <- rank_designs_by_group(cfg, "Gamma") %>% filter(Design == best_row$Design[1])
  rho_stable   <- all(rho_ranks$Rank == 1)
  gamma_stable <- all(gamma_ranks$Rank == 1)
  stable_str <- if (rho_stable && gamma_stable) {
    "holds rank 1 at every level of Rho and Gamma"
  } else if (rho_stable) {
    "stable across all Rho levels but shows minor rank changes across Gamma"
  } else {
    "shows some rank variation across parameter levels"
  }

  # MSE ratio
  mse_ratio_cfg  <- round(worst_row$Avg_MSE[1] / best_row$Avg_MSE[1], 1)

  cat(sprintf("## %s\n\n", cfg_nm))

  cat(sprintf(
    "**Overall Winner:** %s achieves the lowest average MSE (%.4f). Runner-up: %s (%.4f). The winner dominates in %.1f%% of individual scenarios.\n\n",
    best_name, best_row$Avg_MSE[1], second_name, second_row$Avg_MSE[1], dom_vs_second
  ))

  cat(sprintf(
    "**Robustness:** %s %s.\n\n", best_name, stable_str
  ))

  cat(sprintf(
    "**Coverage:** %s achieves coverage of %.3f; worst design (%s) achieves only %.3f.\n\n",
    best_name, best_row$Avg_Coverage[1], worst_name, worst_row$Avg_Coverage[1]
  ))

  cat(sprintf(
    "**Recommendation:** Under %s incidence, select %s. It provides %.1fx lower MSE than %s and near-nominal coverage.\n\n",
    cfg_nm, best_name, mse_ratio_cfg, worst_name
  ))
}
```

---

# Practical Design Selection Guide {#sec-guide}

```{r decision-table}
#| results: asis
#| eval: !expr mle_avail
# Default (overall best)
default_best_short <- modal_best_short

# Best under both-spillover at low Rho
low_rho_thresh <- sort(rho_levels)[2]
both_low_rho_best <- rank_designs_by_group(
  mle_results %>% filter(Spillover_Type == "both", Rho <= low_rho_thresh),
  character(0)
) %>% filter(Rank == 1) %>% pull(Design) %>% first()
both_low_rho_short <- short_design_name(both_low_rho_best)

decision_df <- data.frame(
  Situation = c(
    "Default (uncertain parameters)",
    sprintf("Spillover is 'both' AND Rho <= %.2f", low_rho_thresh),
    "ANY scenario",
    "ANY scenario"
  ),
  Recommended = c(
    default_best_short,
    both_low_rho_short,
    paste0("Avoid ", worst_design_short),
    "Avoid D5: 2x2 Blocking under queen contiguity"
  ),
  Justification = c(
    sprintf("Ranks 1st in %d of %d configs across all Gamma levels", n_configs_modal_best_wins, length(cfg_names)),
    "Winner shifts at this corner; verify from Rho x Spillover_Type heatmap",
    sprintf("Invalid CIs (coverage %s); MSE %sx higher than winner", worst_cov_range, mse_ratio_range),
    "Queen contiguity amplifies 2x2 block effects"
  ),
  stringsAsFactors = FALSE
)

kable(decision_df, booktabs = TRUE, linesep = "",
      col.names = c("Situation", "Recommended Design", "Justification"),
      caption = "Practical design selection guide.") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 9) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "6cm") %>%
  row_spec(1, bold = TRUE)
```

---

# Subgroup Robustness Profiles {#sec-robustness}

```{r subgroup-robustness}
#| eval: !expr mle_avail
#| results: asis
for (cfg_nm in names(mle_cfgs)) {
  cat(sprintf("\n## %s\n\n", cfg_nm))
  cfg <- mle_cfgs[[cfg_nm]]

  invisible(capture.output(rob <- table_robustness(cfg, cfg_nm)))
  tbl_out <- knitr::kable(
    as.data.frame(rob),
    digits  = 4,
    caption = sprintf("MLE robustness profile: %s", gsub("_", " ", cfg_nm))
  )
  print(tbl_out)
  cat("\n")
}
```

## MSE Heatmap

```{r mle-mse-heatmap}
#| fig-cap: "MLE MSE heatmap for iid Uniform incidence."
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  print(plot_mse_heatmap(mle_cfgs[["iid Uniform"]], "iid Uniform"))
}
```

## Design Rank Frequency

```{r mle-ranks}
#| results: asis
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  invisible(capture.output(
    mle_rank_tbl <- table_design_ranks(mle_cfgs[["iid Uniform"]], "iid Uniform")
  ))
  knitr::kable(
    as.data.frame(mle_rank_tbl),
    digits  = 1,
    caption = "MLE: Design rank frequency (%) for iid Uniform incidence. Each cell = % of scenarios where design achieved that rank."
  )
}
```

---

# Conclusions and Future Work {#sec-conclusions}

The simulation study evaluated `r if (mle_avail) n_designs` treatment assignment designs across `r if (mle_avail) format(n_scenarios_total, big.mark = ",")` parameter scenarios.

**Key findings:**

1. **MLE achieves near-nominal coverage.** Average coverage across all scenarios is `r if (mle_avail) overall_cov_mean`, close to the nominal 0.95 target.

2. **`r if (mle_avail) best_design` is the top performer.** It achieves the lowest average MSE (`r if (mle_avail) round(best_mse, 3)`) and coverage of `r if (mle_avail) best_coverage`.

3. **`r if (mle_avail) worst_design_name` is consistently worst.** Highest MSE (`r if (mle_avail) round(worst_mse, 3)`) and lowest coverage (`r if (mle_avail) worst_coverage`). Its perfect spatial alternation creates systematic confounding.

4. **Spillover type is the key moderator.** Under control-only spillover, `r if (mle_avail) best_under_control_only_short` dominates. Under bidirectional spillover, `r if (mle_avail) best_under_both_short` becomes competitive.

5. **Design rankings are stable across incidence modes and Gamma levels.** The ordering is largely consistent, and spillover magnitude does not affect design choice.

## Limitations and Planned Extensions

- **Oracle MLE:** The MLE model uses the true spillover covariate.
- **Fixed $\tau$:** All results use $\tau = 1.0$. Sensitivity to varying $\tau$ is planned.
- **Equal populations:** Poisson mode uses $P_i = 1{,}000$ for all clusters.
- **Grid sensitivity:** Results use $G = 10$ ($N = 100$) only.

---

# Appendix A: Simulation Pseudocode {#sec-appendix-pseudocode}

```
BUILD spatial grid -> coords, W_rook, W_queen, listw_rook, listw_queen
SET I_mat = diag(N)

FOR EACH incidence_mode IN {iid, spatial, poisson}:
  SET rho_X_values = {0} if iid, else {0.20, 0.50}

  FOR EACH rho_X IN rho_X_values:
    GENERATE X_matrix (N x R_o) using incidence_mode, rho_X, W_queen
    SET base_incidence = X_matrix[, 1]

    FOR EACH nb_type IN {rook, queen}:
      SELECT active W, listw for nb_type

      FOR EACH rho IN {0.00, 0.01, 0.20, 0.50}:
        COMPUTE inv_mat = solve(I_mat - rho * W)
        GENERATE Epsilon_matrix (N x R_o) ~ N(0, sigma^2)
        COMPUTE baseline_part = inv_mat %*% (X_matrix * beta + Epsilon_matrix)

        FOR EACH gamma IN {0.50, 0.60, 0.70, 0.80}:
          FOR EACH spill_type IN {control_only, both}:
            FOR EACH design_id IN {1, 2, 3, 4, 5, 6, 7, 8}:

              SET scenario_seed = hash(incidence_mode, rho_X, nb_type,
                                       rho, gamma, spill_type, design_id)
              set.seed(scenario_seed)

              GENERATE Z_matrix (N x R_d)
              FOR d IN 1:R_d:
                Z = Z_matrix[, d]
                COMPUTE spillover = W %*% Z (apply spill_type mask)
                COMPUTE trt_effect = inv_mat %*% (tau * Z + spillover)
                Y_sim = trt_effect + baseline_part
                ESTIMATE tau_hat, CI for each of R_o outcome columns

              COMPUTE Bias, SD, MSE, Coverage, Fail_Rate
              STORE results row
```

---

# Appendix B: File Locations {#sec-appendix-files}

```{r appendix-files}
#| results: asis
if (mle_avail) {
  rds_dir   <- file.path(results_dir, "sim_data")
  rds_files <- list.files(rds_dir, pattern = "\\.rds$", full.names = FALSE)

  if (length(rds_files) > 0) {
    files_df <- data.frame(
      File     = rds_files,
      Location = rep("results/sim_data/", length(rds_files))
    )
    knitr::kable(
      files_df,
      caption = "RDS result files"
    )
  }
}
```

All simulation data files are located in: `results/sim_data/`

Code modules: `code/01_spatial_setup.R` through `code/08_design_recommendations.R`

Reports: `code/00_mathematical_specification.Rmd`, `code/07_results_summary.qmd`, `code/09_MLE_design_recommendation_report.qmd`
