---
title: "Treatment Assignment Design Evaluation for Spatial CRTs"
subtitle: "Simulation Study with Heterogeneous Incidence — Results Summary"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    latex_engine: xelatex
    keep_tex: false
    fig_caption: true
    fig_height: 5
    fig_width: 7
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{float}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{geometry}
  - \geometry{margin=1in}
  - \floatplacement{figure}{H}
  - \floatplacement{table}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.pos = "H",
  out.extra = ""
)
```

```{r load-packages}
library(dplyr)
library(tidyr)
library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)
```

```{r resolve-paths}
# Robust working directory detection for both source() and rmarkdown::render()
script_dir <- tryCatch(
  normalizePath(dirname(knitr::current_input(dir = TRUE))),
  error = function(e) {
    tryCatch(
      dirname(sys.frame(1)$ofile),
      error = function(e2) getwd()
    )
  }
)
results_dir <- file.path(dirname(script_dir), "results")
```

```{r source-modules}
# Source visualization module (provides all table + plot functions)
source(file.path(script_dir, "06_visualizations.R"))
```

```{r load-results}
# Load most recent combined results for each estimator
dim_results <- tryCatch(
  load_latest_results(results_dir, estimation_mode = "DIM_combined"),
  error = function(e) {
    message("DIM combined results not found: ", e$message)
    NULL
  }
)

# DIM is a pre-revision (March 2026) naive baseline: old DGP, 6 designs, and the
# old numbering, in which "Design 7" was Balanced Quartiles (renumbered to Design 6
# on 2026-03-22; current Design 7 is Balanced Halves). Relabel so every DIM exhibit
# and the DIM-vs-MLE join use the current numbering.
if (!is.null(dim_results)) {
  stopifnot(!"Design 6" %in% dim_results$Design)
  dim_results$Design[dim_results$Design == "Design 7"] <- "Design 6"
}

# Oracle tau-sweep results from the 2026-09 revised simulation. No fallback: if the
# file is missing the render must fail rather than silently load archived results.
# ("MLE_tau_sweep" does not match the non-oracle "MLEnonoracle_tau_sweep" files.)
mle_results <- load_latest_results(results_dir, estimation_mode = "MLE_tau_sweep")
stopifnot(all(mle_results$Estimator == "oracle"))

# For tau-sweep results: filter to primary scenario (tau=1.0) before splitting configs.
# Existing plots/tables are not tau-aware; filtering ensures they summarize the primary
# scenario rather than silently averaging across all 5 tau levels.
mle_results_tau1 <- if (!is.null(mle_results) && "True_Tau" %in% names(mle_results)) {
  mle_results[mle_results$True_Tau == 1.0, ]
} else {
  mle_results
}

# Split into per-incidence-config lists
dim_cfgs  <- if (!is.null(dim_results))       split_by_incidence_config(dim_results)       else list()
mle_cfgs  <- if (!is.null(mle_results_tau1))  split_by_incidence_config(mle_results_tau1)  else list()

# Convenience labels
cfg_names <- names(dim_cfgs)
```

\newpage

# Introduction

This report summarizes a simulation study evaluating **eight treatment assignment designs**
for Spatial Cluster Randomized Trials (CRTs) when outcome incidence is heterogeneous
and spatially structured. The central research question is:

> *Given known historical incidence data exhibiting spatial heterogeneity, which
> treatment assignment strategy minimizes estimation error for the direct intervention
> effect $\hat{\tau}$ across a range of spatial dependence and spillover configurations?*

**Application context:** Sudden Unexpected Death (SUD) in North Carolina counties.
The Poisson incidence mode uses an SUD base rate of 35 per 100,000 (Mirzaei et al.),
consistent with county-level analyses by Gan et al. and Watson et al.

The primary estimator is Maximum Likelihood Estimation via a spatial autoregressive
model (MLE), fit to the 2026-09 revised simulation. Difference in Means (DIM) appears
only as a naive baseline, and its results are **pre-revision** (March 2026 run: old
data-generating process, 6 designs), so DIM and MLE numbers are not like-for-like.
Queen contiguity is the primary neighbor structure; rook is a sensitivity analysis.
The primary MLE results
use the $\tau = 1.0$ scenario (2,560 parameter scenarios); a tau sensitivity analysis
across $\tau \in \{0.8, 1.0, 1.5, 2.0, 3.0\}$ (12,800 total scenarios) is presented
in Section \ref{sec:tau-sensitivity}.

---

# Mathematical Framework

## Study Region and Spatial Structure

The simulation operates on a **regular lattice grid** $\mathcal{G} = \{s_1, \ldots, s_N\}$
on $[1, G] \times [1, G]$, with $N = G^2$ clusters ($G = 10$, $N = 100$).

Two contiguity structures define neighbor relationships:

- **Rook contiguity:** $s_j \in \mathcal{N}(s_i)$ iff $s_i$ and $s_j$ share an edge
  (up to 4 neighbors)
- **Queen contiguity:** $s_j \in \mathcal{N}(s_i)$ iff $s_i$ and $s_j$ share an edge
  or corner (up to 8 neighbors)

The spatial weight matrix $\mathbf{W}$ has entries
$w_{ij} = |\mathcal{N}(s_i)|^{-1}$ if $s_j \in \mathcal{N}(s_i)$ and $0$ otherwise
(row-standardized).

## Outcome Data Generating Process

Outcomes follow a **Spatial Durbin Model (SDM)**:

$$\mathbf{Y} = (\mathbf{I} - \rho \mathbf{W})^{-1}
\left[\tau \mathbf{Z} + \gamma \cdot \text{Spill}(\mathbf{Z}) + \beta \mathbf{X} + \boldsymbol{\varepsilon}\right]$$

**Parameter definitions:**

| Symbol | Role | Value / Range |
|--------|------|---------------|
| $\tau$ | Direct treatment effect (estimand) | $\{0.8, 1.0, 1.5, 2.0, 3.0\}$; primary: $1.0$ |
| $\rho$ | Outcome spatial autocorrelation | $\{0.00, 0.01, 0.20, 0.50\}$ |
| $\gamma$ | Spillover magnitude | $\{0.5, 0.6, 0.7, 0.8\}$ |
| $\beta$ | Incidence effect on outcome | $1.0$ (fixed) |
| $\sigma$ | Residual standard deviation | $1.0$ (fixed) |

**Spillover construction:**

$$\text{Spill}_i(\mathbf{Z}) = \frac{\sum_{j \in \mathcal{N}(i)} Z_j}{|\mathcal{N}(i)|}$$

Two spillover modes are evaluated:
- **control\_only:** $\gamma$ applied only to units with $Z_i = 0$
- **both:** $\gamma$ applied to all units regardless of treatment status

Stationarity requires $|\rho| < 1/\lambda_{\max}(\mathbf{W})$; all swept $\rho$ values
satisfy this condition.

## Incidence Generation

Three modes generate the cluster-level covariate $X_i \in [0,1]$, each representing
a different assumption about how historical incidence arises:

**Mode 1 — iid Uniform:**
$$X_i \overset{\text{iid}}{\sim} \text{Uniform}(0, 1)$$

No spatial structure; serves as the baseline. One config (rho\_X = N/A).

**Mode 2 — Spatial (SAR filter):**
$$\mathbf{X}^* = (\mathbf{I} - \rho_X \mathbf{W})^{-1} \mathbf{u}, \quad
\mathbf{u} \sim \mathcal{N}(\mathbf{0}, \mathbf{I})$$
$$X_i = \Phi(X_i^*) \in (0, 1)$$

Spatially correlated via SAR filter; probability integral transform ($\Phi$) ensures
$X_i$ is marginally $\text{Uniform}(0,1)$ but spatially dependent.
Two configs: $\rho_X \in \{0.20, 0.50\}$.

**Mode 3 — Poisson (count rates):**

1. Spatially correlated log-rates:
   $\log \lambda_i^* = \mu_0 + [(\mathbf{I} - \rho_X \mathbf{W})^{-1} \mathbf{u}]_i$
2. Poisson counts: $C_i \sim \text{Poisson}(\lambda_i^* \cdot P_i)$
   where $P_i = 100{,}000$ (equal population per cluster; $\lambda_i^* P_i \approx 35$ expected deaths)
3. Observed rates: $R_i = C_i / P_i$
4. Rank-normalized: $X_i = (\text{rank}(R_i) - 0.5) / N$

Base rate $\mu_0 = \log(35/100{,}000)$ mimics SUD incidence.
Two configs: $\rho_X \in \{0.20, 0.50\}$.

**Critical design invariant:** Incidence surfaces $\mathbf{X}_1, \ldots, \mathbf{X}_{10}$
are generated **once per (mode, $\rho_X$) configuration** and shared by all
($\rho$, $\gamma$, nb\_type, spillover type) scenarios of that configuration; spatial
model parameters affect the outcome DGP, not the incidence itself.
**Matched surfaces:** for each surface $k$, treatment is assigned from $\mathbf{X}_k$,
and the outcome and the analysis use the same $\mathbf{X}_k$. Reported metrics are
therefore averages over incidence surfaces.

## Treatment Assignment Designs

Eight assignment strategies are evaluated, representing qualitatively distinct approaches
to allocating clusters to treatment (all treat exactly 50 of 100 except Isolation Buffer):

| ID | Name | Deterministic? | Key Feature |
|----|------|:-:|-------------|
| 1 | Checkerboard | Yes | Alternating grid; maximizes spatial separation |
| 2 | High Incidence Focus | No | Treats the top-50 incidence clusters (random tie-breaking) |
| 3 | Saturation Quadrants | No | Random permutation of saturations {0.2, 0.4, 0.6, 0.8} over quadrants |
| 4 | Isolation Buffer | No | Greedy random maximal independent set; no adjacent treated clusters (mean treated: rook 38.2, queen 21.4) |
| 5 | 2x2 Blocking | No | 2 of 4 treated within each 2x2 spatial block |
| 6 | Balanced Quartiles | No | Stratified by incidence quartile; exactly 50 treated |
| 7 | Balanced Halves | No | Median split; 25 treated per half |
| 8 | Incidence-Guided Saturation Quadrants | No | Quadrant saturations {0.8, 0.6, 0.4, 0.2} by rank of quadrant mean incidence |

Ties in incidence are broken at random, freshly for every design draw. Checkerboard is
the only **deterministic** design: its assignment is identical on every draw, but each
fit still receives its own outcome noise.

## Estimation Methods

**Difference in Means (DIM):**
$$\hat{\tau}_{\text{DIM}} = \bar{Y}_1 - \bar{Y}_0 = \frac{1}{n_1}\sum_{Z_i=1} Y_i - \frac{1}{n_0}\sum_{Z_i=0} Y_i$$

95\% CI via Neyman variance estimator:
$$\widehat{\text{Var}}(\hat{\tau}) = \frac{s_1^2}{n_1} + \frac{s_0^2}{n_0}$$

**Maximum Likelihood (MLE via SAR):**

Fits the spatial lag model $Y \sim Z + \text{Spill} + X$ by maximum likelihood with
`fit_sar_lag()` (`04_estimation.R`), which matches `spatialreg::lagsarlm(method = "eigen")`
to about $10^{-7}$, simultaneously estimating $\rho$, $\tau$, and regression coefficients.
The true spillover covariate $\text{Spill}(\mathbf{Z})$ is included as an **oracle
regressor** (i.e., the researcher is assumed to know the true spillover structure).
95\% Wald CIs use the ML standard error. A non-oracle fit ($Y \sim Z + X$) was run as a
sensitivity analysis; it is not shown in this report.
Under rook contiguity, Checkerboard has $W\mathbf{Z} = \mathbf{1} - \mathbf{Z}$, so the
oracle Spill column is aliased and $\tau$ is not identified; those estimates are kept
but flagged.

---

# Simulation Algorithm

## Parameter Grid

```{r param-table, results='asis'}
param_df <- data.frame(
  Parameter        = c("Incidence mode",
                       "rho_X (incidence spatial autocorr.)",
                       "nb_type (contiguity)",
                       "rho (outcome spatial autocorr.)",
                       "gamma (spillover magnitude)",
                       "spill_type",
                       "design_id",
                       "TOTAL"),
  Values           = c("iid, spatial, poisson",
                       "N/A (iid); 0.20, 0.50 (spatial, poisson)",
                       "rook, queen",
                       "0.00, 0.01, 0.20, 0.50",
                       "0.5, 0.6, 0.7, 0.8",
                       "control_only, both",
                       "1, 2, 3, 4, 5, 6, 7, 8",
                       ""),
  Levels           = c("5 configs (1 iid + 2 spatial + 2 poisson)",
                       "—",
                       "2",
                       "4",
                       "4",
                       "2",
                       "8",
                       "2,560 scenarios (primary tau=1.0 slice; 12,800 across tau-sweep)")
)

kable(param_df, booktabs = TRUE, linesep = "",
      caption = "Simulation parameter grid. Primary tau=1.0 slice: 2,560 scenarios. Full tau-sweep (tau in {0.8, 1.0, 1.5, 2.0, 3.0}): 12,800 total scenarios.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(nrow(param_df), bold = TRUE)
```

## Resampling Structure

For each MLE scenario, the simulation uses $K = 10$ incidence surfaces and $J = 25$
design draws per surface; every one of the $K \cdot J = 250$ fits has its own outcome
noise column. The DIM baseline (pre-revision) used a different scheme:

| Mode | Design draws | Outcome draws | Fits / scenario |
|------|:---:|:---:|:---:|
| DIM (pre-revision) | 25 | 100 | 2,500 |
| MLE | 25 per surface | 10 surfaces | 250 |

## Evaluation Metrics

For each scenario, across the $n$ valid fits $i = 1, \ldots, n$:

$$\text{Bias} = \bar{\hat{\tau}} - \tau, \quad
\text{SD} = \sqrt{\frac{1}{n-1}\sum_{i=1}^n (\hat{\tau}_i - \bar{\hat{\tau}})^2}$$

$$\text{MSE} = \frac{1}{n}\sum_{i=1}^n (\hat{\tau}_i - \tau)^2$$

$$\text{Coverage} = \frac{1}{n}\sum_{i=1}^n \mathbf{1}\left[\tau \in (\hat{\tau}_{i,L}, \hat{\tau}_{i,U})\right]$$

Monte Carlo standard errors are computed from the 10 surface-level means (the surface
is the primary sampling unit), not from the 250 fits treated as independent.

## Per-Draw Reproducibility

Every random draw is preceded by a key-based seed,
$\texttt{set.seed}(\texttt{digest::digest2int}(\text{key}))$, where the key joins the
fields that define the draw with "|": ("X", mode, $\rho_X$, $k$) for surface $k$;
("Z", mode, $\rho_X$, nb\_type, $\rho$, $\gamma$, spill\_type, $k$, $d$) for design
draws; ("eps", mode, $\rho_X$, nb\_type, $\rho$, $\gamma$, spill\_type) for outcome noise.

Each draw depends only on its key, so results are identical in any run order. Within a
block, all designs share the same noise and incidence surfaces, and every $\tau$ level
reuses the same assignments and noise (common random numbers).

---

# Results: Difference in Means (DIM)

DIM is a naive baseline. All results in this section are **pre-revision** (March 2026
run: old data-generating process, 6 designs, no Balanced Halves or Incidence-Guided
Saturation Quadrants); design labels use the current numbering. Tables pool rook and
queen.

```{r dim-check}
dim_avail <- !is.null(dim_results) && nrow(dim_results) > 0
```

```{r dim-overall-stats, eval=dim_avail}
dim_summary <- dim_results %>%
  summarise(
    N_scenarios = n(),
    Bias_min    = round(min(Bias, na.rm=TRUE), 3),
    Bias_max    = round(max(Bias, na.rm=TRUE), 3),
    Bias_mean   = round(mean(Bias, na.rm=TRUE), 3),
    MSE_min     = round(min(MSE, na.rm=TRUE), 3),
    MSE_max     = round(max(MSE, na.rm=TRUE), 3),
    MSE_mean    = round(mean(MSE, na.rm=TRUE), 3),
    Cov_min     = round(min(Coverage, na.rm=TRUE), 2),
    Cov_max     = round(max(Coverage, na.rm=TRUE), 2),
    Cov_mean    = round(mean(Coverage, na.rm=TRUE), 2)
  )
```

## Overall Summary (All DIM Scenarios)

```{r dim-overall-table, eval=dim_avail, results='asis'}
dim_stats_disp <- data.frame(
  Metric = c("Bias", "MSE", "Coverage"),
  Min    = c(dim_summary$Bias_min, dim_summary$MSE_min, dim_summary$Cov_min),
  Mean   = c(dim_summary$Bias_mean, dim_summary$MSE_mean, dim_summary$Cov_mean),
  Max    = c(dim_summary$Bias_max, dim_summary$MSE_max, dim_summary$Cov_max)
)
kable(dim_stats_disp, booktabs = TRUE, linesep = "", digits = 3,
      caption = paste0("DIM (pre-revision): Summary statistics across all ",
                       dim_summary$N_scenarios, " scenarios")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

## DIM Design Comparison by MSE

```{r dim-design-summary, eval=dim_avail, results='asis'}
dim_by_design <- dim_results %>%
  group_by(Design) %>%
  summarise(
    Mean_Bias     = round(mean(Bias, na.rm=TRUE), 3),
    Median_MSE    = round(median(MSE, na.rm=TRUE), 3),
    Mean_MSE      = round(mean(MSE, na.rm=TRUE), 3),
    Mean_Coverage = round(mean(Coverage, na.rm=TRUE), 3),
    .groups       = "drop"
  ) %>%
  arrange(Mean_MSE)

kable(dim_by_design, booktabs = TRUE, linesep = "",
      col.names = c("Design", "Mean Bias", "Median MSE", "Mean MSE", "Mean Coverage"),
      caption = "DIM (pre-revision): Design performance averaged across all scenarios and incidence modes") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(1, bold = TRUE)
```

## DIM: MSE by Design and Neighbor Type

```{r dim-mse-boxplot, eval=dim_avail, fig.cap="DIM (pre-revision): Distribution of MSE by design, faceted by spatial contiguity structure. Boxes sorted by median MSE within each panel."}
# Show the iid Uniform config as representative
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_mse_by_neighbor(dim_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(dim_cfgs) > 0) {
  print(plot_mse_by_neighbor(dim_cfgs[[1]], names(dim_cfgs)[1]))
}
```

## DIM: MSE Heatmap (Rho x Design)

```{r dim-mse-heatmap, eval=dim_avail, fig.cap="DIM (pre-revision) MSE heatmap for iid Uniform incidence. Cells show average MSE across spillover type and gamma, faceted by neighbor type."}
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_mse_heatmap(dim_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(dim_cfgs) > 0) {
  print(plot_mse_heatmap(dim_cfgs[[1]], names(dim_cfgs)[1]))
}
```

## DIM: Design Rank Frequency

```{r dim-ranks-iid, eval=dim_avail, results='asis'}
if ("iid Uniform" %in% names(dim_cfgs)) {
  invisible(capture.output(rank_tbl <- table_design_ranks(dim_cfgs[["iid Uniform"]], "iid Uniform")))
  kable(as.data.frame(rank_tbl), booktabs = TRUE, linesep = "", digits = 1,
        caption = "DIM (pre-revision): Design rank frequency (\\%) for iid Uniform incidence. Each cell = \\% of scenarios where design achieved that rank (Rank 1 = lowest MSE).") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## DIM: Robustness Profile

```{r dim-robustness-iid, eval=dim_avail, results='asis'}
if ("iid Uniform" %in% names(dim_cfgs)) {
  invisible(capture.output(rob_tbl <- table_robustness(dim_cfgs[["iid Uniform"]], "iid Uniform")))
  kable(as.data.frame(rob_tbl), booktabs = TRUE, linesep = "", digits = 4,
        caption = "DIM (pre-revision): Robustness profile for iid Uniform incidence. Sorted by Median MSE. IQR = interquartile range across scenarios.") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## DIM: Coverage by Design

```{r dim-coverage, eval=dim_avail, fig.cap="DIM (pre-revision): Coverage probability distribution by design across all scenarios. Red dashed line = nominal 95\\% target."}
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_coverage_by_design(dim_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(dim_cfgs) > 0) {
  print(plot_coverage_by_design(dim_cfgs[[1]], names(dim_cfgs)[1]))
}
```

## DIM: Bias-Variance Decomposition

```{r dim-biasvar, eval=dim_avail, fig.cap="DIM (pre-revision): Bias-squared (dark) and variance (light) components of MSE per design for iid Uniform incidence. Total bar height = MSE."}
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_bias_variance(dim_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(dim_cfgs) > 0) {
  print(plot_bias_variance(dim_cfgs[[1]], names(dim_cfgs)[1]))
}
```

---

# Results: Maximum Likelihood (MLE)

```{r mle-check}
mle_avail <- !is.null(mle_results) && nrow(mle_results) > 0
```

```{r mle-overall-stats, eval=mle_avail}
mle_summary <- mle_results_tau1 %>%
  summarise(
    N_scenarios   = n(),
    Bias_min      = round(min(Bias, na.rm=TRUE), 3),
    Bias_max      = round(max(Bias, na.rm=TRUE), 3),
    Bias_mean     = round(mean(Bias, na.rm=TRUE), 3),
    MSE_min       = round(min(MSE, na.rm=TRUE), 3),
    MSE_max       = round(max(MSE, na.rm=TRUE), 3),
    MSE_mean      = round(mean(MSE, na.rm=TRUE), 3),
    Cov_min       = round(min(Coverage, na.rm=TRUE), 2),
    Cov_max       = round(max(Coverage, na.rm=TRUE), 2),
    Cov_mean      = round(mean(Coverage, na.rm=TRUE), 2),
    Fail_mean     = round(mean(Fail_Rate, na.rm=TRUE), 4)
  )
```

## Overall Summary (All MLE Scenarios)

```{r mle-overall-table, eval=mle_avail, results='asis'}
mle_stats_disp <- data.frame(
  Metric = c("Bias", "MSE", "Coverage", "Fail Rate"),
  Min    = c(mle_summary$Bias_min, mle_summary$MSE_min,  mle_summary$Cov_min,  NA),
  Mean   = c(mle_summary$Bias_mean, mle_summary$MSE_mean, mle_summary$Cov_mean, mle_summary$Fail_mean),
  Max    = c(mle_summary$Bias_max, mle_summary$MSE_max,  mle_summary$Cov_max,  NA)
)
kable(mle_stats_disp, booktabs = TRUE, linesep = "", digits = 3, na = "—",
      caption = paste0("MLE: Summary statistics across all ",
                       mle_summary$N_scenarios, " tau = 1.0 scenarios, pooled over rook and queen and over incidence modes. The minimum coverage comes from Checkerboard under rook, where tau is not identified.")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

## MLE Design Comparison by MSE

```{r mle-design-summary, eval=mle_avail, results='asis'}
# Split by neighbor type (queen primary, rook sensitivity); never pool them here.
mle_by_design <- mle_results_tau1 %>%
  group_by(Neighbor_Type, Design) %>%
  summarise(
    Mean_Bias     = round(mean(Bias, na.rm=TRUE), 3),
    Median_MSE    = round(median(MSE, na.rm=TRUE), 3),
    Mean_MSE      = round(mean(MSE, na.rm=TRUE), 3),
    Mean_Coverage = round(mean(Coverage, na.rm=TRUE), 3),
    Fail_Rate     = round(mean(Fail_Rate, na.rm=TRUE), 4),
    .groups       = "drop"
  ) %>%
  arrange(factor(Neighbor_Type, levels = c("queen", "rook")), Mean_MSE)

kable(mle_by_design, booktabs = TRUE, linesep = "",
      col.names = c("Neighbors", "Design", "Mean Bias", "Median MSE", "Mean MSE",
                    "Mean Coverage", "Fail Rate"),
      caption = "MLE: Design performance at tau = 1.0 by neighbor type (queen primary, rook sensitivity), averaged across incidence modes. Checkerboard under rook: tau not identified (WZ = 1 - Z); estimates kept but flagged.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(1, bold = TRUE)
```

## MLE: MSE by Design and Neighbor Type

```{r mle-mse-boxplot, eval=mle_avail, fig.cap="MLE: Distribution of MSE by design at tau = 1.0 (iid Uniform incidence), faceted by spatial contiguity (queen primary, rook sensitivity). Checkerboard under rook: tau not identified; estimates kept but flagged."}
if ("iid Uniform" %in% names(mle_cfgs)) {
  print(plot_mse_by_neighbor(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(mle_cfgs) > 0) {
  print(plot_mse_by_neighbor(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

## MLE: MSE Heatmap

```{r mle-mse-heatmap, eval=mle_avail, fig.cap="MLE MSE heatmap for iid Uniform incidence at tau = 1.0, faceted by neighbor type. Cells show average MSE across spillover type and gamma."}
if ("iid Uniform" %in% names(mle_cfgs)) {
  print(plot_mse_heatmap(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(mle_cfgs) > 0) {
  print(plot_mse_heatmap(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

## MLE: Design Rank Frequency

```{r mle-ranks-iid, eval=mle_avail, results='asis'}
if ("iid Uniform" %in% names(mle_cfgs)) {
  # Queen only (primary); rook is not pooled into the headline rank table.
  mle_iid_queen <- mle_cfgs[["iid Uniform"]] %>% filter(Neighbor_Type == "queen")
  invisible(capture.output(mle_rank_tbl <- table_design_ranks(mle_iid_queen, "iid Uniform")))
  kable(as.data.frame(mle_rank_tbl), booktabs = TRUE, linesep = "", digits = 1,
        caption = "MLE: Design rank frequency (\\%) for iid Uniform incidence, queen contiguity, tau = 1.0.") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## MLE: Robustness Profile

```{r mle-robustness-iid, eval=mle_avail, results='asis'}
if ("iid Uniform" %in% names(mle_cfgs)) {
  mle_iid_queen <- mle_cfgs[["iid Uniform"]] %>% filter(Neighbor_Type == "queen")
  invisible(capture.output(mle_rob_tbl <- table_robustness(mle_iid_queen, "iid Uniform")))
  kable(as.data.frame(mle_rob_tbl), booktabs = TRUE, linesep = "", digits = 4,
        caption = "MLE: Robustness profile for iid Uniform incidence, queen contiguity, tau = 1.0.") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## MLE: Coverage by Design

```{r mle-coverage, eval=mle_avail, fig.cap="MLE: Coverage probability distribution by design (iid Uniform incidence, tau = 1.0), faceted by neighbor type. Coverage is near-nominal for every design except Checkerboard under rook, where tau is not identified. Red dashed line = 95\\%."}
if ("iid Uniform" %in% names(mle_cfgs)) {
  print(plot_coverage_by_design(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(mle_cfgs) > 0) {
  print(plot_coverage_by_design(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

---

# DIM vs. MLE Comparison

## Side-by-Side Metrics

```{r compare-table, eval=dim_avail && mle_avail, results='asis'}
dim_agg <- dim_results %>%
  group_by(Design) %>%
  summarise(DIM_MSE = round(mean(MSE, na.rm=TRUE), 3),
            DIM_Cov = round(mean(Coverage, na.rm=TRUE), 3),
            .groups = "drop")

mle_agg <- mle_results_tau1 %>%
  group_by(Design) %>%
  summarise(MLE_MSE = round(mean(MSE, na.rm=TRUE), 3),
            MLE_Cov = round(mean(Coverage, na.rm=TRUE), 3),
            .groups = "drop")

# Rows = all 8 MLE designs; DIM (6 designs) is joined on, so Design 7 and 8 DIM cells
# are NA by construction.
compare_tbl <- left_join(mle_agg, dim_agg, by = "Design") %>%
  select(Design, DIM_MSE, DIM_Cov, MLE_MSE, MLE_Cov) %>%
  arrange(MLE_MSE)

kable(compare_tbl, booktabs = TRUE, linesep = "",
      col.names = c("Design", "DIM MSE", "DIM Coverage", "MLE MSE", "MLE Coverage"),
      caption = "DIM vs. MLE: Average MSE and coverage by design, pooled over rook and queen and over incidence modes (MLE at tau = 1.0). DIM is the pre-revision baseline (old data-generating process, 6 designs), so the two columns are not like-for-like; Design 7 (Balanced Halves) and Design 8 (Incidence-Guided Saturation Quadrants) were not in the DIM run and are NA by construction. Pooled MLE values for Checkerboard mix queen with rook, where tau is not identified.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  add_header_above(c(" " = 1, "DIM (pre-revision)" = 2, "MLE" = 2))
```

## Coverage Comparison by Estimator

```{r coverage-compare-plot, eval=dim_avail && mle_avail, fig.cap="Coverage comparison: DIM (top, pre-revision baseline) vs MLE (bottom, tau = 1.0) for the iid Uniform incidence configuration. MLE achieves near-nominal coverage for every design except Checkerboard under rook; DIM coverage is mostly below 0.95."}
if ("iid Uniform" %in% names(dim_cfgs) && "iid Uniform" %in% names(mle_cfgs)) {
  p_dim <- plot_coverage_by_design(dim_cfgs[["iid Uniform"]], "DIM | iid Uniform") +
    theme(legend.position = "none")
  p_mle <- plot_coverage_by_design(mle_cfgs[["iid Uniform"]], "MLE | iid Uniform") +
    theme(legend.position = "none")

  # Stack vertically
  gridExtra::grid.arrange(p_dim, p_mle, nrow = 2)
}
```

## Key Observations

```{r compare-obs, results='asis'}
# All numbers below are computed from the loaded results (MLE: tau = 1.0 slice).
obs_by <- mle_results_tau1 %>%
  group_by(Neighbor_Type, Design) %>%
  summarise(MSE = mean(MSE), Var = mean(SD^2), Bias = mean(Bias),
            Cov = mean(Coverage), .groups = "drop")
q_obs  <- obs_by %>% filter(Neighbor_Type == "queen") %>% arrange(MSE)
cb_q   <- obs_by %>% filter(Neighbor_Type == "queen", Design == "Design 1")
cb_r   <- obs_by %>% filter(Neighbor_Type == "rook",  Design == "Design 1")
cov_ok <- obs_by %>% filter(!(Neighbor_Type == "rook" & Design == "Design 1"))

cat("\\begin{itemize}\n")
cat(sprintf("  \\item \\textbf{Coverage does not separate the designs.} MLE coverage averages %.3f--%.3f\n",
            min(cov_ok$Cov), max(cov_ok$Cov)))
cat("    for every design and neighbor type except Checkerboard under rook, i.e.\\ near-nominal\n")
cat("    (a finite-sample Wald shortfall of about one point). MSE is what separates the designs.\n\n")
if (!is.null(dim_results)) {
  cat(sprintf("  \\item \\textbf{DIM baseline (pre-revision):} mean coverage %.2f across its %d scenarios.\n",
              mean(dim_results$Coverage, na.rm = TRUE), nrow(dim_results)))
  cat("    It was run under the old data-generating process, so it is not a like-for-like\n")
  cat("    comparison with the MLE results.\n\n")
}
cat(sprintf("  \\item \\textbf{Checkerboard (Design 1):} highest MSE under queen (%.3f at $\\tau = 1$),\n",
            cb_q$MSE))
cat(sprintf("    with mean bias %.3f, so almost all of it is variance: the oracle model separates $\\tau$ from the spillover\n",
            cb_q$Bias))
cat("    term only weakly under a checkerboard. Under rook, $W\\mathbf{Z} = \\mathbf{1} - \\mathbf{Z}$,\n")
cat(sprintf("    so $\\tau$ is not identified: bias %.3f (approximately $-\\gamma$), coverage %.3f.\n",
            cb_r$Bias, cb_r$Cov))
cat("    These estimates are kept but flagged.\n\n")
cat(sprintf("  \\item \\textbf{Lowest MSE (queen):} %s (%.3f) and %s (%.3f), which are statistically\n",
            sub("^Design [0-9]: ", "", get_design_names(sub("Design ", "", q_obs$Design[1]))), q_obs$MSE[1],
            sub("^Design [0-9]: ", "", get_design_names(sub("Design ", "", q_obs$Design[2]))), q_obs$MSE[2]))
cat("    indistinguishable (eight-design comparisons in \\texttt{results/eight\\_design\\_supplementary/}).\n")
cat("\\end{itemize}\n")
```

---

# Sensitivity Analysis

## Parameter Sensitivity (DIM)

```{r dim-sensitivity, eval=dim_avail, results='asis'}
if ("iid Uniform" %in% names(dim_cfgs)) {
  invisible(capture.output(sens_tbl <- table_sensitivity(dim_cfgs[["iid Uniform"]], "iid Uniform")))
  kable(as.data.frame(sens_tbl), booktabs = TRUE, linesep = "", digits = 4,
        caption = "DIM (pre-revision): Eta-squared (proportion of MSE variance explained) by parameter, for iid Uniform incidence. Higher values indicate parameters where design choice matters more.") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## Effect of Rho on Design Rankings (DIM)

```{r dim-rho-effect, eval=dim_avail, fig.cap="DIM (pre-revision): Per-design MSE line plots across gamma levels, for iid Uniform incidence. Each panel shows one design; lines represent different rho levels."}
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_mse_per_design(dim_cfgs[["iid Uniform"]], "iid Uniform"))
}
```

## Incidence Mode Comparison

```{r incidence-overview, fig.cap="Incidence spatial patterns across the three generation modes for rho\\_X = 0.20 and 0.50. Color represents incidence (darker = higher burden). Spatial and Poisson modes show visible spatial clustering absent from iid.", fig.height=6}
print(plot_incidence_heatmaps(grid_dim = 10))
```

```{r incidence-dists, fig.cap="Marginal distribution of incidence values by mode, pooled across 50 resamples on the 10x10 grid. All modes are marginally Uniform on [0,1]; spatial structure manifests in spatial covariance, not the marginal.", fig.height=5}
print(plot_incidence_distributions(grid_dim = 10, n_resamples = 50))
```

---

# Subgroup Results by Incidence Mode

The following tables report DIM (pre-revision baseline) results separately for each
incidence configuration, pooled over rook and queen.
Results are **never aggregated across incidence modes**, as each represents a
fundamentally different assumption about prior data.

```{r subgroup-loop, eval=dim_avail, results='asis'}
# Sanitize config names for LaTeX captions (replace _ with space)
cap_safe <- function(x) gsub("_", " ", x, fixed = TRUE)

for (cfg_nm in names(dim_cfgs)) {
  cat(sprintf("\n## DIM: %s\n\n", cfg_nm))
  cfg <- dim_cfgs[[cfg_nm]]

  # Robustness table
  invisible(capture.output(rob <- table_robustness(cfg, cfg_nm)))
  tbl_out <- kable(as.data.frame(rob), booktabs = TRUE, linesep = "", digits = 4,
                   caption = sprintf("DIM (pre-revision) robustness profile: %s", cap_safe(cfg_nm))) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
  print(tbl_out)
  cat("\n")
}
```

---

# Tau Sensitivity Analysis {#sec:tau-sensitivity}

The tau-sweep simulation (12,800 scenarios) swept the direct treatment effect $\tau$
across $\{0.8, 1.0, 1.5, 2.0, 3.0\}$. The primary scenario is $\tau = 1.0$; all
standard results above use this slice. This section examines whether design rankings
and statistical power change across effect sizes. Plots show iid Uniform incidence under
queen contiguity (primary). All $\tau$ levels reuse the same assignments and noise
(common random numbers), so agreement across $\tau$ is not independent confirmation.

```{r tau-sensitivity-check}
tau_avail <- !is.null(mle_results) &&
             "True_Tau" %in% names(mle_results) &&
             length(unique(mle_results$True_Tau)) > 1
```

```{r tau-mse-plots, eval=tau_avail, fig.cap="MLE MSE by design across tau values (iid Uniform, queen). Checkerboard has the highest mean MSE at every tau."}
tau_cfgs <- split_by_incidence_config(mle_results)
# Queen only (primary); rook is a sensitivity analysis and is not pooled in here.
tau_cfgs <- lapply(tau_cfgs, function(df) df[df$Neighbor_Type == "queen", ])
if ("iid Uniform" %in% names(tau_cfgs)) {
  p <- plot_mse_vs_tau(tau_cfgs[["iid Uniform"]], "iid Uniform")
  if (!is.null(p)) print(p)
}
```

```{r tau-power-plots, eval=tau_avail, fig.cap="Statistical power P(reject H0: tau=0) by design across tau values (iid Uniform, queen). 80% power reference line shown. Designs with higher MSE require larger tau to achieve adequate power."}
if ("iid Uniform" %in% names(tau_cfgs)) {
  p <- plot_power_curves(tau_cfgs[["iid Uniform"]], "iid Uniform")
  if (!is.null(p)) print(p)
}
```

```{r tau-coverage-plots, eval=tau_avail, fig.cap="MLE coverage by design across tau values (iid Uniform, queen). Nominal 95% reference line shown. Coverage is near-nominal for every design, including Checkerboard; under rook (not shown) Checkerboard is not identified."}
if ("iid Uniform" %in% names(tau_cfgs)) {
  p <- plot_coverage_vs_tau(tau_cfgs[["iid Uniform"]], "iid Uniform")
  if (!is.null(p)) print(p)
}
```

```{r tau-rank-stability, eval=tau_avail, fig.cap="Design rank trajectories across tau values (iid Uniform, queen). Rank 1 = best MSE. Stable trajectories indicate robust design recommendations across effect sizes."}
if ("iid Uniform" %in% names(tau_cfgs)) {
  p <- plot_rank_trajectories_by_tau(tau_cfgs[["iid Uniform"]], "iid Uniform")
  if (!is.null(p)) print(p)
}
```

---

# Conclusions

## Summary of Findings

The simulation study evaluated 8 treatment assignment designs across 2,560 MLE parameter
scenarios (primary $\tau = 1.0$ slice), spanning three incidence generation modes,
two contiguity structures, four spatial autocorrelation levels, four spillover magnitudes,
and two spillover types. The full tau-sweep covers 12,800 scenarios across
$\tau \in \{0.8, 1.0, 1.5, 2.0, 3.0\}$.

```{r concl-nums}
# Numbers quoted in the findings below, computed from the loaded oracle results
# at tau = 1.0, averaged over incidence modes within each neighbor type.
cn <- mle_results_tau1 %>%
  group_by(Neighbor_Type, Design) %>%
  summarise(MSE = mean(MSE), Var = mean(SD^2), Bias = mean(Bias),
            Cov = mean(Coverage), .groups = "drop")
cmse <- function(nb, d) sprintf("%.3f", cn$MSE[cn$Neighbor_Type == nb & cn$Design == paste("Design", d)])
ccov <- cn %>% filter(!(Neighbor_Type == "rook" & Design == "Design 1"))
cb_q <- cn %>% filter(Neighbor_Type == "queen", Design == "Design 1")
cb_r <- cn %>% filter(Neighbor_Type == "rook",  Design == "Design 1")
dim_cov <- if (!is.null(dim_results)) sprintf("%.2f", mean(dim_results$Coverage, na.rm = TRUE)) else "NA"
```

**Key findings** (MLE, $\tau = 1.0$; queen primary, rook sensitivity):

1. **Coverage is near-nominal and does not separate the designs.** Mean coverage is
   `r sprintf("%.3f", min(ccov$Cov))`--`r sprintf("%.3f", max(ccov$Cov))` for every
   design under both neighbor types, except Checkerboard under rook. The design
   differences show up in MSE. The pre-revision DIM baseline under-covers (mean
   `r dim_cov`), but it was run under the old data-generating process and is not a
   like-for-like comparison.

2. **Saturation Quadrants and Incidence-Guided Saturation Quadrants have the lowest MSE**
   (queen: `r cmse("queen", 3)` and `r cmse("queen", 8)`; rook: `r cmse("rook", 3)` and
   `r cmse("rook", 8)`). The two are statistically indistinguishable (queen Nemenyi
   p = 0.985, Holm-adjusted Wilcoxon p = 0.413; eight-design comparisons in
   `results/eight_design_supplementary/`).

3. **Balanced Halves and Balanced Quartiles form the next tier** (queen: `r cmse("queen", 7)`
   and `r cmse("queen", 6)`), and are also statistically indistinguishable (queen Nemenyi
   p = 1.000, Wilcoxon p = 0.884). Isolation Buffer (`r cmse("queen", 4)`),
   High Incidence Focus (`r cmse("queen", 2)`) and 2x2 Blocking (`r cmse("queen", 5)`)
   follow under queen; under rook, 2x2 Blocking (`r cmse("rook", 5)`) and Isolation
   Buffer (`r cmse("rook", 4)`) are close and High Incidence Focus (`r cmse("rook", 2)`)
   is higher.

4. **Checkerboard has the highest MSE.** Under queen its MSE is `r sprintf("%.3f", cb_q$MSE)`,
   with mean bias `r sprintf("%.3f", cb_q$Bias)`, so almost all of it is variance. Under rook,
   $W\mathbf{Z} = \mathbf{1} - \mathbf{Z}$ and $\tau$ is not identified (bias
   `r sprintf("%.3f", cb_r$Bias)`, approximately $-\gamma$; coverage
   `r sprintf("%.3f", cb_r$Cov)`); these estimates are kept but flagged.

5. **The MSE ordering is the same at every $\tau$ under queen**
   ($\tau \in \{0.8, 1.0, 1.5, 2.0, 3.0\}$), with the caveat that all $\tau$ levels share
   the same assignments and noise.

## Limitations and Planned Extensions

- **Oracle MLE:** The primary MLE model uses the true spillover covariate. A non-oracle
  fit ($Y \sim Z + X$) was run as a sensitivity analysis
  (`sim_results_MLEnonoracle_tau_sweep_combined_20260924_025509.rds`) but is not shown here.
- **DIM baseline is pre-revision:** DIM (2,500 fits per scenario) was run under the old
  data-generating process with 6 designs and was not re-run for the 2026-09 revision.
- **Equal populations:** Poisson mode uses $P_i = 100{,}000$ for all clusters.
  Heterogeneous population sizes (log-normal) would more closely match NC county data.
- **Grid sensitivity:** All results use $G = 10$ ($N = 100$). Sensitivity to
  $G = 8$ or $G = 15$ has not been evaluated.
- **Tau sensitivity:** $\tau$ was swept across $\{0.8, 1.0, 1.5, 2.0, 3.0\}$ in the
  completed tau-sweep run (12,800 scenarios). See Section \ref{sec:tau-sensitivity}
  for power and rank-stability results across effect sizes.

---

# References

- Mirzaei, A. et al. (2019). Sudden unexpected death rates. *(SUD base rate 35/100,000)*
- Gan, W. et al. (2019). County-level Poisson regression for SUD mortality.
- Watson, K. et al. (AHA). Census tract-level spatial analysis of SUD.
- LeSage, J. & Pace, R.K. (2009). *Introduction to Spatial Econometrics*. CRC Press.
- Bivand, R., et al. `spdep` R package.
- Bivand, R. & Piras, G. `spatialreg` R package.
- R packages used: `dplyr`, `tidyr`, `ggplot2`, `viridis`, `knitr`, `kableExtra`, `digest`

---

# Appendix: Result File Locations

```{r file-inventory, results='asis'}
files_df <- data.frame(
  File = c(
    "sim_results_MLE_tau_sweep_combined_20260924_025509.rds",
    "sim_results_MLE_tau_sweep_{iid,spatial,poisson}_20260924_025509.rds",
    "sim_results_MLEnonoracle_tau_sweep_combined_20260924_025509.rds",
    "surface_results_MLE_tau_sweep_20260924_025509.rds",
    "sim_results_DIM_combined_20260304_195321.rds",
    "MLE_tau_sweep_design_recommendations.pdf",
    "MLE_tau_sweep_incidence_overview.pdf",
    "mle_per_config/MLE_tau_sweep_*.pdf (5 files, per incidence config)",
    "mle_per_config/MLE_tau_sweep_*_tau_sensitivity.pdf (5 files)",
    "11_statistical_comparisons_report.{html,pdf}",
    "00_mathematical_specification.pdf",
    "07_results_summary.pdf",
    "archive/pre_revision_20260924/"
  ),
  Contents = c(
    "PRIMARY: 12,800 oracle MLE tau-sweep scenarios (2026-09 revised simulation)",
    "Per-incidence-mode splits of the oracle results",
    "Non-oracle MLE (Y ~ Z + X) sensitivity analysis, 12,800 scenarios",
    "One row per (scenario, surface); basis of the Monte Carlo SEs",
    "DIM baseline: 1,920 scenarios (pre-revision DGP, 6-design sweep; its Design 7 is current Design 6)",
    "Design recommendation figures + tables (primary tau=1.0)",
    "Incidence heatmaps and distributions",
    "Per-config plot PDFs (primary tau=1.0 slice)",
    "Per-config tau sensitivity PDFs (MSE/power/coverage vs tau)",
    "Formal statistical comparisons (Friedman, Nemenyi, Wilcoxon)",
    "Mathematical theory document",
    "This report",
    "Superseded pre-revision (March/April 2026) MLE results and reports"
  )
)
kable(files_df, booktabs = TRUE, linesep = "",
      caption = "Key output files in results/sim\\_data/ and results/ directories.") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8)
```

All simulation data files are located in `results/sim_data/`.
All rendered reports and PDFs are in `results/` and `paper/report/`.
