---
title: "Treatment Assignment Design Evaluation for Spatial CRTs"
subtitle: "Simulation Study with Heterogeneous Incidence — Results Summary"
author: "Andrew Walther"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    theme: cosmo
    smooth-scroll: true
    self-contained: true
  pdf:
    toc: true
    number-sections: true
    fig-pos: "htbp"
    fig-height: 4
    fig-width: 6.5
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r}
#| label: load-packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)
```

```{r}
#| label: resolve-paths
# Robust working directory detection for both source() and quarto::render()
script_dir <- tryCatch(
  normalizePath(dirname(knitr::current_input(dir = TRUE))),
  error = function(e) {
    tryCatch(
      dirname(sys.frame(1)$ofile),
      error = function(e2) getwd()
    )
  }
)
results_dir <- file.path(dirname(script_dir), "results")
```

```{r}
#| label: source-modules
# Source visualization module (provides all table + plot functions)
source(file.path(script_dir, "06_visualizations.R"))
```

```{r}
#| label: load-results
# Load most recent MLE combined results (primary estimator)
results <- tryCatch(
  load_latest_results(results_dir, estimation_mode = "MLE_combined"),
  error = function(e) {
    message("MLE combined results not found: ", e$message)
    NULL
  }
)

# Split into per-incidence-config lists
mle_cfgs <- if (!is.null(results)) split_by_incidence_config(results) else list()
```

```{r}
#| label: compute-summary-stats
mle_avail <- !is.null(results) && nrow(results) > 0

if (mle_avail) {
  mle_summary <- results %>%
    summarise(
      N_scenarios   = n(),
      Bias_min      = round(min(Bias, na.rm = TRUE), 3),
      Bias_max      = round(max(Bias, na.rm = TRUE), 3),
      Bias_mean     = round(mean(Bias, na.rm = TRUE), 3),
      MSE_min       = round(min(MSE, na.rm = TRUE), 3),
      MSE_max       = round(max(MSE, na.rm = TRUE), 3),
      MSE_mean      = round(mean(MSE, na.rm = TRUE), 3),
      Cov_min       = round(min(Coverage, na.rm = TRUE), 2),
      Cov_max       = round(max(Coverage, na.rm = TRUE), 2),
      Cov_mean      = round(mean(Coverage, na.rm = TRUE), 2),
      Fail_mean     = round(mean(Fail_Rate, na.rm = TRUE), 4)
    )

  # Per-design summary for narrative
  mle_by_design <- results %>%
    group_by(Design) %>%
    summarise(
      Mean_Bias     = round(mean(Bias, na.rm = TRUE), 3),
      Median_MSE    = round(median(MSE, na.rm = TRUE), 3),
      Mean_MSE      = round(mean(MSE, na.rm = TRUE), 3),
      Mean_Coverage = round(mean(Coverage, na.rm = TRUE), 3),
      Fail_Rate     = round(mean(Fail_Rate, na.rm = TRUE), 4),
      .groups       = "drop"
    ) %>%
    arrange(Mean_MSE)

  # Derived narrative values
  best_design       <- mle_by_design$Design[1]
  worst_design      <- mle_by_design$Design[nrow(mle_by_design)]
  best_mse          <- mle_by_design$Mean_MSE[1]
  worst_mse         <- mle_by_design$Mean_MSE[nrow(mle_by_design)]
  best_coverage     <- mle_by_design$Mean_Coverage[1]
  worst_coverage    <- mle_by_design$Mean_Coverage[nrow(mle_by_design)]

  n_designs         <- length(unique(results$Design))
  rho_levels        <- sort(unique(results$Rho))
  gamma_levels      <- sort(unique(results$Gamma))
}
```

# Introduction

This report summarizes a simulation study evaluating **`r if (mle_avail) n_designs else "six"` treatment assignment designs**
for Spatial Cluster Randomized Trials (CRTs) when outcome incidence is heterogeneous
and spatially structured. The central research question is:

> *Given known historical incidence data exhibiting spatial heterogeneity, which
> treatment assignment strategy minimizes estimation error for the direct intervention
> effect $\hat{\tau}$ across a range of spatial dependence and spillover configurations?*

**Application context:** Sudden Unexpected Death (SUD) in North Carolina counties.
The Poisson incidence mode uses an SUD base rate of 35 per 100,000 (Mirzaei et al.),
consistent with county-level analyses by Gan et al. and Watson et al.

The study uses Maximum Likelihood Estimation via a spatial autoregressive model (MLE)
as the primary estimator, evaluated across
`r if (mle_avail) format(nrow(results), big.mark = ",") else "1,920"` parameter scenarios.

---

# Mathematical Framework

## Study Region and Spatial Structure

The simulation operates on a **regular lattice grid** $\mathcal{G} = \{s_1, \ldots, s_N\}$
on $[1, G] \times [1, G]$, with $N = G^2$ clusters ($G = 10$, $N = 100$).

Two contiguity structures define neighbor relationships:

- **Rook contiguity:** $s_j \in \mathcal{N}(s_i)$ iff $s_i$ and $s_j$ share an edge
  (up to 4 neighbors)
- **Queen contiguity:** $s_j \in \mathcal{N}(s_i)$ iff $s_i$ and $s_j$ share an edge
  or corner (up to 8 neighbors)

The spatial weight matrix $\mathbf{W}$ has entries
$w_{ij} = |\mathcal{N}(s_i)|^{-1}$ if $s_j \in \mathcal{N}(s_i)$ and $0$ otherwise
(row-standardized).

## Outcome Data Generating Process

Outcomes follow a **Spatial Durbin Model (SDM)**:

$$\mathbf{Y} = (\mathbf{I} - \rho \mathbf{W})^{-1}
\left[\tau \mathbf{Z} + \gamma \cdot \text{Spill}(\mathbf{Z}) + \beta \mathbf{X} + \boldsymbol{\varepsilon}\right]$$

**Parameter definitions:**

| Symbol | Role | Value / Range |
|--------|------|---------------|
| $\tau$ | Direct treatment effect (estimand) | $1.0$ (fixed) |
| $\rho$ | Outcome spatial autocorrelation | `r if (mle_avail) paste0("{", paste(rho_levels, collapse = ", "), "}") else "{0.00, 0.01, 0.20, 0.50}"` |
| $\gamma$ | Spillover magnitude | `r if (mle_avail) paste0("{", paste(gamma_levels, collapse = ", "), "}") else "{0.5, 0.6, 0.7, 0.8}"` |
| $\beta$ | Incidence effect on outcome | $1.0$ (fixed) |
| $\sigma$ | Residual standard deviation | $1.0$ (fixed) |

**Spillover construction:**

$$\text{Spill}_i(\mathbf{Z}) = \frac{\sum_{j \in \mathcal{N}(i)} Z_j}{|\mathcal{N}(i)|}$$

Two spillover modes are evaluated:

- **control_only:** $\gamma$ applied only to units with $Z_i = 0$
- **both:** $\gamma$ applied to all units regardless of treatment status

Stationarity requires $|\rho| < 1/\lambda_{\max}(\mathbf{W})$; all swept $\rho$ values
satisfy this condition.

## Incidence Generation

Three modes generate the cluster-level covariate $X_i \in [0,1]$, each representing
a different assumption about how historical incidence arises:

**Mode 1 — iid Uniform:**
$$X_i \overset{\text{iid}}{\sim} \text{Uniform}(0, 1)$$

No spatial structure; serves as the baseline. One config (rho_X = N/A).

**Mode 2 — Spatial (SAR filter):**
$$\mathbf{X}^* = (\mathbf{I} - \rho_X \mathbf{W})^{-1} \mathbf{u}, \quad
\mathbf{u} \sim \mathcal{N}(\mathbf{0}, \mathbf{I})$$
$$X_i = \Phi(X_i^*) \in (0, 1)$$

Spatially correlated via SAR filter; probability integral transform ($\Phi$) ensures
$X_i$ is marginally $\text{Uniform}(0,1)$ but spatially dependent.
Two configs: $\rho_X \in \{0.20, 0.50\}$.

**Mode 3 — Poisson (count rates):**

1. Spatially correlated log-rates:
   $\log \lambda_i^* = \mu_0 + [(\mathbf{I} - \rho_X \mathbf{W})^{-1} \mathbf{u}]_i$
2. Poisson counts: $C_i \sim \text{Poisson}(\lambda_i^* \cdot P_i)$
   where $P_i = 1{,}000$ (equal population per cluster)
3. Observed rates: $R_i = C_i / P_i$
4. Rank-normalized: $X_i = (\text{rank}(R_i) - 0.5) / N$

Base rate $\mu_0 = \log(35/100{,}000)$ mimics SUD incidence.
Two configs: $\rho_X \in \{0.20, 0.50\}$.

**Critical design invariant:** Incidence is generated **once per (mode, $\rho_X$)
configuration** and held fixed across all ($\rho$, $\gamma$, nb_type) scenarios.
This reflects the realistic constraint that a researcher observes historical incidence
once before designing the trial; spatial model parameters affect the outcome DGP,
not the incidence itself.

## Treatment Assignment Designs

```{r}
#| label: design-table
#| results: asis
source(file.path(script_dir, "03_designs.R"))

# Build design metadata from only the designs present in the results
active_ids <- sort(unique(as.integer(gsub("Design ", "", unique(results$Design)))))
all_names  <- get_design_names()

design_meta <- data.frame(
  ID            = active_ids,
  Name          = unname(all_names[as.character(active_ids)]),
  Deterministic = ifelse(
    sapply(active_ids, is_design_deterministic), "Yes", "No"
  )
)

knitr::kable(
  design_meta,
  col.names = c("ID", "Name", "Deterministic?"),
  caption   = paste0(
    nrow(design_meta),
    " treatment assignment strategies evaluated in this simulation"
  )
)
```

Designs 1 and 2 are **deterministic** given the incidence vector: they produce the
same assignment on every resample. The simulation detects this and runs each once,
replicating the result across all design resamples (saving ~25x compute).

## Estimation Method

**Maximum Likelihood (MLE via SAR):**

Fits `lagsarlm(Y ~ Z + Spill + X, listw = W)` from the `spatialreg` package,
simultaneously estimating $\rho$, $\tau$, and regression coefficients. The true
spillover covariate $\text{Spill}(\mathbf{Z})$ is included as an **oracle regressor**
(i.e., the researcher is assumed to know the true spillover structure). CIs are
derived from the asymptotic covariance matrix.

---

# Simulation Algorithm

## Parameter Grid

```{r}
#| label: param-table
#| results: asis
if (mle_avail) {
  spill_types <- sort(unique(results$Spillover_Type))
  nb_types    <- sort(unique(results$Neighbor_Type))
  inc_configs <- sort(unique(paste(results$Incidence_Mode,
                                   ifelse(is.na(results$Rho_Incidence), "",
                                          results$Rho_Incidence))))

  param_df <- data.frame(
    Parameter = c(
      "Incidence mode",
      "rho_X (incidence spatial autocorr.)",
      "nb_type (contiguity)",
      "rho (outcome spatial autocorr.)",
      "gamma (spillover magnitude)",
      "spill_type",
      "design_id",
      "TOTAL"
    ),
    Values = c(
      paste(sort(unique(results$Incidence_Mode)), collapse = ", "),
      "N/A (iid); 0.20, 0.50 (spatial, poisson)",
      paste(nb_types, collapse = ", "),
      paste(rho_levels, collapse = ", "),
      paste(gamma_levels, collapse = ", "),
      paste(spill_types, collapse = ", "),
      paste(active_ids, collapse = ", "),
      ""
    ),
    Levels = c(
      paste0(length(mle_cfgs), " configs (1 iid + 2 spatial + 2 poisson)"),
      "\u2014",
      as.character(length(nb_types)),
      as.character(length(rho_levels)),
      as.character(length(gamma_levels)),
      as.character(length(spill_types)),
      as.character(n_designs),
      format(nrow(results), big.mark = ",")
    )
  )

  knitr::kable(
    param_df,
    caption = paste0(
      "Simulation parameter grid (",
      format(nrow(results), big.mark = ","),
      " total scenarios)"
    )
  )
}
```

## Resampling Structure

For each scenario, the simulation draws:

| Mode | Design resamples ($R_d$) | Outcome resamples ($R_o$) | Iterations / scenario |
|------|:---:|:---:|:---:|
| MLE | 25 | 10 | 250 |

## Evaluation Metrics

For each scenario, across $K$ total iterations (design × outcome resamples):

$$\text{Bias} = \bar{\hat{\tau}} - \tau, \quad
\text{SD} = \sqrt{\frac{1}{K-1}\sum_{k=1}^K (\hat{\tau}_k - \bar{\hat{\tau}})^2}$$

$$\text{MSE} = \text{Bias}^2 + \text{SD}^2$$

$$\text{Coverage} = \frac{1}{K}\sum_{k=1}^K \mathbf{1}\left[\tau \in (\hat{\tau}_{k,L}, \hat{\tau}_{k,U})\right]$$

## Per-Scenario Reproducibility

Each scenario uses a deterministic seed:
$$\text{seed}_s = \texttt{digest::digest2int}(\texttt{paste}(\text{inc\_mode}, \rho_X, \text{nb\_type}, \rho, \gamma, \text{spill\_type}, d_{\text{id}}, \text{sep}=\text{"|}"))$$

This ensures results are reproducible and order-independent: adding or removing
scenarios from the parameter sweep does not affect other scenarios' seeds.

---

# Results: Maximum Likelihood Estimation (MLE)

## Overall Summary

```{r}
#| label: mle-overall-table
#| results: asis
if (mle_avail) {
  mle_stats_disp <- data.frame(
    Metric = c("Bias", "MSE", "Coverage", "Fail Rate"),
    Min    = c(mle_summary$Bias_min, mle_summary$MSE_min,  mle_summary$Cov_min,  NA),
    Mean   = c(mle_summary$Bias_mean, mle_summary$MSE_mean, mle_summary$Cov_mean, mle_summary$Fail_mean),
    Max    = c(mle_summary$Bias_max, mle_summary$MSE_max,  mle_summary$Cov_max,  NA)
  )
  knitr::kable(
    mle_stats_disp,
    digits  = 3,
    na      = "\u2014",
    caption = paste0(
      "MLE: Summary statistics across all ",
      format(nrow(results), big.mark = ","),
      " scenarios"
    )
  )
}
```

## Design Comparison by MSE

```{r}
#| label: mle-design-summary
#| results: asis
if (mle_avail) {
  knitr::kable(
    mle_by_design,
    col.names = c("Design", "Mean Bias", "Median MSE", "Mean MSE",
                  "Mean Coverage", "Fail Rate"),
    digits    = c(0, 3, 3, 3, 3, 4),
    caption   = "MLE: Design performance averaged across all scenarios and incidence modes"
  )
}
```

## MSE by Design and Neighbor Type

```{r}
#| label: mle-mse-boxplot
#| fig-cap: "MLE: Distribution of MSE by design, faceted by spatial contiguity structure. Boxes sorted by median MSE within each panel."
if (mle_avail) {
  if ("iid Uniform" %in% names(mle_cfgs)) {
    print(plot_mse_by_neighbor(mle_cfgs[["iid Uniform"]], "iid Uniform"))
  } else if (length(mle_cfgs) > 0) {
    print(plot_mse_by_neighbor(mle_cfgs[[1]], names(mle_cfgs)[1]))
  }
}
```

## MSE Heatmap

```{r}
#| label: mle-mse-heatmap
#| fig-cap: "MLE MSE heatmap for iid Uniform incidence. Cells show average MSE across spillover type and gamma, faceted by neighbor type."
if (mle_avail) {
  if ("iid Uniform" %in% names(mle_cfgs)) {
    print(plot_mse_heatmap(mle_cfgs[["iid Uniform"]], "iid Uniform"))
  } else if (length(mle_cfgs) > 0) {
    print(plot_mse_heatmap(mle_cfgs[[1]], names(mle_cfgs)[1]))
  }
}
```

## Design Rank Frequency

```{r}
#| label: mle-ranks-iid
#| results: asis
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  invisible(capture.output(
    mle_rank_tbl <- table_design_ranks(mle_cfgs[["iid Uniform"]], "iid Uniform")
  ))
  knitr::kable(
    as.data.frame(mle_rank_tbl),
    digits  = 1,
    caption = "MLE: Design rank frequency (%) for iid Uniform incidence. Each cell = % of scenarios where design achieved that rank (Rank 1 = lowest MSE)."
  )
}
```

## Robustness Profile

```{r}
#| label: mle-robustness-iid
#| results: asis
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  invisible(capture.output(
    mle_rob_tbl <- table_robustness(mle_cfgs[["iid Uniform"]], "iid Uniform")
  ))
  knitr::kable(
    as.data.frame(mle_rob_tbl),
    digits  = 4,
    caption = "MLE: Robustness profile for iid Uniform incidence. Sorted by Median MSE. IQR = interquartile range across scenarios."
  )
}
```

## Coverage by Design

```{r}
#| label: mle-coverage
#| fig-cap: "MLE: Coverage probability distribution by design across all scenarios. Red dashed line = nominal 95% target."
if (mle_avail) {
  if ("iid Uniform" %in% names(mle_cfgs)) {
    print(plot_coverage_by_design(mle_cfgs[["iid Uniform"]], "iid Uniform"))
  } else if (length(mle_cfgs) > 0) {
    print(plot_coverage_by_design(mle_cfgs[[1]], names(mle_cfgs)[1]))
  }
}
```

## Bias-Variance Decomposition

```{r}
#| label: mle-biasvar
#| fig-cap: "MLE: Bias-squared (dark) and variance (light) components of MSE per design for iid Uniform incidence. Total bar height = MSE."
if (mle_avail) {
  if ("iid Uniform" %in% names(mle_cfgs)) {
    print(plot_bias_variance(mle_cfgs[["iid Uniform"]], "iid Uniform"))
  } else if (length(mle_cfgs) > 0) {
    print(plot_bias_variance(mle_cfgs[[1]], names(mle_cfgs)[1]))
  }
}
```

---

# Sensitivity Analysis

## Parameter Sensitivity

```{r}
#| label: mle-sensitivity
#| results: asis
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  invisible(capture.output(
    sens_tbl <- table_sensitivity(mle_cfgs[["iid Uniform"]], "iid Uniform")
  ))
  knitr::kable(
    as.data.frame(sens_tbl),
    digits  = 4,
    caption = "MLE: Eta-squared (proportion of MSE variance explained) by parameter, for iid Uniform incidence. Higher values indicate parameters where design choice matters more."
  )
}
```

## Effect of Rho on Design Rankings

```{r}
#| label: mle-rho-effect
#| fig-cap: "MLE: Per-design MSE line plots across gamma levels, for iid Uniform incidence. Each panel shows one design; lines represent different rho levels."
if (mle_avail && "iid Uniform" %in% names(mle_cfgs)) {
  print(plot_mse_per_design(mle_cfgs[["iid Uniform"]], "iid Uniform"))
}
```

## Incidence Mode Comparison

```{r}
#| label: incidence-overview
#| fig-cap: "Incidence spatial patterns across the three generation modes for rho_X = 0.20 and 0.50. Color represents incidence (darker = higher burden). Spatial and Poisson modes show visible spatial clustering absent from iid."
#| fig-height: 6
print(plot_incidence_heatmaps(grid_dim = 10))
```

```{r}
#| label: incidence-dists
#| fig-cap: "Marginal distribution of incidence values by mode, pooled across 50 resamples on the 10x10 grid. All modes are marginally Uniform on [0,1]; spatial structure manifests in spatial covariance, not the marginal."
#| fig-height: 5
print(plot_incidence_distributions(grid_dim = 10, n_resamples = 50))
```

---

# Subgroup Results by Incidence Mode

The following tables report MLE results separately for each incidence configuration.
Results are **never aggregated across incidence modes**, as each represents a
fundamentally different assumption about prior data.

```{r}
#| label: subgroup-loop
#| results: asis
if (mle_avail) {
  cap_safe <- function(x) gsub("_", " ", x, fixed = TRUE)

  for (cfg_nm in names(mle_cfgs)) {
    cat(sprintf("\n## MLE: %s\n\n", cfg_nm))
    cfg <- mle_cfgs[[cfg_nm]]

    invisible(capture.output(rob <- table_robustness(cfg, cfg_nm)))
    tbl_out <- knitr::kable(
      as.data.frame(rob),
      digits  = 4,
      caption = sprintf("MLE robustness profile: %s", cap_safe(cfg_nm))
    )
    print(tbl_out)
    cat("\n")
  }
}
```

---

# Conclusions

## Summary of Findings

```{r}
#| label: conclusions-setup
if (mle_avail) {
  # Best and worst designs by mean MSE
  best_design_name  <- best_design
  worst_design_name <- worst_design

  # Coverage stats for best/worst designs
  best_cov  <- round(mle_by_design$Mean_Coverage[mle_by_design$Design == best_design_name], 2)
  worst_cov <- round(mle_by_design$Mean_Coverage[mle_by_design$Design == worst_design_name], 2)

  # Checkerboard specifically
  chkbd_row  <- mle_by_design[grepl("Checkerboard|Design 1", mle_by_design$Design, ignore.case = TRUE), ]
  chkbd_mse  <- if (nrow(chkbd_row) > 0) chkbd_row$Mean_MSE[1] else NA
  chkbd_cov  <- if (nrow(chkbd_row) > 0) round(chkbd_row$Mean_Coverage[1], 2) else NA
  chkbd_name <- if (nrow(chkbd_row) > 0) chkbd_row$Design[1] else "Design 1 (Checkerboard)"

  # Overall coverage
  overall_cov_mean <- round(mean(results$Coverage, na.rm = TRUE), 2)
}
```

The simulation study evaluated
`r if (mle_avail) n_designs else "six"` treatment assignment designs across
`r if (mle_avail) format(nrow(results), big.mark = ",") else "1,920"` parameter
scenarios, spanning three incidence generation modes, two contiguity structures,
`r if (mle_avail) length(rho_levels) else "four"` spatial autocorrelation levels,
`r if (mle_avail) length(gamma_levels) else "four"` spillover magnitudes, and two
spillover types.

**Key findings:**

1. **MLE achieves near-nominal coverage.** The average coverage across all scenarios
   is `r if (mle_avail) overall_cov_mean else "~0.94"`, close to the nominal 0.95 target.
   This reflects MLE's explicit modeling of spatial autocorrelation $\rho$, which ensures
   valid inference when spatial dependence is present.

2. **`r if (mle_avail) best_design_name else "Design 3 (Saturation Quadrants)"` is the top performer.**
   It achieves the lowest average MSE (`r if (mle_avail) round(best_mse, 3) else "~0.21"`)
   and a mean coverage of `r if (mle_avail) best_cov else "~0.94"`. Random saturation
   per quadrant introduces sufficient variation in spatial treatment patterns, allowing
   the spatial autoregressive model to cleanly separate $\tau$ from $\rho$.

3. **`r if (mle_avail) worst_design_name else "Design 1 (Checkerboard)"` is the consistently worst design.**
   It achieves the highest average MSE
   (`r if (mle_avail) round(worst_mse, 3) else "~0.65"`)
   and the lowest mean coverage
   (`r if (mle_avail) worst_cov else "~0.72"`).
   Its perfect spatial alternation creates systematic confounding when incidence is
   spatially structured, inflating bias and degrading coverage.

4. **High Incidence Focus and Balanced Quartile/Strata designs are robustly competitive.**
   These designs rank consistently well across incidence mode and parameter regimes.
   Incidence-stratified assignment directly addresses confounding from $X$.

5. **Design rankings are stable across incidence modes.** The ordering of designs by MSE
   is largely consistent across iid, spatial, and Poisson incidence configurations,
   suggesting the findings generalize across different assumptions about prior data structure.

## Limitations and Planned Extensions

- **Oracle MLE:** The MLE model uses the true spillover covariate. Non-oracle
  comparisons (`include_spill_covariate = FALSE`) remain as a planned extension.
- **Iteration count:** MLE uses 250 iterations per scenario. Apparent variance inflation
  at high-$\rho$ may partly reflect this count; a larger sweep would reduce Monte Carlo error.
- **Equal populations:** Poisson mode uses $P_i = 1{,}000$ for all clusters.
  Heterogeneous population sizes (log-normal) would more closely match NC county data.
- **Grid sensitivity:** All results use $G = 10$ ($N = 100$). Sensitivity to
  $G = 8$ or $G = 15$ has not been evaluated.

---

# References

- Mirzaei, A. et al. (2019). Sudden unexpected death rates. *(SUD base rate 35/100,000)*
- Gan, W. et al. (2019). County-level Poisson regression for SUD mortality.
- Watson, K. et al. (AHA). Census tract-level spatial analysis of SUD.
- LeSage, J. & Pace, R.K. (2009). *Introduction to Spatial Econometrics*. CRC Press.
- Bivand, R., et al. `spdep` R package.
- Bivand, R. & Piras, G. `spatialreg` R package.
- R packages used: `dplyr`, `tidyr`, `ggplot2`, `viridis`, `knitr`, `kableExtra`, `digest`

---

# Appendix: Result File Locations

```{r}
#| label: file-inventory
#| results: asis
if (mle_avail) {
  # List actual .rds files present in results_dir
  sim_data_dir <- file.path(results_dir, "sim_data")
  rds_dir      <- if (dir.exists(sim_data_dir)) sim_data_dir else results_dir
  rds_files    <- list.files(rds_dir, pattern = "\\.rds$", full.names = FALSE)

  if (length(rds_files) > 0) {
    files_df <- data.frame(
      File     = rds_files,
      Location = rep(basename(rds_dir), length(rds_files))
    )
    knitr::kable(
      files_df,
      caption = paste0("RDS result files in results/", basename(rds_dir), "/")
    )
  }
}
```

All simulation data files are located in:
`results/sim_data/`
