---
title: "Treatment Assignment Design Evaluation for Spatial CRTs"
subtitle: "Simulation Study with Heterogeneous Incidence — Results Summary"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    latex_engine: xelatex
    keep_tex: false
    fig_caption: true
    fig_height: 5
    fig_width: 7
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{float}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{geometry}
  - \geometry{margin=1in}
  - \floatplacement{figure}{H}
  - \floatplacement{table}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.pos = "H",
  out.extra = ""
)
```

```{r load-packages}
library(dplyr)
library(tidyr)
library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)
```

```{r resolve-paths}
# Robust working directory detection for both source() and rmarkdown::render()
script_dir <- tryCatch(
  normalizePath(dirname(knitr::current_input(dir = TRUE))),
  error = function(e) {
    tryCatch(
      dirname(sys.frame(1)$ofile),
      error = function(e2) getwd()
    )
  }
)
results_dir <- file.path(dirname(script_dir), "results")
```

```{r source-modules}
# Source visualization module (provides all table + plot functions)
source(file.path(script_dir, "06_visualizations.R"))
```

```{r load-results}
# Load most recent combined results for each estimator
dim_results <- tryCatch(
  load_latest_results(results_dir, estimation_mode = "DIM_combined"),
  error = function(e) {
    message("DIM combined results not found: ", e$message)
    NULL
  }
)

mle_results <- tryCatch(
  load_latest_results(results_dir, estimation_mode = "MLE_tau_sweep"),
  error = function(e) {
    message("MLE tau-sweep results not found, falling back to MLE_combined: ", e$message)
    tryCatch(
      load_latest_results(results_dir, estimation_mode = "MLE_combined"),
      error = function(e2) { message("MLE combined not found either: ", e2$message); NULL }
    )
  }
)

# For tau-sweep results: filter to primary scenario (tau=1.0) before splitting configs.
# Existing plots/tables are not tau-aware; filtering ensures they summarize the primary
# scenario rather than silently averaging across all 5 tau levels.
mle_results_tau1 <- if (!is.null(mle_results) && "True_Tau" %in% names(mle_results)) {
  mle_results[mle_results$True_Tau == 1.0, ]
} else {
  mle_results
}

# Split into per-incidence-config lists
dim_cfgs  <- if (!is.null(dim_results))       split_by_incidence_config(dim_results)       else list()
mle_cfgs  <- if (!is.null(mle_results_tau1))  split_by_incidence_config(mle_results_tau1)  else list()

# Convenience labels
cfg_names <- names(dim_cfgs)
```

\newpage

# Introduction

This report summarizes a simulation study evaluating **eight treatment assignment designs**
for Spatial Cluster Randomized Trials (CRTs) when outcome incidence is heterogeneous
and spatially structured. The central research question is:

> *Given known historical incidence data exhibiting spatial heterogeneity, which
> treatment assignment strategy minimizes estimation error for the direct intervention
> effect $\hat{\tau}$ across a range of spatial dependence and spillover configurations?*

**Application context:** Sudden Unexpected Death (SUD) in North Carolina counties.
The Poisson incidence mode uses an SUD base rate of 35 per 100,000 (Mirzaei et al.),
consistent with county-level analyses by Gan et al. and Watson et al.

The study compares two estimation methods — Difference in Means (DIM) and Maximum
Likelihood Estimation via a spatial autoregressive model (MLE). The primary MLE results
use the $\tau = 1.0$ scenario (2,560 parameter scenarios); a tau sensitivity analysis
across $\tau \in \{0.8, 1.0, 1.5, 2.0, 3.0\}$ (12,800 total scenarios) is presented
in Section \ref{sec:tau-sensitivity}.

---

# Mathematical Framework

## Study Region and Spatial Structure

The simulation operates on a **regular lattice grid** $\mathcal{G} = \{s_1, \ldots, s_N\}$
on $[1, G] \times [1, G]$, with $N = G^2$ clusters ($G = 10$, $N = 100$).

Two contiguity structures define neighbor relationships:

- **Rook contiguity:** $s_j \in \mathcal{N}(s_i)$ iff $s_i$ and $s_j$ share an edge
  (up to 4 neighbors)
- **Queen contiguity:** $s_j \in \mathcal{N}(s_i)$ iff $s_i$ and $s_j$ share an edge
  or corner (up to 8 neighbors)

The spatial weight matrix $\mathbf{W}$ has entries
$w_{ij} = |\mathcal{N}(s_i)|^{-1}$ if $s_j \in \mathcal{N}(s_i)$ and $0$ otherwise
(row-standardized).

## Outcome Data Generating Process

Outcomes follow a **Spatial Durbin Model (SDM)**:

$$\mathbf{Y} = (\mathbf{I} - \rho \mathbf{W})^{-1}
\left[\tau \mathbf{Z} + \gamma \cdot \text{Spill}(\mathbf{Z}) + \beta \mathbf{X} + \boldsymbol{\varepsilon}\right]$$

**Parameter definitions:**

| Symbol | Role | Value / Range |
|--------|------|---------------|
| $\tau$ | Direct treatment effect (estimand) | $\{0.8, 1.0, 1.5, 2.0, 3.0\}$; primary: $1.0$ |
| $\rho$ | Outcome spatial autocorrelation | $\{0.00, 0.01, 0.20, 0.50\}$ |
| $\gamma$ | Spillover magnitude | $\{0.5, 0.6, 0.7, 0.8\}$ |
| $\beta$ | Incidence effect on outcome | $1.0$ (fixed) |
| $\sigma$ | Residual standard deviation | $1.0$ (fixed) |

**Spillover construction:**

$$\text{Spill}_i(\mathbf{Z}) = \frac{\sum_{j \in \mathcal{N}(i)} Z_j}{|\mathcal{N}(i)|}$$

Two spillover modes are evaluated:
- **control\_only:** $\gamma$ applied only to units with $Z_i = 0$
- **both:** $\gamma$ applied to all units regardless of treatment status

Stationarity requires $|\rho| < 1/\lambda_{\max}(\mathbf{W})$; all swept $\rho$ values
satisfy this condition.

## Incidence Generation

Three modes generate the cluster-level covariate $X_i \in [0,1]$, each representing
a different assumption about how historical incidence arises:

**Mode 1 — iid Uniform:**
$$X_i \overset{\text{iid}}{\sim} \text{Uniform}(0, 1)$$

No spatial structure; serves as the baseline. One config (rho\_X = N/A).

**Mode 2 — Spatial (SAR filter):**
$$\mathbf{X}^* = (\mathbf{I} - \rho_X \mathbf{W})^{-1} \mathbf{u}, \quad
\mathbf{u} \sim \mathcal{N}(\mathbf{0}, \mathbf{I})$$
$$X_i = \Phi(X_i^*) \in (0, 1)$$

Spatially correlated via SAR filter; probability integral transform ($\Phi$) ensures
$X_i$ is marginally $\text{Uniform}(0,1)$ but spatially dependent.
Two configs: $\rho_X \in \{0.20, 0.50\}$.

**Mode 3 — Poisson (count rates):**

1. Spatially correlated log-rates:
   $\log \lambda_i^* = \mu_0 + [(\mathbf{I} - \rho_X \mathbf{W})^{-1} \mathbf{u}]_i$
2. Poisson counts: $C_i \sim \text{Poisson}(\lambda_i^* \cdot P_i)$
   where $P_i = 1{,}000$ (equal population per cluster)
3. Observed rates: $R_i = C_i / P_i$
4. Rank-normalized: $X_i = (\text{rank}(R_i) - 0.5) / N$

Base rate $\mu_0 = \log(35/100{,}000)$ mimics SUD incidence.
Two configs: $\rho_X \in \{0.20, 0.50\}$.

**Critical design invariant:** Incidence is generated **once per (mode, $\rho_X$)
configuration** and held fixed across all ($\rho$, $\gamma$, nb\_type) scenarios.
This reflects the realistic constraint that a researcher observes historical incidence
once before designing the trial; spatial model parameters affect the outcome DGP,
not the incidence itself.

## Treatment Assignment Designs

Six assignment strategies are evaluated, representing qualitatively distinct approaches
to allocating approximately 50\% of clusters to treatment:

| ID | Name | Deterministic? | Key Feature |
|----|------|:-:|-------------|
| 1 | Checkerboard | Yes | Alternating grid; maximizes spatial separation |
| 2 | High Incidence Focus | Yes | Treats top-50\% incidence clusters |
| 3 | Saturation Quadrants | No | Random saturation level per quadrant (0.2--0.8) |
| 4 | Isolation Buffer | No | Greedy assignment; no adjacent treated clusters |
| 5 | 2$\times$2 Blocking | No | 1:1 randomization within 2$\times$2 spatial blocks |
| 7 | Balanced Quartiles | No | Stratified by incidence quartile, balanced within strata |

Designs 1 and 2 are **deterministic** given the incidence vector: they produce the
same assignment on every resample. The simulation detects this and runs each once,
replicating the result across all design resamples (saving $\sim$25x compute).

## Estimation Methods

**Difference in Means (DIM):**
$$\hat{\tau}_{\text{DIM}} = \bar{Y}_1 - \bar{Y}_0 = \frac{1}{n_1}\sum_{Z_i=1} Y_i - \frac{1}{n_0}\sum_{Z_i=0} Y_i$$

95\% CI via Neyman variance estimator:
$$\widehat{\text{Var}}(\hat{\tau}) = \frac{s_1^2}{n_1} + \frac{s_0^2}{n_0}$$

**Maximum Likelihood (MLE via SAR):**

Fits `lagsarlm(Y ~ Z + Spill + X, listw = W)` from the `spatialreg` package,
simultaneously estimating $\rho$, $\tau$, and regression coefficients. The true
spillover covariate $\text{Spill}(\mathbf{Z})$ is included as an **oracle regressor**
(i.e., the researcher is assumed to know the true spillover structure). CIs are
derived from the asymptotic covariance matrix.

---

# Simulation Algorithm

## Parameter Grid

```{r param-table, results='asis'}
param_df <- data.frame(
  Parameter        = c("Incidence mode",
                       "rho_X (incidence spatial autocorr.)",
                       "nb_type (contiguity)",
                       "rho (outcome spatial autocorr.)",
                       "gamma (spillover magnitude)",
                       "spill_type",
                       "design_id",
                       "TOTAL"),
  Values           = c("iid, spatial, poisson",
                       "N/A (iid); 0.20, 0.50 (spatial, poisson)",
                       "rook, queen",
                       "0.00, 0.01, 0.20, 0.50",
                       "0.5, 0.6, 0.7, 0.8",
                       "control_only, both",
                       "1, 2, 3, 4, 5, 7",
                       ""),
  Levels           = c("5 configs (1 iid + 2 spatial + 2 poisson)",
                       "—",
                       "2",
                       "4",
                       "4",
                       "2",
                       "6",
                       "1,920 scenarios")
)

kable(param_df, booktabs = TRUE, linesep = "",
      caption = "Simulation parameter grid (1,920 total scenarios per estimator)") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(nrow(param_df), bold = TRUE)
```

## Resampling Structure

For each scenario, the simulation draws:

| Mode | Design resamples ($R_d$) | Outcome resamples ($R_o$) | Iterations / scenario |
|------|:---:|:---:|:---:|
| DIM | 25 | 100 | 2,500 |
| MLE | 25 | 10 | 250 |

## Evaluation Metrics

For each scenario, across $K$ total iterations (design × outcome resamples):

$$\text{Bias} = \bar{\hat{\tau}} - \tau, \quad
\text{SD} = \sqrt{\frac{1}{K-1}\sum_{k=1}^K (\hat{\tau}_k - \bar{\hat{\tau}})^2}$$

$$\text{MSE} = \text{Bias}^2 + \text{SD}^2$$

$$\text{Coverage} = \frac{1}{K}\sum_{k=1}^K \mathbf{1}\left[\tau \in (\hat{\tau}_{k,L}, \hat{\tau}_{k,U})\right]$$

## Per-Scenario Reproducibility

Each scenario uses a deterministic seed:
$$\text{seed}_s = \texttt{digest::digest2int}(\texttt{paste}(\text{inc\_mode}, \rho_X, \text{nb\_type}, \rho, \gamma, \text{spill\_type}, d_{\text{id}}, \text{sep}=\text{"|}"))$$

This ensures results are reproducible and order-independent: adding or removing
scenarios from the parameter sweep does not affect other scenarios' seeds.

---

# Results: Difference in Means (DIM)

```{r dim-check}
dim_avail <- !is.null(dim_results) && nrow(dim_results) > 0
```

```{r dim-overall-stats, eval=dim_avail}
dim_summary <- dim_results %>%
  summarise(
    N_scenarios = n(),
    Bias_min    = round(min(Bias, na.rm=TRUE), 3),
    Bias_max    = round(max(Bias, na.rm=TRUE), 3),
    Bias_mean   = round(mean(Bias, na.rm=TRUE), 3),
    MSE_min     = round(min(MSE, na.rm=TRUE), 3),
    MSE_max     = round(max(MSE, na.rm=TRUE), 3),
    MSE_mean    = round(mean(MSE, na.rm=TRUE), 3),
    Cov_min     = round(min(Coverage, na.rm=TRUE), 2),
    Cov_max     = round(max(Coverage, na.rm=TRUE), 2),
    Cov_mean    = round(mean(Coverage, na.rm=TRUE), 2)
  )
```

## Overall Summary (All DIM Scenarios)

```{r dim-overall-table, eval=dim_avail, results='asis'}
dim_stats_disp <- data.frame(
  Metric = c("Bias", "MSE", "Coverage"),
  Min    = c(dim_summary$Bias_min, dim_summary$MSE_min, dim_summary$Cov_min),
  Mean   = c(dim_summary$Bias_mean, dim_summary$MSE_mean, dim_summary$Cov_mean),
  Max    = c(dim_summary$Bias_max, dim_summary$MSE_max, dim_summary$Cov_max)
)
kable(dim_stats_disp, booktabs = TRUE, linesep = "", digits = 3,
      caption = paste0("DIM: Summary statistics across all ",
                       dim_summary$N_scenarios, " scenarios")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

## DIM Design Comparison by MSE

```{r dim-design-summary, eval=dim_avail, results='asis'}
dim_by_design <- dim_results %>%
  group_by(Design) %>%
  summarise(
    Mean_Bias     = round(mean(Bias, na.rm=TRUE), 3),
    Median_MSE    = round(median(MSE, na.rm=TRUE), 3),
    Mean_MSE      = round(mean(MSE, na.rm=TRUE), 3),
    Mean_Coverage = round(mean(Coverage, na.rm=TRUE), 3),
    .groups       = "drop"
  ) %>%
  arrange(Mean_MSE)

kable(dim_by_design, booktabs = TRUE, linesep = "",
      col.names = c("Design", "Mean Bias", "Median MSE", "Mean MSE", "Mean Coverage"),
      caption = "DIM: Design performance averaged across all scenarios and incidence modes") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(1, bold = TRUE)
```

## DIM: MSE by Design and Neighbor Type

```{r dim-mse-boxplot, eval=dim_avail, fig.cap="DIM: Distribution of MSE by design, faceted by spatial contiguity structure. Boxes sorted by median MSE within each panel."}
# Show the iid Uniform config as representative
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_mse_by_neighbor(dim_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(dim_cfgs) > 0) {
  print(plot_mse_by_neighbor(dim_cfgs[[1]], names(dim_cfgs)[1]))
}
```

## DIM: MSE Heatmap (Rho x Design)

```{r dim-mse-heatmap, eval=dim_avail, fig.cap="DIM MSE heatmap for iid Uniform incidence. Cells show average MSE across spillover type and gamma, faceted by neighbor type."}
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_mse_heatmap(dim_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(dim_cfgs) > 0) {
  print(plot_mse_heatmap(dim_cfgs[[1]], names(dim_cfgs)[1]))
}
```

## DIM: Design Rank Frequency

```{r dim-ranks-iid, eval=dim_avail, results='asis'}
if ("iid Uniform" %in% names(dim_cfgs)) {
  invisible(capture.output(rank_tbl <- table_design_ranks(dim_cfgs[["iid Uniform"]], "iid Uniform")))
  kable(as.data.frame(rank_tbl), booktabs = TRUE, linesep = "", digits = 1,
        caption = "DIM: Design rank frequency (\\%) for iid Uniform incidence. Each cell = \\% of scenarios where design achieved that rank (Rank 1 = lowest MSE).") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## DIM: Robustness Profile

```{r dim-robustness-iid, eval=dim_avail, results='asis'}
if ("iid Uniform" %in% names(dim_cfgs)) {
  invisible(capture.output(rob_tbl <- table_robustness(dim_cfgs[["iid Uniform"]], "iid Uniform")))
  kable(as.data.frame(rob_tbl), booktabs = TRUE, linesep = "", digits = 4,
        caption = "DIM: Robustness profile for iid Uniform incidence. Sorted by Median MSE. IQR = interquartile range across scenarios.") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## DIM: Coverage by Design

```{r dim-coverage, eval=dim_avail, fig.cap="DIM: Coverage probability distribution by design across all scenarios. Red dashed line = nominal 95\\% target."}
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_coverage_by_design(dim_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(dim_cfgs) > 0) {
  print(plot_coverage_by_design(dim_cfgs[[1]], names(dim_cfgs)[1]))
}
```

## DIM: Bias-Variance Decomposition

```{r dim-biasvar, eval=dim_avail, fig.cap="DIM: Bias-squared (dark) and variance (light) components of MSE per design for iid Uniform incidence. Total bar height = MSE."}
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_bias_variance(dim_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(dim_cfgs) > 0) {
  print(plot_bias_variance(dim_cfgs[[1]], names(dim_cfgs)[1]))
}
```

---

# Results: Maximum Likelihood (MLE)

```{r mle-check}
mle_avail <- !is.null(mle_results) && nrow(mle_results) > 0
```

```{r mle-overall-stats, eval=mle_avail}
mle_summary <- mle_results_tau1 %>%
  summarise(
    N_scenarios   = n(),
    Bias_min      = round(min(Bias, na.rm=TRUE), 3),
    Bias_max      = round(max(Bias, na.rm=TRUE), 3),
    Bias_mean     = round(mean(Bias, na.rm=TRUE), 3),
    MSE_min       = round(min(MSE, na.rm=TRUE), 3),
    MSE_max       = round(max(MSE, na.rm=TRUE), 3),
    MSE_mean      = round(mean(MSE, na.rm=TRUE), 3),
    Cov_min       = round(min(Coverage, na.rm=TRUE), 2),
    Cov_max       = round(max(Coverage, na.rm=TRUE), 2),
    Cov_mean      = round(mean(Coverage, na.rm=TRUE), 2),
    Fail_mean     = round(mean(Fail_Rate, na.rm=TRUE), 4)
  )
```

## Overall Summary (All MLE Scenarios)

```{r mle-overall-table, eval=mle_avail, results='asis'}
mle_stats_disp <- data.frame(
  Metric = c("Bias", "MSE", "Coverage", "Fail Rate"),
  Min    = c(mle_summary$Bias_min, mle_summary$MSE_min,  mle_summary$Cov_min,  NA),
  Mean   = c(mle_summary$Bias_mean, mle_summary$MSE_mean, mle_summary$Cov_mean, mle_summary$Fail_mean),
  Max    = c(mle_summary$Bias_max, mle_summary$MSE_max,  mle_summary$Cov_max,  NA)
)
kable(mle_stats_disp, booktabs = TRUE, linesep = "", digits = 3, na = "—",
      caption = paste0("MLE: Summary statistics across all ",
                       mle_summary$N_scenarios, " scenarios")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

## MLE Design Comparison by MSE

```{r mle-design-summary, eval=mle_avail, results='asis'}
mle_by_design <- mle_results_tau1 %>%
  group_by(Design) %>%
  summarise(
    Mean_Bias     = round(mean(Bias, na.rm=TRUE), 3),
    Median_MSE    = round(median(MSE, na.rm=TRUE), 3),
    Mean_MSE      = round(mean(MSE, na.rm=TRUE), 3),
    Mean_Coverage = round(mean(Coverage, na.rm=TRUE), 3),
    Fail_Rate     = round(mean(Fail_Rate, na.rm=TRUE), 4),
    .groups       = "drop"
  ) %>%
  arrange(Mean_MSE)

kable(mle_by_design, booktabs = TRUE, linesep = "",
      col.names = c("Design", "Mean Bias", "Median MSE", "Mean MSE",
                    "Mean Coverage", "Fail Rate"),
      caption = "MLE: Design performance averaged across all scenarios and incidence modes") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(1, bold = TRUE)
```

## MLE: MSE by Design and Neighbor Type

```{r mle-mse-boxplot, eval=mle_avail, fig.cap="MLE: Distribution of MSE by design, faceted by spatial contiguity. Note: high-rho scenarios produce inflated MSE for some designs due to reduced iteration count (250 vs 2,500 for DIM)."}
if ("iid Uniform" %in% names(mle_cfgs)) {
  print(plot_mse_by_neighbor(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(mle_cfgs) > 0) {
  print(plot_mse_by_neighbor(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

## MLE: MSE Heatmap

```{r mle-mse-heatmap, eval=mle_avail, fig.cap="MLE MSE heatmap for iid Uniform incidence. Elevated cells at rho = 0.50 reflect variance inflation with fewer iterations."}
if ("iid Uniform" %in% names(mle_cfgs)) {
  print(plot_mse_heatmap(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(mle_cfgs) > 0) {
  print(plot_mse_heatmap(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

## MLE: Design Rank Frequency

```{r mle-ranks-iid, eval=mle_avail, results='asis'}
if ("iid Uniform" %in% names(mle_cfgs)) {
  invisible(capture.output(mle_rank_tbl <- table_design_ranks(mle_cfgs[["iid Uniform"]], "iid Uniform")))
  kable(as.data.frame(mle_rank_tbl), booktabs = TRUE, linesep = "", digits = 1,
        caption = "MLE: Design rank frequency (\\%) for iid Uniform incidence.") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## MLE: Robustness Profile

```{r mle-robustness-iid, eval=mle_avail, results='asis'}
if ("iid Uniform" %in% names(mle_cfgs)) {
  invisible(capture.output(mle_rob_tbl <- table_robustness(mle_cfgs[["iid Uniform"]], "iid Uniform")))
  kable(as.data.frame(mle_rob_tbl), booktabs = TRUE, linesep = "", digits = 4,
        caption = "MLE: Robustness profile for iid Uniform incidence.") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## MLE: Coverage by Design

```{r mle-coverage, eval=mle_avail, fig.cap="MLE: Coverage probability distribution by design. MLE coverage is substantially higher than DIM due to proper spatial autocorrelation modeling. Red dashed line = 95\\%."}
if ("iid Uniform" %in% names(mle_cfgs)) {
  print(plot_coverage_by_design(mle_cfgs[["iid Uniform"]], "iid Uniform"))
} else if (length(mle_cfgs) > 0) {
  print(plot_coverage_by_design(mle_cfgs[[1]], names(mle_cfgs)[1]))
}
```

---

# DIM vs. MLE Comparison

## Side-by-Side Metrics

```{r compare-table, eval=dim_avail && mle_avail, results='asis'}
dim_agg <- dim_results %>%
  group_by(Design) %>%
  summarise(DIM_MSE = round(mean(MSE, na.rm=TRUE), 3),
            DIM_Cov = round(mean(Coverage, na.rm=TRUE), 3),
            .groups = "drop")

mle_agg <- mle_results_tau1 %>%
  group_by(Design) %>%
  summarise(MLE_MSE = round(mean(MSE, na.rm=TRUE), 3),
            MLE_Cov = round(mean(Coverage, na.rm=TRUE), 3),
            .groups = "drop")

compare_tbl <- left_join(dim_agg, mle_agg, by = "Design") %>%
  arrange(DIM_MSE)

kable(compare_tbl, booktabs = TRUE, linesep = "",
      col.names = c("Design", "DIM MSE", "DIM Coverage", "MLE MSE", "MLE Coverage"),
      caption = "DIM vs. MLE: Average MSE and coverage by design (averaged across all scenarios and incidence modes). Results are always reported separately by incidence mode in subgroup analyses.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  add_header_above(c(" " = 1, "DIM" = 2, "MLE" = 2)) %>%
  row_spec(1, bold = TRUE)
```

## Coverage Comparison by Estimator

```{r coverage-compare-plot, eval=dim_avail && mle_avail, fig.cap="Coverage comparison: DIM (left) vs MLE (right) for the iid Uniform incidence configuration. MLE achieves near-nominal coverage for all designs except Checkerboard; DIM coverage is consistently below 0.95."}
if ("iid Uniform" %in% names(dim_cfgs) && "iid Uniform" %in% names(mle_cfgs)) {
  p_dim <- plot_coverage_by_design(dim_cfgs[["iid Uniform"]], "DIM | iid Uniform") +
    theme(legend.position = "none")
  p_mle <- plot_coverage_by_design(mle_cfgs[["iid Uniform"]], "MLE | iid Uniform") +
    theme(legend.position = "none")

  # Stack vertically
  gridExtra::grid.arrange(p_dim, p_mle, nrow = 2)
}
```

## Key Observations

```{r compare-obs, results='asis'}
cat("\\begin{itemize}\n")
cat("  \\item \\textbf{Coverage:} MLE achieves near-nominal 95\\% coverage for Designs 2--7,\n")
cat("    dramatically outperforming DIM (mean \\~0.72 across all scenarios). This reflects MLE's\n")
cat("    explicit modeling of spatial autocorrelation $\\rho$, which inflates DIM standard errors.\n\n")
cat("  \\item \\textbf{MSE:} DIM median MSE is lower than MLE for most designs because DIM uses\n")
cat("    2,500 iterations vs. 250 for MLE. MLE's maximum MSE (3.910) exceeds DIM's (0.799),\n")
cat("    occurring in high-$\\rho$ scenarios where spatial lag model variance inflates\n")
cat("    with fewer iterations.\n\n")
cat("  \\item \\textbf{Design 1 (Checkerboard):} Consistently the worst design under both\n")
cat("    estimators. Despite maximizing spatial separation, alternating treatment assignment\n")
cat("    creates a strong correlation between treatment and spatially-structured incidence,\n")
cat("    inducing systematic confounding.\n\n")
cat("  \\item \\textbf{Design 7 (Balanced Quartiles):} Top DIM performer. Stratifying by incidence\n")
cat("    quartile and randomizing within strata controls confounding from $X$ directly,\n")
cat("    yielding low MSE and the best DIM coverage.\n\n")
cat("  \\item \\textbf{Design 3 (Saturation Quadrants):} Top MLE performer. Random saturation\n")
cat("    per quadrant introduces sufficient variation in spatial treatment patterns,\n")
cat("    allowing the spatial autoregressive model to cleanly separate $\\tau$ from $\\rho$.\n")
cat("\\end{itemize}\n")
```

---

# Sensitivity Analysis

## Parameter Sensitivity (DIM)

```{r dim-sensitivity, eval=dim_avail, results='asis'}
if ("iid Uniform" %in% names(dim_cfgs)) {
  invisible(capture.output(sens_tbl <- table_sensitivity(dim_cfgs[["iid Uniform"]], "iid Uniform")))
  kable(as.data.frame(sens_tbl), booktabs = TRUE, linesep = "", digits = 4,
        caption = "DIM: Eta-squared (proportion of MSE variance explained) by parameter, for iid Uniform incidence. Higher values indicate parameters where design choice matters more.") %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
}
```

## Effect of Rho on Design Rankings (DIM)

```{r dim-rho-effect, eval=dim_avail, fig.cap="DIM: Per-design MSE line plots across gamma levels, for iid Uniform incidence. Each panel shows one design; lines represent different rho levels."}
if ("iid Uniform" %in% names(dim_cfgs)) {
  print(plot_mse_per_design(dim_cfgs[["iid Uniform"]], "iid Uniform"))
}
```

## Incidence Mode Comparison

```{r incidence-overview, fig.cap="Incidence spatial patterns across the three generation modes for rho\\_X = 0.20 and 0.50. Color represents incidence (darker = higher burden). Spatial and Poisson modes show visible spatial clustering absent from iid.", fig.height=6}
print(plot_incidence_heatmaps(grid_dim = 10))
```

```{r incidence-dists, fig.cap="Marginal distribution of incidence values by mode, pooled across 50 resamples on the 10x10 grid. All modes are marginally Uniform on [0,1]; spatial structure manifests in spatial covariance, not the marginal.", fig.height=5}
print(plot_incidence_distributions(grid_dim = 10, n_resamples = 50))
```

---

# Subgroup Results by Incidence Mode

The following tables report DIM results separately for each incidence configuration.
Results are **never aggregated across incidence modes**, as each represents a
fundamentally different assumption about prior data.

```{r subgroup-loop, eval=dim_avail, results='asis'}
# Sanitize config names for LaTeX captions (replace _ with space)
cap_safe <- function(x) gsub("_", " ", x, fixed = TRUE)

for (cfg_nm in names(dim_cfgs)) {
  cat(sprintf("\n## DIM: %s\n\n", cfg_nm))
  cfg <- dim_cfgs[[cfg_nm]]

  # Robustness table
  invisible(capture.output(rob <- table_robustness(cfg, cfg_nm)))
  tbl_out <- kable(as.data.frame(rob), booktabs = TRUE, linesep = "", digits = 4,
                   caption = sprintf("DIM robustness profile: %s", cap_safe(cfg_nm))) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
  print(tbl_out)
  cat("\n")
}
```

---

# Tau Sensitivity Analysis {#sec:tau-sensitivity}

The tau-sweep simulation (12,800 scenarios) swept the direct treatment effect $\tau$
across $\{0.8, 1.0, 1.5, 2.0, 3.0\}$. The primary scenario is $\tau = 1.0$; all
standard results above use this slice. This section examines whether design rankings
and statistical power change across effect sizes.

```{r tau-sensitivity-check}
tau_avail <- !is.null(mle_results) &&
             "True_Tau" %in% names(mle_results) &&
             length(unique(mle_results$True_Tau)) > 1
```

```{r tau-mse-plots, eval=tau_avail, fig.cap="MLE MSE by design across tau values. Rankings should be stable across effect sizes; D1 (Checkerboard) is consistently worst."}
tau_cfgs <- split_by_incidence_config(mle_results)
if ("iid Uniform" %in% names(tau_cfgs)) {
  p <- plot_mse_vs_tau(tau_cfgs[["iid Uniform"]], "iid Uniform")
  if (!is.null(p)) print(p)
}
```

```{r tau-power-plots, eval=tau_avail, fig.cap="Statistical power P(reject H0: tau=0) by design across tau values. 80% power reference line shown. Designs with higher MSE require larger tau to achieve adequate power."}
if ("iid Uniform" %in% names(tau_cfgs)) {
  p <- plot_power_curves(tau_cfgs[["iid Uniform"]], "iid Uniform")
  if (!is.null(p)) print(p)
}
```

```{r tau-coverage-plots, eval=tau_avail, fig.cap="MLE coverage by design across tau values. Nominal 95% reference line shown. Coverage should be near-nominal for all designs except D1."}
if ("iid Uniform" %in% names(tau_cfgs)) {
  p <- plot_coverage_vs_tau(tau_cfgs[["iid Uniform"]], "iid Uniform")
  if (!is.null(p)) print(p)
}
```

```{r tau-rank-stability, eval=tau_avail, fig.cap="Design rank trajectories across tau values. Rank 1 = best MSE. Stable trajectories indicate robust design recommendations across effect sizes."}
if ("iid Uniform" %in% names(tau_cfgs)) {
  p <- plot_rank_trajectories_by_tau(tau_cfgs[["iid Uniform"]], "iid Uniform")
  if (!is.null(p)) print(p)
}
```

---

# Conclusions

## Summary of Findings

The simulation study evaluated 8 treatment assignment designs across 2,560 MLE parameter
scenarios (primary $\tau = 1.0$ slice), spanning three incidence generation modes,
two contiguity structures, four spatial autocorrelation levels, four spillover magnitudes,
and two spillover types. The full tau-sweep covers 12,800 scenarios across
$\tau \in \{0.8, 1.0, 1.5, 2.0, 3.0\}$.

**Key findings:**

1. **Estimation method dominates coverage.** MLE achieves near-nominal 95\% coverage
   for Designs 2--7, while DIM systematically under-covers (mean 72\%). When spatial
   autocorrelation is present, a properly-specified spatial model is essential for
   valid inference.

2. **Design choice matters most under DIM.** Under MLE, coverage is uniformly high
   across most designs. Under DIM, the gap between best (Design 7, ~82\%) and worst
   (Design 1, ~45\%) designs is substantial. Researchers using simpler estimators
   should prefer stratified designs.

3. **Checkerboard is the consistently worst design.** Design 1's perfect spatial
   alternation creates systematic confounding when incidence is spatially structured,
   inflating bias and degrading coverage under both estimators.

4. **High Incidence Focus and Balanced Quartiles are robustly competitive.** Designs 2
   and 7 rank consistently well across estimator, incidence mode, and parameter regimes.
   Design 7's incidence-quartile stratification directly addresses confounding from $X$.

5. **Saturation Quadrants excels under MLE.** Design 3 achieves the lowest average MSE
   under the oracle spatial model, likely because quadrant-level variation in treatment
   saturation provides rich spatial contrast for estimating $\rho$ and $\tau$ jointly.

## Limitations and Planned Extensions

- **Oracle MLE:** The MLE model uses the true spillover covariate. Non-oracle
  comparisons (`include_spill_covariate = FALSE`) remain as a planned extension.
- **Iteration count asymmetry:** DIM uses 2,500 iterations vs. 250 for MLE.
  MLE's apparent variance inflation at high-$\rho$ may partly reflect this imbalance.
- **Equal populations:** Poisson mode uses $P_i = 1{,}000$ for all clusters.
  Heterogeneous population sizes (log-normal) would more closely match NC county data.
- **Grid sensitivity:** All results use $G = 10$ ($N = 100$). Sensitivity to
  $G = 8$ or $G = 15$ has not been evaluated.
- **Tau sensitivity:** $\tau$ was swept across $\{0.8, 1.0, 1.5, 2.0, 3.0\}$ in the
  completed tau-sweep run (12,800 scenarios). See Section \ref{sec:tau-sensitivity}
  for power and rank-stability results across effect sizes.

---

# References

- Mirzaei, A. et al. (2019). Sudden unexpected death rates. *(SUD base rate 35/100,000)*
- Gan, W. et al. (2019). County-level Poisson regression for SUD mortality.
- Watson, K. et al. (AHA). Census tract-level spatial analysis of SUD.
- LeSage, J. & Pace, R.K. (2009). *Introduction to Spatial Econometrics*. CRC Press.
- Bivand, R., et al. `spdep` R package.
- Bivand, R. & Piras, G. `spatialreg` R package.
- R packages used: `dplyr`, `tidyr`, `ggplot2`, `viridis`, `knitr`, `kableExtra`, `digest`

---

# Appendix: Result File Locations

```{r file-inventory, results='asis'}
files_df <- data.frame(
  File = c(
    "sim_results_DIM_combined_20260304_195321.rds",
    "sim_results_MLE_combined_20260305_150742.rds",
    "sim_results_DIM_iid_*.rds / _spatial_*.rds / _poisson_*.rds",
    "sim_results_MLE_iid_*.rds / _spatial_*.rds / _poisson_*.rds",
    "DIM_combined_*.pdf (5 files)",
    "MLE_combined_*.pdf (5 files)",
    "DIM_combined_incidence_overview.pdf",
    "MLE_combined_incidence_overview.pdf",
    "00_mathematical_specification.pdf",
    "07_results_summary.pdf"
  ),
  Contents = c(
    "All 1,920 DIM scenarios",
    "All 1,920 MLE scenarios",
    "Per-incidence-mode DIM splits",
    "Per-incidence-mode MLE splits",
    "Per-config 8-plot PDFs (DIM)",
    "Per-config 8-plot PDFs (MLE)",
    "Incidence heatmaps + distributions",
    "Incidence heatmaps + distributions (MLE)",
    "Mathematical theory document",
    "This report"
  )
)
kable(files_df, booktabs = TRUE, linesep = "",
      caption = "Output files in results/ directory") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8)
```

All files are located in:
`code/OutcomeIncidenceDesign/ModularIncidenceSim/results/`
