---
title: "Personalized Design Recommendation Report"
subtitle: "MLE-Based Analysis for Spatial CRT Treatment Assignment"
author: "Andrew Walther"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    theme: cosmo
    smooth-scroll: true
    self-contained: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    latex-engine: xelatex
    keep-tex: false
    fig-pos: "htbp"
    fig-height: 4
    fig-width: 6.5
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{float}
        \usepackage{amsmath}
        \usepackage{amssymb}
        \usepackage{geometry}
        \usepackage{xcolor}
        \usepackage{mdframed}
        \geometry{margin=1in}
        \floatplacement{figure}{htbp}
        \floatplacement{table}{H}
        \definecolor{boxbg}{RGB}{240,248,255}
        \definecolor{boxframe}{RGB}{70,130,180}
---

```{r setup}
#| include: false
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.pos = "htbp"
)
```

```{r load-packages}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)
```

```{r resolve-paths}
#| include: false
script_dir <- tryCatch(
  normalizePath(dirname(knitr::current_input(dir = TRUE))),
  error = function(e) {
    tryCatch(
      normalizePath(dirname(sys.frame(1)$ofile)),
      error = function(e2) normalizePath(getwd())
    )
  }
)
results_dir <- file.path(dirname(script_dir), "results")
```

```{r source-modules}
#| include: false
# Source recommendation module (which sources 06 -> 01-03)
source(file.path(script_dir, "08_design_recommendations.R"))
```

```{r load-results}
#| include: false
# Load the 2026-09 revised ORACLE tau-sweep results (Y ~ Z + Spill + X).
# No fallback: the pre-revision "MLE_combined" file is archived and superseded,
# so a missing tau-sweep file must stop the render rather than silently load
# stale results.
mle_results_all_nb_full <- load_latest_results(results_dir, estimation_mode = "MLE_tau_sweep")
if (!"Estimator" %in% names(mle_results_all_nb_full) ||
    !all(mle_results_all_nb_full$Estimator == "oracle")) {
  stop("09 report expects the oracle MLE_tau_sweep results; got Estimator = ",
       paste(unique(mle_results_all_nb_full$Estimator), collapse = ", "))
}
# Queen contiguity is the PRIMARY neighbor structure; rook is a sensitivity
# analysis (and the Chapter 2 continuity case). All headline rankings below use
# queen only -- rook and queen are never pooled. Under rook, Checkerboard's tau
# is not identified (WZ = 1 - Z), so its rook estimates are kept but flagged.
mle_results_full <- mle_results_all_nb_full[mle_results_all_nb_full$Neighbor_Type == "queen", ]
# Primary scenario tau = 1.0 (run_recommendation_report() applies the same tau filter).
mle_results        <- mle_results_full[mle_results_full$True_Tau == 1.0, ]
mle_results_all_nb <- mle_results_all_nb_full[mle_results_all_nb_full$True_Tau == 1.0, ]
mle_results_rook   <- mle_results_all_nb[mle_results_all_nb$Neighbor_Type == "rook", ]
tau_sweep_available <- length(unique(mle_results_full$True_Tau)) > 1
mle_avail <- nrow(mle_results) > 0
mle_cfgs  <- if (mle_avail) split_by_incidence_config(mle_results) else list()
cfg_names <- names(mle_cfgs)
# Both neighbor types, per config: used ONLY by the scenario lookup (each lookup
# table fixes a single Neighbor_Type, so nothing is pooled there).
mle_cfgs_all_nb <- split_by_incidence_config(mle_results_all_nb)

# Full design names for prose (tables keep the short "Dn: ..." labels)
full_design_name <- function(d) {
  unname(sub("Design [0-9]+: ", "", get_design_names()[gsub("Design ", "", d)]))
}
```

```{r global-summaries}
#| include: false
# Pre-compute cross-config summary and scenario counts used throughout
if (mle_avail) {
  # Design IDs and names from data (not hardcoded)
  active_design_ids <- sort(unique(as.integer(
    gsub("Design ", "", mle_results$Design)
  )))
  n_designs <- length(active_design_ids)

  # Total scenarios and per-config counts
  n_scenarios_total <- nrow(mle_results)
  n_scenarios_per_config <- n_scenarios_total / length(mle_cfgs)

  # Parameter levels from data
  rho_levels   <- sort(unique(mle_results$Rho))
  gamma_levels <- sort(unique(mle_results$Gamma))
  spill_levels <- sort(unique(mle_results$Spillover_Type))
  nb_levels    <- sort(unique(mle_results$Neighbor_Type))
  n_params_per_design <- n_scenarios_per_config / n_designs  # combos per design per config

  # Ranked summary per config
  all_ranked_list <- lapply(seq_along(mle_cfgs), function(i) {
    r <- rank_designs_by_group(mle_cfgs[[i]], character(0))
    r$Inc_Config <- cfg_names[i]
    r
  })
  all_ranked <- bind_rows(all_ranked_list)

  # Best and worst per config
  best_per_config <- all_ranked %>%
    filter(Rank == 1) %>%
    select(Inc_Config, Design, Avg_MSE, Avg_Coverage)

  worst_per_config <- all_ranked %>%
    filter(Rank == n_designs) %>%
    select(Inc_Config, Design, Avg_MSE, Avg_Coverage)

  # Modal best design (wins most configs)
  modal_best       <- names(sort(table(best_per_config$Design), decreasing = TRUE))[1]
  modal_best_short <- full_design_name(modal_best)
  n_configs_modal_best_wins <- sum(best_per_config$Design == modal_best)

  # Modal worst design
  worst_design       <- names(sort(table(worst_per_config$Design), decreasing = TRUE))[1]
  worst_design_short <- full_design_name(worst_design)

  # Overall rankings across all scenarios (for summary section)
  overall_all <- rank_designs_by_group(mle_results, character(0))
  best_overall       <- overall_all %>% filter(Rank == 1)
  worst_overall      <- overall_all %>% filter(Rank == max(Rank))
  overall_mse_ratio  <- round(worst_overall$Avg_MSE[1] / best_overall$Avg_MSE[1], 1)
  best_overall_short  <- full_design_name(best_overall$Design[1])
  worst_overall_short <- full_design_name(worst_overall$Design[1])

  # MSE ratio for checkerboard vs best (per config)
  mse_ratio_per_config <- all_ranked %>%
    group_by(Inc_Config) %>%
    summarise(
      best_mse  = Avg_MSE[Rank == 1],
      worst_mse = Avg_MSE[Rank == max(Rank)],
      ratio     = round(worst_mse / best_mse, 1),
      .groups   = "drop"
    )
  mse_ratio_range <- paste0(
    min(mse_ratio_per_config$ratio), "--", max(mse_ratio_per_config$ratio)
  )

  # Worst design coverage range
  worst_cov_vals <- worst_per_config$Avg_Coverage
  worst_cov_range <- paste0(
    round(min(worst_cov_vals), 3), "--", round(max(worst_cov_vals), 3)
  )

  # Spillover rank reversal: best design under control_only vs both
  spill_rankings <- lapply(cfg_names, function(cn) {
    cfg <- mle_cfgs[[cn]]
    r <- rank_designs_by_group(cfg, "Spillover_Type")
    r$Inc_Config <- cn
    r
  })
  spill_all <- bind_rows(spill_rankings)

  best_under_control_only <- spill_all %>%
    filter(Spillover_Type == "control_only", Rank == 1) %>%
    count(Design) %>% arrange(desc(n)) %>% slice(1) %>% pull(Design)
  best_under_control_only_short <- full_design_name(best_under_control_only)

  best_under_both <- spill_all %>%
    filter(Spillover_Type == "both", Rank == 1) %>%
    count(Design) %>% arrange(desc(n)) %>% slice(1) %>% pull(Design)
  best_under_both_short <- full_design_name(best_under_both)

  # Runner-up margin range across configs
  runner_up_margins <- all_ranked %>%
    group_by(Inc_Config) %>%
    summarise(
      best_mse   = Avg_MSE[Rank == 1],
      second_mse = Avg_MSE[Rank == 2],
      pct_margin = round((second_mse - best_mse) / best_mse * 100, 1),
      .groups    = "drop"
    )
  margin_range <- paste0(
    min(runner_up_margins$pct_margin), "\\% -- ",
    max(runner_up_margins$pct_margin), "\\%"
  )

  # Second-best design frequency
  second_best_freq <- all_ranked %>%
    filter(Rank == 2) %>%
    count(Design, sort = TRUE)

  # Gamma sensitivity: eta-squared for best design across configs
  gamma_eta_vals <- sapply(cfg_names, function(cn) {
    d_data <- mle_cfgs[[cn]] %>% filter(Design == modal_best)
    gm    <- mean(d_data$MSE, na.rm = TRUE)
    ss_tot <- sum((d_data$MSE - gm)^2, na.rm = TRUE)
    if (ss_tot == 0) return(0)
    gs <- d_data %>%
      group_by(Gamma) %>%
      summarise(gm2 = mean(MSE, na.rm = TRUE), gn = n(), .groups = "drop")
    ss_b <- sum(gs$gn * (gs$gm2 - gm)^2)
    ss_b / ss_tot
  })
  max_gamma_eta <- round(max(gamma_eta_vals), 3)

  # Leading design coverage range (designs other than the worst)
  other_designs_cov <- all_ranked %>%
    filter(Design != worst_design) %>%
    pull(Avg_Coverage)
  leading_cov_lo <- round(min(other_designs_cov), 2)
  leading_cov_hi <- round(max(other_designs_cov), 2)

  # Coverage range over ALL designs x configs (queen): used to state that
  # coverage is near-nominal everywhere under queen and does not separate designs
  all_cov_lo <- round(min(all_ranked$Avg_Coverage), 3)
  all_cov_hi <- round(max(all_ranked$Avg_Coverage), 3)

  # Rook sensitivity: Checkerboard under rook (tau not identified; flagged)
  rook_cb <- mle_results_rook[mle_results_rook$Design == "Design 1", ]
  rook_cb_cov  <- round(mean(rook_cb$Coverage), 2)
  rook_cb_bias <- round(mean(rook_cb$Bias), 2)
}
```

# Executive Summary

This report is a narrative companion to the `MLE_tau_sweep_design_recommendations_queen.pdf`
figure file (and its rook counterpart `..._rook.pdf`), produced by `run_recommendation_report()`
separately for each neighbor type. It provides narrative explanations of **how each
analysis was computed**, **what each figure and table shows**, and **what the results
show** for researchers designing spatial cluster randomized trials (CRTs). The
statements below describe the simulation results; they are not the study's final
design recommendation, which has not yet been chosen.

The results are those of the 2026-09 revised simulation (matched incidence surfaces,
oracle estimator). The simulation evaluates **`r if(mle_avail) n_designs` treatment
assignment designs** across **`r if(mle_avail) n_scenarios_total` parameter scenarios
under queen contiguity** (the primary neighbor structure; rook contiguity is a
sensitivity analysis summarized in @sec-summary), using maximum likelihood estimation
of a spatial autoregressive lag model (the oracle model $Y \sim Z + \text{Spill} + X$,
fit with the lean ML engine `fit_sar_lag()`, which matches `spatialreg::lagsarlm` to
about $10^{-7}$). The estimand is the direct treatment effect $\tau$ (primary scenario:
$\tau = 1.0$; sensitivity across $\tau \in \{0.8, 1.5, 2.0, 3.0\}$ in @sec-tau-sensitivity).

Three analytical questions are addressed:

\begin{mdframed}[backgroundcolor=boxbg, linecolor=boxframe, linewidth=1pt]
\textbf{Q1 -- Per incidence mode:} Which design is best given how historical
incidence was generated (iid, Spatial, Poisson)?

\textbf{Q2 -- Per parameter level:} Which design is best when a specific simulation
parameter takes a particular value (e.g., high spatial autocorrelation $\rho = 0.50$),
marginalizing over all other parameters?

\textbf{Q3 -- Per scenario:} Which design is best for a fully-specified combination
of parameter values?
\end{mdframed}

```{r exec-table}
#| eval: !expr mle_avail
#| results: asis
exec_df <- best_per_config %>%
  mutate(
    Design     = short_design_name(Design),
    Avg_MSE    = round(Avg_MSE, 4),
    Avg_Coverage = round(Avg_Coverage, 3)
  ) %>%
  rename(`Incidence Config` = Inc_Config,
         `Best Design`      = Design,
         `Avg MSE`          = Avg_MSE,
         `Avg Coverage`     = Avg_Coverage)

kable(exec_df, booktabs = TRUE, linesep = "", align = "llrr",
      caption = paste0(
        "Lowest-average-MSE design for each of the ",
        length(cfg_names), " incidence configurations (queen contiguity, tau = 1.0)."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(seq_len(nrow(exec_df)), bold = FALSE)
```

**Key finding (queen):** `r if(mle_avail) modal_best_short` has the lowest average MSE
in `r if(mle_avail) n_configs_modal_best_wins` of `r if(mle_avail) length(cfg_names)`
incidence configurations and Incidence-Guided Saturation Quadrants in the others; the
two saturation-quadrant designs are statistically indistinguishable (see
@sec-mechanism). `r if(mle_avail) worst_design_short` has the highest average MSE in
every configuration. Coverage is near-nominal
(`r if(mle_avail) all_cov_lo`--`r if(mle_avail) all_cov_hi`) for every design under
queen, so it does not separate the designs; MSE does. Spillover type (control-only
vs. both) is by far the most influential parameter for every design except Isolation
Buffer, while spatial autocorrelation $\rho$ and spillover magnitude $\gamma$ have
secondary effects.

# Study Background

## Designs Evaluated

`r if(mle_avail) n_designs` treatment assignment strategies are compared. Every design
except Isolation Buffer treats exactly 50 of the 100 clusters ($10 \times 10$ grid);
Isolation Buffer treats a maximal independent set (about 22 clusters under queen, 38
under rook). Designs that use incidence rank the clusters' incidence $X_k$ with ties
broken at random for every draw:

```{r design-table}
#| results: asis
# Build design_df from 03_designs.R helpers + a description lookup
# Descriptions are structural (not result claims) so remain as prose constants.
design_descriptions <- c(
  "1" = "Alternating grid pattern; maximizes spatial separation of treated and control units",
  "2" = "Treats the 50 highest-incidence clusters (random tie-breaking)",
  "3" = "Assigns random saturation levels (0.2--0.8) within each of four spatial quadrants",
  "4" = "Greedy assignment ensuring no two adjacent clusters are both treated",
  "5" = "1:1 randomization within non-overlapping 2x2 spatial blocks",
  "6" = "Stratified randomization balanced within incidence quartiles",
  "7" = "Stratified randomization balanced within incidence halves (above/below median)",
  "8" = "Quadrant saturations 0.8/0.6/0.4/0.2 assigned by rank of quadrant mean incidence"
)

if (mle_avail) {
  all_design_names <- get_design_names()
  # Restrict to IDs that actually appear in the results
  run_ids <- active_design_ids
  design_df <- data.frame(
    ID          = run_ids,
    Name        = sub("Design [0-9]+: ", "", unname(all_design_names[as.character(run_ids)])),
    Det         = ifelse(sapply(run_ids, is_design_deterministic), "Yes", "No"),
    Description = unname(design_descriptions[as.character(run_ids)]),
    stringsAsFactors = FALSE
  )
  n_det <- sum(design_df$Det == "Yes")
  n_sto <- sum(design_df$Det == "No")
} else {
  design_df <- data.frame(ID=integer(0), Name=character(0), Det=character(0), Description=character(0))
  n_det <- 0L; n_sto <- 0L
}

kable(design_df, booktabs = TRUE, linesep = "",
      col.names = c("ID", "Name", "Deterministic?", "Description"),
      caption = paste0(
        nrow(design_df),
        " treatment assignment designs evaluated. Deterministic designs (",
        paste(design_df$ID[design_df$Det == "Yes"], collapse = ", "),
        ") produce one assignment used for every fit; stochastic designs draw 25 assignments on each of the 10 incidence surfaces."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 9) %>%
  column_spec(4, width = "7cm")
```

## Performance Metrics

For each of the `r if(mle_avail) n_scenarios_total` scenarios, **250 model fits**
(10 incidence surfaces $X_k$ $\times$ 25 design draws per surface; each draw is made
from $X_k$, the outcome and analysis use the same $X_k$, and every fit has its own
noise column) produce the following metrics:

- **Bias** $= \bar{\hat{\tau}} - \tau$: average departure from true effect (primary $\tau = 1.0$)
- **SD**: standard deviation of estimates across iterations
- **MSE** $= \text{Bias}^2 + \text{SD}^2$: total estimation error; the **primary
  ranking criterion** throughout this report
- **Coverage**: fraction of 95\% confidence intervals containing the true $\tau$

Lower MSE is better. Coverage near 0.95 (the nominal level) indicates valid inference.

## Simulation Parameter Space

```{r param-table}
#| results: asis
if (mle_avail) {
  param_df <- data.frame(
    Parameter = c(
      "Incidence mode",
      "rho\\_X (incidence spatial autocorr.)",
      "nb\\_type (contiguity)",
      "Rho (outcome spatial autocorr.)",
      "Gamma (spillover magnitude)",
      "Spillover type",
      "Design",
      "TOTAL"
    ),
    Values = c(
      paste(unique(mle_results$Incidence_Mode), collapse = ", "),
      paste0("N/A (iid); ", paste(sort(unique(mle_results$Rho_Incidence[mle_results$Rho_Incidence > 0])), collapse = ", "), " (Spatial, Poisson)"),
      paste0(paste(nb_levels, collapse = ", "), " (primary; rook is a sensitivity analysis)"),
      paste(rho_levels, collapse = ", "),
      paste(gamma_levels, collapse = ", "),
      paste(spill_levels, collapse = ", "),
      paste(active_design_ids, collapse = ", "),
      ""
    ),
    Levels = c(
      paste0(length(cfg_names), " configs"),
      "---",
      as.character(length(nb_levels)),
      as.character(length(rho_levels)),
      as.character(length(gamma_levels)),
      as.character(length(spill_levels)),
      as.character(n_designs),
      paste0(n_scenarios_total, " scenarios")
    ),
    stringsAsFactors = FALSE
  )
} else {
  param_df <- data.frame(Parameter=character(0), Values=character(0), Levels=character(0))
}

kable(param_df, booktabs = TRUE, linesep = "",
      caption = paste0(
        "Simulation parameter grid. Each of the ",
        if (mle_avail) n_scenarios_total else "?",
        " queen-contiguity scenarios (tau = 1.0) is a unique combination of (incidence config, Rho, Gamma, Spillover type, Design). Results are always reported separately by incidence config and never pooled over rook and queen."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(nrow(param_df), bold = TRUE)
```

# Analytical Methods

This section explains exactly how each analysis in the recommendation report
is computed.

## Core Ranking Method: `rank_designs_by_group()`

All conditional rankings in this report share the same logic, implemented in
`rank_designs_by_group()`:

1. **Group** the `r if(mle_avail) n_scenarios_per_config` scenarios within an
   incidence config by the requested conditioning variables plus Design (e.g.,
   group by `{Rho, Design}`)
2. **Aggregate**: compute average MSE, Coverage, Bias, and SD within each group
3. **Rank**: within each unique combination of the conditioning variables,
   assign integer ranks to designs based on ascending average MSE
   (rank 1 = best; ties broken using minimum rank)
4. **Return** a tidy data frame with one row per `{group, Design}` combination

This is the same ranking logic used in `table_design_ranks()` in
`06_visualizations.R`, extended to support arbitrary conditioning sets.

**Critical invariant:** Rankings are **always computed within a single incidence
configuration**. Results are never aggregated across the `r if(mle_avail) length(cfg_names)` incidence configs
because each represents a fundamentally different assumption about how prior
incidence data arises.

## Q1 — Per-Config Rankings: `table_incidence_rankings()` and `plot_incidence_rankings()`

**What is computed:** For each of the `r if(mle_avail) length(cfg_names)` incidence
configs, all `r if(mle_avail) n_scenarios_per_config` scenarios
(`r if(mle_avail) n_designs` designs $\times$ `r if(mle_avail) n_params_per_design`
parameter combinations) are summarized by computing the average MSE per design.
Designs are then ranked 1--`r if(mle_avail) n_designs` (lowest = best) within
each config.

**What the figure shows** (Page 1 of PDF): A faceted bar chart with one panel
per incidence config. Bars represent average MSE per design, sorted from lowest
to highest within each panel. Rank labels (1--`r if(mle_avail) n_designs`) appear
above each bar.

**How to read it:** Lower bars are better. Rank labels allow quick comparison
across panels. A design ranked consistently high across all panels performs well
regardless of how incidence was generated.

## Q2 — Marginal Rankings: `table_marginal_rankings()` and `plot_rank_trajectories()`

**What "marginal" means:** For a parameter like Rho, we want to know: ignoring
all other parameters, how does each design rank when Rho takes a specific value?
This is computed by grouping all scenarios by `{Rho, Design}` and averaging MSE
across the remaining parameters (Gamma, Spillover\_Type); Neighbor\_Type is fixed
at queen.

**What the rank trajectory plot shows**: A line plot where the x-axis is the
parameter level, the y-axis is design rank (1 at top, `r if(mle_avail) n_designs`
at bottom), and each line traces one design. Crossing lines indicate a **rank
reversal**: a design that is best at one parameter level but not at another.

**What the marginal ranking table shows**: A wide table with parameter levels
as column headers and designs as rows. Each cell reports `Avg_MSE (#Rank)` at
that parameter level, averaged over all other parameters. Designs are ordered
by their overall rank (best at top).

**What the conditional MSE boxplot shows**: Rather than averages, this shows the
**full distribution** of raw scenario-level MSE values for each design at each
parameter level. This reveals whether a design's advantage is consistent or
comes from a few favorable extreme scenarios.

## Q3 — Best Design Heatmap: `plot_best_design_heatmap()`

**What is computed:** For every combination of two parameters (e.g., Rho and
Gamma), all scenarios sharing that combination are grouped, average MSE is
computed per design, and the design with the minimum average MSE is identified
as the winner.

**What the heatmap shows**: A grid of colored tiles where each cell corresponds
to one `{Rho, Gamma}` combination. The color and text label identify the winning
design. The MSE value inside each tile is the winning design's average MSE at
that combination.

**Interpretation guidance:** If one design wins all tiles, it dominates
unconditionally. If tiles show different winners, the choice of design should
adapt to the anticipated parameter regime.

## Programmatic Commentary: `generate_commentary()`

For each incidence config, six structured findings are automatically derived
from the results:

| Finding | Computed as |
|---------|-------------|
| Overall winner | Design with Rank 1 from ungrouped `rank_designs_by_group()` |
| Dominance % | From scenario-level pairwise comparison: $\frac{\#\{s : \text{MSE}_{\text{best},s} < \text{MSE}_{\text{2nd},s}\}}{`r if(mle_avail) n_params_per_design`}$ |
| Rank stability | Whether the best design holds rank 1 at every level of Rho and every level of Gamma |
| Coverage | Average Coverage for the best and worst designs |
| Sensitivity | Eta-squared ($\eta^2 = SS_{\text{between}} / SS_{\text{total}}$) for each parameter |
| Summary | Template string synthesizing findings 1--5 (descriptive) |

# Q1: Design Rankings by Incidence Mode

## Cross-Config MSE Rankings

```{r q1-mse-plot-cap, include=FALSE}
q1_mse_cap <- paste0(
  "Average MSE per design for each of the ",
  if (mle_avail) length(cfg_names) else "?",
  " incidence configurations (queen contiguity, tau = 1.0). Bars are sorted left-to-right within each panel",
  " by MSE (lowest = best). Rank labels above bars. Lower bars are better.",
  " Note the shared y-axis: ",
  if (mle_avail) worst_design_short else "the worst design",
  "'s much higher MSE compresses the other bars."
)
```

```{r q1-mse-plot}
#| eval: !expr mle_avail
#| fig-cap: !expr q1_mse_cap
#| fig-height: 5.0
print(plot_incidence_rankings(mle_results) +
  theme(text        = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        strip.text  = element_text(size = 9, face = "bold"),
        plot.title  = element_text(size = 11),
        plot.subtitle = element_text(size = 9)))
```

**Reading the plot:** The `r if(mle_avail) length(cfg_names)` panels correspond
to the `r if(mle_avail) length(cfg_names)` incidence configurations. Within each
panel, designs are arranged from best (left) to worst (right), with the rank number
printed above each bar. The two saturation-quadrant designs (Saturation Quadrants and
Incidence-Guided Saturation Quadrants) occupy the two leftmost positions in every panel.

```{r q1-mse-obs-setup}
#| include: false
#| eval: !expr mle_avail
# Compute data-driven observations about MSE spread
best_mse_range <- round(range(best_per_config$Avg_MSE), 3)
worst_mse_range_vals <- worst_per_config$Avg_MSE
```

**Key observation:** `r if(mle_avail) modal_best_short` ranks first in
`r if(mle_avail) n_configs_modal_best_wins` of `r if(mle_avail) length(cfg_names)`
incidence configurations; the winning design's average MSE ranges from
`r if(mle_avail) best_mse_range[1]` to `r if(mle_avail) best_mse_range[2]`
depending on the config. The worst design (`r if(mle_avail) worst_design_short`) has
`r if(mle_avail) mse_ratio_range`x the winner's MSE in every configuration.

## Cross-Config Coverage Rankings

```{r q1-cov-cap, include=FALSE}
q1_cov_cap <- paste0(
  "Average 95% CI coverage probability per design for each incidence configuration",
  " (queen contiguity, tau = 1.0). Red dashed line = nominal 0.95. Under queen,",
  " every design's average coverage lies in ",
  if (mle_avail) paste0(all_cov_lo, "--", all_cov_hi) else "?",
  ", so coverage does not separate the designs."
)
```

```{r q1-cov-plot}
#| eval: !expr mle_avail
#| fig-cap: !expr q1_cov_cap
#| fig-height: 5.0
print(plot_incidence_coverage(mle_results) +
  theme(text        = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        strip.text  = element_text(size = 9, face = "bold"),
        plot.title  = element_text(size = 11),
        plot.subtitle = element_text(size = 9)))
```

**Reading the plot:** The red dashed line at 0.95 is the nominal coverage target.
Bars above this line are over-covering (conservative CIs); bars below are under-covering
(anti-conservative). Under queen, every design, including
`r if(mle_avail) worst_design_short` (`r if(mle_avail) worst_cov_range`), is close to
nominal (`r if(mle_avail) all_cov_lo`--`r if(mle_avail) all_cov_hi`); the roughly
one-point shortfall is the finite-sample behavior of the Wald interval.

**Key observation:** Coverage does not separate the designs under queen; MSE does.
The one coverage failure in the study is `r if(mle_avail) worst_design_short` under
rook contiguity, where $WZ = 1 - Z$, $\tau$ is not identified, and coverage falls to
`r if(mle_avail) rook_cb_cov` (see @sec-summary).

## Detailed Rankings by Incidence Config

```{r q1-detail-table}
#| eval: !expr mle_avail
#| results: asis
for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  r <- rank_designs_by_group(cfg, character(0)) %>%
    mutate(
      Design       = short_design_name(Design),
      Avg_MSE      = round(Avg_MSE, 4),
      Avg_Coverage = round(Avg_Coverage, 3),
      Avg_Bias     = round(Avg_Bias, 4)
    ) %>%
    select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias)

  best_mse   <- r$Avg_MSE[1]
  second_mse <- r$Avg_MSE[2]
  pct_diff   <- round((second_mse - best_mse) / best_mse * 100, 1)
  worst_mse  <- r$Avg_MSE[nrow(r)]
  ratio      <- round(worst_mse / best_mse, 1)

  cap_safe_nm <- gsub("_", " ", cfg_nm)
  tbl_out <- kable(r, booktabs = TRUE, linesep = "", align = "rlrrr",
        col.names = c("Rank", "Design", "Avg MSE", "Avg Coverage", "Avg Bias"),
        caption = sprintf(
          "MLE design rankings for %s (queen). Runner-up MSE is %.1f\\%% higher than the winner; worst design MSE is %.1fx higher.",
          cap_safe_nm, pct_diff, ratio)) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
    row_spec(1, bold = TRUE)
  print(tbl_out)
  cat("\n")
}
```

```{r q1-patterns-setup}
#| include: false
#| eval: !expr mle_avail
# Compute cross-config ranking patterns for narrative
best_n_wins <- n_configs_modal_best_wins

# Runner-up: which design ranks 2nd most often
runner_up_design       <- second_best_freq$Design[1]
runner_up_short        <- full_design_name(runner_up_design)
runner_up_n_times      <- second_best_freq$n[1]

# Margin range (min and max % gap between best and runner-up)
margin_min <- min(runner_up_margins$pct_margin)
margin_max <- max(runner_up_margins$pct_margin)

# Worst coverage
worst_cov_max <- round(max(worst_per_config$Avg_Coverage), 2)

# Second runner-up
runner_up2_design <- if (nrow(second_best_freq) > 1) second_best_freq$Design[2] else NA
runner_up2_short  <- if (!is.na(runner_up2_design)) full_design_name(runner_up2_design) else "N/A"
runner_up2_n      <- if (nrow(second_best_freq) > 1) second_best_freq$n[2] else 0
```

**Notable patterns across configs (queen):**

- **`r if(mle_avail) modal_best_short`** ranks 1st in `r if(mle_avail) best_n_wins` of
  `r if(mle_avail) length(cfg_names)` configs.
  Its runner-up margin ranges from `r if(mle_avail) margin_min`\% to
  `r if(mle_avail) margin_max`\% depending on incidence configuration.
- **`r if(mle_avail) runner_up_short`** is the most consistent runner-up, ranking 2nd
  in `r if(mle_avail) runner_up_n_times` of `r if(mle_avail) length(cfg_names)` configs.
- **`r if(mle_avail) runner_up2_short`** ranks 2nd in the remaining
  `r if(mle_avail) runner_up2_n` config(s).
- **`r if(mle_avail) worst_design_short`** is last in all configs with MSE
  `r if(mle_avail) mse_ratio_range`x that of the winner, although its coverage is
  near-nominal (at most `r if(mle_avail) worst_cov_max`).

# Q2: Marginal Rankings by Parameter Level

This section answers: **holding all other parameters at their average, how does
each design's rank change as one parameter varies?**

## Effect of Outcome Spatial Autocorrelation (Rho)

```{r q2-rho-cap, include=FALSE}
q2_rho_cap <- paste0(
  "Design rank trajectories across Rho for each incidence config (one panel per config).",
  " Rank 1 = best. Lines that stay flat indicate robust designs;",
  " crossing lines reveal parameter-driven rank reversals (queen contiguity)."
)
```

```{r q2-rho-trajectories}
#| eval: !expr mle_avail
#| fig-cap: !expr q2_rho_cap
#| fig-height: 8.0
p_list <- lapply(seq_along(mle_cfgs), function(i) {
  plot_rank_trajectories(mle_cfgs[[i]], "Rho", cfg_names[i],
                         point_size = 2.5, line_size = 0.9, label_size = 2.0) +
    theme(legend.position = if (i == length(mle_cfgs)) "right" else "none",
          plot.title    = element_text(size = 9),
          plot.subtitle = element_text(size = 8),
          axis.text     = element_text(size = 8),
          axis.title    = element_text(size = 9),
          legend.text   = element_text(size = 8),
          legend.title  = element_text(size = 9))
})
gridExtra::grid.arrange(grobs = p_list, ncol = 1)
```

**How to read the trajectory plots:** Rank 1 sits at the top; rank
`r if(mle_avail) n_designs` at the bottom. A flat horizontal line means a
design's rank does not change as Rho increases. A downward slope means the
design falls in rank as Rho increases. Crossing lines between two designs
indicate a rank reversal.

```{r q2-rho-findings-setup}
#| include: false
#| eval: !expr mle_avail
# Determine Rho stability of modal best and worst design across all configs
best_rho_stable_all <- all(sapply(cfg_names, function(cn) {
  rr <- rank_designs_by_group(mle_cfgs[[cn]], "Rho") %>%
    filter(Design == modal_best)
  all(rr$Rank == 1)
}))

worst_rho_stable_all <- all(sapply(cfg_names, function(cn) {
  rr <- rank_designs_by_group(mle_cfgs[[cn]], "Rho") %>%
    filter(Design == worst_design)
  all(rr$Rank == n_designs)
}))

# Where best design cedes rank 1 under Rho (if any)
rho_exceptions <- lapply(cfg_names, function(cn) {
  rr <- rank_designs_by_group(mle_cfgs[[cn]], "Rho") %>%
    filter(Design == modal_best)
  if (any(rr$Rank != 1)) {
    bad_rho <- rr$Rho[rr$Rank != 1]
    sprintf("%s at Rho=%s", cn, paste(bad_rho, collapse=","))
  } else NULL
})
rho_exceptions <- Filter(Negate(is.null), rho_exceptions)
rho_exception_str <- if (length(rho_exceptions) == 0) {
  "no exceptions found"
} else {
  paste(rho_exceptions, collapse = "; ")
}

# Do the two saturation-quadrant designs (3, 8) hold ranks 1-2 at every level
# of a parameter in every config?  (Checked, not assumed.)
sat_pair <- c("Design 3", "Design 8")
sat_top2_all <- function(param) {
  all(sapply(cfg_names, function(cn) {
    rr <- rank_designs_by_group(mle_cfgs[[cn]], param)
    all(tapply(rr$Design[rr$Rank <= 2], rr[[param]][rr$Rank <= 2],
               function(d) setequal(d, sat_pair)))
  }))
}
sat_top2_rho   <- sat_top2_all("Rho")
sat_top2_gamma <- sat_top2_all("Gamma")

# Ranks 5-8 unchanged across Gamma in every config?
low_ranks_fixed_gamma <- all(sapply(cfg_names, function(cn) {
  rr <- rank_designs_by_group(mle_cfgs[[cn]], "Gamma") %>% filter(Rank >= 5)
  all(tapply(rr$Rank, rr$Design, function(x) length(unique(x)) == 1))
}))
```

**Findings:**

- **`r if(mle_avail) modal_best_short`**
  `r if(mle_avail) ifelse(best_rho_stable_all, "maintains rank 1 across all Rho levels in every incidence config", paste0("does not hold rank 1 at every Rho level; it cedes rank 1 in: ", rho_exception_str))`.
  `r if(mle_avail) ifelse(sat_top2_rho, "At every Rho level in every config, ranks 1 and 2 are held by the two saturation-quadrant designs, so the exceptions are swaps within that pair.", "Ranks 1 and 2 are not always held by the two saturation-quadrant designs.")`
- **`r if(mle_avail) worst_design_short`**
  `r if(mle_avail) ifelse(worst_rho_stable_all, "consistently occupies last rank across all Rho values, confirming its failure is not a high-Rho artifact", "generally occupies the bottom rank but shows some variation across Rho levels")`.

## Effect of Spillover Magnitude (Gamma)

```{r q2-gamma-cap, include=FALSE}
q2_gamma_cap <- paste0(
  "Design rank trajectories across Gamma. Gamma controls the magnitude of",
  " treatment spillover to neighbors (queen contiguity). For ",
  if (mle_avail) modal_best_short else "the best design",
  ", Gamma explains little MSE variation (eta-squared at most ",
  if (mle_avail) max_gamma_eta else "?",
  " across configs)."
)
```

```{r q2-gamma-trajectories}
#| eval: !expr mle_avail
#| fig-cap: !expr q2_gamma_cap
#| fig-height: 8.0
p_list2 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_rank_trajectories(mle_cfgs[[i]], "Gamma", cfg_names[i],
                         point_size = 2.5, line_size = 0.9, label_size = 2.0) +
    theme(legend.position = if (i == length(mle_cfgs)) "right" else "none",
          plot.title    = element_text(size = 9),
          plot.subtitle = element_text(size = 8),
          axis.text     = element_text(size = 8),
          axis.title    = element_text(size = 9),
          legend.text   = element_text(size = 8),
          legend.title  = element_text(size = 9))
})
gridExtra::grid.arrange(grobs = p_list2, ncol = 1)
```

**Findings:** Across Gamma = `r if(mle_avail) min(gamma_levels)` to
`r if(mle_avail) max(gamma_levels)`, the design rankings change only by swaps between
designs with near-identical MSE:
`r if(mle_avail) ifelse(sat_top2_gamma, "the two saturation-quadrant designs hold ranks 1 and 2 at every Gamma level in every config (trading places)", "the two saturation-quadrant designs do not always hold ranks 1 and 2")`,
and `r if(mle_avail) ifelse(low_ranks_fixed_gamma, "ranks 5 to 8 do not change at all", "ranks 5 to 8 also shift in some configs")`.
For `r if(mle_avail) modal_best_short`, Gamma explains at most
`r if(mle_avail) ceiling(max_gamma_eta * 100)`\% of MSE variation (eta-squared
$\le$ `r if(mle_avail) max_gamma_eta`). Isolation Buffer differs from the other designs:
spillover type explains almost none of its MSE variation (eta-squared below 0.05 in
every config under queen, versus above 0.9 for every other design; computed from the
queen, tau = 1.0 slice with the same $SS_{\text{between}}/SS_{\text{total}}$ formula
used in the per-config findings).

## Marginal Ranking Tables

The following tables report average MSE (and rank in parentheses) at each level
of each key parameter, averaged over all other simulation parameters.

```{r q2-marginal-tables}
#| eval: !expr mle_avail
#| results: asis
params_to_show <- c("Rho", "Gamma", "Spillover_Type")

for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  overall_order <- rank_designs_by_group(cfg, character(0)) %>%
    arrange(Rank) %>% pull(Design)

  cap_safe_nm <- gsub("_", " ", cfg_nm)
  cat(sprintf("\n### %s\n\n", cfg_nm))

  for (param in params_to_show) {
    ranked <- rank_designs_by_group(cfg, param) %>%
      mutate(cell = sprintf("%.4f (#%d)", Avg_MSE, Rank)) %>%
      select(Design, all_of(param), cell) %>%
      pivot_wider(names_from = all_of(param), values_from = cell,
                  names_prefix = paste0(param, "=")) %>%
      mutate(Design = factor(Design, levels = overall_order)) %>%
      arrange(Design) %>%
      mutate(Design = short_design_name(as.character(Design)))

    param_label <- switch(param,
      "Rho"          = "Rho (outcome spatial autocorrelation)",
      "Gamma"        = "Gamma (spillover magnitude)",
      "Spillover_Type" = "Spillover Type",
      param)

    tbl_out <- kable(ranked, booktabs = TRUE, linesep = "",
          caption = sprintf(
            "%s | Marginal rankings by %s. Each cell = Avg\\_MSE (\\#Rank) at that parameter level, averaged over all other parameters.",
            cap_safe_nm, param_label)) %>%
      kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                    font_size = 8) %>%
      row_spec(1, bold = TRUE)
    print(tbl_out)
    cat("\n")
  }
}
```

```{r q2-spillover-setup}
#| include: false
#| eval: !expr mle_avail
# Determine the rank reversal pattern between control_only and both
# Identify which design ranks 1st under each spillover type most often
spill_n_configs_control_only <- sum(spill_all$Spillover_Type == "control_only" &
                                    spill_all$Design == best_under_control_only &
                                    spill_all$Rank == 1)
spill_n_configs_both         <- sum(spill_all$Spillover_Type == "both" &
                                    spill_all$Design == best_under_both &
                                    spill_all$Rank == 1)
spill_total_groups           <- length(cfg_names)  # one per incidence config

# Check if same design wins overall regardless of spillover
same_winner_both_types <- (best_under_control_only == best_under_both)

# Per-regime MSE (queen, tau = 1.0), averaged over configs and the remaining
# parameters, for the saturation pair (3, 8) and the balanced pair (6, 7)
regime_mse <- mle_results %>%
  filter(Design %in% c("Design 3", "Design 6", "Design 7", "Design 8")) %>%
  group_by(Spillover_Type, Design) %>%
  summarise(MSE = mean(MSE), .groups = "drop")
rm_get <- function(st, d) sprintf("%.3f", regime_mse$MSE[regime_mse$Spillover_Type == st & regime_mse$Design == d])
```

**Key takeaway from the Spillover\_Type marginal table (queen):** The most striking
pattern across all configs is the **rank comparison by spillover type**:

- Under **"control\_only"** spillover (only untreated units experience spillover
  from neighbors), **`r if(mle_avail) best_under_control_only_short`** ranks 1st
  in `r if(mle_avail) spill_n_configs_control_only` of
  `r if(mle_avail) spill_total_groups` configs.
- Under **"both"** spillover (treatment and control units both experience spillover),
  **`r if(mle_avail) best_under_both_short`**
  `r if(mle_avail) ifelse(same_winner_both_types, "also ranks 1st most often", paste0("ranks 1st in ", spill_n_configs_both, " of ", spill_total_groups, " configs (Balanced Halves in the others)"))`.

The regimes differ in how much the designs differ. Averaged over configs, under
"both" the leading designs are close (Balanced Quartiles `r if(mle_avail) rm_get("both", "Design 6")`,
Balanced Halves `r if(mle_avail) rm_get("both", "Design 7")`, Saturation Quadrants
`r if(mle_avail) rm_get("both", "Design 3")`, Incidence-Guided Saturation Quadrants
`r if(mle_avail) rm_get("both", "Design 8")`), whereas under "control\_only" the
saturation-quadrant designs (`r if(mle_avail) rm_get("control_only", "Design 3")`,
`r if(mle_avail) rm_get("control_only", "Design 8")`) have clearly lower MSE than the
balanced designs (`r if(mle_avail) rm_get("control_only", "Design 6")`,
`r if(mle_avail) rm_get("control_only", "Design 7")`). Averaged over both regimes,
the saturation-quadrant designs have lower MSE than the balanced designs because
their control-only advantage is larger than their disadvantage under "both".

# Q3: Best Design for Parameter Combinations

## Rho x Gamma Best-Design Maps

```{r q3-heatmaps-cap, include=FALSE}
q3_heatmaps_cap <- paste0(
  "Best design heatmap: Rho vs. Gamma for each incidence config (queen contiguity).",
  " Each tile shows which design achieves the lowest average MSE at that (Rho, Gamma)",
  " combination, averaged over Spillover Type.",
  " Tile text shows the winning design abbreviation and its average MSE."
)
```

```{r q3-heatmaps}
#| eval: !expr mle_avail
#| fig-cap: !expr q3_heatmaps_cap
#| fig-height: 8.0
p_list3 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_best_design_heatmap(mle_cfgs[[i]], "Rho", "Gamma", cfg_names[i],
                           text_size = 3, text_color = "white",
                           compact_labels = TRUE) +
    labs(title = cfg_names[i], subtitle = NULL) +
    theme(plot.title  = element_text(size = 9, face = "bold"),
          axis.text   = element_text(size = 8),
          axis.title  = element_text(size = 9),
          legend.position = "none")
})
gridExtra::grid.arrange(grobs = p_list3, ncol = 2)
```

**How to read the maps:** Each tile corresponds to one (Rho, Gamma) combination.
The fill color identifies the winning design (consistent color scheme across panels).
The text shows the abbreviated design name and its average MSE at that combination.

```{r q3-heatmap-findings}
#| include: false
#| eval: !expr mle_avail
# Count how many Rho x Gamma tiles each design wins (aggregated across all configs)
rho_gamma_winners <- lapply(cfg_names, function(cn) {
  r <- rank_designs_by_group(mle_cfgs[[cn]], c("Rho", "Gamma")) %>%
    filter(Rank == 1) %>%
    select(Design)
  r
})
rho_gamma_all <- bind_rows(rho_gamma_winners)
rho_gamma_freq <- rho_gamma_all %>% count(Design, sort = TRUE)
total_rho_gamma_tiles <- nrow(rho_gamma_all)
best_rho_gamma_design <- rho_gamma_freq$Design[1]
best_rho_gamma_short  <- full_design_name(best_rho_gamma_design)
best_rho_gamma_tiles  <- rho_gamma_freq$n[1]
pct_rho_gamma_tiles   <- round(best_rho_gamma_tiles / total_rho_gamma_tiles * 100)
sat_pair_tiles        <- sum(rho_gamma_all$Design %in% c("Design 3", "Design 8"))

# Check if MSE increases with Rho (for best design)
rho_mse_trend <- rank_designs_by_group(mle_results, "Rho") %>%
  filter(Design == modal_best) %>%
  arrange(Rho)
rho_mse_monotone <- all(diff(rho_mse_trend$Avg_MSE) >= 0)
```

**Findings:**

- **The two saturation-quadrant designs win
  `r if(mle_avail) sat_pair_tiles` of `r if(mle_avail) total_rho_gamma_tiles` Rho x
  Gamma tiles** across all configs; `r if(mle_avail) best_rho_gamma_short` wins
  `r if(mle_avail) best_rho_gamma_tiles` (`r if(mle_avail) pct_rho_gamma_tiles`\%),
  so which of the two wins a given tile is close to a coin flip.
- **MSE is largely insensitive to Gamma** (the tiles within a Rho row show similar
  MSE values). This re-confirms the Gamma insensitivity finding from Q2.
- **MSE `r if(mle_avail) ifelse(rho_mse_monotone, "increases monotonically", "is not monotone")` in Rho**
  for `r if(mle_avail) modal_best_short` (average MSE
  `r if(mle_avail) paste(sprintf("%.4f", rho_mse_trend$Avg_MSE), collapse = ", ")` at
  Rho = `r if(mle_avail) paste(rho_mse_trend$Rho, collapse = ", ")`, averaged over
  configs).
  `r if(mle_avail) ifelse(sat_top2_rho, "The two saturation-quadrant designs hold ranks 1 and 2 at every Rho level.", "The two saturation-quadrant designs do not hold ranks 1 and 2 at every Rho level.")`

## Rho x Spillover Type Best-Design Maps

```{r q3-heatmaps-spill-cap, include=FALSE}
q3_spill_cap <- paste0(
  "Best design heatmap: Rho vs. Spillover Type for each incidence config (queen contiguity).",
  " This reveals the key interaction: under both-direction spillover the winner",
  " is usually a balanced design, under control-only spillover a saturation-quadrant design."
)
```

```{r q3-heatmaps-spill}
#| eval: !expr mle_avail
#| fig-cap: !expr q3_spill_cap
#| fig-height: 7.5
p_list4 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_best_design_heatmap(mle_cfgs[[i]], "Rho", "Spillover_Type", cfg_names[i],
                           text_size = 3, text_color = "white",
                           compact_labels = TRUE) +
    labs(title = cfg_names[i], subtitle = NULL) +
    theme(plot.title  = element_text(size = 9, face = "bold"),
          axis.text   = element_text(size = 8),
          axis.title  = element_text(size = 9),
          legend.position = "none")
})
gridExtra::grid.arrange(grobs = p_list4, ncol = 2)
```

```{r q3-spillover-interaction}
#| include: false
#| eval: !expr mle_avail
# Count Rho x Spillover_Type tiles won per design
rho_spill_winners <- lapply(cfg_names, function(cn) {
  r <- rank_designs_by_group(mle_cfgs[[cn]], c("Rho", "Spillover_Type")) %>%
    filter(Rank == 1)
  r$Inc_Config <- cn
  r
})
rho_spill_all <- bind_rows(rho_spill_winners)

# Tiles won under control_only
control_tiles_by_design <- rho_spill_all %>%
  filter(Spillover_Type == "control_only") %>%
  count(Design, sort = TRUE)
control_best_design <- control_tiles_by_design$Design[1]
control_best_short  <- full_design_name(control_best_design)
control_best_tiles  <- control_tiles_by_design$n[1]
total_control_tiles <- sum(rho_spill_all$Spillover_Type == "control_only")
control_pct         <- round(control_best_tiles / total_control_tiles * 100)

# Tiles won under both
both_tiles_by_design <- rho_spill_all %>%
  filter(Spillover_Type == "both") %>%
  count(Design, sort = TRUE)
both_best_design <- both_tiles_by_design$Design[1]
both_best_short  <- full_design_name(both_best_design)
both_best_tiles  <- both_tiles_by_design$n[1]
total_both_tiles <- sum(rho_spill_all$Spillover_Type == "both")
both_pct         <- round(both_best_tiles / total_both_tiles * 100)
```

**Key finding:** The Rho x Spillover\_Type heatmap reveals the most practically
important interaction:

- When spillover is **"control\_only"**: `r if(mle_avail) control_best_short` wins
  `r if(mle_avail) control_best_tiles` of `r if(mle_avail) total_control_tiles`
  tiles (`r if(mle_avail) control_pct`\%) across all Rho levels and all configs.
- When spillover is **"both"**: `r if(mle_avail) both_best_short` wins
  `r if(mle_avail) both_best_tiles` of `r if(mle_avail) total_both_tiles` tiles
  (`r if(mle_avail) both_pct`\%).

This interaction is the primary driver of the overall MSE competition between
`r if(mle_avail) control_best_short` and `r if(mle_avail) both_best_short`.
Averaged over both spillover types, the saturation-quadrant designs have lower MSE
than the balanced designs, because the MSE gaps under "control\_only" are much
larger than those under "both" (see the Spillover\_Type discussion in Q2).

# Per-Config Narrative Findings

This section synthesizes the analytical results for each incidence configuration
into a cohesive narrative, presenting the six structured findings produced by
`generate_commentary()` (queen contiguity, $\tau = 1.0$).

```{r per-config-commentary}
#| eval: !expr mle_avail
#| results: asis
for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  cap_safe_nm <- gsub("_", " ", cfg_nm)

  # --- Compute all findings ---
  overall <- rank_designs_by_group(cfg, character(0))
  best_row   <- overall %>% filter(Rank == 1)
  worst_row  <- overall %>% filter(Rank == max(Rank))
  second_row <- overall %>% filter(Rank == 2)

  best_name   <- full_design_name(best_row$Design[1])
  worst_name  <- full_design_name(worst_row$Design[1])
  second_name <- full_design_name(second_row$Design[1])

  # Pairwise dominance
  scenario_ids <- c("Neighbor_Type", "Rho", "Gamma", "Spillover_Type")
  wide <- cfg %>%
    select(all_of(c(scenario_ids, "Design", "MSE"))) %>%
    pivot_wider(names_from = Design, values_from = MSE, id_cols = all_of(scenario_ids))
  dom_vs_second <- round(mean(wide[[best_row$Design[1]]] < wide[[second_row$Design[1]]], na.rm=TRUE)*100, 1)
  dom_vs_worst  <- round(mean(wide[[best_row$Design[1]]] < wide[[worst_row$Design[1]]], na.rm=TRUE)*100, 1)

  # Rank stability
  rho_ranks   <- rank_designs_by_group(cfg, "Rho")   %>% filter(Design == best_row$Design[1])
  gamma_ranks <- rank_designs_by_group(cfg, "Gamma") %>% filter(Design == best_row$Design[1])
  rho_stable   <- all(rho_ranks$Rank == 1)
  gamma_stable <- all(gamma_ranks$Rank == 1)
  stable_str <- if (rho_stable && gamma_stable) {
    "holds rank 1 at every level of Rho and Gamma (no rank crossover)"
  } else if (rho_stable) {
    "stable across all Rho levels but shows minor rank changes across Gamma"
  } else if (gamma_stable) {
    sprintf("stable across all Gamma levels; briefly cedes rank 1 at Rho = %s",
            paste(rho_ranks$Rho[rho_ranks$Rank != 1], collapse = ", "))
  } else {
    "shows rank reversals across both Rho and Gamma levels"
  }

  # Sensitivity
  params <- c("Rho", "Gamma", "Spillover_Type")  # Neighbor_Type fixed at queen
  d_data <- cfg %>% filter(Design == best_row$Design[1])
  gm     <- mean(d_data$MSE, na.rm=TRUE)
  ss_tot <- sum((d_data$MSE - gm)^2, na.rm=TRUE)
  eta_sq <- sapply(params, function(p) {
    gs <- d_data %>% group_by(.data[[p]]) %>%
      summarise(gm2 = mean(MSE, na.rm=TRUE), gn = n(), .groups="drop")
    ss_b <- sum(gs$gn * (gs$gm2 - gm)^2)
    if (ss_tot > 0) ss_b / ss_tot else 0
  })
  names(eta_sq) <- params
  top_param  <- names(which.max(eta_sq))
  low_params <- names(eta_sq[eta_sq < 0.05])

  # MSE ratio
  mse_ratio_cfg  <- round(worst_row$Avg_MSE[1] / best_row$Avg_MSE[1], 1)
  pct_vs_second  <- round((second_row$Avg_MSE[1] - best_row$Avg_MSE[1]) / best_row$Avg_MSE[1] * 100, 1)

  # --- Print ---
  cat(sprintf("## %s\n\n", cfg_nm))

  cat(sprintf(
    "**Finding 1 -- Overall Winner:** %s achieves the lowest average MSE (%.4f) across all %d parameter combinations in this incidence configuration. The runner-up is %s (avg MSE = %.4f), which is %.1f\\%% higher.\n\n",
    best_name, best_row$Avg_MSE[1],
    as.integer(n_params_per_design),
    second_name, second_row$Avg_MSE[1],
    pct_vs_second
  ))

  cat(sprintf(
    "**Finding 2 -- Dominance:** %s achieves lower MSE than the runner-up (%s) in %.1f\\%% of individual scenarios, and beats the worst performer (%s) in %.1f\\%% of scenarios. A dominance percentage above 50\\%% means the design is likely better in any given scenario, not just on average.\n\n",
    best_name, second_name, dom_vs_second,
    worst_name, dom_vs_worst
  ))

  cat(sprintf(
    "**Finding 3 -- Robustness:** %s %s.\n\n",
    best_name, stable_str
  ))

  cat(sprintf(
    "**Finding 4 -- Coverage:** %s achieves average 95\\%% CI coverage of %.3f (nominal = 0.95); the highest-MSE design (%s) achieves %.3f. Under queen, coverage is near-nominal for every design and does not separate them.\n\n",
    best_name, best_row$Avg_Coverage[1],
    worst_name, worst_row$Avg_Coverage[1]
  ))

  cat(sprintf(
    "**Finding 5 -- Sensitivity:** For %s, the most influential simulation parameter is %s (eta-squared = %.3f), accounting for %.1f\\%% of the design's MSE variation across scenarios. ",
    best_name, top_param, eta_sq[top_param], eta_sq[top_param] * 100
  ))
  if (length(low_params) > 0) {
    cat(sprintf(
      "Parameters with negligible influence (eta-squared $< 0.05$): %s.\n\n",
      paste(low_params, collapse = ", ")
    ))
  } else {
    cat("All parameters have non-negligible influence on this design's MSE.\n\n")
  }

  cat(sprintf(
    "**Finding 6 -- Summary (descriptive):** Under %s incidence, %s has the lowest average MSE, %.1fx lower than the highest-MSE design, with near-nominal coverage (%.3f).\n\n",
    cfg_nm, best_name, mse_ratio_cfg, best_row$Avg_Coverage[1]
  ))
}
```

# Scenario-Specific Design Lookup

For practitioners who can specify all four scenario parameters (Rho, Gamma,
Spillover\_Type, Neighbor\_Type), the following tables provide exact design
rankings for a selection of illustrative scenarios. Each table fixes a single
neighbor type. The queen scenario is the primary case; the rook scenario is a
sensitivity case, and under rook Checkerboard's $\tau$ is not identified
($WZ = 1 - Z$), so its row is shown but flagged.

```{r scenario-lookups}
#| eval: !expr mle_avail
#| results: asis
# Define representative scenarios using actual data values (not hardcoded)
if (mle_avail) {
  rho_mid  <- sort(rho_levels)[ceiling(length(rho_levels) / 2)]    # e.g. 0.20
  rho_high <- max(rho_levels)                                        # e.g. 0.50
  gamma_mid  <- sort(gamma_levels)[ceiling(length(gamma_levels) / 2)]  # e.g. 0.7
  gamma_high <- max(gamma_levels)                                        # e.g. 0.8
  spill_both    <- spill_levels[spill_levels != "control_only"][1]
  spill_control <- "control_only"
  nb_all   <- sort(unique(mle_results_all_nb$Neighbor_Type))  # nb_levels is queen-only
  nb_queen <- nb_all[grep("queen", nb_all)][1]
  nb_rook  <- nb_all[grep("rook",  nb_all)][1]
}

scenario_specs <- list(
  list(rho = rho_mid,  gamma = gamma_mid,  spill = spill_both,    nb = nb_queen,
       label = sprintf("Rho = %.2f, Both Spillover, Queen", rho_mid)),
  list(rho = rho_high, gamma = gamma_high, spill = spill_control, nb = nb_rook,
       label = sprintf("High Rho (%.2f), Control-Only Spillover, Rook (sensitivity; Checkerboard not identified)", rho_high))
)

for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs_all_nb[[cfg_nm]]  # both nb types; each lookup fixes one
  cap_safe_nm <- gsub("_", " ", cfg_nm)
  cat(sprintf("\n## %s\n\n", cfg_nm))

  for (spec in scenario_specs) {
    filtered <- cfg %>%
      filter(Rho == spec$rho, Gamma == spec$gamma,
             Spillover_Type == spec$spill, Neighbor_Type == spec$nb)

    if (nrow(filtered) == 0) stop("Scenario lookup matched no rows: ", spec$label, " / ", cfg_nm)

    ranked <- rank_designs_by_group(filtered, character(0)) %>%
      mutate(
        Design       = short_design_name(Design),
        Avg_MSE      = round(Avg_MSE, 4),
        Avg_Coverage = round(Avg_Coverage, 3),
        Avg_Bias     = sprintf("%+.4f", Avg_Bias),
        Avg_SD       = round(Avg_SD, 4)
      ) %>%
      select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias, Avg_SD)

    best_r   <- ranked %>% filter(Rank == 1)
    second_r <- ranked %>% filter(Rank == 2)
    pct_gap  <- round((as.numeric(second_r$Avg_MSE[1]) - as.numeric(best_r$Avg_MSE[1])) /
                        as.numeric(best_r$Avg_MSE[1]) * 100, 1)

    spill_display <- gsub("_", "-", spec$spill)   # "control-only" avoids LaTeX _ issue
    tbl_out <- kable(ranked, booktabs = TRUE, linesep = "", align = "rlrrrr",
          col.names = c("Rank", "Design", "MSE", "Coverage", "Bias", "SD"),
          caption = sprintf(
            "%s | Scenario: %s. Winner MSE %.1f\\%% lower than runner-up.",
            cap_safe_nm, spec$label, pct_gap)) %>%
      kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
      row_spec(1, bold = TRUE)
    print(tbl_out)
    cat("\n")
  }
}
```

**How to use the lookup tables:** Identify the row that matches your anticipated
trial parameters. The design at Rank 1 has the lowest MSE in that scenario. The ``Bias'' column
shows whether estimates are systematically above or below $\tau = 1.0$; a Bias
close to 0 with high Coverage indicates that both point estimates and confidence
intervals are reliable.

# Practical Design Selection Guide

## Decision Framework

The table below summarizes, for several situations, which design has the lowest
average MSE in the queen-contiguity results. It is descriptive: it reports where
each design does best and where that does not hold, and it is not the study's final
design recommendation (that choice has not yet been made). Rows other than the
per-config default average over the incidence configurations named in the row.

```{r decision-table}
#| results: asis
#| eval: !expr mle_avail
# Build decision_df programmatically from results (queen, tau = 1.0)

# Winner and its MSE within a filtered slice
slice_winner <- function(df) {
  rank_designs_by_group(df, character(0)) %>% filter(Rank == 1) %>% slice(1)
}

# Default (overall best)
default_best       <- modal_best
default_best_short <- short_design_name(modal_best)

# Best under both-spillover at low Rho (first two Rho levels), averaged over configs
low_rho_thresh <- sort(rho_levels)[2]  # second-lowest rho
w_both_low <- slice_winner(mle_results %>% filter(Spillover_Type == "both", Rho <= low_rho_thresh))

# Best under iid + lowest Rho
w_iid_low <- slice_winner(mle_results %>% filter(grepl("iid", Incidence_Mode), Rho == min(rho_levels)))

# Best under spatial incidence (rho_X = 0.20 and 0.50) + highest Rho
w_sp_high <- slice_winner(mle_results %>% filter(grepl("spatial", Incidence_Mode, ignore.case = TRUE),
                                                 Rho == max(rho_levels)))

# 2x2 Blocking queen vs rook (single-nb averages, reported side by side, not pooled)
d5_queen <- mean(mle_results_all_nb$MSE[mle_results_all_nb$Design == "Design 5" &
                                        mle_results_all_nb$Neighbor_Type == "queen"])
d5_rook  <- mean(mle_results_all_nb$MSE[mle_results_all_nb$Design == "Design 5" &
                                        mle_results_all_nb$Neighbor_Type == "rook"])

decision_df <- data.frame(
  Situation = c(
    "Averaged over all parameters (per config)",
    sprintf("Spillover is 'both' AND Rho <= %.2f (all configs)", low_rho_thresh),
    sprintf("Incidence is iid AND Rho = %.2f", min(rho_levels)),
    sprintf("Spatial incidence (rho_X = 0.20, 0.50) AND Rho = %.2f", max(rho_levels)),
    "Highest average MSE",
    "2x2 Blocking, queen vs. rook"
  ),
  Design = c(
    default_best_short,
    short_design_name(w_both_low$Design),
    short_design_name(w_iid_low$Design),
    short_design_name(w_sp_high$Design),
    short_design_name(worst_design),
    short_design_name("Design 5")
  ),
  Basis = c(
    sprintf("Lowest MSE in %d of %d configs; D8: Inc.-Guided Sat. Q. in the others (statistically indistinguishable)",
            n_configs_modal_best_wins, length(cfg_names)),
    sprintf("Avg MSE %.4f%s", w_both_low$Avg_MSE,
            if (w_both_low$Design != default_best) "; differs from the overall lowest-MSE design" else ""),
    sprintf("Avg MSE %.4f", w_iid_low$Avg_MSE),
    sprintf("Avg MSE %.4f", w_sp_high$Avg_MSE),
    sprintf("MSE %sx the winner's in every config; coverage near nominal under queen (%s); tau not identified under rook (coverage %.2f)",
            mse_ratio_range, worst_cov_range, rook_cb_cov),
    sprintf("Queen MSE %.4f is %.1fx its rook MSE %.4f", d5_queen, d5_queen / d5_rook, d5_rook)
  ),
  stringsAsFactors = FALSE
)

kable(decision_df, booktabs = TRUE, linesep = "",
      col.names = c("Situation", "Lowest-MSE design (or design described)", "Basis"),
      caption = "Descriptive summary of design performance by situation (queen contiguity, tau = 1.0 unless stated). Not a final design recommendation.") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "6cm") %>%
  row_spec(1, bold = TRUE)
```

## Why `r if(mle_avail) modal_best_short` Wins: Mechanistic Explanation {#sec-mechanism}

`r if(mle_avail) modal_best_short` works by dividing the $10 \times 10$ grid into
four $5 \times 5$ quadrants, where each quadrant receives a different treatment
saturation level: the four levels (0.20, 0.40, 0.60, 0.80) are randomly permuted over
the quadrants. Within each quadrant, clusters are randomly selected for treatment at
the assigned saturation rate. Incidence-Guided Saturation Quadrants uses the same
quadrant structure but assigns the saturations by the rank of each quadrant's mean
incidence (highest mean $\to$ 0.80). Under queen at $\tau = 1.0$ the two designs are
statistically indistinguishable (average MSE 0.0900 vs. 0.0907; Nemenyi $p = 0.985$,
Holm-adjusted Wilcoxon $p = 0.413$; `results/eight_design_supplementary/eight_design_summary.txt`),
so the explanation below concerns the shared quadrant-saturation structure, not the
use of incidence.

Plausible reasons this structure does well (interpretation, not tested directly):

1. **Quadrant-level saturation variation creates spatial contrast.** The ML
   estimator must disentangle the direct treatment effect $\tau$ from the spillover
   term and the spatial lag parameter $\rho$. Variable saturation makes a cluster's
   own treatment $Z$ and its neighbors' treatment $WZ$ vary more independently,
   which provides information about how outcomes change as treatment density
   changes spatially.

2. **Randomness within quadrants prevents systematic confounding.** Random
   selection within quadrants introduces variation uncorrelated with spatially
   structured incidence or outcome patterns.

3. **Quadrant-level structure respects spatial scale.** The $5 \times 5$ quadrant
   blocks are coarser than the neighborhoods (rook/queen) through which spillover
   operates, providing more contrast in $WZ$ than finer (2x2) structures.

## Why `r if(mle_avail) worst_design_short` Fails: Mechanistic Explanation

`r if(mle_avail) worst_design_short` assigns treatment in a perfectly alternating,
deterministic pattern, which leaves almost no independent variation in the
neighbors' treatment $WZ$ (computed from the row-standardized weight matrices in
`01_spatial_setup.R`):

- **Queen (primary):** every interior cluster has four opposite-arm edge neighbors
  and four same-arm diagonal neighbors, so $WZ = 0.5$ for 64 of the 100 clusters and
  varies only on the boundary (SD of $WZ$ = 0.066). The spillover covariate is
  therefore nearly constant, and $\hat{\tau}$ is very imprecise: the average MSE of
  `r if(mle_avail) sprintf("%.2f", worst_overall$Avg_MSE[1])` is essentially all
  variance, bias is near zero, and coverage stays near-nominal
  (`r if(mle_avail) worst_cov_range`). The problem is worst under control-only
  spillover.
- **Rook (sensitivity):** every neighbor is in the opposite arm, so $WZ = 1 - Z$
  exactly. $Z$ and the spillover term are aliased, $\tau$ is not identified, and the
  oracle fit drops the Spill column (all such fits are flagged, `Z_WZ_rank_deficient`).
  The estimate absorbs the spillover (average bias `r if(mle_avail) rook_cb_bias`,
  approximately $-\gamma$) and coverage falls to `r if(mle_avail) rook_cb_cov`. These
  estimates are kept in the results but flagged.

# Summary of Key Results {#sec-summary}

```{r summary-table}
#| eval: !expr mle_avail
#| results: asis
overall_summary <- rank_designs_by_group(mle_results, character(0)) %>%
  mutate(
    Design       = short_design_name(Design),
    Avg_MSE      = round(Avg_MSE, 4),
    Avg_Coverage = round(Avg_Coverage, 3),
    Avg_Bias     = round(Avg_Bias, 4)
  ) %>%
  select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias, N_Scenarios)

kable(overall_summary, booktabs = TRUE, linesep = "", align = "rlrrrr",
      col.names = c("Rank", "Design", "Avg MSE", "Avg Coverage",
                    "Avg Bias", "N Scenarios"),
      caption = paste0(
        "Overall MLE design rankings under queen contiguity (primary), averaged across all ",
        n_scenarios_total,
        " queen scenarios at tau = 1.0 (all incidence configs combined). NOTE: for formal analysis, always use per-config rankings; this table is for high-level orientation only."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(1, bold = TRUE) %>%
  row_spec(nrow(overall_summary), color = "gray")
```

**Rook contiguity (sensitivity analysis).** The same ranking under rook contiguity is
shown separately below; it is never pooled with queen. Under rook, Checkerboard's
$\tau$ is not identified ($WZ = 1 - Z$), so its row is kept but flagged.

```{r summary-table-rook}
#| eval: !expr mle_avail
#| results: asis
rook_summary <- rank_designs_by_group(mle_results_rook, character(0)) %>%
  mutate(
    Design       = ifelse(Design == "Design 1",
                          paste0(short_design_name(Design), " (not identified; flagged)"),
                          short_design_name(Design)),
    Avg_MSE      = round(Avg_MSE, 4),
    Avg_Coverage = round(Avg_Coverage, 3),
    Avg_Bias     = round(Avg_Bias, 4)
  ) %>%
  select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias, N_Scenarios)

kable(rook_summary, booktabs = TRUE, linesep = "", align = "rlrrrr",
      col.names = c("Rank", "Design", "Avg MSE", "Avg Coverage",
                    "Avg Bias", "N Scenarios"),
      caption = paste0(
        "Rook contiguity (sensitivity analysis): MLE design rankings averaged across all ",
        nrow(mle_results_rook),
        " rook scenarios at tau = 1.0 (all incidence configs combined). Not pooled with queen."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

```{r leading-coverage-setup}
#| include: false
#| eval: !expr mle_avail
# Coverage range over all designs overall (queen)
overall_cov_lo <- round(min(overall_all$Avg_Coverage), 3)
overall_cov_hi <- round(max(overall_all$Avg_Coverage), 3)
# Rook: does the queen ordering of the two saturation-quadrant designs at the top hold?
rook_overall   <- rank_designs_by_group(mle_results_rook, character(0))
rook_top2      <- rook_overall %>% filter(Rank <= 2) %>% pull(Design)
rook_top2_sat  <- setequal(rook_top2, c("Design 3", "Design 8"))

# Determine whether Gamma effect on rankings is nil across all configs
gamma_stable_all <- all(sapply(cfg_names, function(cn) {
  gamma_r <- rank_designs_by_group(mle_cfgs[[cn]], "Gamma")
  # Check if best design keeps rank 1 at all Gamma
  best_d <- rank_designs_by_group(mle_cfgs[[cn]], character(0)) %>%
    filter(Rank == 1) %>% pull(Design) %>% first()
  all(gamma_r$Rank[gamma_r$Design == best_d] == 1)
}))
gamma_stability_str <- ifelse(gamma_stable_all,
  "The lowest-MSE design in each config holds rank 1 at every Gamma level.",
  paste0("Design rankings are largely stable across Gamma = ",
         min(gamma_levels), " to ", max(gamma_levels),
         "; the shifts that occur are swaps between designs with near-identical MSE (see Q2).")
)
```

**Conclusions (descriptive; queen contiguity unless stated):**

1. **Lowest average MSE:** Under queen, **`r if(mle_avail) best_overall_short`** has the
   lowest MSE averaged over all queen scenarios, `r if(mle_avail) overall_mse_ratio`x
   lower than the highest-MSE design. It is rank 1 in `r if(mle_avail) n_configs_modal_best_wins`
   of `r if(mle_avail) length(cfg_names)` incidence configs; Incidence-Guided
   Saturation Quadrants is rank 1 in the others, and the two are statistically
   indistinguishable (@sec-mechanism). Under rook (sensitivity), the two
   saturation-quadrant designs
   `r if(mle_avail) ifelse(rook_top2_sat, "again hold ranks 1 and 2", "do not both hold ranks 1 and 2")`.
   This is a description of the results, not the study's final design recommendation.

2. **Spillover type is the key moderator.** When spillover direction is "both",
   **`r if(mle_avail) best_under_both_short`** (and Balanced Halves) have the lowest MSE,
   but the leading designs differ little. When spillover is "control\_only", the two
   saturation-quadrant designs have clearly lower MSE than all others, splitting the
   Rho x Spillover\_Type tiles between them (`r if(mle_avail) control_best_short`
   `r if(mle_avail) control_best_tiles` of `r if(mle_avail) total_control_tiles`).

3. **`r if(mle_avail) worst_design_short` has the highest MSE.** Under queen its
   near-constant $WZ$ makes $\hat{\tau}$ very imprecise (coverage stays near-nominal);
   under rook $WZ = 1 - Z$, $\tau$ is not identified, and coverage falls to
   `r if(mle_avail) rook_cb_cov`.

4. **Gamma has little effect on the ranking.** `r if(mle_avail) gamma_stability_str`

5. **Coverage is near-nominal for every design under queen**
   (`r if(mle_avail) overall_cov_lo`--`r if(mle_avail) overall_cov_hi` averaged over
   scenarios), about one point below 0.95 because of the finite-sample Wald interval.
   Coverage therefore does not separate the designs; MSE does. The only coverage
   failure is Checkerboard under rook.

# Sensitivity of Design Rankings to $\tau$ {#sec-tau-sensitivity}

```{r tau-sensitivity-available}
#| results: asis
#| echo: false
if (!tau_sweep_available) {
  stop("Tau-sweep data not loaded: this section requires the MLE_tau_sweep results.")
}
```

The tau-sweep simulation swept $\tau \in \{0.8, 1.0, 1.5, 2.0, 3.0\}$.
The question here is whether the design rankings found at $\tau = 1.0$ hold
across other plausible effect sizes. The figures below show the iid Uniform
incidence config under queen contiguity. The $\tau$ levels share the same design
draws and noise (common random numbers), so they are not independent replications.

```{r tau-best-design-heatmap, eval=tau_sweep_available, fig.cap="Winning design per tau level (iid Uniform, queen contiguity). A stable winner across tau means the ranking does not depend on the effect size."}
if (tau_sweep_available) {
  tau_cfgs_full <- split_by_incidence_config(mle_results_full)
  if ("iid Uniform" %in% names(tau_cfgs_full)) {
    p <- plot_best_design_per_tau(tau_cfgs_full[["iid Uniform"]], "iid Uniform")
    if (!is.null(p)) print(p)
  }
}
```

```{r tau-rank-trajectories, eval=tau_sweep_available, fig.cap="Design rank trajectories across tau values (iid Uniform, queen contiguity; rank 1 = best MSE). Flat lines mean the tau = 1.0 ranking holds at other effect sizes."}
if (tau_sweep_available) {
  tau_cfgs_full <- split_by_incidence_config(mle_results_full)
  if ("iid Uniform" %in% names(tau_cfgs_full)) {
    p <- plot_rank_trajectories_by_tau(tau_cfgs_full[["iid Uniform"]], "iid Uniform")
    if (!is.null(p)) print(p)
  }
}
```

---

# References

- Mirzaei, A. et al. (2019). Sudden unexpected death rates.
  *(SUD base rate 35/100,000)*
- LeSage, J. \& Pace, R.K. (2009). *Introduction to Spatial Econometrics*. CRC Press.
- Bivand, R., et al. `spdep` R package.
- Bivand, R. \& Piras, G. `spatialreg` R package.
- R packages used: `dplyr`, `tidyr`, `ggplot2`, `viridis`, `knitr`,
  `kableExtra`, `gridExtra`, `digest`

---

# Appendix: Output Files

```{r appendix-files}
#| results: asis
if (mle_avail) {
  # Find actual result file names from results_dir
  rds_files <- list.files(file.path(results_dir, "sim_data"),
                          pattern = "^sim_results_MLE_tau_sweep_combined_.*\\.rds$",
                          full.names = FALSE)
  latest_rds <- if (length(rds_files) > 0) {
    rds_files[which.max(file.mtime(file.path(results_dir, "sim_data", rds_files)))]
  } else {
    stop("No sim_results_MLE_tau_sweep_combined_*.rds found")
  }

  files_df <- data.frame(
    File = c(
      "MLE_tau_sweep_design_recommendations_{queen,rook}.pdf",
      latest_rds,
      "09_MLE_design_recommendation_report.{html,pdf}"
    ),
    Contents = c(
      "Figures from 08 (pools rook and queen)",
      paste0("Oracle results: ", nrow(mle_results_all_nb_full), " scenarios x ",
             ncol(mle_results_all_nb_full), " columns"),
      "This narrative companion report"
    ),
    Location = c("results/", "results/sim_data/", "results/"),
    stringsAsFactors = FALSE
  )
} else {
  files_df <- data.frame(
    File = character(0), Contents = character(0), Location = character(0)
  )
}

kable(files_df, booktabs = TRUE, linesep = "",
      caption = "Output files for the design recommendation analysis.") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"), font_size = 9)
```
