---
title: "Personalized Design Recommendation Report"
subtitle: "MLE-Based Analysis for Spatial CRT Treatment Assignment"
author: "Andrew Walther"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    theme: cosmo
    smooth-scroll: true
    self-contained: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    latex-engine: xelatex
    keep-tex: false
    fig-pos: "htbp"
    fig-height: 4
    fig-width: 6.5
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{float}
        \usepackage{amsmath}
        \usepackage{amssymb}
        \usepackage{geometry}
        \usepackage{xcolor}
        \usepackage{mdframed}
        \geometry{margin=1in}
        \floatplacement{figure}{htbp}
        \floatplacement{table}{H}
        \definecolor{boxbg}{RGB}{240,248,255}
        \definecolor{boxframe}{RGB}{70,130,180}
---

```{r setup}
#| include: false
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.pos = "htbp"
)
```

```{r load-packages}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)
```

```{r resolve-paths}
#| include: false
script_dir <- tryCatch(
  normalizePath(dirname(knitr::current_input(dir = TRUE))),
  error = function(e) {
    tryCatch(
      normalizePath(dirname(sys.frame(1)$ofile)),
      error = function(e2) normalizePath(getwd())
    )
  }
)
results_dir <- file.path(dirname(script_dir), "results")
```

```{r source-modules}
#| include: false
# Source recommendation module (which sources 06 -> 01-03)
source(file.path(script_dir, "08_design_recommendations.R"))
```

```{r load-results}
#| include: false
mle_results <- tryCatch(
  load_latest_results(results_dir, estimation_mode = "MLE_combined"),
  error = function(e) {
    message("MLE combined results not found: ", e$message)
    NULL
  }
)
mle_avail <- !is.null(mle_results) && nrow(mle_results) > 0
mle_cfgs  <- if (mle_avail) split_by_incidence_config(mle_results) else list()
cfg_names <- names(mle_cfgs)
```

```{r global-summaries}
#| include: false
# Pre-compute cross-config summary and scenario counts used throughout
if (mle_avail) {
  # Design IDs and names from data (not hardcoded)
  active_design_ids <- sort(unique(as.integer(
    gsub("Design ", "", mle_results$Design)
  )))
  n_designs <- length(active_design_ids)

  # Total scenarios and per-config counts
  n_scenarios_total <- nrow(mle_results)
  n_scenarios_per_config <- n_scenarios_total / length(mle_cfgs)

  # Parameter levels from data
  rho_levels   <- sort(unique(mle_results$Rho))
  gamma_levels <- sort(unique(mle_results$Gamma))
  spill_levels <- sort(unique(mle_results$Spillover_Type))
  nb_levels    <- sort(unique(mle_results$Neighbor_Type))
  n_params_per_design <- n_scenarios_per_config / n_designs  # combos per design per config

  # Ranked summary per config
  all_ranked_list <- lapply(seq_along(mle_cfgs), function(i) {
    r <- rank_designs_by_group(mle_cfgs[[i]], character(0))
    r$Inc_Config <- cfg_names[i]
    r
  })
  all_ranked <- bind_rows(all_ranked_list)

  # Best and worst per config
  best_per_config <- all_ranked %>%
    filter(Rank == 1) %>%
    select(Inc_Config, Design, Avg_MSE, Avg_Coverage)

  worst_per_config <- all_ranked %>%
    filter(Rank == n_designs) %>%
    select(Inc_Config, Design, Avg_MSE, Avg_Coverage)

  # Modal best design (wins most configs)
  modal_best       <- names(sort(table(best_per_config$Design), decreasing = TRUE))[1]
  modal_best_short <- short_design_name(modal_best)
  n_configs_modal_best_wins <- sum(best_per_config$Design == modal_best)

  # Modal worst design
  worst_design       <- names(sort(table(worst_per_config$Design), decreasing = TRUE))[1]
  worst_design_short <- short_design_name(worst_design)

  # Overall rankings across all scenarios (for summary section)
  overall_all <- rank_designs_by_group(mle_results, character(0))
  best_overall       <- overall_all %>% filter(Rank == 1)
  worst_overall      <- overall_all %>% filter(Rank == max(Rank))
  overall_mse_ratio  <- round(worst_overall$Avg_MSE[1] / best_overall$Avg_MSE[1], 1)
  best_overall_short  <- short_design_name(best_overall$Design[1])
  worst_overall_short <- short_design_name(worst_overall$Design[1])

  # MSE ratio for checkerboard vs best (per config)
  mse_ratio_per_config <- all_ranked %>%
    group_by(Inc_Config) %>%
    summarise(
      best_mse  = Avg_MSE[Rank == 1],
      worst_mse = Avg_MSE[Rank == max(Rank)],
      ratio     = round(worst_mse / best_mse, 1),
      .groups   = "drop"
    )
  mse_ratio_range <- paste0(
    min(mse_ratio_per_config$ratio), "--", max(mse_ratio_per_config$ratio)
  )

  # Worst design coverage range
  worst_cov_vals <- worst_per_config$Avg_Coverage
  worst_cov_range <- paste0(
    round(min(worst_cov_vals), 2), "--", round(max(worst_cov_vals), 2)
  )

  # Spillover rank reversal: best design under control_only vs both
  spill_rankings <- lapply(cfg_names, function(cn) {
    cfg <- mle_cfgs[[cn]]
    r <- rank_designs_by_group(cfg, "Spillover_Type")
    r$Inc_Config <- cn
    r
  })
  spill_all <- bind_rows(spill_rankings)

  best_under_control_only <- spill_all %>%
    filter(Spillover_Type == "control_only", Rank == 1) %>%
    count(Design) %>% arrange(desc(n)) %>% slice(1) %>% pull(Design)
  best_under_control_only_short <- short_design_name(best_under_control_only)

  best_under_both <- spill_all %>%
    filter(Spillover_Type == "both", Rank == 1) %>%
    count(Design) %>% arrange(desc(n)) %>% slice(1) %>% pull(Design)
  best_under_both_short <- short_design_name(best_under_both)

  # Runner-up margin range across configs
  runner_up_margins <- all_ranked %>%
    group_by(Inc_Config) %>%
    summarise(
      best_mse   = Avg_MSE[Rank == 1],
      second_mse = Avg_MSE[Rank == 2],
      pct_margin = round((second_mse - best_mse) / best_mse * 100, 1),
      .groups    = "drop"
    )
  margin_range <- paste0(
    min(runner_up_margins$pct_margin), "\\% -- ",
    max(runner_up_margins$pct_margin), "\\%"
  )

  # Second-best design frequency
  second_best_freq <- all_ranked %>%
    filter(Rank == 2) %>%
    count(Design, sort = TRUE)

  # Gamma sensitivity: eta-squared for best design across configs
  gamma_eta_vals <- sapply(cfg_names, function(cn) {
    d_data <- mle_cfgs[[cn]] %>% filter(Design == modal_best)
    gm    <- mean(d_data$MSE, na.rm = TRUE)
    ss_tot <- sum((d_data$MSE - gm)^2, na.rm = TRUE)
    if (ss_tot == 0) return(0)
    gs <- d_data %>%
      group_by(Gamma) %>%
      summarise(gm2 = mean(MSE, na.rm = TRUE), gn = n(), .groups = "drop")
    ss_b <- sum(gs$gn * (gs$gm2 - gm)^2)
    ss_b / ss_tot
  })
  max_gamma_eta <- round(max(gamma_eta_vals), 3)

  # Leading design coverage range (designs other than the worst)
  other_designs_cov <- all_ranked %>%
    filter(Design != worst_design) %>%
    pull(Avg_Coverage)
  leading_cov_lo <- round(min(other_designs_cov), 2)
  leading_cov_hi <- round(max(other_designs_cov), 2)
}
```

# Executive Summary

This report is a companion to the `MLE_combined_design_recommendations.pdf` figure
file. It provides narrative explanations of **how each analysis was computed**,
**what each figure and table shows**, and **what the results mean in practice** for
researchers designing spatial cluster randomized trials (CRTs).

The simulation evaluates **`r if(mle_avail) n_designs` treatment assignment designs**
across **`r if(mle_avail) n_scenarios_total` parameter scenarios** using Maximum
Likelihood Estimation (MLE) via a spatial autoregressive model (`lagsarlm`). The
estimand is the direct treatment effect $\tau = 1.0$.

Three analytical questions are addressed:

\begin{mdframed}[backgroundcolor=boxbg, linecolor=boxframe, linewidth=1pt]
\textbf{Q1 -- Per incidence mode:} Which design is best given how historical
incidence was generated (iid, Spatial, Poisson)?

\textbf{Q2 -- Per parameter level:} Which design is best when a specific simulation
parameter takes a particular value (e.g., high spatial autocorrelation $\rho = 0.50$),
marginalizing over all other parameters?

\textbf{Q3 -- Per scenario:} Which design is best for a fully-specified combination
of parameter values?
\end{mdframed}

```{r exec-table}
#| eval: !expr mle_avail
#| results: asis
exec_df <- best_per_config %>%
  mutate(
    Design     = short_design_name(Design),
    Avg_MSE    = round(Avg_MSE, 4),
    Avg_Coverage = round(Avg_Coverage, 3)
  ) %>%
  rename(`Incidence Config` = Inc_Config,
         `Best Design`      = Design,
         `Avg MSE`          = Avg_MSE,
         `Avg Coverage`     = Avg_Coverage)

kable(exec_df, booktabs = TRUE, linesep = "", align = "llrr",
      caption = paste0(
        "Best MLE design (lowest avg MSE) for each of the ",
        length(cfg_names), " incidence configurations."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(seq_len(nrow(exec_df)), bold = FALSE)
```

**Key finding:** `r if(mle_avail) modal_best_short` achieves the lowest average MSE
in `r if(mle_avail) n_configs_modal_best_wins` of `r if(mle_avail) length(cfg_names)`
incidence configurations, with `r if(mle_avail) worst_design_short` consistently
worst. Spillover type (control-only vs. both) is by far the most influential parameter
for all leading designs, while spatial autocorrelation $\rho$ and spillover magnitude
$\gamma$ have secondary effects.

# Study Background

## Designs Evaluated

`r if(mle_avail) n_designs` treatment assignment strategies are compared. Each
allocates approximately 50\% of the 100 clusters ($10 \times 10$ grid) to treatment:

```{r design-table}
#| results: asis
# Build design_df from 03_designs.R helpers + a description lookup
# Descriptions are structural (not result claims) so remain as prose constants.
design_descriptions <- c(
  "1" = "Alternating grid pattern; maximizes spatial separation of treated and control units",
  "2" = "Treats the top-50\\% incidence clusters deterministically",
  "3" = "Assigns random saturation levels (0.2--0.8) within each of four spatial quadrants",
  "4" = "Greedy assignment ensuring no two adjacent clusters are both treated",
  "5" = "1:1 randomization within non-overlapping 2x2 spatial blocks",
  "6" = "Stratified randomization balanced within incidence quartiles",
  "7" = "Stratified randomization balanced within incidence halves (above/below median)"
)

if (mle_avail) {
  all_design_names <- get_design_names()
  # Restrict to IDs that actually appear in the results
  run_ids <- active_design_ids
  design_df <- data.frame(
    ID          = run_ids,
    Name        = sub("Design [0-9]+: ", "", unname(all_design_names[as.character(run_ids)])),
    Det         = ifelse(sapply(run_ids, is_design_deterministic), "Yes", "No"),
    Description = unname(design_descriptions[as.character(run_ids)]),
    stringsAsFactors = FALSE
  )
  n_det <- sum(design_df$Det == "Yes")
  n_sto <- sum(design_df$Det == "No")
} else {
  design_df <- data.frame(ID=integer(0), Name=character(0), Det=character(0), Description=character(0))
  n_det <- 0L; n_sto <- 0L
}

kable(design_df, booktabs = TRUE, linesep = "",
      col.names = c("ID", "Name", "Deterministic?", "Description"),
      caption = paste0(
        nrow(design_df),
        " treatment assignment designs evaluated. Deterministic designs (",
        paste(design_df$ID[design_df$Det == "Yes"], collapse = ", "),
        ") produce one assignment and replicate it; stochastic designs resample across 25 replications."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 9) %>%
  column_spec(4, width = "7cm")
```

## Performance Metrics

For each of the `r if(mle_avail) n_scenarios_total` scenarios, **250 simulation
iterations** (25 design resamples $\times$ 10 outcome resamples) produce the
following metrics:

- **Bias** $= \bar{\hat{\tau}} - \tau$: average departure from true effect $\tau = 1.0$
- **SD**: standard deviation of estimates across iterations
- **MSE** $= \text{Bias}^2 + \text{SD}^2$: total estimation error; the **primary
  ranking criterion** throughout this report
- **Coverage**: fraction of 95\% confidence intervals containing $\tau = 1.0$

Lower MSE is better. Coverage near 0.95 (the nominal level) indicates valid inference.

## Simulation Parameter Space

```{r param-table}
#| results: asis
if (mle_avail) {
  param_df <- data.frame(
    Parameter = c(
      "Incidence mode",
      "rho\\_X (incidence spatial autocorr.)",
      "nb\\_type (contiguity)",
      "Rho (outcome spatial autocorr.)",
      "Gamma (spillover magnitude)",
      "Spillover type",
      "Design",
      "TOTAL"
    ),
    Values = c(
      paste(unique(mle_results$Incidence_Mode), collapse = ", "),
      paste0("N/A (iid); ", paste(sort(unique(mle_results$Rho_Incidence[mle_results$Rho_Incidence > 0])), collapse = ", "), " (Spatial, Poisson)"),
      paste(nb_levels, collapse = ", "),
      paste(rho_levels, collapse = ", "),
      paste(gamma_levels, collapse = ", "),
      paste(spill_levels, collapse = ", "),
      paste(active_design_ids, collapse = ", "),
      ""
    ),
    Levels = c(
      paste0(length(cfg_names), " configs"),
      "---",
      as.character(length(nb_levels)),
      as.character(length(rho_levels)),
      as.character(length(gamma_levels)),
      as.character(length(spill_levels)),
      as.character(n_designs),
      paste0(n_scenarios_total, " scenarios")
    ),
    stringsAsFactors = FALSE
  )
} else {
  param_df <- data.frame(Parameter=character(0), Values=character(0), Levels=character(0))
}

kable(param_df, booktabs = TRUE, linesep = "",
      caption = paste0(
        "Simulation parameter grid. Each of the ",
        if (mle_avail) n_scenarios_total else "?",
        " scenarios is a unique combination of (incidence config, nb\\_type, Rho, Gamma, Spillover type, Design). Results are always reported separately by incidence config."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(nrow(param_df), bold = TRUE)
```

# Analytical Methods

This section explains exactly how each analysis in the recommendation report
is computed.

## Core Ranking Method: `rank_designs_by_group()`

All conditional rankings in this report share the same logic, implemented in
`rank_designs_by_group()`:

1. **Group** the `r if(mle_avail) n_scenarios_per_config` scenarios within an
   incidence config by the requested conditioning variables plus Design (e.g.,
   group by `{Rho, Design}`)
2. **Aggregate**: compute average MSE, Coverage, Bias, and SD within each group
3. **Rank**: within each unique combination of the conditioning variables,
   assign integer ranks to designs based on ascending average MSE
   (rank 1 = best; ties broken using minimum rank)
4. **Return** a tidy data frame with one row per `{group, Design}` combination

This is the same ranking logic used in `table_design_ranks()` in
`06_visualizations.R`, extended to support arbitrary conditioning sets.

**Critical invariant:** Rankings are **always computed within a single incidence
configuration**. Results are never aggregated across the `r if(mle_avail) length(cfg_names)` incidence configs
because each represents a fundamentally different assumption about how prior
incidence data arises.

## Q1 — Per-Config Rankings: `table_incidence_rankings()` and `plot_incidence_rankings()`

**What is computed:** For each of the `r if(mle_avail) length(cfg_names)` incidence
configs, all `r if(mle_avail) n_scenarios_per_config` scenarios
(`r if(mle_avail) n_designs` designs $\times$ `r if(mle_avail) n_params_per_design`
parameter combinations) are summarized by computing the average MSE per design.
Designs are then ranked 1--`r if(mle_avail) n_designs` (lowest = best) within
each config.

**What the figure shows** (Page 1 of PDF): A faceted bar chart with one panel
per incidence config. Bars represent average MSE per design, sorted from lowest
to highest within each panel. Rank labels (1--`r if(mle_avail) n_designs`) appear
above each bar.

**How to read it:** Lower bars are better. Rank labels allow quick comparison
across panels. A design ranked consistently high across all panels is a robust
global recommendation.

## Q2 — Marginal Rankings: `table_marginal_rankings()` and `plot_rank_trajectories()`

**What "marginal" means:** For a parameter like Rho, we want to know: ignoring
all other parameters, how does each design rank when Rho takes a specific value?
This is computed by grouping all scenarios by `{Rho, Design}` and averaging MSE
across the remaining parameters (Gamma, Spillover\_Type, Neighbor\_Type).

**What the rank trajectory plot shows**: A line plot where the x-axis is the
parameter level, the y-axis is design rank (1 at top, `r if(mle_avail) n_designs`
at bottom), and each line traces one design. Crossing lines indicate a **rank
reversal**: a design that is best at one parameter level but not at another.

**What the marginal ranking table shows**: A wide table with parameter levels
as column headers and designs as rows. Each cell reports `Avg_MSE (#Rank)` at
that parameter level, averaged over all other parameters. Designs are ordered
by their overall rank (best at top).

**What the conditional MSE boxplot shows**: Rather than averages, this shows the
**full distribution** of raw scenario-level MSE values for each design at each
parameter level. This reveals whether a design's advantage is consistent or
comes from a few favorable extreme scenarios.

## Q3 — Best Design Heatmap: `plot_best_design_heatmap()`

**What is computed:** For every combination of two parameters (e.g., Rho and
Gamma), all scenarios sharing that combination are grouped, average MSE is
computed per design, and the design with the minimum average MSE is identified
as the winner.

**What the heatmap shows**: A grid of colored tiles where each cell corresponds
to one `{Rho, Gamma}` combination. The color and text label identify the winning
design. The MSE value inside each tile is the winning design's average MSE at
that combination.

**Interpretation guidance:** If one design wins all tiles, it dominates
unconditionally. If tiles show different winners, the choice of design should
adapt to the anticipated parameter regime.

## Programmatic Commentary: `generate_commentary()`

For each incidence config, six structured findings are automatically derived
from the results:

| Finding | Computed as |
|---------|-------------|
| Overall winner | Design with Rank 1 from ungrouped `rank_designs_by_group()` |
| Dominance % | From scenario-level pairwise comparison: $\frac{\#\{s : \text{MSE}_{\text{best},s} < \text{MSE}_{\text{2nd},s}\}}{64}$ |
| Rank stability | Whether the best design holds rank 1 at every level of Rho and every level of Gamma |
| Coverage | Average Coverage for the best and worst designs |
| Sensitivity | Eta-squared ($\eta^2 = SS_{\text{between}} / SS_{\text{total}}$) for each parameter |
| Recommendation | Template string synthesizing findings 1--5 |

# Q1: Design Rankings by Incidence Mode

## Cross-Config MSE Rankings

```{r q1-mse-plot-cap, include=FALSE}
q1_mse_cap <- paste0(
  "Average MSE per design for each of the ",
  if (mle_avail) length(cfg_names) else "?",
  " incidence configurations. Bars are sorted left-to-right within each panel",
  " by MSE (lowest = best). Rank labels above bars. Lower bars are better.",
  " Note the shared y-axis: ",
  if (mle_avail) worst_design_short else "the worst design",
  " is clipped in most panels due to its substantially higher MSE."
)
```

```{r q1-mse-plot}
#| eval: !expr mle_avail
#| fig-cap: !expr q1_mse_cap
#| fig-height: 5.0
print(plot_incidence_rankings(mle_results) +
  theme(text        = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        strip.text  = element_text(size = 9, face = "bold"),
        plot.title  = element_text(size = 11),
        plot.subtitle = element_text(size = 9)))
```

**Reading the plot:** The `r if(mle_avail) length(cfg_names)` panels correspond
to the `r if(mle_avail) length(cfg_names)` incidence configurations. Within each
panel, designs are arranged from best (left) to worst (right), with the rank number
printed above each bar. The consistent leftward position of `r if(mle_avail) modal_best_short`
across all panels is the primary finding.

```{r q1-mse-obs-setup}
#| include: false
#| eval: !expr mle_avail
# Compute data-driven observations about MSE spread
best_mse_range <- round(range(best_per_config$Avg_MSE), 3)
worst_mse_range_vals <- worst_per_config$Avg_MSE
```

**Key observation:** `r if(mle_avail) modal_best_short` ranks first in
`r if(mle_avail) n_configs_modal_best_wins` of `r if(mle_avail) length(cfg_names)`
incidence configurations, with average MSE ranging from
`r if(mle_avail) best_mse_range[1]` to `r if(mle_avail) best_mse_range[2]`
depending on the config. This `r if(mle_avail) mse_ratio_range`x MSE advantage
over the worst design (`r if(mle_avail) worst_design_short`) is stable regardless
of how the historical incidence was generated.

## Cross-Config Coverage Rankings

```{r q1-cov-cap, include=FALSE}
q1_cov_cap <- paste0(
  "Average 95% CI coverage probability per design for each incidence configuration.",
  " Red dashed line = nominal 0.95. Coverage near 0.95 indicates valid inference; ",
  if (mle_avail) worst_design_short else "worst design",
  " coverage falls to ",
  if (mle_avail) worst_cov_range else "?",
  " across all configs."
)
```

```{r q1-cov-plot}
#| eval: !expr mle_avail
#| fig-cap: !expr q1_cov_cap
#| fig-height: 5.0
print(plot_incidence_coverage(mle_results) +
  theme(text        = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        strip.text  = element_text(size = 9, face = "bold"),
        plot.title  = element_text(size = 11),
        plot.subtitle = element_text(size = 9)))
```

**Reading the plot:** The red dashed line at 0.95 is the nominal coverage target.
Bars above this line are over-covering (conservative CIs); bars below are under-covering
(anti-conservative). Under MLE, designs other than `r if(mle_avail) worst_design_short`
all achieve reasonable coverage (`r if(mle_avail) leading_cov_lo`--`r if(mle_avail) leading_cov_hi`),
but `r if(mle_avail) worst_design_short` falls dramatically short.

**Key observation:** `r if(mle_avail) worst_design_short`'s poor coverage
(`r if(mle_avail) worst_cov_range`) makes it unsuitable for inference regardless
of MSE. Even in the rare scenario where its MSE is competitive, its confidence
intervals are invalid.

## Detailed Rankings by Incidence Config

```{r q1-detail-table}
#| eval: !expr mle_avail
#| results: asis
for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  r <- rank_designs_by_group(cfg, character(0)) %>%
    mutate(
      Design       = short_design_name(Design),
      Avg_MSE      = round(Avg_MSE, 4),
      Avg_Coverage = round(Avg_Coverage, 3),
      Avg_Bias     = round(Avg_Bias, 4)
    ) %>%
    select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias)

  best_mse   <- r$Avg_MSE[1]
  second_mse <- r$Avg_MSE[2]
  pct_diff   <- round((second_mse - best_mse) / best_mse * 100, 1)
  worst_mse  <- r$Avg_MSE[nrow(r)]
  ratio      <- round(worst_mse / best_mse, 1)

  cap_safe_nm <- gsub("_", " ", cfg_nm)
  tbl_out <- kable(r, booktabs = TRUE, linesep = "", align = "rlrrr",
        col.names = c("Rank", "Design", "Avg MSE", "Avg Coverage", "Avg Bias"),
        caption = sprintf(
          "MLE design rankings for %s. Runner-up MSE is %.1f\\%% higher than the winner; worst design MSE is %.1fx higher.",
          cap_safe_nm, pct_diff, ratio)) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
    row_spec(1, bold = TRUE)
  print(tbl_out)
  cat("\n")
}
```

```{r q1-patterns-setup}
#| include: false
#| eval: !expr mle_avail
# Compute cross-config ranking patterns for narrative
best_n_wins <- n_configs_modal_best_wins

# Runner-up: which design ranks 2nd most often
runner_up_design       <- second_best_freq$Design[1]
runner_up_short        <- short_design_name(runner_up_design)
runner_up_n_times      <- second_best_freq$n[1]

# Margin range (min and max % gap between best and runner-up)
margin_min <- min(runner_up_margins$pct_margin)
margin_max <- max(runner_up_margins$pct_margin)

# Worst coverage
worst_cov_max <- round(max(worst_per_config$Avg_Coverage), 2)

# Second runner-up
runner_up2_design <- if (nrow(second_best_freq) > 1) second_best_freq$Design[2] else NA
runner_up2_short  <- if (!is.na(runner_up2_design)) short_design_name(runner_up2_design) else "N/A"
runner_up2_n      <- if (nrow(second_best_freq) > 1) second_best_freq$n[2] else 0
```

**Notable patterns across configs:**

- **`r if(mle_avail) modal_best_short`** ranks 1st in all `r if(mle_avail) best_n_wins` configs.
  Its runner-up margin ranges from `r if(mle_avail) margin_min`\% to
  `r if(mle_avail) margin_max`\% depending on incidence configuration.
- **`r if(mle_avail) runner_up_short`** is the most consistent runner-up, ranking 2nd
  in `r if(mle_avail) runner_up_n_times` of `r if(mle_avail) length(cfg_names)` configs.
- **`r if(mle_avail) runner_up2_short`** ranks 2nd in the remaining
  `r if(mle_avail) runner_up2_n` config(s).
- **`r if(mle_avail) worst_design_short`** is last in all configs with MSE
  `r if(mle_avail) mse_ratio_range`x higher than the winner and coverage below
  `r if(mle_avail) worst_cov_max`.

# Q2: Marginal Rankings by Parameter Level

This section answers: **holding all other parameters at their average, how does
each design's rank change as one parameter varies?**

## Effect of Outcome Spatial Autocorrelation (Rho)

```{r q2-rho-cap, include=FALSE}
q2_rho_cap <- paste0(
  "Design rank trajectories across Rho for each incidence config (one panel per config).",
  " Rank 1 = best. Lines that stay flat indicate robust designs;",
  " crossing lines reveal parameter-driven rank reversals. ",
  if (mle_avail) modal_best_short else "Best design",
  " stays near rank 1 across all Rho levels in most configs."
)
```

```{r q2-rho-trajectories}
#| eval: !expr mle_avail
#| fig-cap: !expr q2_rho_cap
#| fig-height: 8.0
p_list <- lapply(seq_along(mle_cfgs), function(i) {
  plot_rank_trajectories(mle_cfgs[[i]], "Rho", cfg_names[i],
                         point_size = 2.5, line_size = 0.9, label_size = 2.0) +
    theme(legend.position = if (i == length(mle_cfgs)) "right" else "none",
          plot.title    = element_text(size = 9),
          plot.subtitle = element_text(size = 8),
          axis.text     = element_text(size = 8),
          axis.title    = element_text(size = 9),
          legend.text   = element_text(size = 8),
          legend.title  = element_text(size = 9))
})
gridExtra::grid.arrange(grobs = p_list, ncol = 1)
```

**How to read the trajectory plots:** Rank 1 sits at the top; rank
`r if(mle_avail) n_designs` at the bottom. A flat horizontal line means a
design's rank does not change as Rho increases. A downward slope means the
design falls in rank as Rho increases. Crossing lines between two designs
indicate a rank reversal.

```{r q2-rho-findings-setup}
#| include: false
#| eval: !expr mle_avail
# Determine Rho stability of modal best and worst design across all configs
best_rho_stable_all <- all(sapply(cfg_names, function(cn) {
  rr <- rank_designs_by_group(mle_cfgs[[cn]], "Rho") %>%
    filter(Design == modal_best)
  all(rr$Rank == 1)
}))

worst_rho_stable_all <- all(sapply(cfg_names, function(cn) {
  rr <- rank_designs_by_group(mle_cfgs[[cn]], "Rho") %>%
    filter(Design == worst_design)
  all(rr$Rank == n_designs)
}))

# Where best design cedes rank 1 under Rho (if any)
rho_exceptions <- lapply(cfg_names, function(cn) {
  rr <- rank_designs_by_group(mle_cfgs[[cn]], "Rho") %>%
    filter(Design == modal_best)
  if (any(rr$Rank != 1)) {
    bad_rho <- rr$Rho[rr$Rank != 1]
    sprintf("%s at Rho=%s", cn, paste(bad_rho, collapse=","))
  } else NULL
})
rho_exceptions <- Filter(Negate(is.null), rho_exceptions)
rho_exception_str <- if (length(rho_exceptions) == 0) {
  "no exceptions found"
} else {
  paste(rho_exceptions, collapse = "; ")
}
```

**Findings:**

- **`r if(mle_avail) modal_best_short`**
  `r if(mle_avail) ifelse(best_rho_stable_all, "maintains rank 1 across all Rho levels in every incidence config", paste0("is largely stable across Rho levels, with exceptions: ", rho_exception_str))`.
- **`r if(mle_avail) worst_design_short`**
  `r if(mle_avail) ifelse(worst_rho_stable_all, "consistently occupies last rank across all Rho values, confirming its failure is not a high-Rho artifact", "generally occupies the bottom rank but shows some variation across Rho levels")`.

## Effect of Spillover Magnitude (Gamma)

```{r q2-gamma-cap, include=FALSE}
q2_gamma_cap <- paste0(
  "Design rank trajectories across Gamma. Gamma controls the magnitude of",
  " treatment spillover to neighbors. Unlike Rho, Gamma has minimal effect",
  " on design rankings under MLE (eta-squared < ",
  if (mle_avail) max_gamma_eta else "?",
  " for all designs): all trajectory lines are nearly flat,",
  " confirming Gamma is not a discriminating factor for design selection."
)
```

```{r q2-gamma-trajectories}
#| eval: !expr mle_avail
#| fig-cap: !expr q2_gamma_cap
#| fig-height: 8.0
p_list2 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_rank_trajectories(mle_cfgs[[i]], "Gamma", cfg_names[i],
                         point_size = 2.5, line_size = 0.9, label_size = 2.0) +
    theme(legend.position = if (i == length(mle_cfgs)) "right" else "none",
          plot.title    = element_text(size = 9),
          plot.subtitle = element_text(size = 8),
          axis.text     = element_text(size = 8),
          axis.title    = element_text(size = 9),
          legend.text   = element_text(size = 8),
          legend.title  = element_text(size = 9))
})
gridExtra::grid.arrange(grobs = p_list2, ncol = 1)
```

**Findings:** Gamma (spillover magnitude) has virtually no effect on design rankings.
All `r if(mle_avail) n_designs` designs maintain their relative ranks across Gamma =
`r if(mle_avail) min(gamma_levels)` to `r if(mle_avail) max(gamma_levels)` within
every incidence config. This is consistent with the sensitivity analysis finding that
Gamma explains less than `r if(mle_avail) ceiling(max_gamma_eta * 100)`\% of MSE
variance (eta-squared $<$ `r if(mle_avail) max_gamma_eta`) for all designs.
Researchers need not tailor design selection to anticipated spillover magnitude.

## Marginal Ranking Tables

The following tables report average MSE (and rank in parentheses) at each level
of each key parameter, averaged over all other simulation parameters.

```{r q2-marginal-tables}
#| eval: !expr mle_avail
#| results: asis
params_to_show <- c("Rho", "Gamma", "Spillover_Type")

for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  overall_order <- rank_designs_by_group(cfg, character(0)) %>%
    arrange(Rank) %>% pull(Design)

  cap_safe_nm <- gsub("_", " ", cfg_nm)
  cat(sprintf("\n### %s\n\n", cfg_nm))

  for (param in params_to_show) {
    ranked <- rank_designs_by_group(cfg, param) %>%
      mutate(cell = sprintf("%.4f (#%d)", Avg_MSE, Rank)) %>%
      select(Design, all_of(param), cell) %>%
      pivot_wider(names_from = all_of(param), values_from = cell,
                  names_prefix = paste0(param, "=")) %>%
      mutate(Design = factor(Design, levels = overall_order)) %>%
      arrange(Design) %>%
      mutate(Design = short_design_name(as.character(Design)))

    param_label <- switch(param,
      "Rho"          = "Rho (outcome spatial autocorrelation)",
      "Gamma"        = "Gamma (spillover magnitude)",
      "Spillover_Type" = "Spillover Type",
      param)

    tbl_out <- kable(ranked, booktabs = TRUE, linesep = "",
          caption = sprintf(
            "%s | Marginal rankings by %s. Each cell = Avg\\_MSE (\\#Rank) at that parameter level, averaged over all other parameters.",
            cap_safe_nm, param_label)) %>%
      kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                    font_size = 8) %>%
      row_spec(1, bold = TRUE)
    print(tbl_out)
    cat("\n")
  }
}
```

```{r q2-spillover-setup}
#| include: false
#| eval: !expr mle_avail
# Determine the rank reversal pattern between control_only and both
# Identify which design ranks 1st under each spillover type most often
spill_n_configs_control_only <- sum(spill_all$Spillover_Type == "control_only" &
                                    spill_all$Design == best_under_control_only &
                                    spill_all$Rank == 1)
spill_n_configs_both         <- sum(spill_all$Spillover_Type == "both" &
                                    spill_all$Design == best_under_both &
                                    spill_all$Rank == 1)
spill_total_groups           <- length(cfg_names)  # one per incidence config

# Check if same design wins overall regardless of spillover
same_winner_both_types <- (best_under_control_only == best_under_both)
```

**Key takeaway from the Spillover\_Type marginal table:** The most striking pattern
across all configs is the **rank comparison by spillover type**:

- Under **"control\_only"** spillover (only untreated units experience spillover
  from neighbors), **`r if(mle_avail) best_under_control_only_short`** ranks 1st
  in `r if(mle_avail) spill_n_configs_control_only` of
  `r if(mle_avail) spill_total_groups` configs.
- Under **"both"** spillover (treatment and control units both experience spillover),
  **`r if(mle_avail) best_under_both_short`**
  `r if(mle_avail) ifelse(same_winner_both_types, "also dominates", "competes strongly with the control_only winner, winning in several configs")`.

This is the single most actionable finding for practitioners: **if the spillover
mechanism is known a priori, the design choice should reflect it.** When uncertain,
`r if(mle_avail) modal_best_short` is the safer default as it achieves a better
average across both types.

# Q3: Best Design for Parameter Combinations

## Rho x Gamma Best-Design Maps

```{r q3-heatmaps-cap, include=FALSE}
q3_heatmaps_cap <- paste0(
  "Best design heatmap: Rho vs. Gamma for each incidence config.",
  " Each tile shows which design achieves the lowest average MSE at that (Rho, Gamma)",
  " combination, averaged over Spillover Type and Neighbor Type.",
  " Tile text shows the winning design abbreviation and its average MSE."
)
```

```{r q3-heatmaps}
#| eval: !expr mle_avail
#| fig-cap: !expr q3_heatmaps_cap
#| fig-height: 8.0
p_list3 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_best_design_heatmap(mle_cfgs[[i]], "Rho", "Gamma", cfg_names[i],
                           text_size = 3, text_color = "white",
                           compact_labels = TRUE) +
    labs(title = cfg_names[i], subtitle = NULL) +
    theme(plot.title  = element_text(size = 9, face = "bold"),
          axis.text   = element_text(size = 8),
          axis.title  = element_text(size = 9),
          legend.position = "none")
})
gridExtra::grid.arrange(grobs = p_list3, ncol = 2)
```

**How to read the maps:** Each tile corresponds to one (Rho, Gamma) combination.
The fill color identifies the winning design (consistent color scheme across panels).
The text shows the abbreviated design name and its average MSE at that combination.

```{r q3-heatmap-findings}
#| include: false
#| eval: !expr mle_avail
# Count how many Rho x Gamma tiles each design wins (aggregated across all configs)
rho_gamma_winners <- lapply(cfg_names, function(cn) {
  r <- rank_designs_by_group(mle_cfgs[[cn]], c("Rho", "Gamma")) %>%
    filter(Rank == 1) %>%
    select(Design)
  r
})
rho_gamma_all <- bind_rows(rho_gamma_winners)
rho_gamma_freq <- rho_gamma_all %>% count(Design, sort = TRUE)
total_rho_gamma_tiles <- nrow(rho_gamma_all)
best_rho_gamma_design <- rho_gamma_freq$Design[1]
best_rho_gamma_short  <- short_design_name(best_rho_gamma_design)
best_rho_gamma_tiles  <- rho_gamma_freq$n[1]
pct_rho_gamma_tiles   <- round(best_rho_gamma_tiles / total_rho_gamma_tiles * 100)

# Check if MSE increases with Rho (for best design)
rho_mse_trend <- rank_designs_by_group(mle_results, "Rho") %>%
  filter(Design == modal_best) %>%
  arrange(Rho)
rho_mse_monotone <- all(diff(rho_mse_trend$Avg_MSE) >= 0)
```

**Findings:**

- **`r if(mle_avail) best_rho_gamma_short` dominates the Rho x Gamma space**,
  winning `r if(mle_avail) best_rho_gamma_tiles` of
  `r if(mle_avail) total_rho_gamma_tiles` tiles
  (`r if(mle_avail) pct_rho_gamma_tiles`\%) across all configs.
- **MSE is largely insensitive to Gamma** (the tiles within a Rho row show similar
  MSE values). This re-confirms the Gamma insensitivity finding from Q2.
- **MSE `r if(mle_avail) ifelse(rho_mse_monotone, "increases monotonically", "generally increases")` with Rho**
  for `r if(mle_avail) modal_best_short`, but the relative design ranking is stable.

## Rho x Spillover Type Best-Design Maps

```{r q3-heatmaps-spill-cap, include=FALSE}
q3_spill_cap <- paste0(
  "Best design heatmap: Rho vs. Spillover Type for each incidence config.",
  " This reveals the key interaction: under both-direction spillover,",
  " the winner sometimes switches from ",
  if (mle_avail) modal_best_short else "best design",
  " to ",
  if (mle_avail) best_under_both_short else "alternative",
  " at low Rho."
)
```

```{r q3-heatmaps-spill}
#| eval: !expr mle_avail
#| fig-cap: !expr q3_spill_cap
#| fig-height: 7.5
p_list4 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_best_design_heatmap(mle_cfgs[[i]], "Rho", "Spillover_Type", cfg_names[i],
                           text_size = 3, text_color = "white",
                           compact_labels = TRUE) +
    labs(title = cfg_names[i], subtitle = NULL) +
    theme(plot.title  = element_text(size = 9, face = "bold"),
          axis.text   = element_text(size = 8),
          axis.title  = element_text(size = 9),
          legend.position = "none")
})
gridExtra::grid.arrange(grobs = p_list4, ncol = 2)
```

```{r q3-spillover-interaction}
#| include: false
#| eval: !expr mle_avail
# Count Rho x Spillover_Type tiles won per design
rho_spill_winners <- lapply(cfg_names, function(cn) {
  r <- rank_designs_by_group(mle_cfgs[[cn]], c("Rho", "Spillover_Type")) %>%
    filter(Rank == 1)
  r$Inc_Config <- cn
  r
})
rho_spill_all <- bind_rows(rho_spill_winners)

# Tiles won under control_only
control_tiles_by_design <- rho_spill_all %>%
  filter(Spillover_Type == "control_only") %>%
  count(Design, sort = TRUE)
control_best_design <- control_tiles_by_design$Design[1]
control_best_short  <- short_design_name(control_best_design)
control_best_tiles  <- control_tiles_by_design$n[1]
total_control_tiles <- sum(rho_spill_all$Spillover_Type == "control_only")
control_pct         <- round(control_best_tiles / total_control_tiles * 100)

# Tiles won under both
both_tiles_by_design <- rho_spill_all %>%
  filter(Spillover_Type == "both") %>%
  count(Design, sort = TRUE)
both_best_design <- both_tiles_by_design$Design[1]
both_best_short  <- short_design_name(both_best_design)
both_best_tiles  <- both_tiles_by_design$n[1]
total_both_tiles <- sum(rho_spill_all$Spillover_Type == "both")
both_pct         <- round(both_best_tiles / total_both_tiles * 100)
```

**Key finding:** The Rho x Spillover\_Type heatmap reveals the most practically
important interaction:

- When spillover is **"control\_only"**: `r if(mle_avail) control_best_short` wins
  `r if(mle_avail) control_best_tiles` of `r if(mle_avail) total_control_tiles`
  tiles (`r if(mle_avail) control_pct`\%) across all Rho levels and all configs.
- When spillover is **"both"**: `r if(mle_avail) both_best_short` wins
  `r if(mle_avail) both_best_tiles` of `r if(mle_avail) total_both_tiles` tiles
  (`r if(mle_avail) both_pct`\%).

This interaction is the primary driver of the overall MSE competition between
`r if(mle_avail) control_best_short` and `r if(mle_avail) both_best_short`.
In the absence of prior knowledge about spillover direction, `r if(mle_avail) modal_best_short`
is recommended because its control\_only advantage more than compensates for any
"both" disadvantage.

# Per-Config Narrative Findings

This section synthesizes the analytical results for each incidence configuration
into a cohesive narrative, presenting the six structured findings produced by
`generate_commentary()`.

```{r per-config-commentary}
#| eval: !expr mle_avail
#| results: asis
for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  cap_safe_nm <- gsub("_", " ", cfg_nm)

  # --- Compute all findings ---
  overall <- rank_designs_by_group(cfg, character(0))
  best_row   <- overall %>% filter(Rank == 1)
  worst_row  <- overall %>% filter(Rank == max(Rank))
  second_row <- overall %>% filter(Rank == 2)

  best_name   <- short_design_name(best_row$Design[1])
  worst_name  <- short_design_name(worst_row$Design[1])
  second_name <- short_design_name(second_row$Design[1])

  # Pairwise dominance
  scenario_ids <- c("Neighbor_Type", "Rho", "Gamma", "Spillover_Type")
  wide <- cfg %>%
    select(all_of(c(scenario_ids, "Design", "MSE"))) %>%
    pivot_wider(names_from = Design, values_from = MSE, id_cols = all_of(scenario_ids))
  dom_vs_second <- round(mean(wide[[best_row$Design[1]]] < wide[[second_row$Design[1]]], na.rm=TRUE)*100, 1)
  dom_vs_worst  <- round(mean(wide[[best_row$Design[1]]] < wide[[worst_row$Design[1]]], na.rm=TRUE)*100, 1)

  # Rank stability
  rho_ranks   <- rank_designs_by_group(cfg, "Rho")   %>% filter(Design == best_row$Design[1])
  gamma_ranks <- rank_designs_by_group(cfg, "Gamma") %>% filter(Design == best_row$Design[1])
  rho_stable   <- all(rho_ranks$Rank == 1)
  gamma_stable <- all(gamma_ranks$Rank == 1)
  stable_str <- if (rho_stable && gamma_stable) {
    "holds rank 1 at every level of Rho and Gamma (no rank crossover)"
  } else if (rho_stable) {
    "stable across all Rho levels but shows minor rank changes across Gamma"
  } else if (gamma_stable) {
    sprintf("stable across all Gamma levels; briefly cedes rank 1 at Rho = %s",
            paste(rho_ranks$Rho[rho_ranks$Rank != 1], collapse = ", "))
  } else {
    "shows rank reversals across both Rho and Gamma levels"
  }

  # Sensitivity
  params <- c("Rho", "Gamma", "Spillover_Type", "Neighbor_Type")
  d_data <- cfg %>% filter(Design == best_row$Design[1])
  gm     <- mean(d_data$MSE, na.rm=TRUE)
  ss_tot <- sum((d_data$MSE - gm)^2, na.rm=TRUE)
  eta_sq <- sapply(params, function(p) {
    gs <- d_data %>% group_by(.data[[p]]) %>%
      summarise(gm2 = mean(MSE, na.rm=TRUE), gn = n(), .groups="drop")
    ss_b <- sum(gs$gn * (gs$gm2 - gm)^2)
    if (ss_tot > 0) ss_b / ss_tot else 0
  })
  names(eta_sq) <- params
  top_param  <- names(which.max(eta_sq))
  low_params <- names(eta_sq[eta_sq < 0.05])

  # MSE ratio
  mse_ratio_cfg  <- round(worst_row$Avg_MSE[1] / best_row$Avg_MSE[1], 1)
  pct_vs_second  <- round((second_row$Avg_MSE[1] - best_row$Avg_MSE[1]) / best_row$Avg_MSE[1] * 100, 1)

  # --- Print ---
  cat(sprintf("## %s\n\n", cfg_nm))

  cat(sprintf(
    "**Finding 1 -- Overall Winner:** %s achieves the lowest average MSE (%.4f) across all %d scenarios in this incidence configuration. The runner-up is %s (avg MSE = %.4f), which is %.1f\\%% higher.\n\n",
    best_name, best_row$Avg_MSE[1],
    n_scenarios_per_config,
    second_name, second_row$Avg_MSE[1],
    pct_vs_second
  ))

  cat(sprintf(
    "**Finding 2 -- Dominance:** %s achieves lower MSE than the runner-up (%s) in %.1f\\%% of individual scenarios, and beats the worst performer (%s) in %.1f\\%% of scenarios. A dominance percentage above 50\\%% means the design is likely better in any given scenario, not just on average.\n\n",
    best_name, second_name, dom_vs_second,
    worst_name, dom_vs_worst
  ))

  cat(sprintf(
    "**Finding 3 -- Robustness:** %s %s. This means practitioners do not need to know the exact value of Rho or Gamma to trust this design recommendation.\n\n",
    best_name, stable_str
  ))

  cat(sprintf(
    "**Finding 4 -- Coverage:** %s achieves average 95\\%% CI coverage of %.3f (nominal = 0.95). The worst design (%s) achieves only %.3f, meaning its confidence intervals are severely anti-conservative and should not be used for inference.\n\n",
    best_name, best_row$Avg_Coverage[1],
    worst_name, worst_row$Avg_Coverage[1]
  ))

  cat(sprintf(
    "**Finding 5 -- Sensitivity:** For %s, the most influential simulation parameter is %s (eta-squared = %.3f), accounting for %.1f\\%% of the design's MSE variation across scenarios. ",
    best_name, top_param, eta_sq[top_param], eta_sq[top_param] * 100
  ))
  if (length(low_params) > 0) {
    cat(sprintf(
      "Parameters with negligible influence (eta-squared $< 0.05$): %s. These can be safely ignored when selecting this design.\n\n",
      paste(low_params, collapse = ", ")
    ))
  } else {
    cat("All parameters have non-negligible influence on this design's MSE.\n\n")
  }

  cat(sprintf(
    "**Finding 6 -- Practical Recommendation:** Under %s incidence, select %s for treatment assignment. It provides %.1fx lower MSE than the worst design and near-nominal coverage (%.3f), making it both accurate and inferentially valid across the full range of tested parameter values.\n\n",
    cfg_nm, best_name, mse_ratio_cfg, best_row$Avg_Coverage[1]
  ))
}
```

# Scenario-Specific Design Lookup

For practitioners who can specify all four scenario parameters (Rho, Gamma,
Spillover\_Type, Neighbor\_Type), the following tables provide exact design
rankings for a selection of illustrative scenarios.

```{r scenario-lookups}
#| eval: !expr mle_avail
#| results: asis
# Define representative scenarios using actual data values (not hardcoded)
if (mle_avail) {
  rho_mid  <- sort(rho_levels)[ceiling(length(rho_levels) / 2)]    # e.g. 0.20
  rho_high <- max(rho_levels)                                        # e.g. 0.50
  gamma_mid  <- sort(gamma_levels)[ceiling(length(gamma_levels) / 2)]  # e.g. 0.7
  gamma_high <- max(gamma_levels)                                        # e.g. 0.8
  spill_both    <- spill_levels[spill_levels != "control_only"][1]
  spill_control <- "control_only"
  nb_queen <- nb_levels[grep("queen", nb_levels)][1]
  nb_rook  <- nb_levels[grep("rook",  nb_levels)][1]
}

scenario_specs <- list(
  list(rho = rho_mid,  gamma = gamma_mid,  spill = spill_both,    nb = nb_queen,
       label = sprintf("Moderate Rho (%.2f), Both Spillover, Queen", rho_mid)),
  list(rho = rho_high, gamma = gamma_high, spill = spill_control, nb = nb_rook,
       label = sprintf("High Rho (%.2f), Control-Only Spillover, Rook", rho_high))
)

for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  cap_safe_nm <- gsub("_", " ", cfg_nm)
  cat(sprintf("\n## %s\n\n", cfg_nm))

  for (spec in scenario_specs) {
    filtered <- cfg %>%
      filter(Rho == spec$rho, Gamma == spec$gamma,
             Spillover_Type == spec$spill, Neighbor_Type == spec$nb)

    if (nrow(filtered) == 0) next

    ranked <- rank_designs_by_group(filtered, character(0)) %>%
      mutate(
        Design       = short_design_name(Design),
        Avg_MSE      = round(Avg_MSE, 4),
        Avg_Coverage = round(Avg_Coverage, 3),
        Avg_Bias     = sprintf("%+.4f", Avg_Bias),
        Avg_SD       = round(Avg_SD, 4)
      ) %>%
      select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias, Avg_SD)

    best_r   <- ranked %>% filter(Rank == 1)
    second_r <- ranked %>% filter(Rank == 2)
    pct_gap  <- round((as.numeric(second_r$Avg_MSE[1]) - as.numeric(best_r$Avg_MSE[1])) /
                        as.numeric(best_r$Avg_MSE[1]) * 100, 1)

    spill_display <- gsub("_", "-", spec$spill)   # "control-only" avoids LaTeX _ issue
    tbl_out <- kable(ranked, booktabs = TRUE, linesep = "", align = "rlrrrr",
          col.names = c("Rank", "Design", "MSE", "Coverage", "Bias", "SD"),
          caption = sprintf(
            "%s | Scenario: %s. Winner MSE %.1f\\%% lower than runner-up.",
            cap_safe_nm, spec$label, pct_gap)) %>%
      kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
      row_spec(1, bold = TRUE)
    print(tbl_out)
    cat("\n")
  }
}
```

**How to use the lookup tables:** Identify the row that matches your anticipated
trial parameters. The design at Rank 1 is recommended. The ``Bias'' column
shows whether estimates are systematically above or below $\tau = 1.0$; a Bias
close to 0 with high Coverage indicates that both point estimates and confidence
intervals are reliable.

# Practical Design Selection Guide

## Decision Framework

```{r decision-table}
#| results: asis
#| eval: !expr mle_avail
# Build decision_df programmatically from results

# Default (overall best)
default_best       <- modal_best
default_best_short <- modal_best_short

# Best under both-spillover at low Rho (first two Rho levels)
low_rho_thresh <- sort(rho_levels)[2]  # second-lowest rho
both_low_rho_best <- rank_designs_by_group(
  mle_results %>% filter(Spillover_Type == "both", Rho <= low_rho_thresh),
  character(0)
) %>% filter(Rank == 1) %>% pull(Design) %>% first()
both_low_rho_short <- short_design_name(both_low_rho_best)

# Best under iid + very low Rho
iid_very_low_rho_best <- rank_designs_by_group(
  mle_results %>% filter(grepl("iid", Incidence_Mode), Rho == min(rho_levels)),
  character(0)
) %>% filter(Rank == 1) %>% pull(Design) %>% first()
iid_vlr_short <- short_design_name(iid_very_low_rho_best)

# Best under high spatial clustering + high Rho
high_spatial_high_rho_best <- rank_designs_by_group(
  mle_results %>% filter(grepl("spatial", Incidence_Mode, ignore.case = TRUE),
                         Rho == max(rho_levels)),
  character(0)
) %>% filter(Rank == 1) %>% pull(Design) %>% first()
hs_hr_short <- short_design_name(high_spatial_high_rho_best)

# Always-worst design
always_worst_short <- worst_design_short

# Coverage of worst design (range)
worst_cov_str <- worst_cov_range

# MSE ratio of worst vs best (range)
mse_ratio_str <- mse_ratio_range

# Design 5 queen vs rook comparison (if Design 5 in results)
d5_present <- "Design 5" %in% mle_results$Design
if (d5_present) {
  d5_queen <- mean(mle_results$MSE[mle_results$Design == "Design 5" &
                                   mle_results$Neighbor_Type == "queen"], na.rm = TRUE)
  d5_rook  <- mean(mle_results$MSE[mle_results$Design == "Design 5" &
                                   mle_results$Neighbor_Type == "rook"],  na.rm = TRUE)
  d5_ratio <- round(d5_queen / d5_rook, 1)
  d5_warn  <- sprintf("Queen contiguity amplifies 2x2 block effects; queen MSE is %.1fx rook MSE", d5_ratio)
  d5_name  <- short_design_name("Design 5")
} else {
  d5_warn <- "Queen contiguity amplifies 2x2 block effects for this design"
  d5_name <- "D5: 2x2 Blocking"
}

decision_df <- data.frame(
  Situation = c(
    "Default (uncertain parameters)",
    sprintf("Spillover is 'both' AND Rho <= %.2f", low_rho_thresh),
    sprintf("Incidence is iid AND Rho = %.2f", min(rho_levels)),
    sprintf("High spatial clustering AND Rho = %.2f", max(rho_levels)),
    "ANY scenario",
    "ANY scenario"
  ),
  Recommended = c(
    default_best_short,
    both_low_rho_short,
    iid_vlr_short,
    hs_hr_short,
    paste0("Avoid ", always_worst_short),
    paste0("Avoid ", d5_name, " under queen contiguity")
  ),
  Justification = c(
    sprintf("Ranks 1st in %d of %d configs across all Gamma levels", n_configs_modal_best_wins, length(cfg_names)),
    "Winner shifts at this corner; verify from Rho x Spillover_Type heatmap",
    "Deterministic targeting of high-incidence clusters aligns with iid low-Rho regime",
    sprintf("%s still wins at max Rho in high-spatial-clustering configs", hs_hr_short),
    sprintf("Invalid CIs (coverage %s); MSE %sx higher than winner", worst_cov_str, mse_ratio_str),
    d5_warn
  ),
  stringsAsFactors = FALSE
)

kable(decision_df, booktabs = TRUE, linesep = "",
      col.names = c("Situation", "Recommended Design", "Justification"),
      caption = "Practical design selection guide. 'Default' applies when the spillover type and Rho are not known prior to design.") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "6cm") %>%
  row_spec(1, bold = TRUE)
```

## Why `r if(mle_avail) modal_best_short` Wins: Mechanistic Explanation

`r if(mle_avail) modal_best_short` works by dividing the $10 \times 10$ grid into
four $5 \times 5$ quadrants, where each quadrant receives a random treatment
saturation level drawn from a discrete set (0.20, 0.40, 0.60, 0.80). Within each
quadrant, clusters are randomly selected for treatment at the assigned saturation rate.

This design outperforms others because:

1. **Quadrant-level saturation variation creates spatial contrast.** The MLE
   estimator (`lagsarlm`) must disentangle the direct treatment effect $\tau$
   from the spatial lag parameter $\rho$. When treatment is uniformly distributed
   or strongly correlated with incidence, this separation is harder. Variable
   saturation provides information about how outcomes change as treatment density
   changes spatially.

2. **Randomness within quadrants prevents systematic confounding.** Unlike
   deterministic designs, idiosyncratic variation uncorrelated with spatially-structured
   incidence or outcome patterns is introduced.

3. **Quadrant-level structure respects spatial scale.** The $5 \times 5$ quadrant
   blocks match the scale at which spatial autocorrelation operates (rook/queen
   neighborhoods), providing richer contrast than finer (2x2) or coarser structures.

## Why `r if(mle_avail) worst_design_short` Fails: Mechanistic Explanation

`r if(mle_avail) worst_design_short` assigns treatment in a perfectly alternating
pattern. This creates a fundamental identification problem:

- The treatment assignment vector $Z$ is a deterministic function of position on
  the grid.
- The spatial weight matrix $W$ encodes neighbor relationships, which are also
  determined by position.
- Therefore, $Z$ and $W \cdot Z$ (the spillover term) are collinear with the
  spatial lag of the outcome $W \cdot Y$ that the SAR model needs to estimate
  $\rho$.

This collinearity inflates variance, biases $\hat{\tau}$, and degrades coverage ---
all of which are observed in the simulation results.

# Summary of Key Results

```{r summary-table}
#| eval: !expr mle_avail
#| results: asis
overall_summary <- rank_designs_by_group(mle_results, character(0)) %>%
  mutate(
    Design       = short_design_name(Design),
    Avg_MSE      = round(Avg_MSE, 4),
    Avg_Coverage = round(Avg_Coverage, 3),
    Avg_Bias     = round(Avg_Bias, 4)
  ) %>%
  select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias, N_Scenarios)

kable(overall_summary, booktabs = TRUE, linesep = "", align = "rlrrrr",
      col.names = c("Rank", "Design", "Avg MSE", "Avg Coverage",
                    "Avg Bias", "N Scenarios"),
      caption = paste0(
        "Overall MLE design rankings averaged across all ",
        n_scenarios_total,
        " scenarios (all incidence configs combined). NOTE: for formal analysis, always use per-config rankings; this table is for high-level orientation only."
      )) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(1, bold = TRUE) %>%
  row_spec(nrow(overall_summary), color = "gray")
```

```{r leading-coverage-setup}
#| include: false
#| eval: !expr mle_avail
# Coverage range for top-4 designs overall
top4_designs <- overall_all %>% arrange(Rank) %>% slice(1:4) %>% pull(Design)
top4_cov <- overall_all %>% filter(Design %in% top4_designs) %>% pull(Avg_Coverage)
top4_cov_lo <- round(min(top4_cov), 2)
top4_cov_hi <- round(max(top4_cov), 2)

# Determine whether Gamma effect on rankings is nil across all configs
gamma_stable_all <- all(sapply(cfg_names, function(cn) {
  gamma_r <- rank_designs_by_group(mle_cfgs[[cn]], "Gamma")
  # Check if best design keeps rank 1 at all Gamma
  best_d <- rank_designs_by_group(mle_cfgs[[cn]], character(0)) %>%
    filter(Rank == 1) %>% pull(Design) %>% first()
  all(gamma_r$Rank[gamma_r$Design == best_d] == 1)
}))
gamma_stability_str <- ifelse(gamma_stable_all,
  "Regardless of the anticipated spillover magnitude, the design ranking is stable. Researchers can ignore this parameter when selecting a design.",
  paste0("Design rankings are largely stable across Gamma = ",
         min(gamma_levels), " to ", max(gamma_levels),
         ", though minor shifts occur in some configs.")
)
```

**Conclusions:**

1. **Universal recommendation:** Under MLE estimation, **`r if(mle_avail) best_overall_short`**
   is the best treatment assignment design across all incidence modes, Rho levels,
   and Gamma levels tested. It achieves `r if(mle_avail) overall_mse_ratio`x lower
   MSE than the worst design.

2. **Spillover type is the key moderator.** When spillover direction is "both",
   **`r if(mle_avail) best_under_both_short`** becomes competitive and should be
   considered. When spillover is "control\_only", `r if(mle_avail) best_under_control_only_short`'s
   advantage is unambiguous (`r if(mle_avail) control_pct`\% of tiles).

3. **`r if(mle_avail) worst_design_short` should never be used.** Its perfectly
   regular spatial structure creates collinearity that invalidates both point
   estimates and confidence intervals under the MLE spatial autoregressive model.

4. **Gamma does not affect design choice.** `r if(mle_avail) gamma_stability_str`

5. **Coverage is near-nominal for leading designs.** Under MLE, the top
   `r if(mle_avail) length(top4_designs)` designs all achieve
   `r if(mle_avail) top4_cov_lo`--`r if(mle_avail) top4_cov_hi`\% coverage
   across the tested scenarios, confirming that MLE-based inference is valid
   when a well-chosen spatial design is used.

---

# References

- Mirzaei, A. et al. (2019). Sudden unexpected death rates.
  *(SUD base rate 35/100,000)*
- LeSage, J. \& Pace, R.K. (2009). *Introduction to Spatial Econometrics*. CRC Press.
- Bivand, R., et al. `spdep` R package.
- Bivand, R. \& Piras, G. `spatialreg` R package.
- R packages used: `dplyr`, `tidyr`, `ggplot2`, `viridis`, `knitr`,
  `kableExtra`, `gridExtra`, `digest`

---

# Appendix: Output Files

```{r appendix-files}
#| results: asis
if (mle_avail) {
  # Find actual result file names from results_dir
  rds_files <- list.files(file.path(results_dir, "sim_data"), pattern = "MLE_combined.*\\.rds$",
                          full.names = FALSE)
  latest_rds <- if (length(rds_files) > 0) {
    rds_files[which.max(file.mtime(file.path(results_dir, "sim_data", rds_files)))]
  } else {
    "sim_results_MLE_combined_<timestamp>.rds"
  }

  files_df <- data.frame(
    File = c(
      "MLE_combined_design_recommendations.pdf",
      latest_rds,
      "MLE_design_recommendation_report.pdf"
    ),
    Contents = c(
      "Raw figure output: all recommendation plots",
      paste0("Source data: ", n_scenarios_total, " MLE scenarios x ", ncol(mle_results), " columns"),
      "This narrative companion report"
    ),
    Location = c("results/", "results/sim_data/", "results/"),
    stringsAsFactors = FALSE
  )
} else {
  files_df <- data.frame(
    File = character(0), Contents = character(0), Location = character(0)
  )
}

kable(files_df, booktabs = TRUE, linesep = "",
      caption = "Output files for the design recommendation analysis.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```
