---
title: "Personalized Design Recommendation Report"
subtitle: "MLE-Based Analysis for Spatial CRT Treatment Assignment"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    latex_engine: xelatex
    keep_tex: false
    fig_caption: true
    fig_height: 4
    fig_width: 6.5
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{float}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{geometry}
  - \usepackage{xcolor}
  - \usepackage{mdframed}
  - \geometry{margin=1in}
  - \floatplacement{figure}{htbp}
  - \floatplacement{table}{H}
  - \definecolor{boxbg}{RGB}{240,248,255}
  - \definecolor{boxframe}{RGB}{70,130,180}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.pos = "htbp"
)
```

```{r load-packages}
library(dplyr)
library(tidyr)
library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)
```

```{r resolve-paths}
script_dir <- tryCatch(
  normalizePath(dirname(knitr::current_input(dir = TRUE))),
  error = function(e) {
    tryCatch(
      normalizePath(dirname(sys.frame(1)$ofile)),
      error = function(e2) normalizePath(getwd())
    )
  }
)
results_dir <- file.path(dirname(script_dir), "results")
```

```{r source-modules}
# Source recommendation module (which sources 06 -> 01-03)
source(file.path(script_dir, "08_design_recommendations.R"))
```

```{r load-results}
mle_results <- tryCatch(
  load_latest_results(results_dir, estimation_mode = "MLE_combined"),
  error = function(e) {
    message("MLE combined results not found: ", e$message)
    NULL
  }
)
mle_avail <- !is.null(mle_results) && nrow(mle_results) > 0
mle_cfgs  <- if (mle_avail) split_by_incidence_config(mle_results) else list()
cfg_names <- names(mle_cfgs)
```

```{r global-summaries}
# Pre-compute cross-config ranked summary used throughout
if (mle_avail) {
  all_ranked_list <- lapply(seq_along(mle_cfgs), function(i) {
    r <- rank_designs_by_group(mle_cfgs[[i]], character(0))
    r$Inc_Config <- cfg_names[i]
    r
  })
  all_ranked <- bind_rows(all_ranked_list)

  # Best design in each config
  best_per_config <- all_ranked %>%
    filter(Rank == 1) %>%
    select(Inc_Config, Design, Avg_MSE, Avg_Coverage)

  # Design that is best in most configs
  modal_best <- names(sort(table(best_per_config$Design), decreasing = TRUE))[1]
  modal_best_short <- short_design_name(modal_best)

  # Overall worst (highest avg MSE across all configs)
  worst_design <- all_ranked %>%
    group_by(Design) %>%
    summarise(Grand_MSE = mean(Avg_MSE), .groups = "drop") %>%
    arrange(desc(Grand_MSE)) %>%
    slice(1) %>%
    pull(Design)
  worst_design_short <- short_design_name(worst_design)
}
```

# Executive Summary

This report is a companion to the `MLE_combined_design_recommendations.pdf` figure
file. It provides narrative explanations of **how each analysis was computed**,
**what each figure and table shows**, and **what the results mean in practice** for
researchers designing spatial cluster randomized trials (CRTs).

The simulation evaluates **six treatment assignment designs** across **1,920 parameter
scenarios** using Maximum Likelihood Estimation (MLE) via a spatial autoregressive
model (`lagsarlm`). The estimand is the direct treatment effect $\tau = 1.0$.

Three analytical questions are addressed:

\begin{mdframed}[backgroundcolor=boxbg, linecolor=boxframe, linewidth=1pt]
\textbf{Q1 -- Per incidence mode:} Which design is best given how historical
incidence was generated (iid, Spatial, Poisson)?

\textbf{Q2 -- Per parameter level:} Which design is best when a specific simulation
parameter takes a particular value (e.g., high spatial autocorrelation $\rho = 0.50$),
marginalizing over all other parameters?

\textbf{Q3 -- Per scenario:} Which design is best for a fully-specified combination
of parameter values?
\end{mdframed}

```{r exec-table, eval=mle_avail, results='asis'}
exec_df <- best_per_config %>%
  mutate(
    Design     = short_design_name(Design),
    Avg_MSE    = round(Avg_MSE, 4),
    Avg_Coverage = round(Avg_Coverage, 3)
  ) %>%
  rename(`Incidence Config` = Inc_Config,
         `Best Design`      = Design,
         `Avg MSE`          = Avg_MSE,
         `Avg Coverage`     = Avg_Coverage)

kable(exec_df, booktabs = TRUE, linesep = "", align = "llrr",
      caption = "Best MLE design (lowest avg MSE) for each incidence configuration.
      All 5 configurations select the same winner.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(seq_len(nrow(exec_df)), bold = FALSE)
```

**Key finding:** `r if(mle_avail) modal_best_short` achieves the lowest average MSE
in every incidence configuration, with `r if(mle_avail) worst_design_short` consistently
worst. Spillover type (control-only vs. both) is by far the most influential parameter
for all leading designs, while spatial autocorrelation $\rho$ and spillover magnitude
$\gamma$ have secondary effects.

# Study Background

## Designs Evaluated

Six treatment assignment strategies are compared. Each allocates approximately 50\%
of the 100 clusters ($10 \times 10$ grid) to treatment:

```{r design-table, results='asis'}
design_df <- data.frame(
  ID   = c(1, 2, 3, 4, 5, 7),
  Name = c("Checkerboard", "High Incidence Focus", "Saturation Quadrants",
           "Isolation Buffer", "2x2 Blocking", "Balanced Quartiles"),
  Det  = c("Yes", "Yes", "No", "No", "No", "No"),
  Description = c(
    "Alternating grid pattern; maximizes spatial separation of treated and control units",
    "Treats the top-50\\% incidence clusters deterministically",
    "Assigns random saturation levels (0.2--0.8) within each of four spatial quadrants",
    "Greedy assignment ensuring no two adjacent clusters are both treated",
    "1:1 randomization within non-overlapping 2x2 spatial blocks",
    "Stratified randomization balanced within incidence quartiles"
  )
)
kable(design_df, booktabs = TRUE, linesep = "",
      col.names = c("ID", "Name", "Deterministic?", "Description"),
      caption = "Six treatment assignment designs evaluated. Deterministic designs
      (1, 2) produce one assignment and replicate it; stochastic designs resample
      across 25 replications.") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 9) %>%
  column_spec(4, width = "7cm")
```

## Performance Metrics

For each of the 1,920 scenarios, **250 simulation iterations** (25 design
resamples $\times$ 10 outcome resamples) produce the following metrics:

- **Bias** $= \bar{\hat{\tau}} - \tau$: average departure from true effect $\tau = 1.0$
- **SD**: standard deviation of estimates across iterations
- **MSE** $= \text{Bias}^2 + \text{SD}^2$: total estimation error; the **primary
  ranking criterion** throughout this report
- **Coverage**: fraction of 95\% confidence intervals containing $\tau = 1.0$

Lower MSE is better. Coverage near 0.95 (the nominal level) indicates valid inference.

## Simulation Parameter Space

```{r param-table, results='asis'}
param_df <- data.frame(
  Parameter = c(
    "Incidence mode",
    "rho\\_X (incidence spatial autocorr.)",
    "nb\\_type (contiguity)",
    "Rho (outcome spatial autocorr.)",
    "Gamma (spillover magnitude)",
    "Spillover type",
    "Design",
    "TOTAL"
  ),
  Values = c(
    "iid, Spatial, Poisson",
    "N/A (iid); 0.20, 0.50 (Spatial, Poisson)",
    "rook, queen",
    "0.00, 0.01, 0.20, 0.50",
    "0.5, 0.6, 0.7, 0.8",
    "control\\_only, both",
    "1, 2, 3, 4, 5, 7",
    ""
  ),
  Levels = c("5 configs", "---", "2", "4", "4", "2", "6", "1,920 scenarios")
)
kable(param_df, booktabs = TRUE, linesep = "",
      caption = "Simulation parameter grid. Each of the 1,920 scenarios is a unique
      combination of (incidence config, nb\\_type, Rho, Gamma, Spillover type, Design).
      Results are always reported separately by incidence config.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(nrow(param_df), bold = TRUE)
```

# Analytical Methods

This section explains exactly how each analysis in the recommendation report
is computed.

## Core Ranking Method: `rank_designs_by_group()`

All conditional rankings in this report share the same logic, implemented in
`rank_designs_by_group()`:

1. **Group** the 384 scenarios within an incidence config by the requested
   conditioning variables plus Design (e.g., group by `{Rho, Design}`)
2. **Aggregate**: compute average MSE, Coverage, Bias, and SD within each group
3. **Rank**: within each unique combination of the conditioning variables,
   assign integer ranks to designs based on ascending average MSE
   (rank 1 = best; ties broken using minimum rank)
4. **Return** a tidy data frame with one row per `{group, Design}` combination

This is the same ranking logic used in `table_design_ranks()` in
`06_visualizations.R`, extended to support arbitrary conditioning sets.

**Critical invariant:** Rankings are **always computed within a single incidence
configuration**. Results are never aggregated across the five incidence configs
because each represents a fundamentally different assumption about how prior
incidence data arises.

## Q1 — Per-Config Rankings: `table_incidence_rankings()` and `plot_incidence_rankings()`

**What is computed:** For each of the 5 incidence configs, all 384 scenarios
(6 designs $\times$ 64 parameter combinations) are summarized by computing the
average MSE per design. Designs are then ranked 1--6 (lowest = best) within
each config.

**What the figure shows** (Page 1 of PDF): A faceted bar chart with one panel
per incidence config. Bars represent average MSE per design, sorted from lowest
to highest within each panel. Rank labels (1--6) appear above each bar.

**How to read it:** Lower bars are better. Rank labels allow quick comparison
across panels. A design ranked consistently high across all panels is a robust
global recommendation.

## Q2 — Marginal Rankings: `table_marginal_rankings()` and `plot_rank_trajectories()`

**What "marginal" means:** For a parameter like Rho, we want to know: ignoring
all other parameters, how does each design rank when Rho takes a specific value?
This is computed by grouping all scenarios by `{Rho, Design}` and averaging MSE
across the remaining parameters (Gamma, Spillover\_Type, Neighbor\_Type).

**What the rank trajectory plot shows**: A line plot where the x-axis is the
parameter level, the y-axis is design rank (1 at top, 6 at bottom), and each
line traces one design. Crossing lines indicate a **rank reversal**: a design
that is best at one parameter level but not at another.

**What the marginal ranking table shows**: A wide table with parameter levels
as column headers and designs as rows. Each cell reports `Avg_MSE (#Rank)` at
that parameter level, averaged over all other parameters. Designs are ordered
by their overall rank (best at top).

**What the conditional MSE boxplot shows**: Rather than averages, this shows the
**full distribution** of raw scenario-level MSE values for each design at each
parameter level. This reveals whether a design's advantage is consistent or
comes from a few favorable extreme scenarios.

## Q3 — Best Design Heatmap: `plot_best_design_heatmap()`

**What is computed:** For every combination of two parameters (e.g., Rho and
Gamma), all scenarios sharing that combination are grouped, average MSE is
computed per design, and the design with the minimum average MSE is identified
as the winner.

**What the heatmap shows**: A grid of colored tiles where each cell corresponds
to one `{Rho, Gamma}` combination. The color and text label identify the winning
design. The MSE value inside each tile is the winning design's average MSE at
that combination.

**Interpretation guidance:** If one design wins all tiles, it dominates
unconditionally. If tiles show different winners, the choice of design should
adapt to the anticipated parameter regime.

## Programmatic Commentary: `generate_commentary()`

For each incidence config, six structured findings are automatically derived
from the results:

| Finding | Computed as |
|---------|-------------|
| Overall winner | Design with Rank 1 from ungrouped `rank_designs_by_group()` |
| Dominance % | From scenario-level pairwise comparison: $\frac{\#\{s : \text{MSE}_{\text{best},s} < \text{MSE}_{\text{2nd},s}\}}{64}$ |
| Rank stability | Whether the best design holds rank 1 at every level of Rho and every level of Gamma |
| Coverage | Average Coverage for the best and worst designs |
| Sensitivity | Eta-squared ($\eta^2 = SS_{\text{between}} / SS_{\text{total}}$) for each parameter |
| Recommendation | Template string synthesizing findings 1--5 |

# Q1: Design Rankings by Incidence Mode

## Cross-Config MSE Rankings

```{r q1-mse-plot, eval=mle_avail, fig.cap="Average MSE per design for each incidence configuration. Bars are sorted left-to-right within each panel by MSE (lowest = best). Rank labels above bars. Lower bars are better. Note the shared y-axis: Design 1 (Checkerboard) is clipped in most panels due to its substantially higher MSE.", fig.height=5.0}
print(plot_incidence_rankings(mle_results) +
  theme(text        = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        strip.text  = element_text(size = 9, face = "bold"),
        plot.title  = element_text(size = 11),
        plot.subtitle = element_text(size = 9)))
```

**Reading the plot:** The five panels correspond to the five incidence configurations.
Within each panel, designs are arranged from best (left) to worst (right), with the
rank number printed above each bar. The consistent leftward position of Design 3
across all panels is the primary finding.

**Key observation:** Design 3 (Saturation Quadrants) ranks first in every single
incidence configuration, with average MSE ranging from 0.075 to 0.085 depending
on the config. This 8--11x MSE advantage over the worst design (Design 1,
Checkerboard) is stable regardless of how the historical incidence was generated.

## Cross-Config Coverage Rankings

```{r q1-cov-plot, eval=mle_avail, fig.cap="Average 95\\% CI coverage probability per design for each incidence configuration. Red dashed line = nominal 0.95. Coverage near 0.95 indicates valid inference; Design 1 coverage falls to 0.53--0.57 across all configs.", fig.height=5.0}
print(plot_incidence_coverage(mle_results) +
  theme(text        = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8),
        strip.text  = element_text(size = 9, face = "bold"),
        plot.title  = element_text(size = 11),
        plot.subtitle = element_text(size = 9)))
```

**Reading the plot:** The red dashed line at 0.95 is the nominal coverage target.
Bars above this line are over-covering (conservative CIs); bars below are under-covering
(anti-conservative). Under MLE, Designs 2--7 all achieve reasonable coverage (0.90--0.97),
but Design 1 falls dramatically short.

**Key observation:** Design 1's poor coverage (0.53--0.57) makes it unsuitable for
inference regardless of MSE. Even in the rare scenario where its MSE is competitive,
its confidence intervals are invalid.

## Detailed Rankings by Incidence Config

```{r q1-detail-table, eval=mle_avail, results='asis'}
for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  r <- rank_designs_by_group(cfg, character(0)) %>%
    mutate(
      Design       = short_design_name(Design),
      Avg_MSE      = round(Avg_MSE, 4),
      Avg_Coverage = round(Avg_Coverage, 3),
      Avg_Bias     = round(Avg_Bias, 4)
    ) %>%
    select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias)

  # Determine dominance: best vs second best
  best_mse <- r$Avg_MSE[1]
  second_mse <- r$Avg_MSE[2]
  pct_diff <- round((second_mse - best_mse) / best_mse * 100, 1)
  worst_mse <- r$Avg_MSE[nrow(r)]
  ratio <- round(worst_mse / best_mse, 1)

  cap_safe_nm <- gsub("_", " ", cfg_nm)
  tbl_out <- kable(r, booktabs = TRUE, linesep = "", align = "rlrrr",
        col.names = c("Rank", "Design", "Avg MSE", "Avg Coverage", "Avg Bias"),
        caption = sprintf(
          "MLE design rankings for %s. Runner-up MSE is %.1f\\%% higher than the winner; worst design MSE is %.1fx higher.",
          cap_safe_nm, pct_diff, ratio)) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
    row_spec(1, bold = TRUE)
  print(tbl_out)
  cat("\n")
}
```

**Notable patterns across configs:**

- **Design 3 (Saturation Quadrants)** ranks 1st in all 5 configs. Its runner-up
  margin ranges from 9\% (vs. Design 2 in iid Uniform) to 38\% (vs. Design 7 in
  Spatial rho\_X = 0.20).
- **Design 7 (Balanced Quartiles)** is the most consistent runner-up, ranking 2nd
  in 3 of 5 configs.
- **Design 2 (High Incidence Focus)** ranks 2nd in configs where the incidence
  structure aligns closely with the Spatial DGP (iid Uniform and Spatial rho\_X = 0.50).
- **Design 4 (Isolation Buffer)** ranks 3rd--4th consistently. Its constraint
  (no adjacent treated clusters) reduces the effective treated fraction, which
  inflates variance.
- **Design 5 (2x2 Blocking)** shows the largest queen vs. rook performance gap:
  queen-neighbor MSE is 2--3x rook-neighbor MSE, reflecting sensitivity to how
  spatial dependence is measured.
- **Design 1 (Checkerboard)** is last in all configs with MSE 8.6--11x higher
  than the winner and coverage below 0.57.

# Q2: Marginal Rankings by Parameter Level

This section answers: **holding all other parameters at their average, how does
each design's rank change as one parameter varies?**

## Effect of Outcome Spatial Autocorrelation (Rho)

```{r q2-rho-trajectories, eval=mle_avail, fig.cap="Design rank trajectories across Rho for each incidence config (one panel per config). Rank 1 = best. Lines that stay flat indicate robust designs; crossing lines reveal parameter-driven rank reversals. Design 3 (teal) stays near rank 1 across all Rho levels in most configs.", fig.height=8.0}
# One trajectory plot per config stacked in a single column (full width per panel)
p_list <- lapply(seq_along(mle_cfgs), function(i) {
  plot_rank_trajectories(mle_cfgs[[i]], "Rho", cfg_names[i],
                         point_size = 2.5, line_size = 0.9, label_size = 2.0) +
    theme(legend.position = if (i == length(mle_cfgs)) "right" else "none",
          plot.title    = element_text(size = 9),
          plot.subtitle = element_text(size = 8),
          axis.text     = element_text(size = 8),
          axis.title    = element_text(size = 9),
          legend.text   = element_text(size = 8),
          legend.title  = element_text(size = 9))
})
gridExtra::grid.arrange(grobs = p_list, ncol = 1)
```

**How to read the trajectory plots:** Rank 1 sits at the top; rank 6 at the bottom.
A flat horizontal line means a design's rank does not change as Rho increases.
A downward slope means the design falls in rank as Rho increases. Crossing lines
between two designs indicate a rank reversal.

**Findings:**

- **Design 3** maintains rank 1 across all Rho levels in the Spatial and Poisson
  configs. In iid Uniform, it cedes rank 1 to Design 2 at low Rho (0.00, 0.01)
  but reclaims it at Rho = 0.20.
- **Design 2 (High Incidence Focus)** is strongly Rho-sensitive under iid Uniform
  and Poisson: it excels at low Rho but degrades substantially at Rho = 0.20--0.50.
  This reflects its deterministic assignment's interaction with outcome spatial
  autocorrelation.
- **Design 1 (Checkerboard)** consistently occupies rank 6 across all Rho values,
  confirming its failure is not a high-Rho artifact.
- **Designs 4, 5, 7** show stable relative positions --- no major rank crossovers
  among themselves across Rho levels.

## Effect of Spillover Magnitude (Gamma)

```{r q2-gamma-trajectories, eval=mle_avail, fig.cap="Design rank trajectories across Gamma. Gamma controls the magnitude of treatment spillover to neighbors. Unlike Rho, Gamma has minimal effect on design rankings under MLE: all trajectory lines are nearly flat, confirming Gamma is not a discriminating factor for design selection.", fig.height=8.0}
p_list2 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_rank_trajectories(mle_cfgs[[i]], "Gamma", cfg_names[i],
                         point_size = 2.5, line_size = 0.9, label_size = 2.0) +
    theme(legend.position = if (i == length(mle_cfgs)) "right" else "none",
          plot.title    = element_text(size = 9),
          plot.subtitle = element_text(size = 8),
          axis.text     = element_text(size = 8),
          axis.title    = element_text(size = 9),
          legend.text   = element_text(size = 8),
          legend.title  = element_text(size = 9))
})
gridExtra::grid.arrange(grobs = p_list2, ncol = 1)
```

**Findings:** Gamma (spillover magnitude) has virtually no effect on design rankings.
All six designs maintain their relative ranks across Gamma = 0.5 to 0.8 within every
incidence config. This is consistent with the sensitivity analysis finding that
Gamma explains less than 5\% of MSE variance (eta-squared $< 0.05$) for all designs.
Researchers need not tailor design selection to anticipated spillover magnitude.

## Marginal Ranking Tables

The following tables report average MSE (and rank in parentheses) at each level
of each key parameter, averaged over all other simulation parameters.

```{r q2-marginal-tables, eval=mle_avail, results='asis'}
params_to_show <- c("Rho", "Gamma", "Spillover_Type")

for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  overall_order <- rank_designs_by_group(cfg, character(0)) %>%
    arrange(Rank) %>% pull(Design)

  cap_safe_nm <- gsub("_", " ", cfg_nm)
  cat(sprintf("\n### %s\n\n", cfg_nm))

  for (param in params_to_show) {
    ranked <- rank_designs_by_group(cfg, param) %>%
      mutate(cell = sprintf("%.4f (#%d)", Avg_MSE, Rank)) %>%
      select(Design, all_of(param), cell) %>%
      pivot_wider(names_from = all_of(param), values_from = cell,
                  names_prefix = paste0(param, "=")) %>%
      mutate(Design = factor(Design, levels = overall_order)) %>%
      arrange(Design) %>%
      mutate(Design = short_design_name(as.character(Design)))

    param_label <- switch(param,
      "Rho"          = "Rho (outcome spatial autocorrelation)",
      "Gamma"        = "Gamma (spillover magnitude)",
      "Spillover_Type" = "Spillover Type",
      param)

    tbl_out <- kable(ranked, booktabs = TRUE, linesep = "",
          caption = sprintf(
            "%s | Marginal rankings by %s. Each cell = Avg\\_MSE (\\#Rank) at that parameter level, averaged over all other parameters.",
            cap_safe_nm, param_label)) %>%
      kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                    font_size = 8) %>%
      row_spec(1, bold = TRUE)
    print(tbl_out)
    cat("\n")
  }
}
```

**Key takeaway from the Spillover\_Type marginal table:** The most striking pattern
across all configs is the **rank reversal between Design 3 and Design 7 by spillover
type**:

- Under **"both"** spillover (treatment and control units both experience spillover),
  **Design 7 (Balanced Quartiles)** often ranks 1st or 2nd with the lowest MSE.
- Under **"control\_only"** spillover (only untreated units experience spillover from
  neighbors), **Design 3 (Saturation Quadrants)** consistently ranks 1st with clear
  separation from the field.

This is the single most actionable finding for practitioners: **if the spillover
mechanism is known a priori, the design choice should reflect it.** When uncertain,
Design 3 is the safer default as it achieves the better average across both types.

# Q3: Best Design for Parameter Combinations

## Rho x Gamma Best-Design Maps

```{r q3-heatmaps, eval=mle_avail, fig.cap="Best design heatmap: Rho vs. Gamma for each incidence config. Each tile shows which design achieves the lowest average MSE at that (Rho, Gamma) combination, averaged over Spillover\\_Type and Neighbor\\_Type. Tile text shows the winning design abbreviation and its average MSE.", fig.height=8.0}
p_list3 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_best_design_heatmap(mle_cfgs[[i]], "Rho", "Gamma", cfg_names[i],
                           text_size = 3, text_color = "white",
                           compact_labels = TRUE) +
    labs(title = cfg_names[i], subtitle = NULL) +
    theme(plot.title  = element_text(size = 9, face = "bold"),
          axis.text   = element_text(size = 8),
          axis.title  = element_text(size = 9),
          legend.position = "none")
})
gridExtra::grid.arrange(grobs = p_list3, ncol = 2)
```

**How to read the maps:** Each tile corresponds to one (Rho, Gamma) combination.
The fill color identifies the winning design (consistent color scheme across panels).
The text shows the abbreviated design name and its average MSE at that combination.

**Findings:**

- **Design 3 dominates most of the Rho x Gamma space** across all configs. The
  sole consistent exception occurs at low Rho (0.00--0.01) in iid Uniform and
  Poisson configs, where Design 2 (High Incidence Focus) or Design 7 (Balanced
  Quartiles) occasionally wins.
- **MSE is largely insensitive to Gamma** (the tiles within a Rho row are
  similar in MSE). This re-confirms the Gamma insensitivity finding from Q2.
- **MSE increases with Rho**, especially for Design 1, but the relative ranking
  of Designs 2--7 is stable. Design 3 is the best choice regardless of anticipated
  spatial autocorrelation.

## Rho x Spillover Type Best-Design Maps

```{r q3-heatmaps-spill, eval=mle_avail, fig.cap="Best design heatmap: Rho vs. Spillover\\_Type for each incidence config. This reveals the key interaction: under both-direction spillover, the winner sometimes switches from Design 3 to Design 7 at low Rho.", fig.height=7.5}
p_list4 <- lapply(seq_along(mle_cfgs), function(i) {
  plot_best_design_heatmap(mle_cfgs[[i]], "Rho", "Spillover_Type", cfg_names[i],
                           text_size = 3, text_color = "white",
                           compact_labels = TRUE) +
    labs(title = cfg_names[i], subtitle = NULL) +
    theme(plot.title  = element_text(size = 9, face = "bold"),
          axis.text   = element_text(size = 8),
          axis.title  = element_text(size = 9),
          legend.position = "none")
})
gridExtra::grid.arrange(grobs = p_list4, ncol = 2)
```

**Key finding:** The Rho x Spillover\_Type heatmap reveals the most practically
important interaction:

- When spillover is **"control\_only"**: Design 3 wins across all Rho levels and
  all configs without exception.
- When spillover is **"both"**: Design 7 competes strongly with Design 3, winning
  at low Rho in several configs (iid Uniform, Spatial, Poisson).

This interaction is the primary driver of the overall MSE competition between
Designs 3 and 7. In the absence of prior knowledge about spillover direction,
Design 3 is recommended because its control\_only advantage more than compensates
for its slight "both" disadvantage.

# Per-Config Narrative Findings

This section synthesizes the analytical results for each incidence configuration
into a cohesive narrative, presenting the six structured findings produced by
`generate_commentary()`.

```{r per-config-commentary, eval=mle_avail, results='asis'}
for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  cap_safe_nm <- gsub("_", " ", cfg_nm)

  # --- Compute all findings ---
  overall <- rank_designs_by_group(cfg, character(0))
  best_row  <- overall %>% filter(Rank == 1)
  worst_row <- overall %>% filter(Rank == max(Rank))
  second_row <- overall %>% filter(Rank == 2)

  best_name  <- short_design_name(best_row$Design[1])
  worst_name <- short_design_name(worst_row$Design[1])
  second_name <- short_design_name(second_row$Design[1])

  # Pairwise dominance
  scenario_ids <- c("Neighbor_Type", "Rho", "Gamma", "Spillover_Type")
  wide <- cfg %>%
    select(all_of(c(scenario_ids, "Design", "MSE"))) %>%
    pivot_wider(names_from = Design, values_from = MSE, id_cols = all_of(scenario_ids))
  dom_vs_second <- round(mean(wide[[best_row$Design[1]]] < wide[[second_row$Design[1]]], na.rm=TRUE)*100, 1)
  dom_vs_worst  <- round(mean(wide[[best_row$Design[1]]] < wide[[worst_row$Design[1]]], na.rm=TRUE)*100, 1)

  # Rank stability
  rho_ranks   <- rank_designs_by_group(cfg, "Rho")   %>% filter(Design == best_row$Design[1])
  gamma_ranks <- rank_designs_by_group(cfg, "Gamma") %>% filter(Design == best_row$Design[1])
  rho_stable   <- all(rho_ranks$Rank == 1)
  gamma_stable <- all(gamma_ranks$Rank == 1)
  stable_str   <- if (rho_stable && gamma_stable) {
    "holds rank 1 at every level of Rho and Gamma (no rank crossover)"
  } else if (rho_stable) {
    "stable across all Rho levels but shows minor rank changes across Gamma"
  } else if (gamma_stable) {
    sprintf("stable across all Gamma levels; briefly cedes rank 1 at Rho = %s",
            paste(rho_ranks$Rho[rho_ranks$Rank != 1], collapse = ", "))
  } else {
    "shows rank reversals across both Rho and Gamma levels"
  }

  # Sensitivity
  params <- c("Rho", "Gamma", "Spillover_Type", "Neighbor_Type")
  d_data <- cfg %>% filter(Design == best_row$Design[1])
  gm     <- mean(d_data$MSE, na.rm=TRUE)
  ss_tot <- sum((d_data$MSE - gm)^2, na.rm=TRUE)
  eta_sq <- sapply(params, function(p) {
    gs <- d_data %>% group_by(.data[[p]]) %>%
      summarise(gm2 = mean(MSE, na.rm=TRUE), gn = n(), .groups="drop")
    ss_b <- sum(gs$gn * (gs$gm2 - gm)^2)
    if (ss_tot > 0) ss_b / ss_tot else 0
  })
  names(eta_sq) <- params
  top_param <- names(which.max(eta_sq))
  low_params <- names(eta_sq[eta_sq < 0.05])

  # MSE ratio
  mse_ratio <- round(worst_row$Avg_MSE[1] / best_row$Avg_MSE[1], 1)
  pct_vs_second <- round((second_row$Avg_MSE[1] - best_row$Avg_MSE[1]) / best_row$Avg_MSE[1] * 100, 1)

  # --- Print ---
  cat(sprintf("## %s\n\n", cfg_nm))

  cat(sprintf(
    "**Finding 1 -- Overall Winner:** %s achieves the lowest average MSE
    (%.4f) across all 64 scenarios in this incidence configuration. The runner-up
    is %s (avg MSE = %.4f), which is %.1f\\%% higher.\n\n",
    best_name, best_row$Avg_MSE[1],
    second_name, second_row$Avg_MSE[1],
    pct_vs_second
  ))

  cat(sprintf(
    "**Finding 2 -- Dominance:** %s achieves lower MSE than the runner-up (%s)
    in %.1f\\%% of individual scenarios, and beats the worst performer (%s)
    in %.1f\\%% of scenarios. A dominance percentage above 50\\%% means the
    design is likely better in any given scenario, not just on average.\n\n",
    best_name, second_name, dom_vs_second,
    worst_name, dom_vs_worst
  ))

  cat(sprintf(
    "**Finding 3 -- Robustness:** %s %s. This means practitioners
    do not need to know the exact value of Rho or Gamma to trust this design
    recommendation.\n\n",
    best_name, stable_str
  ))

  cat(sprintf(
    "**Finding 4 -- Coverage:** %s achieves average 95\\%% CI coverage of %.3f
    (nominal = 0.95). The worst design (%s) achieves only %.3f, meaning its
    confidence intervals are severely anti-conservative and should not be used
    for inference.\n\n",
    best_name, best_row$Avg_Coverage[1],
    worst_name, worst_row$Avg_Coverage[1]
  ))

  cat(sprintf(
    "**Finding 5 -- Sensitivity:** For %s, the most influential simulation
    parameter is %s (eta-squared = %.3f), accounting for %.1f\\%% of the
    design's MSE variation across scenarios. ",
    best_name, top_param, eta_sq[top_param], eta_sq[top_param] * 100
  ))
  if (length(low_params) > 0) {
    cat(sprintf(
      "Parameters with negligible influence (eta-squared $< 0.05$): %s.
      These can be safely ignored when selecting this design.\n\n",
      paste(low_params, collapse = ", ")
    ))
  } else {
    cat("All parameters have non-negligible influence on this design's MSE.\n\n")
  }

  cat(sprintf(
    "**Finding 6 -- Practical Recommendation:** Under %s incidence, select
    %s for treatment assignment. It provides %.1fx lower MSE than the worst
    design and near-nominal coverage (%.3f), making it both accurate and
    inferentially valid across the full range of tested parameter values.\n\n",
    cfg_nm, best_name, mse_ratio, best_row$Avg_Coverage[1]
  ))
}
```

# Scenario-Specific Design Lookup

For practitioners who can specify all four scenario parameters (Rho, Gamma,
Spillover\_Type, Neighbor\_Type), the following tables provide exact design
rankings for a selection of illustrative scenarios.

```{r scenario-lookups, eval=mle_avail, results='asis'}
# Define two representative scenarios to display for each config
scenario_specs <- list(
  list(rho = 0.20, gamma = 0.7, spill = "both",         nb = "queen",
       label = "Moderate Rho, Both Spillover, Queen"),
  list(rho = 0.50, gamma = 0.8, spill = "control_only", nb = "rook",
       label = "High Rho, Control-Only Spillover, Rook")
)

for (cfg_nm in cfg_names) {
  cfg <- mle_cfgs[[cfg_nm]]
  cap_safe_nm <- gsub("_", " ", cfg_nm)
  cat(sprintf("\n## %s\n\n", cfg_nm))

  for (spec in scenario_specs) {
    filtered <- cfg %>%
      filter(Rho == spec$rho, Gamma == spec$gamma,
             Spillover_Type == spec$spill, Neighbor_Type == spec$nb)

    if (nrow(filtered) == 0) next

    ranked <- rank_designs_by_group(filtered, character(0)) %>%
      mutate(
        Design       = short_design_name(Design),
        Avg_MSE      = round(Avg_MSE, 4),
        Avg_Coverage = round(Avg_Coverage, 3),
        Avg_Bias     = sprintf("%+.4f", Avg_Bias),
        Avg_SD       = round(Avg_SD, 4)
      ) %>%
      select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias, Avg_SD)

    best_r    <- ranked %>% filter(Rank == 1)
    second_r  <- ranked %>% filter(Rank == 2)
    pct_gap   <- round((as.numeric(second_r$Avg_MSE[1]) - as.numeric(best_r$Avg_MSE[1])) /
                         as.numeric(best_r$Avg_MSE[1]) * 100, 1)

    spill_display <- gsub("_", "-", spec$spill)   # "control-only" avoids LaTeX _ issue
    tbl_out <- kable(ranked, booktabs = TRUE, linesep = "", align = "rlrrrr",
          col.names = c("Rank", "Design", "MSE", "Coverage", "Bias", "SD"),
          caption = sprintf(
            "%s | Scenario: %s (Rho=%.2f, Gamma=%.1f, Spillover=%s, Neighbor=%s). Winner MSE %.1f\\%% lower than runner-up.",
            cap_safe_nm, spec$label,
            spec$rho, spec$gamma, spill_display, spec$nb, pct_gap)) %>%
      kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
      row_spec(1, bold = TRUE)
    print(tbl_out)
    cat("\n")
  }
}
```

**How to use the lookup tables:** Identify the row that matches your anticipated
trial parameters. The design at Rank 1 is recommended. The ``Bias'' column
shows whether estimates are systematically above or below $\tau = 1.0$; a Bias
close to 0 with high Coverage indicates that both point estimates and confidence
intervals are reliable.

# Practical Design Selection Guide

## Decision Framework

The following guide summarizes when to deviate from the global recommendation
of Design 3 (Saturation Quadrants):

```{r decision-table, results='asis'}
decision_df <- data.frame(
  Situation = c(
    "Default (uncertain parameters)",
    "Spillover mechanism is 'both' AND Rho is low (< 0.10)",
    "Incidence is iid Uniform AND Rho is very low (0.00)",
    "Incidence has high spatial clustering AND Rho is very high (0.50)",
    "ANY scenario",
    "ANY scenario"
  ),
  Recommended = c(
    "Design 3: Saturation Quadrants",
    "Design 7: Balanced Quartiles (wins marginally)",
    "Design 2: High Incidence Focus (competitive at Rho=0)",
    "Design 3: Saturation Quadrants (still wins)",
    "Avoid Design 1: Checkerboard (always worst)",
    "Avoid Design 5: 2x2 Blocking under queen contiguity (MSE 2x rook)"
  ),
  Justification = c(
    "Ranks 1st in all 5 configs, all Gamma levels; only slight risk at very low Rho with both-spillover",
    "Designs 3 and 7 are nearly tied; 7 holds a small advantage in this corner",
    "Design 2's deterministic targeting of high-incidence clusters aligns with iid assignment",
    "Design 3's random quadrant saturation provides sufficient spatial variation for MLE estimation",
    "Invalid CIs (coverage 0.53-0.57); MSE 8-11x higher than winner",
    "Queen contiguity amplifies 2x2 block effects; rook contiguity is substantially better for this design"
  )
)

kable(decision_df, booktabs = TRUE, linesep = "",
      col.names = c("Situation", "Recommended Design", "Justification"),
      caption = "Practical design selection guide. 'Default' applies when the
      spillover type and Rho are not known prior to design.") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "6cm") %>%
  row_spec(1, bold = TRUE)
```

## Why Design 3 Wins: Mechanistic Explanation

Design 3 (Saturation Quadrants) works as follows: the $10 \times 10$ grid is
divided into four $5 \times 5$ quadrants, and each quadrant receives a random
treatment saturation level drawn from Uniform(0.2, 0.8). Within each quadrant,
clusters are randomly selected for treatment at the assigned saturation rate.

This design outperforms others because:

1. **Quadrant-level saturation variation creates spatial contrast.** The MLE
   estimator (`lagsarlm`) must disentangle the direct treatment effect $\tau$
   from the spatial lag parameter $\rho$. When treatment is uniformly distributed
   (Checkerboard) or strongly correlated with incidence (High Incidence Focus at
   high Rho), this separation is harder. Variable saturation provides information
   about how outcomes change as treatment density changes spatially.

2. **Randomness within quadrants prevents systematic confounding.** Unlike Design
   1 (perfectly regular) or Design 2 (purely incidence-driven), Design 3
   introduces idiosyncratic variation that is uncorrelated with spatially-structured
   incidence or outcome patterns.

3. **Quadrant-level structure respects spatial scale.** The $5 \times 5$ quadrant
   blocks match the scale at which spatial autocorrelation operates (rook/queen
   neighborhoods), providing richer contrast than finer (2x2) or coarser structures.

## Why Design 1 Fails: Mechanistic Explanation

Design 1 (Checkerboard) assigns treatment in a perfectly alternating $\{0,1,0,1,...\}$
pattern. This creates a fundamental identification problem:

- The treatment assignment vector $Z$ is a deterministic function of position on
  the grid.
- The spatial weight matrix $W$ encodes neighbor relationships, which are also
  determined by position.
- Therefore, $Z$ and $W \cdot Z$ (the spillover term) are collinear with the
  spatial lag of the outcome $W \cdot Y$ that the SAR model needs to estimate
  $\rho$.

This collinearity inflates variance, biases $\hat{\tau}$, and degrades coverage ---
all of which are observed in the simulation results.

# Summary of Key Results

```{r summary-table, eval=mle_avail, results='asis'}
overall_summary <- rank_designs_by_group(mle_results %>%
    filter(TRUE),
  character(0)) %>%
  mutate(
    Design       = short_design_name(Design),
    Avg_MSE      = round(Avg_MSE, 4),
    Avg_Coverage = round(Avg_Coverage, 3),
    Avg_Bias     = round(Avg_Bias, 4)
  ) %>%
  select(Rank, Design, Avg_MSE, Avg_Coverage, Avg_Bias, N_Scenarios)

kable(overall_summary, booktabs = TRUE, linesep = "", align = "rlrrrr",
      col.names = c("Rank", "Design", "Avg MSE", "Avg Coverage",
                    "Avg Bias", "N Scenarios"),
      caption = "Overall MLE design rankings averaged across all 1,920 scenarios
      (all incidence configs combined). NOTE: for formal analysis, always use
      per-config rankings; this table is for high-level orientation only.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
  row_spec(1, bold = TRUE) %>%
  row_spec(nrow(overall_summary), color = "gray")
```

```{r final-conclusions, results='asis'}
if (mle_avail) {
  overall <- rank_designs_by_group(mle_results %>% filter(TRUE), character(0))
  best <- overall %>% filter(Rank == 1)
  worst <- overall %>% filter(Rank == max(Rank))
  ratio <- round(worst$Avg_MSE / best$Avg_MSE, 1)
  best_short <- short_design_name(best$Design[1])
  worst_short <- short_design_name(worst$Design[1])
}
```

**Conclusions:**

1. **Universal recommendation:** Under MLE estimation, **`r if(mle_avail) best_short`**
   is the best treatment assignment design across all incidence modes, Rho levels,
   and Gamma levels tested. It achieves `r if(mle_avail) ratio[1]`x lower MSE than
   the worst design.

2. **Spillover type is the key moderator.** When spillover direction is "both"
   (treated and control units both experience spillover), Design 7 (Balanced
   Quartiles) becomes competitive and should be considered. When spillover is
   "control\_only", Design 3's advantage is unambiguous.

3. **Design 1 (Checkerboard) should never be used.** Its perfectly regular spatial
   structure creates collinearity that invalidates both point estimates and confidence
   intervals under the MLE spatial autoregressive model.

4. **Gamma does not affect design choice.** Regardless of the anticipated spillover
   magnitude (0.5 to 0.8), the design ranking is stable. Researchers can ignore
   this parameter when selecting a design.

5. **Coverage is near-nominal for leading designs.** Under MLE, Designs 3, 7, 4,
   and 2 all achieve 93--97\% coverage across the tested scenarios, confirming that
   MLE-based inference is valid when a well-chosen spatial design is used.

---

# References

- Mirzaei, A. et al. (2019). Sudden unexpected death rates.
  *(SUD base rate 35/100,000)*
- LeSage, J. \& Pace, R.K. (2009). *Introduction to Spatial Econometrics*. CRC Press.
- Bivand, R., et al. `spdep` R package.
- Bivand, R. \& Piras, G. `spatialreg` R package.
- R packages used: `dplyr`, `tidyr`, `ggplot2`, `viridis`, `knitr`,
  `kableExtra`, `gridExtra`, `digest`

---

# Appendix: Output Files

```{r appendix-files, results='asis'}
files_df <- data.frame(
  File = c(
    "MLE_combined_design_recommendations.pdf",
    "sim_results_MLE_combined_20260305_150742.rds",
    "MLE_design_recommendation_report.pdf"
  ),
  Contents = c(
    "Raw figure output: all recommendation plots (27 pages)",
    "Source data: 1,920 MLE scenarios x 13 columns",
    "This narrative companion report"
  ),
  Location = c("results/", "results/", "results/")
)
kable(files_df, booktabs = TRUE, linesep = "",
      caption = "Output files for the design recommendation analysis.") %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```
