---
title: "Statistical Comparison of Treatment Assignment Designs"
subtitle: "Formal Hypothesis Testing for Design Selection in Spatial CRTs"
author: "Andrew Walther"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    theme: cosmo
    smooth-scroll: true
    code-fold: true
    code-summary: "Show code"
    self-contained: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    latex-engine: xelatex
    keep-tex: false
    fig-pos: "htbp"
    fig-height: 4
    fig-width: 6.5
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{float}
        \usepackage{amsmath}
        \usepackage{amssymb}
        \usepackage{geometry}
        \usepackage{xcolor}
        \usepackage{mdframed}
        \geometry{margin=1in}
        \floatplacement{figure}{htbp}
        \floatplacement{table}{H}
        \definecolor{boxbg}{RGB}{240,248,255}
        \definecolor{boxframe}{RGB}{70,130,180}
---

```{r setup}
#| include: false
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.pos = "htbp"
)
```

```{r load-packages}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(viridis)
library(knitr)
library(kableExtra)
library(PMCMRplus)
library(patchwork)
```

```{r resolve-paths}
#| include: false
script_dir <- tryCatch(
  normalizePath(dirname(knitr::current_input(dir = TRUE))),
  error = function(e) {
    tryCatch(
      normalizePath(dirname(sys.frame(1)$ofile)),
      error = function(e2) normalizePath(getwd())
    )
  }
)
results_dir <- file.path(dirname(script_dir), "results")
```

```{r source-modules}
#| include: false
source(file.path(script_dir, "10_statistical_comparisons.R"))
```

```{r load-results}
#| include: false
mle_results <- load_latest_results(results_dir, estimation_mode = "MLE_combined")
n_scenarios <- nrow(mle_results)
n_designs <- length(unique(mle_results$Design))
n_blocks <- n_scenarios / n_designs
```

```{r run-tests}
#| include: false
# Run all core tests
fr  <- run_friedman_test(mle_results)
nem <- run_nemenyi_posthoc(mle_results)
wil <- run_pairwise_wilcoxon(mle_results)

# Run conditional tests
cond_params <- c("Rho", "Gamma", "Spillover_Type", "Neighbor_Type", "Incidence_Mode")
cond_results <- list()
cond_summaries <- list()
for (param in cond_params) {
  cr <- run_conditional_tests(mle_results, param)
  cond_results[[param]] <- cr
  cond_summaries[[param]] <- summarize_conditional_tests(cr)
}
```

# Introduction

This report presents formal statistical hypothesis tests to compare the performance of `r n_designs` treatment assignment designs evaluated in the IncidenceDesign simulation study for Spatial Cluster Randomized Trials (CRTs). While prior analyses have characterized design performance descriptively using mean MSE, coverage probability, and win-rate rankings, these comparisons lack the statistical rigor needed to declare one design significantly better than another.

The central question is: **can we provide statistical evidence that certain designs yield significantly better estimation accuracy (lower MSE for $\hat{\tau}$) than others?** Answering this question is essential for providing actionable guidance to investigators planning future spatial CRTs.

The simulation evaluated `r n_scenarios` scenarios spanning `r n_blocks` unique parameter combinations, with each combination tested under all `r n_designs` designs. This paired structure is exploited by the non-parametric tests described below.

# Methods

## Overview of the Comparison Problem

We seek to determine whether the `r n_designs` treatment assignment designs differ *significantly* in their ability to estimate the treatment effect $\tau$, as measured by MSE. This is fundamentally a **multiple treatment comparison** problem: we have $k = `r n_designs`$ designs, each observed under the same set of experimental conditions (parameter combinations), and we wish to test whether any design is systematically better or worse.

Because the same data-generating conditions are shared across all designs within each parameter combination, we have a **paired / blocked** experimental structure. Standard parametric tests (e.g., repeated-measures ANOVA) assume normally distributed residuals, which may not hold for MSE values. We therefore use **non-parametric rank-based tests** that make no distributional assumptions.

The total number of unique pairwise comparisons among $k = `r n_designs`$ designs is:
$$\binom{k}{2} = \binom{`r n_designs`}{2} = `r choose(n_designs, 2)`$$

## Blocking Structure

Each scenario is defined by a unique combination of simulation parameters:

| Parameter | Levels | Count |
|-----------|--------|:-----:|
| Incidence Mode | iid, spatial, poisson (with $\rho_X \in \{0.20, 0.50\}$) | 5 configs |
| Neighbor Type | rook, queen | 2 |
| $\rho$ (outcome spatial autocorrelation) | 0.00, 0.01, 0.20, 0.50 | 4 |
| $\gamma$ (spillover magnitude) | 0.50, 0.60, 0.70, 0.80 | 4 |
| Spillover Type | control-only, bidirectional | 2 |

This produces $5 \times 2 \times 4 \times 4 \times 2 = `r n_blocks`$ **blocks**. Within each block, all `r n_designs` designs were evaluated under identical data-generating conditions, creating a natural repeated-measures / paired design. The metric of interest is the **Mean Squared Error (MSE)** of the MLE estimator $\hat{\tau}$ for the true treatment effect $\tau = 1.0$.

Each design's MSE per block is aggregated from 250 simulation iterations (25 treatment assignment resamples $\times$ 10 outcome resamples).

## Friedman Test (Omnibus)

The **Friedman test** (Friedman, 1937) is a non-parametric alternative to one-way repeated-measures ANOVA. It is the standard method for comparing multiple treatments or methods measured under matched conditions.

**Procedure:** Within each of the $N = `r n_blocks`$ blocks, the $k = `r n_designs`$ designs are ranked by MSE (rank 1 = lowest MSE = best performance). The test then evaluates whether the average ranks differ across designs more than expected by chance.

**Hypotheses:**

- $H_0$: All $k$ designs have equal average MSE ranks across the $N$ blocks. No design is systematically better or worse.
- $H_1$: At least one design's average rank differs from the others.

The Friedman test statistic is:
$$Q = \frac{12N}{k(k+1)} \left[\sum_{j=1}^{k} \bar{R}_j^2 - \frac{k(k+1)^2}{4}\right]$$

where $\bar{R}_j$ is the average rank of design $j$ across all blocks. Under $H_0$, $Q$ follows a $\chi^2$ distribution with $k - 1 = `r n_designs - 1`$ degrees of freedom.

> **Reference:** Friedman, M. (1937). The use of ranks to avoid the assumption of normality implicit in the analysis of variance. *Journal of the American Statistical Association*, 32(200), 675-701.

## Nemenyi Post-hoc Test

When the Friedman test rejects $H_0$ (indicating at least one design differs), we need post-hoc pairwise comparisons to identify *which* designs differ. The **Nemenyi test** (Nemenyi, 1963) is the non-parametric analogue of the Tukey HSD test and controls the **family-wise error rate** across all $\binom{k}{2} = `r choose(n_designs, 2)`$ simultaneous comparisons.

Two designs $i$ and $j$ are declared significantly different at level $\alpha$ if and only if their average rank difference $|\bar{R}_i - \bar{R}_j|$ exceeds the **Critical Difference (CD)**:

$$CD = \frac{q_{\alpha, k, \infty}}{\sqrt{2}} \times \sqrt{\frac{k(k+1)}{6N}}$$

where $q_{\alpha, k, \infty}$ is the critical value of the Studentized range distribution with $k$ groups and infinite degrees of freedom, $k = `r n_designs`$, and $N = `r n_blocks`$ blocks.

Results are presented as a **Critical Difference (CD) diagram** (introduced to the machine learning community by Demšar, 2006). In this diagram:

- Designs are placed on a horizontal number line by their **average rank** (lower = better MSE).
- Thick horizontal bars connect groups of designs that are **NOT** significantly different from each other — these form **equivalence groups**.
- If two designs are *not* connected by a shared bar, their performance difference *is* statistically significant.
- A red arrow at the bottom shows the CD scale for reference.

> **References:**
>
> - Nemenyi, P.B. (1963). *Distribution-free multiple comparisons*. Ph.D. dissertation, Princeton University.
> - Demšar, J. (2006). Statistical comparisons of classifiers over multiple data sets. *Journal of Machine Learning Research*, 7, 1-30.

## Pairwise Wilcoxon Signed-Rank Tests

As a **sensitivity analysis** and to provide a more widely-known test alongside the Friedman/Nemenyi framework, we also perform pairwise **Wilcoxon signed-rank tests** (Wilcoxon, 1945) on the paired MSE values.

**Hypotheses (for each pair of designs $i, j$):**

- $H_0$: The distribution of paired MSE differences $(\text{MSE}_i - \text{MSE}_j)$ is symmetric about zero. That is, designs $i$ and $j$ have equivalent MSE performance.
- $H_1$: The distribution is not symmetric about zero. One design systematically outperforms the other.

This yields `r choose(n_designs, 2)` individual tests. To control the **family-wise error rate** across all tests, p-values are adjusted using the **Holm step-down procedure** (Holm, 1979), which is uniformly more powerful than Bonferroni correction while still controlling the Type I error rate.

> **References:**
>
> - Wilcoxon, F. (1945). Individual comparisons by ranking methods. *Biometrics Bulletin*, 1(6), 80-83.
> - Holm, S. (1979). A simple sequentially rejective multiple test procedure. *Scandinavian Journal of Statistics*, 6(2), 65-70.

## Significance Notation

Throughout this report, statistical significance is indicated using the following star notation:

| Symbol | Meaning | Interpretation |
|:------:|---------|----------------|
| `***` | $p < 0.001$ | Very strong evidence against $H_0$ |
| `**` | $p < 0.01$ | Strong evidence against $H_0$ |
| `*` | $p < 0.05$ | Moderate evidence against $H_0$ |
| `ns` | $p \geq 0.05$ | Insufficient evidence to reject $H_0$ |

# Results: Aggregate Analysis {#sec-aggregate}

## Friedman Omnibus Test

```{r friedman-result}
friedman_df <- data.frame(
  Statistic = sprintf("%.2f", fr$statistic),
  df = fr$n_designs - 1,
  `P-value` = format.pval(fr$p_value, digits = 3),
  `N Blocks` = fr$n_blocks,
  Decision = ifelse(fr$p_value < 0.05, "Reject H0", "Fail to reject H0"),
  check.names = FALSE
)
kable(friedman_df, caption = "Friedman omnibus test result.",
      align = "c") %>%
  kable_styling(full_width = FALSE, position = "center")
```

The Friedman test yields $\chi^2 = `r sprintf("%.2f", fr$statistic)`$ with $`r n_designs - 1`$ degrees of freedom ($p `r ifelse(fr$p_value < 2.2e-16, "< 2.2 \\times 10^{-16}", sprintf("= %.4f", fr$p_value))`$). We **reject the null hypothesis**: there is overwhelming evidence that the `r n_designs` designs differ in their MSE performance.

## Average Ranks

```{r avg-ranks-table}
rank_df <- data.frame(
  Design = names(fr$avg_ranks),
  `Average Rank` = sprintf("%.3f", fr$avg_ranks),
  `Rank Position` = seq_along(fr$avg_ranks),
  check.names = FALSE
)
kable(rank_df, caption = "Designs ordered by average MSE rank across all scenarios (1 = best).",
      align = c("l", "c", "c")) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  row_spec(1:2, bold = TRUE)
```

Designs 3 (Saturation Quadrants) and 8 (Incidence-Guided Saturation Quadrants) occupy the top two positions with nearly identical average ranks (`r sprintf("%.3f", fr$avg_ranks[1])` and `r sprintf("%.3f", fr$avg_ranks[2])`), while Design 1 (Checkerboard) ranks last at `r sprintf("%.3f", fr$avg_ranks[length(fr$avg_ranks)])`.

## Critical Difference Diagram {#sec-cd-diagram}

```{r cd-diagram}
#| fig-cap: "Critical Difference diagram. Designs are placed by average MSE rank (lower = better). Horizontal bars connect designs that are NOT significantly different at the 0.05 level. The red arrow shows the critical difference scale."
#| fig-height: 4
#| fig-width: 6.5
plot_cd_diagram(nem)
```

**How to read this diagram:** Each design is positioned on the number line by its average rank across all `r n_blocks` blocks (lower = better). The thick dark bars above the axis connect designs that are **statistically equivalent** — i.e., their pairwise Nemenyi p-value is $\geq 0.05$. Designs that do *not* share a bar are significantly different from each other.

The red double-arrow labeled "CD" at the bottom shows the **Critical Difference** threshold: if two designs are separated by more than this distance on the rank axis, their difference is statistically significant.

```{r cd-groups}
groups <- find_cd_groups(nem$avg_ranks, nem$p_matrix, 0.05)
```

The CD diagram reveals **`r length(groups)` equivalence group(s)**:

```{r cd-groups-list}
#| results: asis
for (i in seq_along(groups)) {
  cat(sprintf("- **Group %d**: %s (avg ranks %.2f -- %.2f)\n", i,
              paste(groups[[i]], collapse = ", "),
              min(nem$avg_ranks[groups[[i]]]),
              max(nem$avg_ranks[groups[[i]]])))
}
```

The Nemenyi critical difference is **CD = `r sprintf("%.3f", nem$critical_diff)`** at $\alpha = 0.05$. Designs whose average rank difference exceeds `r sprintf("%.3f", nem$critical_diff)` are declared significantly different.

## Pairwise Wilcoxon Results

```{r wilcoxon-summary}
n_sig_wil <- sum(wil$sig_matrix[upper.tri(wil$sig_matrix)])
n_nonsig_wil <- choose(n_designs, 2) - n_sig_wil
```

Of the `r choose(n_designs, 2)` pairwise comparisons, **`r n_sig_wil` are statistically significant** (Holm-adjusted $p < 0.05$) and `r n_nonsig_wil` are not.

```{r pvalue-heatmap-wilcoxon}
#| fig-cap: "Pairwise Wilcoxon signed-rank p-values (Holm-adjusted). Stars indicate significance: *** p < 0.001, ** p < 0.01, * p < 0.05, ns = not significant."
#| fig-height: 6
#| fig-width: 6.5
plot_pvalue_heatmap(wil, "Wilcoxon (Holm)")
```

```{r pvalue-heatmap-nemenyi}
#| fig-cap: "Pairwise Nemenyi post-hoc p-values from the Friedman test."
#| fig-height: 6
#| fig-width: 6.5
plot_pvalue_heatmap(nem, "Nemenyi")
```

The non-significant pairs (Wilcoxon) identify designs whose MSE performance is statistically indistinguishable:

```{r nonsig-pairs}
designs <- rownames(wil$p_matrix)
nonsig_pairs <- data.frame(Design_A = character(), Design_B = character(),
                           Wilcoxon_p = numeric(), Nemenyi_p = numeric(),
                           stringsAsFactors = FALSE)
for (i in 1:(length(designs) - 1)) {
  for (j in (i + 1):length(designs)) {
    if (!wil$sig_matrix[designs[i], designs[j]]) {
      nonsig_pairs <- rbind(nonsig_pairs, data.frame(
        Design_A = designs[i], Design_B = designs[j],
        Wilcoxon_p = wil$p_matrix[designs[i], designs[j]],
        Nemenyi_p = nem$p_matrix[designs[i], designs[j]],
        stringsAsFactors = FALSE
      ))
    }
  }
}
if (nrow(nonsig_pairs) > 0) {
  nonsig_pairs$Wilcoxon_p <- sprintf("%.4f", nonsig_pairs$Wilcoxon_p)
  nonsig_pairs$Nemenyi_p <- sprintf("%.4f", nonsig_pairs$Nemenyi_p)
  kable(nonsig_pairs,
        caption = "Design pairs with no significant MSE difference (Wilcoxon).",
        col.names = c("Design A", "Design B", "Wilcoxon p", "Nemenyi p"),
        align = "c") %>%
    kable_styling(full_width = FALSE, position = "center")
} else {
  cat("All pairwise comparisons are statistically significant.")
}
```

## MSE Distribution with Significance

The following boxplot shows the full distribution of scenario-level MSE values for each design, ordered by median MSE (best on the left). Brackets above the boxes with significance stars indicate pairwise comparisons from the Wilcoxon signed-rank test (Holm-adjusted). To avoid visual clutter, up to 8 key comparisons are shown, prioritizing those involving the best- and worst-performing designs.

```{r boxplot-stars}
#| fig-cap: "Boxplot of MSE by design (ordered by median MSE). Brackets with significance stars show Wilcoxon signed-rank test results (Holm-adjusted). Stars: *** p < 0.001, ** p < 0.01, * p < 0.05."
#| fig-height: 6
#| fig-width: 6.5
plot_mse_boxplot_with_stars(mle_results, wil)
```

# Results: Conditional Analysis {#sec-conditional}

To assess whether design rankings are **robust** across simulation conditions, we repeat the Friedman test within strata defined by individual parameters. If the Friedman test remains significant within every stratum and the best-ranked designs are consistent, the recommendation is robust.

```{r conditional-setup}
#| include: false
# Pre-compute conditional summaries for each parameter
all_cond_summary <- do.call(rbind, lapply(names(cond_summaries), function(param) {
  df <- cond_summaries[[param]]
  df$Parameter <- param
  df
}))
```

## Summary of Conditional Friedman Tests

```{r conditional-summary-table}
all_cond_summary$P_value_fmt <- ifelse(
  all_cond_summary$P_value < 2.2e-16,
  "< 2.2e-16",
  sprintf("%.2e", all_cond_summary$P_value)
)
all_cond_summary$Significant <- ifelse(all_cond_summary$P_value < 0.05, "Yes", "No")

display_df <- all_cond_summary %>%
  select(Parameter, Stratum, Chi_squared, P_value_fmt, N_blocks, Best_Group, Significant)

kable(display_df,
      caption = "Friedman test results within each parameter stratum. 'Best Group' lists designs in the top equivalence group (statistically indistinguishable from the best).",
      col.names = c("Parameter", "Stratum", "Chi-squared", "P-value",
                     "N Blocks", "Best Group", "Significant"),
      align = c("l", "l", "c", "c", "c", "l", "c")) %>%
  kable_styling(full_width = FALSE, font_size = 11, latex_options = c("hold_position", "scale_down"))
```

The Friedman test is **significant in every stratum** ($p < 2.2 \times 10^{-16}$ in all cases), indicating that design differences are not an artifact of any particular parameter setting.

## Conditional CD Diagrams

The following CD diagrams show how design rankings shift (or remain stable) across levels of key simulation parameters.

### By Outcome Spatial Autocorrelation ($\rho$)

```{r cd-rho}
#| fig-cap: "CD diagrams stratified by outcome spatial autocorrelation (Rho). Each panel shows one stratum."
#| fig-height: 7
#| fig-width: 6.5
cd_plots_rho <- plot_conditional_cd_diagrams(cond_results[["Rho"]], "Rho")
wrap_plots(cd_plots_rho, ncol = 2)
```

### By Spillover Magnitude ($\gamma$)

```{r cd-gamma}
#| fig-cap: "CD diagrams stratified by spillover magnitude (Gamma). Each panel shows one stratum."
#| fig-height: 7
#| fig-width: 6.5
cd_plots_gamma <- plot_conditional_cd_diagrams(cond_results[["Gamma"]], "Gamma")
wrap_plots(cd_plots_gamma, ncol = 2)
```

### By Spillover Type

```{r cd-spillover}
#| fig-cap: "CD diagrams stratified by spillover type."
#| fig-height: 3.5
#| fig-width: 6.5
cd_plots_spill <- plot_conditional_cd_diagrams(cond_results[["Spillover_Type"]], "Spillover_Type")
wrap_plots(cd_plots_spill, ncol = 2)
```

### By Neighbor Type

```{r cd-neighbor}
#| fig-cap: "CD diagrams stratified by neighbor type."
#| fig-height: 3.5
#| fig-width: 6.5
cd_plots_nb <- plot_conditional_cd_diagrams(cond_results[["Neighbor_Type"]], "Neighbor_Type")
wrap_plots(cd_plots_nb, ncol = 2)
```

### By Incidence Mode

```{r cd-incidence}
#| fig-cap: "CD diagrams stratified by incidence generation mode. Each panel shows one stratum."
#| fig-height: 9
#| fig-width: 6.5
cd_plots_inc <- plot_conditional_cd_diagrams(cond_results[["Incidence_Mode"]], "Incidence_Mode")
wrap_plots(cd_plots_inc, ncol = 2)
```

# Discussion

## Key Findings

```{r discussion-stats}
#| include: false
best_design <- names(fr$avg_ranks)[1]
second_design <- names(fr$avg_ranks)[2]
worst_design <- names(fr$avg_ranks)[length(fr$avg_ranks)]
best_rank <- fr$avg_ranks[1]
worst_rank <- fr$avg_ranks[length(fr$avg_ranks)]
rank_gap <- worst_rank - best_rank

# Check if best two are in same equivalence group
best_two_equiv <- !nem$sig_matrix[best_design, second_design]
best_worst_p <- wil$p_matrix[best_design, worst_design]
```

1. **Overwhelming evidence of design differences.** The Friedman test ($\chi^2 = `r sprintf("%.2f", fr$statistic)`$, $p `r ifelse(fr$p_value < 2.2e-16, "< 2.2 \\times 10^{-16}", sprintf("= %.4f", fr$p_value))`$) decisively rejects the null hypothesis that all designs perform equally. The average rank gap between the best (`r best_design`, rank `r sprintf("%.2f", best_rank)`) and worst (`r worst_design`, rank `r sprintf("%.2f", worst_rank)`) design is `r sprintf("%.2f", rank_gap)` on an 8-point scale.

2. **`r best_design` and `r second_design` are the top performers.** These two designs `r ifelse(best_two_equiv, "are statistically indistinguishable from each other (Nemenyi $p > 0.05$) and form", "together form")` the top equivalence group in the CD diagram. Both employ quadrant-based saturation strategies, with `r best_design` using random saturation assignment and `r second_design` guiding saturation by observed incidence.

3. **`r worst_design` (Checkerboard) is significantly worse than all other designs.** The pairwise comparison between `r best_design` and `r worst_design` yields $p `r ifelse(best_worst_p < 0.001, "< 0.001", sprintf("= %.4f", best_worst_p))`$ (Wilcoxon, Holm-adjusted). The checkerboard pattern, while intuitive, fails to account for spatial heterogeneity in outcomes.

4. **Rankings are robust across all simulation parameters.** The Friedman test is significant within every stratum tested (all $p < 2.2 \times 10^{-16}$), and the top designs remain consistent regardless of the level of spatial autocorrelation, spillover magnitude, spillover type, neighbor contiguity, or incidence generation mode.

## Implications for Study Design

For investigators planning a spatial CRT with spatially heterogeneous outcomes, these results provide strong statistical evidence to recommend **saturation quadrant designs** (`r best_design` or `r second_design`) over alternative strategies. The recommendation is not sensitive to specific assumptions about the data-generating process within the range of parameters explored.

In particular:

- **Avoid the Checkerboard design** (`r worst_design`) — it performs significantly worse than all alternatives under MLE estimation.
- **Saturation quadrant designs** leverage spatial structure by assigning different treatment saturation levels to different regions, which provides better identification of the treatment effect under spatial dependence.
- When prior incidence data is available, `r second_design` (Incidence-Guided) may offer a slight advantage by directing higher saturation to higher-incidence areas, though the improvement over `r best_design` is not statistically significant.

## Limitations

- **Fixed $\tau = 1.0$**: All tests condition on a single true treatment effect size. A planned sensitivity analysis varying $\tau \in \{0.8, 1.0, 1.5, 2.0, 3.0\}$ will assess robustness to effect size.
- **Oracle spillover**: The MLE estimator includes the true spillover covariate, which may not be available in practice.
- **Simulation-specific**: Results are specific to the 10×10 grid, SAR data-generating process, and parameter ranges explored.

# Conclusion

```{r conclusion-counts}
#| include: false
n_sig_nem <- sum(nem$sig_matrix[upper.tri(nem$sig_matrix)])
```

Using a Friedman test with Nemenyi post-hoc comparisons and corroborated by pairwise Wilcoxon signed-rank tests, we find:

- **`r n_sig_nem` of `r choose(n_designs, 2)` design pairs** are significantly different at the $\alpha = 0.05$ level (Nemenyi post-hoc), and **`r n_sig_wil` of `r choose(n_designs, 2)`** under the Wilcoxon signed-rank test with Holm correction.
- **`r best_design`** (Saturation Quadrants) and **`r second_design`** (Incidence-Guided Saturation Quadrants) are the recommended designs, forming the top equivalence group with average ranks of `r sprintf("%.2f", fr$avg_ranks[1])` and `r sprintf("%.2f", fr$avg_ranks[2])`.
- These findings are **robust** across all tested levels of spatial autocorrelation, spillover magnitude, spillover type, neighbor contiguity, and incidence generation mode.

This analysis provides the statistical foundation for recommending specific treatment assignment designs for future spatial CRT studies.

# Appendix: Test Details {.appendix}

## Software and Packages

- **R** version `r paste(R.version$major, R.version$minor, sep = ".")`
- **PMCMRplus** `r packageVersion("PMCMRplus")`: Friedman test, Nemenyi post-hoc
- **stats** (base R): Wilcoxon signed-rank test, Holm p-value adjustment
- **Simulation results**: `r basename(attr(mle_results, "source") %||% "sim_results_MLE_combined_20260322_151030.rds")`

## Nemenyi P-value Matrix

```{r nemenyi-full-table}
nem_p_display <- nem$p_matrix
nem_p_display[is.na(nem_p_display)] <- NA
for (i in 1:nrow(nem_p_display)) {
  for (j in 1:ncol(nem_p_display)) {
    if (!is.na(nem_p_display[i, j])) {
      nem_p_display[i, j] <- sprintf("%.4f", as.numeric(nem_p_display[i, j]))
    }
  }
}
diag(nem_p_display) <- "—"
kable(nem_p_display,
      caption = "Full Nemenyi post-hoc p-value matrix.",
      align = "c") %>%
  kable_styling(font_size = 9, full_width = FALSE, latex_options = c("hold_position", "scale_down"))
```

## Wilcoxon P-value Matrix (Holm-adjusted)

```{r wilcoxon-full-table}
wil_p_display <- wil$p_matrix
for (i in 1:nrow(wil_p_display)) {
  for (j in 1:ncol(wil_p_display)) {
    if (!is.na(wil_p_display[i, j])) {
      wil_p_display[i, j] <- sprintf("%.4f", as.numeric(wil_p_display[i, j]))
    }
  }
}
diag(wil_p_display) <- "—"
kable(wil_p_display,
      caption = "Full pairwise Wilcoxon signed-rank p-value matrix (Holm-adjusted).",
      align = "c") %>%
  kable_styling(font_size = 9, full_width = FALSE, latex_options = c("hold_position", "scale_down"))
```
