---
title: "Spatial Sim Estimates Binary"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output: html_document
---

### Preliminaries

```{r, message=FALSE, warning=FALSE}
# set seed
set.seed(2024) # ensures reproducibility

# load packages
library(tidyverse)
library(ggplot2)
library(sf) # simple features-store/manipulate spatial data
library(reshape2)
library(gridExtra)
library(spdep)
library(spatialreg)
library(tictoc) # measure function elapsed time

### Set Constants ###
# parameters for simulation
N <- 50  # Number of iterations
points_per_iteration <- 2000  # Number of points per dataset (to place on 1000x100 cell grid)
grid_size <- 1000 # Set dimension of grid for simulated data
NeighborDist <- 100 # set maximum distance for two points to be considered "neighbors" (shrink???)

# Define response model constants (true values)
alpha <- 0.2
beta <- 1
psi <- 0.8 # maximum spillover effect (binary)
rho <- 0.01 # spatial correlation parameter t
sd <- 0.1 # set standard deviation (for epsilon) -> change this to reduce "noise"/more consistent estimates

# max distance (between intervention & spillover boundaries) (max(d_i))
max_distance <- sqrt((133-333)^2 + (866-666)^2) # ~282.84 units
```

### Setup Intervention & Spillover Polygons

```{r}
### Create intervention & spillover polygons ###
# Define the intervention zone polygon (333,333) to (666,666)
intervention_zone <- st_polygon(list(matrix(c(333, 333, 666, 333, 666, 666, 333, 666, 333, 333), ncol = 2, byrow = TRUE)))

# Define the spillover zone polygon (133,133) to (866,866)
spillover_zone <- st_polygon(list(matrix(c(133, 133, 866, 133, 866, 866, 133, 866, 133, 133), ncol = 2, byrow = TRUE)))

# Create sf objects for both polygons (simple feature) (CRS=NA is unit-based instead of map-based)
intervention_sf <- st_sfc(intervention_zone, crs = NA_crs_)
spillover_sf <- st_sfc(spillover_zone, crs = NA_crs_)
```

### Simulate Datasets

```{r}
# initialize object to store all N=500 datasets
simulated_datasets <- vector("list", N)

### initialize objects to store parameter estimates##
# No spatial correlation estimates
alpha_estimates <- numeric(N) # baseline response
alpha_estimates_SE <- numeric(N)
beta_estimates <- numeric(N) # intervention effect
beta_estimates_SE <- numeric(N)
psi_estimates <- numeric(N) # spillover effect
psi_estimates_SE <- numeric(N)

# indicator based spatial correlation
alpha_estimates_ind <- numeric(N) # baseline response
alpha_estimates_SE_ind <- numeric(N)
beta_estimates_ind <- numeric(N) # intervention effect
beta_estimates_SE_ind <- numeric(N)
psi_estimates_ind <- numeric(N) # spillover effect
psi_estimates_SE_ind <- numeric(N)
rho_estimates_ind <- numeric(N) # spatial correlation
rho_estimates_SE_ind <- numeric(N)

# distance based spatial correlation
alpha_estimates_dist <- numeric(N) # baseline response
alpha_estimates_SE_dist <- numeric(N)
beta_estimates_dist <- numeric(N) # intervention effect
beta_estimates_SE_dist <- numeric(N)
psi_estimates_dist <- numeric(N) # spillover effect
psi_estimates_SE_dist <- numeric(N)
rho_estimates_dist <- numeric(N) # spatial correlation
rho_estimates_SE_dist <- numeric(N)
```

### Simulation Loop

```{r}
### Loop over N to generate datasets/compute response/obtain parameter estimates ###
for(i in 1:N){
  start_time <- Sys.time() # start timer for each iteration
  ### 1) Data Simulation ###
  # Simulate random points on the grid with integer coordinates
  points <- tibble(x = sample(1:grid_size, points_per_iteration, replace = TRUE),
                   y = sample(1:grid_size, points_per_iteration, replace = TRUE))
  
  # Convert points to sf objects
  points_sf <- st_as_sf(points, coords = c("x", "y"), crs = NA_crs_)
  ####################################################################################################
  # 2) Calculate distance from each point to the intervention zone boundary
  distances <- st_distance(points_sf, intervention_sf)
  points$intervention_distance <- as.vector(distances)
  intervention_distance <- points$intervention_distance # for use in spillover formulas
  
  # Assign zones based on their location (intervention/spillover/control)
  points$intervention_zone <- ifelse(st_within(points_sf, intervention_sf, sparse = FALSE), 1, 0) # intervention
  points$spillover_zone <- ifelse(
    st_within(points_sf, spillover_sf, 
              sparse = FALSE) & !st_within(points_sf, intervention_sf, sparse = FALSE), 1, 0) # spillover
  
  # Add zone label ("Intervention", "Spillover", "Control")
  points$zone <- ifelse(points$intervention_zone == 1, "Intervention",
                        ifelse(points$spillover_zone == 1, "Spillover", "Control"))
  ####################################################################################################
  ### 3A) Compute Response w/ Binary Spillover ###
  # Generate random noise (epsilon) from normal distribution
  epsilon <- rnorm(points_per_iteration, mean = 0, sd = sd)
  
  # Compute response w/ binary spillover (spillover gets 80% of intervention effect, need to incorporate spatial correlation?)
  points$response <- alpha + (beta*points$intervention_zone) + (psi*points$spillover_zone) # initialize general response
  points$response_binary <- points$response + epsilon # add random error component (response_binary)
  ####################################################################################################
  ### 3B) Compute response w/ binary spillover (Indicator spatial correlation) ###
  # Create spatial weights matrix
  coordinates <- as.matrix(points[, c("x", "y")])
  dlist <- dnearneigh(coordinates, d1 = 0, 
                      d2 = NeighborDist, longlat = FALSE) # list of "neighbors" for each point (0, NeighborDist)
  W_ind <- nb2listw(dlist, style = "W", zero.policy = TRUE)
  W.ind.dense <- as(as_dgRMatrix_listw(W_ind), "matrix") # convert to dense matrix
  W.ind.dense[is.na(W.ind.dense)] <- 0
  
  I <- diag(points_per_iteration) # create identity matrix
  
  # generate linear response (from 3A)
  linear_response <- points$response_binary
  linear_response[is.na(linear_response)] <- 0
  
  # solve for y using closed-form expression
  A.ind <- I - rho * W.ind.dense # (I - rho*W)
  response.ind <- solve(A.ind, linear_response) # (I - rho W)^(-1) * (a + XB + e)
  points$response_binary_IndCorr <- response.ind # simultaneous response (response_binary_IndCorr) (1)
  
  # # Compute the spatially correlated response using indicator-based weights
  # Wy_ind <- lag.listw(W_ind, linear_response) # matrix multiplication and turn into list (Wy) (neighborhood info)
  # points$response_binary_IndCorr_NotSimul <- linear_response + rho * Wy_ind + epsilon # spatial ind. response + spatial dep. adjust)
  ####################################################################################################
  ### 3C) Compute response w/ binary spillover (Distance-based spatial correlation) ###
  # Calculate the distance matrix
  coordinates <- as.matrix(points[, c("x", "y")])
  distance_matrix <- as.matrix(dist(coordinates))
  # linear decay for distance-based weights
  W_matrix <- ifelse(distance_matrix <= NeighborDist & distance_matrix > 0, 1 / distance_matrix, 0) # inverse distance decay weights
  W_matrix <- W_matrix / rowSums(W_matrix, na.rm = TRUE) # normalize weights
  W_matrix[is.na(W_matrix)] <- 0 # set potential NaNs to 0
  W_dist <- mat2listw(W_matrix, style = "W", 
                      row.names = rownames(points), zero.policy = TRUE) # convert weights matrix to listw object
  W.dist.dense <- as(as_dgRMatrix_listw(W_dist), "matrix")
  W.dist.dense[is.na(W.dist.dense)] <- 0
  
  I <- diag(points_per_iteration) # create identity matrix
  
  # generate linear response (from 3A)
  linear_response <- points$response_binary
  linear_response[is.na(linear_response)] <- 0

  # solve for y using closed-form expression
  A.dist <- I - rho * W.dist.dense # (I - rho*W)
  response.dist <- solve(A.dist, linear_response) # (I - rho W)^(-1) * (linear_response)
  points$response_binary_DistCorr <- response.dist # simultaneous response (response_binary_DistCorr) (1)
  
  # # Compute spatially correlated response using the distance-based weights
  # Wy_dist <- lag.listw(W_dist, linear_response)
  # points$response_binary_DistCorr_NotSimul <- linear_response + rho * Wy_dist + epsilon
  ####################################################################################################
  ### 4A) Estimate Parameter Values via modeling ###
  model <- lm(response_binary ~ intervention_zone + spillover_zone, data = points)

  # Store the estimates (no spatial correlation matrix)
  alpha_estimates[i] <- coef(model)[1]  # Intercept (alpha)
  beta_estimates[i] <- coef(model)[2]   # Coefficient for intervention_zone (beta)
  psi_estimates[i] <- coef(model)[3]    # Coefficient for linear spillover effect (psi)
  
  # Store the standard errors
  alpha_estimates_SE[i] <- summary(model)$coefficients[1, 2]
  beta_estimates_SE[i] <- summary(model)$coefficients[2, 2]
  psi_estimates_SE[i] <- summary(model)$coefficients[3, 2]
  ####################################################################################################
  ### 4B) Neighbor indicator weight matrix  ###
  # Determine neighbors up to 100 distance units (coords/min dist/max dist -> output IDs of points that are neighbors)
  coordinates <- as.matrix(points[, c("x", "y")]) # coordinates of each point (x and y)
  dlist <- dnearneigh(coordinates, d1 = 0, d2 = NeighborDist, longlat = FALSE) # d1 = min neighbor dist, d2 = max neighbor dist
  W_ind <- nb2listw(dlist, style = "W", zero.policy = TRUE) # spatial weights matrix -> for spatial lag model (neighboring points influence effect)
  W_ind[is.na(W_ind)] <- 0
  
  # Fit a Spatial Lag Model (SLM) w/ intervention effect, spillover effect, & spatial weights matrix (adapt for distance vs. indicator)
  model_ind <- lagsarlm(response_binary_IndCorr ~ intervention_zone + spillover_zone, 
                        data = points, listw = W_ind) # lag SAR lm

  # Store the estimates (indicator based correlation matrix)
  alpha_estimates_ind[i] <- coef(model_ind)[1] # Intercept (alpha)
  beta_estimates_ind[i] <- coef(model_ind)[2] # Coefficient for intervention_zone (beta)
  psi_estimates_ind[i] <- coef(model_ind)[3] # Coefficient for linear spillover effect (psi)
  rho_estimates_ind[i] <- model_ind$rho # spatial lag parameter
  
  # Store the standard errors
  alpha_estimates_SE_ind[i] <- summary(model_ind)$Coef[1, 2]
  beta_estimates_SE_ind[i] <- summary(model_ind)$Coef[2, 2]
  psi_estimates_SE_ind[i] <- summary(model_ind)$Coef[3, 2]
  rho_estimates_SE_ind[i] <- summary(model_ind)$rho.se
  ####################################################################################################  
  ### 4C) Distance-based weight matrix ###
  # Apply a decay function to create distance-based weights
  coordinates <- as.matrix(points[, c("x", "y")]) # coordinates of each point (x and y)
  distance_matrix <- as.matrix(dist(coordinates))
  W_matrix <- ifelse(distance_matrix <= NeighborDist & distance_matrix > 0, 1 / distance_matrix, 0) # linear decay w/ inc. distance
  # Normalize the weights by RowSums to ensure they sum to 1
  W_matrix <- W_matrix / rowSums(W_matrix, na.rm = TRUE) 
  # Convert the weights matrix into a listw object
  W_dist <- mat2listw(W_matrix, style = "W", row.names = rownames(coordinates), zero.policy = TRUE)
  W_dist[is.na(W_dist)] <- 0

  # Fit a Spatial Lag Model (SLM) w/ intervention & spillover effects, & spatial weights matrix (adapt for distance vs. indicator)
  model_dist <- lagsarlm(response_binary_DistCorr ~ intervention_zone + spillover_zone, 
                         data = points, listw = W_dist)

  # Store the estimates (distance based correlation matrix)
  alpha_estimates_dist[i] <- coef(model_dist)[1] # Intercept (alpha)
  beta_estimates_dist[i] <- coef(model_dist)[2] # Coefficient for intervention_zone (beta)
  psi_estimates_dist[i] <- coef(model_dist)[3] # Coefficient for linear spillover effect (psi)
  rho_estimates_dist[i] <- model_dist$rho # spatial lag parameter
  
  # Store the standard errors
  alpha_estimates_SE_dist[i] <- summary(model_dist)$Coef[1, 2]
  beta_estimates_SE_dist[i] <- summary(model_dist)$Coef[2, 2]
  psi_estimates_SE_dist[i] <- summary(model_dist)$Coef[3, 2]
  rho_estimates_SE_dist[i] <- summary(model_dist)$rho.se
  ####################################################################################################
  # 5) Store the dataset for this iteration in the list (ith simulated point locations)
  simulated_datasets[[i]] <- points
  # measure elapsed time for iteration
  elapsed_time <- Sys.time() - start_time
  # print elapsed time for iteration
  cat(sprintf("Iteration %d: %.2f seconds elapsed\n", i, as.numeric(elapsed_time, units = "secs")))
}
```

### Parameter Estimates 

```{r}
### 1) Table of all parameter estimates ###
estimates_table <- tibble(
  alpha = alpha_estimates, alpha_SE = alpha_estimates_SE, # no spatial correlation
  beta = beta_estimates, beta_SE = beta_estimates_SE,
  psi = psi_estimates, psi_SE = psi_estimates_SE,
  alpha_ind = alpha_estimates_ind, alpha_SE_ind = alpha_estimates_SE_ind, # indicator spatial correlation
  beta_ind = beta_estimates_ind, beta_SE_ind = beta_estimates_SE_ind,
  psi_ind = psi_estimates_ind, psi_SE_ind = psi_estimates_SE_ind,
  rho_ind = rho_estimates_ind, rho_SE_ind = rho_estimates_SE_ind,
  alpha_dist = alpha_estimates_dist, alpha_SE_dist = alpha_estimates_SE_dist, # distance spatial correlation
  beta_dist = beta_estimates_dist, beta_SE_dist = beta_estimates_SE_dist,
  psi_dist = psi_estimates_dist, psi_SE_dist = psi_estimates_SE_dist,
  rho_dist = rho_estimates_dist, rho_SE_dist = rho_estimates_SE_dist,
)
#print(estimates_table)
####################################################################################################
### Compute Final Parameter Estimates & SEs ###
## 2A) No spatial correlation ###
alpha_mean <- mean(alpha_estimates, na.rm = TRUE) # estimate means
beta_mean <- mean(beta_estimates, na.rm = TRUE)
psi_mean <- mean(psi_estimates, na.rm = TRUE)
alpha_SE_avg <- sqrt(mean(alpha_estimates_SE^2)) # estimate SE means
beta_SE_avg <- sqrt(mean(beta_estimates_SE^2))
psi_SE_avg <- sqrt(mean(psi_estimates_SE^2))

## 2B) Neighbor-based spatial correlation ###
alpha_ind_mean <- mean(alpha_estimates_ind, na.rm = TRUE) # estimate means
beta_ind_mean <- mean(beta_estimates_ind, na.rm = TRUE)
psi_ind_mean <- mean(psi_estimates_ind, na.rm = TRUE)
rho_ind_mean <- mean(rho_estimates_ind, na.rm = TRUE)
alpha_ind_SE_avg <- sqrt(mean(alpha_estimates_SE_ind^2)) # estimate SE means
beta_ind_SE_avg <- sqrt(mean(beta_estimates_SE_ind^2))
psi_ind_SE_avg <- sqrt(mean(psi_estimates_SE_ind^2))
rho_ind_SE_avg <- sqrt(mean(rho_estimates_SE_ind^2))

## 2C) Distance-based spatial correlation ###
alpha_dist_mean <- mean(alpha_estimates_dist, na.rm = TRUE) # estimate means
beta_dist_mean <- mean(beta_estimates_dist, na.rm = TRUE)
psi_dist_mean <- mean(psi_estimates_dist, na.rm = TRUE)
rho_dist_mean <- mean(rho_estimates_dist, na.rm = TRUE)
alpha_dist_SE_avg <- sqrt(mean(alpha_estimates_SE_dist^2)) # estimate SE means
beta_dist_SE_avg <- sqrt(mean(beta_estimates_SE_dist^2))
psi_dist_SE_avg <- sqrt(mean(psi_estimates_SE_dist^2))
rho_dist_SE_avg <- sqrt(mean(rho_estimates_SE_dist^2))
####################################################################################################
# 3) Store the results in a table
results_summary <- tibble(
  Parameter = c("Alpha", "Beta", "Psi", 
                "Alpha_ind", "Beta_ind", "Psi_ind", "Rho_ind", 
                "Alpha_dist", "Beta_dist", "Psi_dist", "Rho_dist"),
  Mean = c(alpha_mean, beta_mean, psi_mean, 
           alpha_ind_mean, beta_ind_mean, psi_ind_mean, rho_ind_mean, 
           alpha_dist_mean, beta_dist_mean, psi_dist_mean, rho_dist_mean),
  Bias = c(alpha_mean-alpha, beta_mean-beta, psi_mean-psi,
           alpha_ind_mean-alpha, beta_ind_mean-beta, psi_ind_mean-psi, rho_ind_mean-rho,
           alpha_dist_mean-alpha, beta_dist_mean-beta, psi_dist_mean-psi, rho_dist_mean-rho),
  SE = c(alpha_SE_avg, beta_SE_avg, psi_SE_avg, 
         alpha_ind_SE_avg, beta_ind_SE_avg, psi_ind_SE_avg, rho_ind_SE_avg,
         alpha_dist_SE_avg, beta_dist_SE_avg, psi_dist_SE_avg, rho_dist_SE_avg)
  ) %>% mutate(across(where(is.numeric), ~ round(., 5))) # Round to 5 decimal places

# Print the summary table
print(results_summary)
```

- Simulated response: does not include spatial correlation! -> updated simulated responses to include both indicator & distance based spatial correlation matrices!

- No spatial weight matrix: most accurate estimation of parameter values vs. true values

- Indicator spatial weight matrix: poor accuracy in estimation of parameter values vs. true values. Likely due to lack of spatial correlation in the simulated response data.

- Distance spatial weight matrix: poor accuracy in estimation of parameter values vs. true values. Likely due to lack of spatial correlation in the simulated response data.

### Plots of Parameter Estimates

```{r}
### Plots of Individual Estimates and their 95% Confidence Intervals ###
### 1) Alpha Plot ###
# Create a tibble to hold the alpha estimates and their standard errors for each dataset
alpha_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  alpha = alpha_estimates,  # mean alpha estimates for each dataset
  alpha_SE = alpha_estimates_SE  # standard error of alpha estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
alpha_plot_data <- alpha_plot_data %>%
  mutate(
    lower_ci = alpha - 1.96 * alpha_SE,
    upper_ci = alpha + 1.96 * alpha_SE
  )

# Create the plot
alpha_plot <- ggplot(alpha_plot_data, aes(x = dataset_id, y = alpha)) +
  geom_point(color = "blue") +  # Add points for alpha estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = alpha_mean, linetype = "dashed", color = "blue") +  # Add horizontal line at alpha mean
  labs(
    title = "Alpha Estimates with 95% CIs",
    x = "Dataset",
    y = "Alpha Estimate"
  ) +
  theme_classic() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
### 2) Beta Plot ###
# Create a tibble to hold the estimates and their standard errors for each dataset
beta_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  beta = beta_estimates,  # mean beta estimates for each dataset
  beta_SE = beta_estimates_SE  # standard error of beta estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
beta_plot_data <- beta_plot_data %>%
  mutate(
    lower_ci = beta - 1.96 * beta_SE,
    upper_ci = beta + 1.96 * beta_SE
  )

# Create the beta plot
beta_plot <- ggplot(beta_plot_data, aes(x = dataset_id, y = beta)) +
  geom_point(color = "red") +  # Add points for beta estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = beta_mean, linetype = "dashed", color = "red") +  # Add horizontal line at beta mean
  labs(
    title = "Beta Estimates with 95% CIs",
    x = "Dataset",
    y = "Beta Estimate"
  ) +
  theme_minimal() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
### 3) Psi Plot ###
# Create a tibble for psi estimates and their standard errors
psi_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  psi = psi_estimates,  # mean psi estimates for each dataset
  psi_SE = psi_estimates_SE  # standard error of psi estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
psi_plot_data <- psi_plot_data %>%
  mutate(
    lower_ci = psi - 1.96 * psi_SE,
    upper_ci = psi + 1.96 * psi_SE
  )

# Create the psi plot
psi_plot <- ggplot(psi_plot_data, aes(x = dataset_id, y = psi)) +
  geom_point(color = "purple") +  # Add points for psi estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = psi_mean, linetype = "dashed", color = "purple") +  # Add horizontal line at psi mean
  labs(
    title = "Psi Estimates with 95% CIs",
    x = "Dataset",
    y = "Psi Estimate"
  ) +
  theme_minimal() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
# Print the plots
print(alpha_plot)
print(beta_plot)
print(psi_plot)

# Combine all plots into a single layout
combined_plot <- grid.arrange(
  alpha_plot,       # Plot for Alpha
  beta_plot,        # Plot for Beta
  psi_plot,         # Plot for Psi
  ncol = 2,         # Arrange plots in 2 columns
  nrow = 2          # Arrange plots in 2 rows
)
```

```{r}
### Plots of Estimates and their 95% Confidence Intervals (Indicator Spatial Weights) ###
### Alpha Plot ###
# Create a tibble to hold the alpha estimates and their standard errors for each dataset
alpha_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  alpha = alpha_estimates_ind,  # mean alpha estimates for each dataset
  alpha_SE = alpha_estimates_SE_ind  # standard error of alpha estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
alpha_plot_data <- alpha_plot_data %>%
  mutate(
    lower_ci = alpha - 1.96 * alpha_SE,
    upper_ci = alpha + 1.96 * alpha_SE
  )

# Create the plot
alpha_plot <- ggplot(alpha_plot_data, aes(x = dataset_id, y = alpha)) +
  geom_point(color = "blue") +  # Add points for alpha estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = alpha_ind_mean, linetype = "dashed", color = "blue") +  # Add horizontal line at alpha mean
  labs(
    title = "Alpha Estimates with 95% CIs",
    x = "Dataset",
    y = "Alpha Estimate"
  ) +
  theme_classic() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
### Beta Plot ###
# Create a tibble to hold the estimates and their standard errors for each dataset
beta_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  beta = beta_estimates_ind,  # mean beta estimates for each dataset
  beta_SE = beta_estimates_SE_ind  # standard error of beta estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
beta_plot_data <- beta_plot_data %>%
  mutate(
    lower_ci = beta - 1.96 * beta_SE,
    upper_ci = beta + 1.96 * beta_SE
  )

# Create the beta plot
beta_plot <- ggplot(beta_plot_data, aes(x = dataset_id, y = beta)) +
  geom_point(color = "red") +  # Add points for beta estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = beta_ind_mean, linetype = "dashed", color = "red") +  # Add horizontal line at beta mean
  labs(
    title = "Beta Estimates with 95% CIs",
    x = "Dataset",
    y = "Beta Estimate"
  ) +
  theme_minimal() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
### Psi Plot ###
# Create a tibble for psi estimates and their standard errors
psi_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  psi = psi_estimates_ind,  # mean psi estimates for each dataset
  psi_SE = psi_estimates_SE_ind  # standard error of psi estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
psi_plot_data <- psi_plot_data %>%
  mutate(
    lower_ci = psi - 1.96 * psi_SE,
    upper_ci = psi + 1.96 * psi_SE
  )

# Create the psi plot
psi_plot <- ggplot(psi_plot_data, aes(x = dataset_id, y = psi)) +
  geom_point(color = "purple") +  # Add points for psi estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = psi_ind_mean, linetype = "dashed", color = "purple") +  # Add horizontal line at psi mean
  labs(
    title = "Psi Estimates with 95% CIs",
    x = "Dataset",
    y = "Psi Estimate"
  ) +
  theme_minimal() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
### Rho Plot ###
# Create a tibble for rho estimates and their standard errors
rho_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  rho = rho_estimates_ind,  # mean rho estimates for each dataset
  rho_SE = rho_estimates_SE_ind  # standard error of rho estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
rho_plot_data <- rho_plot_data %>%
  mutate(
    lower_ci = rho - 1.96 * rho_SE,
    upper_ci = rho + 1.96 * rho_SE
  )

# Create the rho plot
rho_plot <- ggplot(rho_plot_data, aes(x = dataset_id, y = rho)) +
  geom_point(color = "purple") +  # Add points for rho estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = rho_ind_mean, linetype = "dashed", color = "purple") +  # Add horizontal line at rho mean
  labs(
    title = "Rho Estimates with 95% CIs",
    x = "Dataset",
    y = "Rho Estimate"
  ) +
  theme_minimal() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
# Print the plots
print(alpha_plot)
print(beta_plot)
print(psi_plot)
print(rho_plot)

# Combine all plots into a single layout
combined_plot <- grid.arrange(
  alpha_plot,       # Plot for Alpha
  beta_plot,        # Plot for Beta
  psi_plot,         # Plot for Psi
  rho_plot,         # Plot for Rho
  ncol = 2,         # Arrange plots in 2 columns
  nrow = 2          # Arrange plots in 2 rows
)
```

```{r}
### Plots of Estimates and their 95% Confidence Intervals (Distance-based Spatial Weights) ###
### Alpha Plot ###
# Create a tibble to hold the alpha estimates and their standard errors for each dataset
alpha_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  alpha = alpha_estimates_dist,  # mean alpha estimates for each dataset
  alpha_SE = alpha_estimates_SE_dist  # standard error of alpha estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
alpha_plot_data <- alpha_plot_data %>%
  mutate(
    lower_ci = alpha - 1.96 * alpha_SE,
    upper_ci = alpha + 1.96 * alpha_SE
  )

# Create the plot
alpha_plot <- ggplot(alpha_plot_data, aes(x = dataset_id, y = alpha)) +
  geom_point(color = "blue") +  # Add points for alpha estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = alpha_dist_mean, linetype = "dashed", color = "blue") +  # Add horizontal line at alpha mean
  labs(
    title = "Alpha Estimates with 95% CIs",
    x = "Dataset",
    y = "Alpha Estimate"
  ) +
  theme_classic() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
### Beta Plot ###
# Create a tibble to hold the estimates and their standard errors for each dataset
beta_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  beta = beta_estimates_dist,  # mean beta estimates for each dataset
  beta_SE = beta_estimates_SE_dist  # standard error of beta estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
beta_plot_data <- beta_plot_data %>%
  mutate(
    lower_ci = beta - 1.96 * beta_SE,
    upper_ci = beta + 1.96 * beta_SE
  )

# Create the beta plot
beta_plot <- ggplot(beta_plot_data, aes(x = dataset_id, y = beta)) +
  geom_point(color = "red") +  # Add points for beta estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = beta_dist_mean, linetype = "dashed", color = "red") +  # Add horizontal line at beta mean
  labs(
    title = "Beta Estimates with 95% CIs",
    x = "Dataset",
    y = "Beta Estimate"
  ) +
  theme_minimal() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
### Psi Plot ###
# Create a tibble for psi estimates and their standard errors
psi_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  psi = psi_estimates_dist,  # mean psi estimates for each dataset
  psi_SE = psi_estimates_SE_dist  # standard error of psi estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
psi_plot_data <- psi_plot_data %>%
  mutate(
    lower_ci = psi - 1.96 * psi_SE,
    upper_ci = psi + 1.96 * psi_SE
  )

# Create the psi plot
psi_plot <- ggplot(psi_plot_data, aes(x = dataset_id, y = psi)) +
  geom_point(color = "purple") +  # Add points for psi estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = psi_dist_mean, linetype = "dashed", color = "purple") +  # Add horizontal line at psi mean
  labs(
    title = "Psi Estimates with 95% CIs",
    x = "Dataset",
    y = "Psi Estimate"
  ) +
  theme_minimal() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
### Rho Plot ###
# Create a tibble for rho estimates and their standard errors
rho_plot_data <- tibble(
  dataset_id = 1:N,  # dataset identifier (1 to N)
  rho = rho_estimates_dist,  # mean rho estimates for each dataset
  rho_SE = rho_estimates_SE_dist  # standard error of rho estimates
)

# Compute the 95% confidence intervals (1.96 * SE for the error bars)
rho_plot_data <- rho_plot_data %>%
  mutate(
    lower_ci = rho - 1.96 * rho_SE,
    upper_ci = rho + 1.96 * rho_SE
  )

# Create the rho plot
rho_plot <- ggplot(rho_plot_data, aes(x = dataset_id, y = rho)) +
  geom_point(color = "purple") +  # Add points for rho estimates
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +  # Add error bars for 95% CI
  geom_hline(yintercept = rho_dist_mean, linetype = "dashed", color = "purple") +  # Add horizontal line at rho mean
  labs(
    title = "Rho Estimates with 95% CIs",
    x = "Dataset",
    y = "Rho Estimate"
  ) +
  theme_minimal() +  # Clean theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )
####################################################################################################
# Print the plots
print(alpha_plot)
print(beta_plot)
print(psi_plot)
print(rho_plot)

# Combine all plots into a single layout
combined_plot <- grid.arrange(
  alpha_plot,       # Plot for Alpha
  beta_plot,        # Plot for Beta
  psi_plot,         # Plot for Psi
  rho_plot,         # Plot for Rho
  ncol = 2,         # Arrange plots in 2 columns
  nrow = 2          # Arrange plots in 2 rows
)
```