---
title: "SpatialSim_3x4"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output: html_document
---

### Objecive

- Expand spatial simulation w/ spillover estimation to a 3x4 grid (beyond previous 4x2 grid) to understand estimation efficiency on larger spaces.

### Preliminaries

```{r Load Libraries, message=FALSE, warning=FALSE}
# set seed
set.seed(2024) # ensures reproducibility

# load packages
library(tidyverse)
library(ggplot2)
library(sf) # simple features-store/manipulate spatial data
library(reshape2)
library(gridExtra)
library(spdep)
library(spatialreg)
library(tictoc) # measure function elapsed time
library(combinat)
```

```{r Initiate Constants}
### Set Constants ###
# parameters for simulation
N <- 10 # number of datasets to generate (iterate over each trt combo for each - 50*70=3500)  
Num.Combos <- 924 # Number of trt combos to iterate over
points_per_iteration <- 240  # Number of points per dataset (20 per district)
grid_width <- 400 # Set dimensions of grid for simulated data
grid_height <- 300
cell_length <- 100

# Define response model constants (true values)
alpha <- 0.2 # intercept/baseline effecgt
beta <- 1 # consider a range of intervention effects (start with Null case -> 1)
psi <- 0.8 # maximum spillover effect (binary)
rho <- 0.00 # spatial correlation parameter
sd <- 0.1 # set standard deviation (for epsilon) -> change this to reduce "noise"/more consistent estimates
```

- Additionally, 3x4 grid (12 cells) with 6 intervention and 6 control districts has 12 choose 6 = 924 different combinations to choose the grid setup.

### Data Setup

```{r Identify all combinations of 4 Intervention & Control}
### Generate combinations of 8 districts (4 intervention, 4 control)
# Create a vector representing the 8 districts
districts <- 1:12

# Generate all combinations of 4 intervention districts out of 8
combinations <- combn(districts, 6)

# Initialize an empty data frame for the results
results <- data.frame(Combination = 1:ncol(combinations))

# Loop through each combination and create a row for the table
for (i in 1:ncol(combinations)) {
  # Create a vector of 0s (control) and 1s (intervention)
  treatment_assignment <- ifelse(districts %in% combinations[, i], 1, 0)
  
  # Add the treatment assignment for this combination as a new column
  results[i, 2:13] <- treatment_assignment
}

# Rename the columns
colnames(results) <- c('Combination', paste('Cell', 1:12))

# Print the results table
print(results)
```

```{r Assign table of Rook Neighbors for 8 districts}
### Table of Rook Neighbor Assignments ###
# neighbors are cells that are directly adjacent - "rook" case contiguity (not diagonal) to a reference cell
# Initialize the 8x8 matrix with zeros (no neighbors initially)
neighbor_matrix <- matrix(0, nrow = 12, ncol = 12)

# Define the neighbor relationships (cells are indexed from 1 to 8)
rook_neighbors <- list(
  `1` = c(2, 5), # Cell 1 neighbors
  `2` = c(1, 3, 6), # Cell 2 neighbors
  `3` = c(2, 4, 7), # Cell 3 neighbors
  `4` = c(3, 8), # Cell 4 neighbors
  `5` = c(1, 6, 9), # Cell 5 neighbors
  `6` = c(2, 5, 7, 10), # Cell 6 neighbors
  `7` = c(3, 6, 8, 11), # Cell 7 neighbors
  `8` = c(4, 7, 12), # Cell 8 neighbors
  `9` = c(5, 10), # Cell 9 neighbors
  `10` = c(6, 9, 11), # Cell 10 neighbors
  `11` = c(7, 10, 12), # Cell 11 neighbors
  `12` = c(8, 11) # Cell 9 neighbors
)

# Loop through each cell and mark its neighbors in the matrix
for (cell in names(rook_neighbors)) {
  for (neighbor in rook_neighbors[[cell]]) {
    neighbor_matrix[as.numeric(cell), neighbor] <- 1
  }
}

# Print the resulting matrix
print(neighbor_matrix)
```

```{r}
### Define the coordinates for each district (100x100 units) ###
# Row 1 (top)
district_1 <- st_polygon(list(matrix(c(0, 200, 100, 200, 100, 300, 0, 300, 0, 200), ncol = 2, byrow = TRUE)))
district_2 <- st_polygon(list(matrix(c(100, 200, 200, 200, 200, 300, 100, 300, 100, 200), ncol = 2, byrow = TRUE)))
district_3 <- st_polygon(list(matrix(c(200, 200, 300, 200, 300, 300, 200, 300, 200, 200), ncol = 2, byrow = TRUE)))
district_4 <- st_polygon(list(matrix(c(300, 200, 400, 200, 400, 300, 300, 300, 300, 200), ncol = 2, byrow = TRUE)))

# Row 2 (middle)
district_5 <- st_polygon(list(matrix(c(0, 100, 100, 100, 100, 200, 0, 200, 0, 100), ncol = 2, byrow = TRUE)))
district_6 <- st_polygon(list(matrix(c(100, 100, 200, 100, 200, 200, 100, 200, 100, 100), ncol = 2, byrow = TRUE)))
district_7 <- st_polygon(list(matrix(c(200, 100, 300, 100, 300, 200, 200, 200, 200, 100), ncol = 2, byrow = TRUE)))
district_8 <- st_polygon(list(matrix(c(300, 100, 400, 100, 400, 200, 300, 200, 300, 100), ncol = 2, byrow = TRUE)))

# Row 3 (bottom)
district_9  <- st_polygon(list(matrix(c(0, 0, 100, 0, 100, 100, 0, 100, 0, 0), ncol = 2, byrow = TRUE)))
district_10 <- st_polygon(list(matrix(c(100, 0, 200, 0, 200, 100, 100, 100, 100, 0), ncol = 2, byrow = TRUE)))
district_11 <- st_polygon(list(matrix(c(200, 0, 300, 0, 300, 100, 200, 100, 200, 0), ncol = 2, byrow = TRUE)))
district_12 <- st_polygon(list(matrix(c(300, 0, 400, 0, 400, 100, 300, 100, 300, 0), ncol = 2, byrow = TRUE)))

# Combine all districts
districts_list <- list(district_1, district_2, district_3, district_4,
                       district_5, district_6, district_7, district_8,
                       district_9, district_10, district_11, district_12)

districts_sf <- st_sfc(districts_list, crs = NA_crs_)

### Adjusted Centroids for 3x4 grid ###
district_names <- as.character(1:12)
label_positions <- data.frame(
  district = district_names,
  x = rep(c(50, 150, 250, 350), 3),          # Repeating x-centroids per column
  y = rep(c(250, 150, 50), each = 4)          # Repeating y-centroids per row
)
label_sf <- st_as_sf(label_positions, coords = c("x", "y"), crs = NA_crs_)

# Plot
ggplot() +
  geom_sf(data = districts_sf, fill = "white", color = "black") +
  geom_sf_text(data = label_sf, aes(label = district), size = 5, color = "black") +
  theme_minimal() +
  ggtitle("Spatial region with district labels (1–12)") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )
```

```{r Plot all possible treatment assignment combos}
# ### Plot Treatment assignments for all possible combinations ###
# # Generate all 924 treatment assignments
# districts <- 1:12
# combinations <- combn(districts, 6, simplify = FALSE)
# 
# # Loop through each treatment combination and plot
# for (i in seq_along(combinations)) {
#   
#   # Assign intervention (1) and control (0) based on the current combination
#   treatment_assignment <- ifelse(districts %in% combinations[[i]], 1, 0)
#   
#   # Convert to factor with labels
#   label_sf$treatment <- factor(treatment_assignment, levels = c(0, 1), labels = c("Control", "Intervention"))
#   
#   # Generate plot
#   p <- ggplot() +
#     geom_sf(data = districts_sf, aes(fill = label_sf$treatment), color = "black") +
#     geom_sf_text(data = label_sf, aes(label = district), size = 5, color = "black") +
#     scale_fill_manual(values = c("Control" = "blue", "Intervention" = "red")) +
#     labs(fill = "Treatment") +
#     ggtitle(paste("Treatment Combination", i, "(Intervention/Control)")) +
#     theme_minimal() +
#     theme(
#       plot.title = element_text(hjust = 0.5),
#       axis.text = element_blank(),
#       axis.ticks = element_blank(),
#       axis.title = element_blank()
#     )
#   
#   # Print plot to display
#   print(p)
#   
#   # Short delay to prevent overloading the graphics device
#   Sys.sleep(0.3)  # Adjust as needed
# }
```

- Combos that satisfy "block stratification": 313 & 612
- Combos that satisfy "random sampling/other" (intervention districts adjacent to each other): all others!

```{r Identify trt/ctrl combos satisfying block stratification}
### Identify combinations that satisfy block stratification rules ###
# Intervention neighbors with only control and vice versa
# Define neighbors using Rook's contiguity (used in simulation)
rook_neighbors <- list(
  "1" = c(2, 5), # Cell 1 neighbors
  "2" = c(1, 3, 6), # Cell 2 neighbors
  "3" = c(2, 4, 7), # Cell 3 neighbors
  "4" = c(3, 8), # Cell 4 neighbors
  "5" = c(1, 6, 9), # Cell 5 neighbors
  "6" = c(2, 5, 7, 10), # Cell 6 neighbors
  "7" = c(3, 6, 8, 11), # Cell 7 neighbors
  "8" = c(4, 7, 12), # Cell 8 neighbors
  "9" = c(5, 10), # Cell 9 neighbors
  "10" = c(6, 9, 11), # Cell 10 neighbors
  "11" = c(7, 10, 12), # Cell 11 neighbors
  "12" = c(8, 11) # Cell 9 neighbors
)

# Generate all 6-intervention, 6-control assignments (used in simulation)
districts <- 1:12
combinations <- combn(districts, 6, simplify = FALSE)
###########################################################################
# Function 1: Check if an assignment satisfies full block stratification
is_valid_assignment_full <- function(intervention_cells) {
  
  # Convert to character for lookup
  intervention_cells <- as.character(intervention_cells)
  
  # Determine control cells
  control_cells <- setdiff(as.character(districts), intervention_cells)
  
  # Check Rook's contiguity for intervention cells
  for (cell in intervention_cells) {
    neighbors <- as.character(rook_neighbors[[cell]])
    if (any(neighbors %in% intervention_cells)) {
      return(FALSE)  # Found an intervention neighbor -> Invalid
    }
  }
  
  # Check Rook's contiguity for control cells
  for (cell in control_cells) {
    neighbors <- as.character(rook_neighbors[[cell]])
    if (any(neighbors %in% control_cells)) {
      return(FALSE)  # Found a control neighbor -> Invalid
    }
  }
  
  return(TRUE)  # If all conditions passed, this assignment is valid!
}

# Function 2: Check if an assignment satisfies intervention-only separation
is_valid_assignment_intervention_only <- function(intervention_cells) {
  
  # Convert to character for lookup
  intervention_cells <- as.character(intervention_cells)
  
  # Check Rook's contiguity ONLY for intervention cells
  for (cell in intervention_cells) {
    neighbors <- as.character(rook_neighbors[[cell]])
    if (any(neighbors %in% intervention_cells)) {
      return(FALSE)  # Found an intervention neighbor -> Invalid
    }
  }
  
  return(TRUE)  # If all conditions passed, this assignment is valid!
}

###########################################################################
### Apply functions to all 924 assignments ###
valid_combinations_full <- Filter(is_valid_assignment_full, combinations)
valid_combinations_intervention_only <- Filter(is_valid_assignment_intervention_only, combinations)

###########################################################################
### Print counts and contents of valid assignments ###
print(paste("Number of valid assignments (full separation):", length(valid_combinations_full)))
print(paste("Number of valid assignments (intervention-only separation):", length(valid_combinations_intervention_only)))

# Print valid assignments for full separation
if (length(valid_combinations_full) > 0) {
  for (i in seq_along(valid_combinations_full)) {
    cat(sprintf("Full Separation - Valid Combination %d: Intervention = %s, Control = %s\n", 
                i, paste(valid_combinations_full[[i]], collapse = ", "), 
                paste(setdiff(districts, valid_combinations_full[[i]]), collapse = ", ")))
  }
}

# Print valid assignments for intervention-only separation
if (length(valid_combinations_intervention_only) > 0) {
  for (i in seq_along(valid_combinations_intervention_only)) {
    cat(sprintf("Intervention-Only Separation - Valid Combination %d: Intervention = %s, Control = %s\n", 
                i, paste(valid_combinations_intervention_only[[i]], collapse = ", "), 
                paste(setdiff(districts, valid_combinations_intervention_only[[i]]), collapse = ", ")))
  }
}

### Print indices of all combinations where these sets occur ###
valid_indices_full <- which(sapply(combinations, is_valid_assignment_full))
valid_indices_intervention_only <- which(sapply(combinations, is_valid_assignment_intervention_only))

print(paste("Valid combinations (full separation) occur at indices:", paste(valid_indices_full, collapse = ", ")))
print(paste("Valid combinations (intervention-only separation) occur at indices:", paste(valid_indices_intervention_only, collapse = ", ")))

###########################################################################
### Print Plots of trt/ctrl combos satisfying block stratification ###
# Function to plot a specific treatment combination
plot_combination <- function(index, intervention_cells) {
  # Assign intervention (1) and control (0)
  treatment_assignment <- rep(0, 12)
  treatment_assignment[intervention_cells] <- 1  # Mark intervention cells
  
  # Convert to factor for coloring
  label_sf$treatment <- factor(treatment_assignment, levels = c(0, 1), labels = c("Control", "Intervention"))
  
  # Plot the treatment layout
  ggplot() +
    geom_sf(data = districts_sf, aes(fill = label_sf$treatment), color = "black") +
    geom_sf_text(data = label_sf, aes(label = district), size = 5, color = "black") +
    scale_fill_manual(values = c("Control" = "blue", "Intervention" = "red")) +
    labs(fill = "Treatment") +
    ggtitle(paste("Treatment Combination", index, "(Intervention/Control)")) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    )
}

# # Loop through valid indices and print the plots for full separation
# for (valid_index in valid_indices_full) {
#   print(plot_combination(valid_index, combinations[[valid_index]]))
# }
# 
# # Loop through valid indices and print the plots for intervention-only separation
# for (valid_index in valid_indices_intervention_only) {
#   print(plot_combination(valid_index, combinations[[valid_index]]))
# }
```

- Note: combos 313 & 612 both have the "checkerboard" pattern that we see for block stratification when the number of intervention & control districts are the same.

### Simulation Datasets

```{r}
### Setup simulation datasets, neighbor matrix, treatment combos ###
# Define neighbors using Rook's contiguity (used in simulation)
rook_neighbors <- list(
  "1" = c(2, 5), # Cell 1 neighbors
  "2" = c(1, 3, 6), # Cell 2 neighbors
  "3" = c(2, 4, 7), # Cell 3 neighbors
  "4" = c(3, 8), # Cell 4 neighbors
  "5" = c(1, 6, 9), # Cell 5 neighbors
  "6" = c(2, 5, 7, 10), # Cell 6 neighbors
  "7" = c(3, 6, 8, 11), # Cell 7 neighbors
  "8" = c(4, 7, 12), # Cell 8 neighbors
  "9" = c(5, 10), # Cell 9 neighbors
  "10" = c(6, 9, 11), # Cell 10 neighbors
  "11" = c(7, 10, 12), # Cell 11 neighbors
  "12" = c(8, 11) # Cell 9 neighbors
)

# Generate all 4-intervention, 4-control assignments (used in simulation)
districts <- 1:12
combinations <- combn(districts, 6, simplify = FALSE)

# Create a single 8x8 district adjacency matrix (rook neighbors)
neighbor_matrix <- matrix(0, nrow = 12, ncol = 12, dimnames = list(1:12, 1:12))

# Fill in the adjacency matrix based on rook_neighbors
for (i in 1:12) {
  if (!is.null(rook_neighbors[[as.character(i)]])) {
    neighbor_matrix[i, rook_neighbors[[as.character(i)]]] <- 1
  }
}

# initialize object to store all N=50 datasets
simulated_datasets <- matrix(list(), nrow = N, ncol = Num.Combos) # 70 combinations * 50 datasets

# indicator based w/ spatial correlation (estimates for each combo of trt/ctrl assignments)
alpha_estimates <- matrix(, nrow = N, ncol = Num.Combos) # baseline response
alpha_estimates_SE <- matrix(, nrow = N, ncol = Num.Combos)
beta_estimates <- matrix(, nrow = N, ncol = Num.Combos) # intervention effect
beta_estimates_SE <- matrix(, nrow = N, ncol = Num.Combos)
psi_estimates <- matrix(, nrow = N, ncol = Num.Combos) # spillover effect
psi_estimates_SE <- matrix(, nrow = N, ncol = Num.Combos)
rho_estimates <- matrix(, nrow = N, ncol = Num.Combos) # spatial correlation
rho_estimates_SE <- matrix(, nrow = N, ncol = Num.Combos)

# Generate all 70 treatment assignments combinations
districts <- 1:12
combinations <- combn(districts, 6, simplify = FALSE)

# Function to assign district based on the coordinates for 3x3 grid
assign_district <- function(x, y) {
  if (x >= 0   & x < 100  & y >= 200 & y < 300) return(1) # row 1 (left)
  if (x >= 100 & x < 200  & y >= 200 & y < 300) return(2)
  if (x >= 200 & x < 300  & y >= 200 & y < 300) return(3)
  if (x >= 300 & x < 400  & y >= 200 & y < 300) return(4) # row 1 (right)

  if (x >= 0   & x < 100  & y >= 100 & y < 200) return(5) # row 2 (left)
  if (x >= 100 & x < 200  & y >= 100 & y < 200) return(6)
  if (x >= 200 & x < 300  & y >= 100 & y < 200) return(7)
  if (x >= 300 & x < 400  & y >= 100 & y < 200) return(8) # row 2 (right)

  if (x >= 0   & x < 100  & y >= 0   & y < 100) return(9) # row 3 (left)
  if (x >= 100 & x < 200  & y >= 0   & y < 100) return(10)
  if (x >= 200 & x < 300  & y >= 0   & y < 100) return(11)
  if (x >= 300 & x < 400  & y >= 0   & y < 100) return(12) # row 4 (right)
}
```

### Simulation Loop

- for each set of trt/control assignments, generate 20 subjects in each cell (180 total).
- generate response: assign baseline effect, treatment effect, spillover effect (fixed amount to neighbor cells)
- fit spatial lag model to compute: baseline estimate, direct effect estimate, spillover effect estimate, spatial autocorrelation parameter estimate
- iterate over each set of trt/control assignments and aggregate estimates for each parameter
- compare: (1) random assignment vs. (2) block stratified)

- Spatial Lag Model: $$y = \rho Wy + X\beta + \varepsilon$$

```{r Spatial Effects Simulation}
### Loop over (70 trt combos) and (N resampled point sets) ###
# 1) generate datasets, 2) compute response, 3) obtain parameter estimates
# compare methods: (A) simple random assignment (all indices) vs. (B) block stratification (28, 43)
####################################################################################################
# Outer loop: iterate over each intervention/control combination (70 combos)
for (combo_index in 1:length(combinations)) {
  # Get the current intervention/control combination (set of cells receiving intervention)
  current_combination <- combinations[[combo_index]]
  
  # Inner loop: iterate over the number of datasets (N) to generate for each combination
  for (dataset_num in 1:N) {
    start_time <- Sys.time() # start timer for each iteration (50 reps x 70 combos = 3500 iterations)
    
    # Simulate random points on the grid with integer coordinates
    points <- tibble(x = sample(1:grid_width-1, points_per_iteration, replace = TRUE),
                     y = sample(1:grid_height-1, points_per_iteration, replace = TRUE))
    
    # Convert points to sf objects
    points_sf <- st_as_sf(points, coords = c("x", "y"), crs = NA_crs_)
    
    # Assign districts based on the x and y coordinates
    points$district <- mapply(assign_district, points$x, points$y)
    ####################################################################################################
    # Assign the intervention/control treatment based on the district for the current trt cell combo
    points$treatment <- ifelse(points$district %in% current_combination, "intervention", "control")
    points$intervention <- ifelse(points$treatment == "intervention", 1, 0)
    points$spillover <- 0 # initialize spillover vector (will change to 1 if nb.i & trt.i = 1)
    
    # Add neighbor columns (nb.1 to nb.8) and treatment columns (trt.1 to trt.8)
    for (i in 1:12) {
      points[[paste0("nb.", i)]] <- ifelse(points$district %in% rook_neighbors[[as.character(i)]], 1, 0)
      points[[paste0("trt.", i)]] <- ifelse(i %in% current_combination, 1, 0)
    }
    
    # Assign spillover if a point has a neighboring treated district (points in trt can't get spillover)
    # # only allow spillover on control districts (case 1)
    # for (i in 1:8) {
    #   points$spillover <- ifelse(points[[paste0("nb.", i)]] == 1 & 
    #                                points[[paste0("trt.", i)]] == 1 & 
    #                                points$treatment == "control", 1, points$spillover)
    # }
    
    # allow spillover on intervention & control districts (case 2)
    for (i in 1:12) {
      points$spillover <- ifelse(points[[paste0("nb.", i)]] == 1 & 
                                   points[[paste0("trt.", i)]] == 1, 1, points$spillover)
    }
    
    # Remove unnecessary columns after assigning spillover
    points <- points %>% select(-starts_with("nb."), -starts_with("trt."))
    ####################################################################################################
    ### Generate Response w/ Spatial Lag Model for all points ###
    # generate response (based on intervention/spillover status)
    # Assign neighbors to the neighbor_matrix based on district adjacency (replacement of dlist and W matrix)
    neighbor_matrix <- matrix(0, points_per_iteration, points_per_iteration)  # Initialize a zero matrix
    for (i in 1:points_per_iteration) {
      # Get the district of the current point
      district_i <- points$district[i]
      
      # Find which districts are neighbors of the current district
      neighbors <- rook_neighbors[[as.character(district_i)]]
      
      # For each neighbor district, mark the appropriate points in the neighbor_matrix as neighbors
      for (neighbor_district in neighbors) {
        # Find all points in the neighbor district
        neighbor_indices <- which(points$district == neighbor_district)
        
        # Mark these points as neighbors of point i
        neighbor_matrix[i, neighbor_indices] <- 1
      }
    }
    W <- as.matrix(neighbor_matrix)
    
    # create identity matrix
    I <- diag(points_per_iteration) 
    
    # add random noise (epsilon)
    epsilon <- rnorm(points_per_iteration, mean = 0, sd = sd) 
    
    # linear response: A + XBeta + ZPsi + E
    linear_response <- alpha + (beta*points$intervention) + (psi*points$spillover) + epsilon 
    
    # compute spatial lag response (solve for y using closed-form expression)
    A <- I - rho * W # (I - rho*W)
    points$response <- solve(A, linear_response) # (I - rho W)^(-1) * (a + XB + e) - simultaneous response
    ####################################################################################################
    ### Fit Spatial Lag Model for Parameter Estimation on response values ###
    # Convert the matrix to a neighbor list (listw)
    listw <- mat2listw(W, style = "W")  # 'style = "W"' ensures row-standardized weights

    # fit the model
    model <- lagsarlm(response ~ intervention + spillover, 
                          data = points, listw = listw) # lag SAR lm
    ####################################################################################################
    # ### Extract Model Parameters (alpha/beta/psi/rho) ###
    # parameter estimates
    alpha_estimates[dataset_num, combo_index] <- coef(model)[2] # intercept (alpha) -> row=interation/col=combo
    beta_estimates[dataset_num, combo_index] <- coef(model)[3] # intervention effect (beta) -> row=interation/col=combo
    psi_estimates[dataset_num, combo_index] <- coef(model)[4] # spillover effect (psi) -> row=interation/col=combo
    rho_estimates[dataset_num, combo_index] <- coef(model)[1] # spatial correlation (rho) -> row=interation/col=combo

    # estimate standard errors
    alpha_estimates_SE[dataset_num, combo_index] <- summary(model)$Coef[1,2] # intercept (alpha)
    beta_estimates_SE[dataset_num, combo_index] <- summary(model)$Coef[2,2] # intervention effect (beta)
    psi_estimates_SE[dataset_num, combo_index] <- tryCatch(summary(model)$Coef[3, 2],
                                                           error = function(e) NA
                                                           ) # spillover effect (psi)
    rho_estimates_SE[dataset_num, combo_index] <- summary(model)$rho.se # spatial correlation (rho)
    ####################################################################################################
    # Save the dataset in the appropriate row (dataset_num) and column (combo_index)
    simulated_datasets[[dataset_num, combo_index]] <- points
    # measure elapsed time for iteration
    elapsed_time <- Sys.time() - start_time
    # print elapsed time for iteration
    cat(sprintf("Iteration %d-%d: %.2f seconds elapsed\n", 
                combo_index, dataset_num, as.numeric(elapsed_time, units = "secs")))
  }
}

# print first sim dataset iteration
print(simulated_datasets[[dataset_num,combo_index]])
table(simulated_datasets[[dataset_num,combo_index]][,3]) # table of district assignments
```

```{r}
### Print simulated dataset points on the spatial object ###
# Plot the spatial object and the simulated points
ggplot() +
  # Plot the spatial grid (districts)
  geom_sf(data = districts_sf, fill = "white", color = "black") +
  
  # Plot the points, colored by district
  geom_sf(data = points_sf, aes(color = as.factor(points$district)), size = 2) +
  
  # Customize the color scale for districts
  scale_color_manual(values = c("1" = "red", "2" = "blue", "3" = "green", "4" = "seagreen3", 
                                "5" = "purple", "6" = "orange", "7" = "hotpink", "8" = "darkturquoise", "9" = "dodgerblue")) +
  
  # Add labels and titles
  labs(color = "District") +
  theme_minimal() +
  ggtitle("Simulated Points on Districts Grid") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )
```

```{r}
### Save current R environment (after simulation) ###
#save.image(file='SpatialSim_NC_DOC_noTrtSpill.RData') # save environment
#load('SpatialSim_NC_DOC_noTrtSpill.RData') # load environment objects

#save.image(file='SpatialSim_NC_DOC_TrtSpill.RData') # save environment
#load('SpatialSim_NC_DOC_TrtSpill.RData') # load environment objects
```

### Model Parameter Estimates (all combos at the same time)

```{r compute bias, variance, and mse for model estiamtes}
### Compute bias, variance, mse for each combination ###
compute_metrics <- function(beta_estimates, true_value) {
  results <- as.data.frame(t(apply(beta_estimates, 2, function(estimates) {
    bias <- mean(estimates) - true_value
    bias.abs <- abs(mean(estimates) - true_value)
    variance <- var(estimates)
    mse <- mean((estimates - true_value)^2)
    return(c(bias = bias, bias.abs = bias.abs, variance = variance, MSE = mse))
  })))
  return(results)
}

# results for alpha & beta
beta.mse <- compute_metrics(beta_estimates, true_value = beta)
alpha.mse <- compute_metrics(alpha_estimates, true_value = alpha)
psi.mse <- compute_metrics(psi_estimates, true_value = psi)
rho.mse <- compute_metrics(rho_estimates, true_value = rho)

# save results to CSV (AX_BX_PX_RX where X is the value)
# write.csv(beta.mse, "beta_mse/beta_mse_results_TrtSpill_3x4_A02_B1_P08_R001.csv", row.names = TRUE)
# write.csv(alpha.mse, "alpha_mse/alpha_mse_results_TrtSpill_3x4_A02_B1_P08_R001.csv", row.names = TRUE)
# write.csv(psi.mse, "psi_mse/psi_mse_results_TrtSpill_3x4_A02_B1_P08_R001.csv", row.names = TRUE)
# write.csv(rho.mse, "rho_mse/rho_mse_results_TrtSpill_3x4_A02_B1_P08_R001.csv", row.names = TRUE)

#write.csv(beta.mse, "beta_mse_results_noTrtSpill.csv", row.names = TRUE)
#write.csv(beta.mse, "beta_mse_results_TrtSpill.csv", row.names = TRUE)
```