---
title: "SpatialSim_NC_DOC"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output: html_document
---

### Goal

- The purpose of this code is to design a spatial simulation where the direct and indirect effects of an arbitrary intervention are assessed over a grid structure designed to be representative of the spatial arrangement of districts in eastern North Carolina. This space is divided into 8 districts.

- Each district is composed of a possible number of counties in North Carolina and has approximately 20 subjects (law enforcement officers) upon which the intervention (training) is applied. (Do we allow 20 to vary by randomly selecting across the whole space?)

- Each of the 8 districts will be assigned to either the intervention or control based on one of two possible methods: (1) intervention assigned randomly to 4 districts, (2) intervention and control assigned according to "blocking" stratification where pairs of adjacent cells/districts are assigned as one to intervention and the other to control. This strategy prefers that adjacent cells are not either both intervention or both control. 

- A third assignment strategy will be considered in a subsequent project where (3) intervention is assigned to districts with consideration for underlying case incidence levels and effort to isolate intervention districts with control districts surrounding

- For method (1), all permutations of the arrangement of 4 intervention and 4 control districts will be simulated to determine the overall "consistency" (variance) of the estimate of the direct effect (intervention).

- Our overall goal is to understand whether method (1) or (2) leads to an overall more consistent (less variable among many simulations) estimate of the intervention effect. In all cases, spillover effects may be observed in districts neighboring the districts assigned to have an intervention applied.

### Preliminaries

```{r Load Libraries, message=FALSE, warning=FALSE}
# set seed
set.seed(2024) # ensures reproducibility

# load packages
library(tidyverse)
library(ggplot2)
library(sf) # simple features-store/manipulate spatial data
library(reshape2)
library(gridExtra)
library(spdep)
library(spatialreg)
library(tictoc) # measure function elapsed time
library(combinat)
```

```{r Initiate Constants}
### Set Constants ###
# parameters for simulation
N <- 50 # number of datasets to generate (iterate over each trt combo for each - 50*70=3500)  
Num.Combos <- 70 # Number of trt combos to iterate over
points_per_iteration <- 160  # Number of points per dataset (20 per district)
grid_width <- 400 # Set dimensions of grid for simulated data
grid_height <- 200
cell_length <- 100

# Define response model constants (true values)
alpha <- 0.2 # intercept/baseline effecgt
beta <- 1 # consider a range of intervention effects (start with Null case -> 1)
psi <- 0.8 # maximum spillover effect (binary)
rho <- 0.00 # spatial correlation parameter
sd <- 0.1 # set standard deviation (for epsilon) -> change this to reduce "noise"/more consistent estimates
```

- There are 70 possible combinations of the (1) simple random assignment intervention/control strategy and 10 possible combinations of the (2) blocking stratification strategy. We can ID the appropriate indices of the blocking stratification treatment assignments to use for comparison to the random assignment method (70 cases vs. 10 cases).

### Data Setup

```{r Identify all combinations of 4 Intervention & Control}
### Generate combinations of 8 districts (4 intervention, 4 control)
# Create a vector representing the 8 districts
districts <- 1:8

# Generate all combinations of 4 intervention districts out of 8
combinations <- combn(districts, 4)

# Initialize an empty data frame for the results
results <- data.frame(Combination = 1:ncol(combinations))

# Loop through each combination and create a row for the table
for (i in 1:ncol(combinations)) {
  # Create a vector of 0s (control) and 1s (intervention)
  treatment_assignment <- ifelse(districts %in% combinations[, i], 1, 0)
  
  # Add the treatment assignment for this combination as a new column
  results[i, 2:9] <- treatment_assignment
}

# Rename the columns
colnames(results) <- c('Combination', paste('Cell', 1:8))

# Print the results table
print(results)
```

```{r Assign table of Rook Neighbors for 8 districts}
### Table of Rook Neighbor Assignments ###
# neighbors are cells that are directly adjacent - "rook" case contiguity (not diagonal) to a reference cell
# Initialize the 8x8 matrix with zeros (no neighbors initially)
neighbor_matrix <- matrix(0, nrow = 8, ncol = 8)

# Define the neighbor relationships (cells are indexed from 1 to 8)
rook_neighbors <- list(
  `1` = c(2, 3), # Cell 1 neighbors
  `2` = c(1, 4), # Cell 2 neighbors
  `3` = c(1, 4, 5), # Cell 3 neighbors
  `4` = c(2, 3, 6), # Cell 4 neighbors
  `5` = c(3, 6, 7), # Cell 5 neighbors
  `6` = c(4, 5, 8), # Cell 6 neighbors
  `7` = c(5, 8), # Cell 7 neighbors
  `8` = c(6, 7) # Cell 8 neighbors
)

# Loop through each cell and mark its neighbors in the matrix
for (cell in names(rook_neighbors)) {
  for (neighbor in rook_neighbors[[cell]]) {
    neighbor_matrix[as.numeric(cell), neighbor] <- 1
  }
}

# Print the resulting matrix
print(neighbor_matrix)
```
- List of neighbors (rook case contiguity) for 8 cell 2x4 spatial polygon

### Setup Spatial Polygons

```{r Define spatial polygon 2x4 grid}
### Define the coordinates for each district (100x100 units) ###
district_1 <- st_polygon(list(matrix(c(300, 100, 400, 100, 400, 200, 300, 200, 300, 100), 
                                     ncol = 2, byrow = TRUE))) # District 1 (top-right)
district_2 <- st_polygon(list(matrix(c(300, 0, 400, 0, 400, 100, 300, 100, 300, 0), 
                                     ncol = 2, byrow = TRUE))) # District 2 (bottom-right)
district_3 <- st_polygon(list(matrix(c(200, 100, 300, 100, 300, 200, 200, 200, 200, 100), 
                                     ncol = 2, byrow = TRUE))) # District 3 (top-center-right)
district_4 <- st_polygon(list(matrix(c(200, 0, 300, 0, 300, 100, 200, 100, 200, 0), 
                                     ncol = 2, byrow = TRUE))) # District 4 (bottom-center-right)
district_5 <- st_polygon(list(matrix(c(100, 100, 200, 100, 200, 200, 100, 200, 100, 100), 
                                     ncol = 2, byrow = TRUE))) # District 5 (top-center-left)
district_6 <- st_polygon(list(matrix(c(100, 0, 200, 0, 200, 100, 100, 100, 100, 0), 
                                     ncol = 2, byrow = TRUE))) # District 6 (bottom-center-left)
district_7 <- st_polygon(list(matrix(c(0, 100, 100, 100, 100, 200, 0, 200, 0, 100), 
                                     ncol = 2, byrow = TRUE))) # District 7 (top-left)
district_8 <- st_polygon(list(matrix(c(0, 0, 100, 0, 100, 100, 0, 100, 0, 0), 
                                     ncol = 2, byrow = TRUE))) # District 8 (bottom-left)

# Combine all districts into one list
districts_list <- list(district_1, district_2, district_3, district_4, district_5, district_6, district_7, district_8)
districts_sf <- st_sfc(districts_list, crs = NA_crs_) # this is the spatial object?

### Manually Adjusted Centroids ###
district_names <- c("1", "2", "3", "4", "5", "6", "7", "8")
label_positions <- data.frame(
  district = district_names,
  x = c(350, 350, 250, 250, 150, 150, 50, 50),  # X-coordinates
  y = c(150, 50, 150, 50, 150, 50, 150, 50)     # Y-coordinates
)
label_sf <- st_as_sf(label_positions, coords = c("x", "y"), crs = NA_crs_)

# Plot with corrected labels
ggplot() +
  geom_sf(data = districts_sf, fill = "white", color = "black") +
  geom_sf_text(data = label_sf, aes(label = district), size = 5, color = "black") +
  theme_minimal() +
  ggtitle("Spatial region with district labels (1-8)") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )

# ### Example: Plot single random treatment assignment combination ###
# # Randomly assign 4 districts as intervention (1) and the remaining 4 as control (0)
# treatment_assignment <- sample(c(1, 0), 8, replace = TRUE)
# treatment_assignment[order(treatment_assignment)] <- c(rep(1, 4), rep(0, 4))  # Ensure 4 intervention and 4 control
# 
# # Add treatment column to centroids_sf
# label_sf$treatment <- factor(treatment_assignment, levels = c(0, 1), labels = c("Control", "Intervention"))
# 
# # Plot the districts with labels and color by treatment
# ggplot() +
#   geom_sf(data = districts_sf, aes(fill = label_sf$treatment), color = "black") +
#   geom_sf_text(data = label_sf, aes(label = district), size = 5, color = "black") +
#   scale_fill_manual(values = c("Control" = "blue", "Intervention" = "red")) +
#   labs(fill = "Treatment") +
#   theme_minimal() +
#   ggtitle("Spatial Layout with Treatment Assignment") +
#   theme(
#     plot.title = element_text(hjust = 0.5),
#     axis.text = element_blank(),
#     axis.ticks = element_blank(),
#     axis.title = element_blank()
#   )
```

```{r Plot all possible treatment assignment combos}
### Plot Treatment assignments for all possible combinations ###
# Generate all 70 treatment assignments
districts <- 1:8
combinations <- combn(districts, 4, simplify = FALSE)

# Loop through each treatment combination and plot
for (i in seq_along(combinations)) {
  
  # Assign intervention (1) and control (0) based on the current combination
  treatment_assignment <- ifelse(districts %in% combinations[[i]], 1, 0)
  
  # Convert to factor with labels
  label_sf$treatment <- factor(treatment_assignment, levels = c(0, 1), labels = c("Control", "Intervention"))
  
  # Generate plot
  p <- ggplot() +
    geom_sf(data = districts_sf, aes(fill = label_sf$treatment), color = "black") +
    geom_sf_text(data = label_sf, aes(label = district), size = 5, color = "black") +
    scale_fill_manual(values = c("Control" = "blue", "Intervention" = "red")) +
    labs(fill = "Treatment") +
    ggtitle(paste("Treatment Combination", i, "(Intervention/Control)")) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    )
  
  # Print plot to display
  print(p)
  
  # Short delay to prevent overloading the graphics device
  Sys.sleep(0.3)  # Adjust as needed
}
```

```{r Identify trt/ctrl combos satisfying block stratification}
### Identify combinations that satisfy block stratification rules ###
# Intervention neighbors with only control and vice versa
# Define neighbors using Rook's contiguity (used in simulation)
rook_neighbors <- list(
  "1" = c(2,3),
  "2" = c(1,4),
  "3" = c(1,4,5),
  "4" = c(2,3,6),
  "5" = c(3,6,7),
  "6" = c(4,5,8),
  "7" = c(5,8),
  "8" = c(6,7)
)

# Generate all 4-intervention, 4-control assignments (used in simulation)
districts <- 1:8
combinations <- combn(districts, 4, simplify = FALSE)
###########################################################################
# Function to check if an assignment satisfies the separation rule (block stratification)
is_valid_assignment <- function(intervention_cells) {
  
  # Convert to character for lookup
  intervention_cells <- as.character(intervention_cells)
  
  # Determine control cells
  control_cells <- setdiff(as.character(districts), intervention_cells)
  
  # Check Rook's contiguity
  for (cell in intervention_cells) {
    neighbors <- as.character(rook_neighbors[[cell]])
    if (any(neighbors %in% intervention_cells)) {
      return(FALSE)  # Found an intervention neighbor -> Invalid
    }
  }
  
  for (cell in control_cells) {
    neighbors <- as.character(rook_neighbors[[cell]])
    if (any(neighbors %in% control_cells)) {
      return(FALSE)  # Found a control neighbor -> Invalid
    }
  }
  
  return(TRUE)  # If all conditions passed, this assignment is valid!
}

# Apply function to all 70 assignments
valid_combinations <- Filter(is_valid_assignment, combinations)
###########################################################################
### Print count and contents of valid assignments ###
print(paste("Number of valid assignments:", length(valid_combinations)))

# Print valid assignments
if (length(valid_combinations) > 0) {
  for (i in seq_along(valid_combinations)) {
    cat(sprintf("Valid Combination %d: Intervention = %s, Control = %s\n", 
                i, paste(valid_combinations[[i]], collapse = ", "), 
                paste(setdiff(districts, valid_combinations[[i]]), collapse = ", ")))
  }
}

### Print indices of all combinations where these sets occur ###
# Store valid indices
valid_indices <- which(sapply(combinations, is_valid_assignment))

# Print the valid indices
print(paste("Valid combinations occur at indices:", paste(valid_indices, collapse = ", ")))

### Print Plots of trt/ctrl combos satisfying block stratification ###
# Function to plot a specific treatment combination
plot_combination <- function(index, intervention_cells) {
  # Assign intervention (1) and control (0)
  treatment_assignment <- rep(0, 8)
  treatment_assignment[intervention_cells] <- 1  # Mark intervention cells
  
  # Convert to factor for coloring
  label_sf$treatment <- factor(treatment_assignment, levels = c(0, 1), labels = c("Control", "Intervention"))
  
  # Plot the treatment layout
  ggplot() +
    geom_sf(data = districts_sf, aes(fill = label_sf$treatment), color = "black") +
    geom_sf_text(data = label_sf, aes(label = district), size = 5, color = "black") +
    scale_fill_manual(values = c("Control" = "blue", "Intervention" = "red")) +
    labs(fill = "Treatment") +
    ggtitle(paste("Treatment Combination", index, "(Intervention/Control)")) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank()
    )
}

# Loop through valid indices and print the plots
for (valid_index in valid_indices) {
  print(plot_combination(valid_index, combinations[[valid_index]]))
}
```

### Simulation Datasets

```{r}
### Setup simulation datasets, neighbor matrix, treatment combos ###
# Define neighbors using Rook's contiguity (used in simulation)
rook_neighbors <- list(
  "1" = c(2,3),
  "2" = c(1,4),
  "3" = c(1,4,5),
  "4" = c(2,3,6),
  "5" = c(3,6,7),
  "6" = c(4,5,8),
  "7" = c(5,8),
  "8" = c(6,7)
)

# Generate all 4-intervention, 4-control assignments (used in simulation)
districts <- 1:8
combinations <- combn(districts, 4, simplify = FALSE)

# Create a single 8x8 district adjacency matrix (rook neighbors)
neighbor_matrix <- matrix(0, nrow = 8, ncol = 8, dimnames = list(1:8, 1:8))

# Fill in the adjacency matrix based on rook_neighbors
for (i in 1:8) {
  if (!is.null(rook_neighbors[[as.character(i)]])) {
    neighbor_matrix[i, rook_neighbors[[as.character(i)]]] <- 1
  }
}

# initialize object to store all N=50 datasets
simulated_datasets <- matrix(list(), nrow = N, ncol = Num.Combos) # 70 combinations * 50 datasets

# indicator based w/ spatial correlation (estimates for each combo of trt/ctrl assignments)
alpha_estimates <- matrix(, nrow = N, ncol = Num.Combos) # baseline response
alpha_estimates_SE <- matrix(, nrow = N, ncol = Num.Combos)
beta_estimates <- matrix(, nrow = N, ncol = Num.Combos) # intervention effect
beta_estimates_SE <- matrix(, nrow = N, ncol = Num.Combos)
psi_estimates <- matrix(, nrow = N, ncol = Num.Combos) # spillover effect
psi_estimates_SE <- matrix(, nrow = N, ncol = Num.Combos)
rho_estimates <- matrix(, nrow = N, ncol = Num.Combos) # spatial correlation
rho_estimates_SE <- matrix(, nrow = N, ncol = Num.Combos)

# Generate all 70 treatment assignments combinations
districts <- 1:8
combinations <- combn(districts, 4, simplify = FALSE)

# Function to assign district based on the coordinates
assign_district <- function(x, y) {
  if (x >= 300 & x < 400 & y >= 100 & y < 200) return(1) # District 1
  if (x >= 200 & x < 300 & y >= 100 & y < 200) return(5) # District 5
  if (x >= 100 & x < 200 & y >= 100 & y < 200) return(7) # District 7
  if (x >= 0 & x < 100 & y >= 100 & y < 200) return(8)  # District 8
  if (x >= 300 & x < 400 & y >= 0 & y < 100) return(3)  # District 3
  if (x >= 200 & x < 300 & y >= 0 & y < 100) return(6)  # District 6
  if (x >= 100 & x < 200 & y >= 0 & y < 100) return(4)  # District 4
  if (x >= 0 & x < 100 & y >= 0 & y < 100) return(2)    # District 2
}
```

### Simulation Loop

- for each set of trt/control assignments, generate 20 subjects in each cell (160 total).
- generate response: assign baseline effect, treatment effect, spillover effect (fixed amount to neighbor cells)
- fit spatial lag model to compute: baseline estimate, direct effect estimate, spillover effect estimate, spatial autocorrelation parameter estimate
- iterate over each set of trt/control assignments and aggregate estimates for each parameter
- compare: (1) random assignment vs. (2) block stratified)

- Spatial Lag Model: $$y = \rho Wy + X\beta + \varepsilon$$

```{r Spatial Effects Simulation}
### Loop over (70 trt combos) and (N resampled point sets) ###
# 1) generate datasets, 2) compute response, 3) obtain parameter estimates
# compare methods: (A) simple random assignment (all indices) vs. (B) block stratification (28, 43)
####################################################################################################
# Outer loop: iterate over each intervention/control combination (70 combos)
for (combo_index in 1:length(combinations)) {
  # Get the current intervention/control combination (set of cells receiving intervention)
  current_combination <- combinations[[combo_index]]
  
  # Inner loop: iterate over the number of datasets (N) to generate for each combination
  for (dataset_num in 1:N) {
    start_time <- Sys.time() # start timer for each iteration (50 reps x 70 combos = 3500 iterations)
    
    # Simulate random points on the grid with integer coordinates
    points <- tibble(x = sample(1:grid_width-1, points_per_iteration, replace = TRUE),
                     y = sample(1:grid_height-1, points_per_iteration, replace = TRUE))
    
    # Convert points to sf objects
    points_sf <- st_as_sf(points, coords = c("x", "y"), crs = NA_crs_)
    
    # Assign districts based on the x and y coordinates
    points$district <- mapply(assign_district, points$x, points$y)
    ####################################################################################################
    # Assign the intervention/control treatment based on the district for the current trt cell combo
    points$treatment <- ifelse(points$district %in% current_combination, "intervention", "control")
    points$intervention <- ifelse(points$treatment == "intervention", 1, 0)
    points$spillover <- 0 # initialize spillover vector (will change to 1 if nb.i & trt.i = 1)
    
    # Add neighbor columns (nb.1 to nb.8) and treatment columns (trt.1 to trt.8)
    for (i in 1:8) {
      points[[paste0("nb.", i)]] <- ifelse(points$district %in% rook_neighbors[[as.character(i)]], 1, 0)
      points[[paste0("trt.", i)]] <- ifelse(i %in% current_combination, 1, 0)
    }
    
    # Assign spillover if a point has a neighboring treated district (points in trt can't get spillover)
    # can points in intervention receive spillover? or just points in control? (both when adjacent to intervention)
    for (i in 1:8) {
      points$spillover <- ifelse(points[[paste0("nb.", i)]] == 1 & 
                                   points[[paste0("trt.", i)]] == 1 & 
                                   points$treatment == "control", 1, points$spillover)
    }
    
    # Remove unnecessary columns after assigning spillover
    points <- points %>% select(-starts_with("nb."), -starts_with("trt."))
    ####################################################################################################
    ### Generate Response w/ Spatial Lag Model for all points ###
    # generate response (based on intervention/spillover status)
    # Assign neighbors to the neighbor_matrix based on district adjacency (replacement of dlist and W matrix)
    neighbor_matrix <- matrix(0, points_per_iteration, points_per_iteration)  # Initialize a zero matrix
    for (i in 1:points_per_iteration) {
      # Get the district of the current point
      district_i <- points$district[i]
      
      # Find which districts are neighbors of the current district
      neighbors <- rook_neighbors[[as.character(district_i)]]
      
      # For each neighbor district, mark the appropriate points in the neighbor_matrix as neighbors
      for (neighbor_district in neighbors) {
        # Find all points in the neighbor district
        neighbor_indices <- which(points$district == neighbor_district)
        
        # Mark these points as neighbors of point i
        neighbor_matrix[i, neighbor_indices] <- 1
      }
    }
    W <- as.matrix(neighbor_matrix)
    
    # create identity matrix
    I <- diag(points_per_iteration) 
    
    # add random noise (epsilon)
    epsilon <- rnorm(points_per_iteration, mean = 0, sd = sd) 
    
    # linear response: A + XBeta + ZPsi + E
    linear_response <- alpha + (beta*points$intervention) + (psi*points$spillover) + epsilon 
    
    # compute spatial lag response (solve for y using closed-form expression)
    A <- I - rho * W # (I - rho*W)
    points$response <- solve(A, linear_response) # (I - rho W)^(-1) * (a + XB + e) - simultaneous response
    ####################################################################################################
    ### Fit Spatial Lag Model for Parameter Estimation on response values ###
    # Convert the matrix to a neighbor list (listw)
    listw <- mat2listw(W, style = "W")  # 'style = "W"' ensures row-standardized weights

    # fit the model
    model <- lagsarlm(response ~ intervention + spillover, 
                          data = points, listw = listw) # lag SAR lm
    ####################################################################################################
    # ### Extract Model Parameters (alpha/beta/psi/rho) ###
    # parameter estimates
    alpha_estimates[dataset_num, combo_index] <- coef(model)[1] # intercept (alpha) -> row=interation/col=combo
    beta_estimates[dataset_num, combo_index] <- coef(model)[2] # intervention effect (beta) -> row=interation/col=combo
    #psi_estimates[dataset_num, combo_index] <- coef(model)[3] # spillover effect (psi) -> row=interation/col=combo
    rho_estimates[dataset_num, combo_index] <- model$rho # spatial correlation (rho) -> row=interation/col=combo

    # estimate standard errors
    alpha_estimates_SE[dataset_num, combo_index] <- summary(model)$Coef[1,2] # intercept (alpha)
    beta_estimates_SE[dataset_num, combo_index] <- summary(model)$Coef[2,2] # intervention effect (beta)
    #psi_estimates_SE[dataset_num, combo_index] <- summary(model)$Coef[3,2] # spillover effect (psi)
    rho_estimates_SE[dataset_num, combo_index] <- summary(model)$rho.se # spatial correlation (rho)
    ####################################################################################################
    # Save the dataset in the appropriate row (dataset_num) and column (combo_index)
    simulated_datasets[[dataset_num, combo_index]] <- points
    # measure elapsed time for iteration
    elapsed_time <- Sys.time() - start_time
    # print elapsed time for iteration
    cat(sprintf("Iteration %d-%d: %.2f seconds elapsed\n", 
                combo_index, dataset_num, as.numeric(elapsed_time, units = "secs")))
  }
}

# print first sim dataset iteration
print(simulated_datasets[[dataset_num,combo_index]])
table(simulated_datasets[[dataset_num,combo_index]][,3]) # table of district assignments
```

```{r}
### Print simulated dataset points on the spatial object ###
# Plot the spatial object and the simulated points
ggplot() +
  # Plot the spatial grid (districts)
  geom_sf(data = districts_sf, fill = "white", color = "black") +
  
  # Plot the points, colored by district
  geom_sf(data = points_sf, aes(color = as.factor(points$district)), size = 2) +
  
  # Customize the color scale for districts
  scale_color_manual(values = c("1" = "red", "2" = "blue", "3" = "green", "4" = "seagreen3", 
                                "5" = "purple", "6" = "orange", "7" = "hotpink", "8" = "darkturquoise")) +
  
  # Add labels and titles
  labs(color = "District") +
  theme_minimal() +
  ggtitle("Simulated Points on Districts Grid") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )
```

### Model Parameter Estimates (all combos at the same time)

```{r}
### Grand Means ###
# Random Sampling
RandomSampling <- data.frame(
  Parameter = c("Alpha", "Beta"),
  Mean = c(mean(alpha_estimates, na.rm = TRUE), 
           mean(beta_estimates, na.rm = TRUE)),
  SE = c(sqrt(mean(alpha_estimates_SE^2, na.rm = TRUE)), 
         sqrt(mean(beta_estimates_SE^2, na.rm = TRUE)))
)
print(RandomSampling)

# Block Stratification (28 & 43)
BlockStratification <- data.frame(
  Parameter = c("Alpha", "Beta"),
  Mean = c(mean(alpha_estimates[,c(28, 43)], na.rm = TRUE), 
           mean(beta_estimates[,c(28, 43)], na.rm = TRUE)),
  SE = c(sqrt(mean(alpha_estimates_SE[,c(28, 43)]^2, na.rm = TRUE)), 
         sqrt(mean(beta_estimates_SE[,c(28, 43)]^2, na.rm = TRUE)))
)
print(BlockStratification)
```
```{r}
# Combine datasets with a method identifier
RandomSampling$Method <- "Random Sampling"
BlockStratification$Method <- "Block Stratification"
comparison_df <- bind_rows(RandomSampling, BlockStratification)

# Create the plot with recoded labels for Alpha and Beta
ggplot(comparison_df, aes(x = recode(Parameter, "Alpha" = "Baseline", "Beta" = "Intervention"), 
                          y = Mean, color = Method)) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +  # Plot points
  geom_errorbar(aes(ymin = Mean - 1.96 * SE, ymax = Mean + 1.96 * SE),
                position = position_dodge(width = 0.5), width = 0.2) +  # Error bars for 95% CI
  labs(title = "Random vs. Blocking treatment assignment model estimates ",
       y = "Parameter Estimate",
       x = "Effect Type",
       color = "Treatment Assignment Method") +
  theme_minimal() +
  theme(text = element_text(size = 14), legend.position = "bottom")

```

- can we scale this due to the difference between 70 combos & 2 combos?
- at present, the block stratification method has a larger standard error of the baseline & intervention estimates (this isn't what we expected to see!)

### Model Parameter Estimates (1 random vs. 1 blocking)

```{r}
# Alpha: combo Means & SEs
AlphaMeans <- colMeans(alpha_estimates)
AlphaSEs <- apply(alpha_estimates, 2, function(x) sd(x) / sqrt(length(x)))
AlphaResults <- as.data.frame(cbind(AlphaMeans, AlphaSEs))
AlphaResults$Parameter <- "Alpha"
colnames(AlphaResults) <- c("Mean", "SE", "Parameter")

# Alpha: combo Means & SEs
BetaMeans <- colMeans(beta_estimates)
BetaSEs <- apply(beta_estimates, 2, function(x) sd(x) / sqrt(length(x)))
BetaResults <- as.data.frame(cbind(BetaMeans, BetaSEs))
BetaResults$Parameter <- "Beta"
colnames(BetaResults) <- c("Mean", "SE", "Parameter")

# Randomly Select 1 from 1-70 & 1 from 28 & 43 to compare
RandomSampleIndex <- sample(1:70, 1) # Randomly select an integer from 1 to 70
BlockStratificationIndex <- sample(c(28, 43), 1) # Randomly select integer from either 28 or 43

# combine alpha & beta results of randomly selected indices for the two methods
RandomSampleResult <- rbind(AlphaResults[RandomSampleIndex,], BetaResults[RandomSampleIndex,])
RandomSampleResult$Index <- RandomSampleIndex
RandomSampleResult$Method <- "Random Sampling"

BlockStratificationResult <- rbind(AlphaResults[BlockStratificationIndex,], BetaResults[BlockStratificationIndex,])
BlockStratificationResult$Index <- BlockStratificationIndex
BlockStratificationResult$Method <- "Block Stratification"

CombinedResults <- rbind(RandomSampleResult, BlockStratificationResult) # combine the random & block results

# Make Plot
ggplot(CombinedResults, aes(x = recode(Parameter, "Alpha" = "Baseline", "Beta" = "Intervention"), 
                          y = Mean, color = Method)) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +  # Plot points
  geom_errorbar(aes(ymin = Mean - 1.96 * SE, ymax = Mean + 1.96 * SE),
                position = position_dodge(width = 0.5), width = 0.2) +  # Error bars for 95% CI
  labs(title = "Random vs. Blocking treatment assignment model estimates ",
       y = "Parameter Estimate",
       x = "Effect Type",
       color = "Treatment Assignment Method") +
  theme_minimal() +
  theme(text = element_text(size = 14), legend.position = "bottom")
```

