---
title: "NC SUD Application: Smoke and Pilot Evaluation"
format:
  html:
    toc: true
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(dplyr)
library(ggplot2)
library(knitr)

app_dir <- dirname(knitr::current_input())
source(file.path(app_dir, "application_designs.R"))
result_dirs <- file.path(app_dir, "results", c("smoke", "pilot"))
available <- result_dirs[file.exists(file.path(result_dirs, "summary_results.csv"))]

read_profile <- function(dir, file) {
  path <- file.path(dir, file)
  if (file.exists(path)) read.csv(path, stringsAsFactors = FALSE) else NULL
}

summary_results <- bind_rows(lapply(available, read_profile, file = "summary_results.csv"))
region_balance <- bind_rows(lapply(available, function(dir) {
  x <- read_profile(dir, "region_balance_diagnostics.csv")
  if (!is.null(x)) x$profile <- basename(dir)
  x
}))
incidence_data <- bind_rows(lapply(available, function(dir) {
  x <- read_profile(dir, "synthetic_incidence.csv")
  if (!is.null(x)) x$profile <- basename(dir)
  x
}))
```

## Status

This report is intentionally limited to the `smoke` and `pilot` profiles. The full profile is defined but was not run in this phase because it requires 160,000 MLE fits. Results below validate the application pipeline and provide preliminary ranking behavior only; they are not final study evidence.

```{r}
if (nrow(summary_results) == 0) {
  cat("No smoke or pilot result files were found.")
} else {
  summary_results |>
    count(profile, name = "scenario_rows") |>
    kable()
}
```

```{r}
if (nrow(incidence_data) > 0 && "population_source" %in% names(incidence_data)) {
  incidence_data |>
    distinct(profile, population_source) |>
    kable(col.names = c("Profile", "Population source"))
}
```

## K-Means Region Balance

```{r}
if (nrow(region_balance) > 0) {
  region_balance |>
    select(profile, region_id, n_clusters, n_counties, population, population_share, mean_incidence_rank01) |>
    kable(digits = 3)
}
```

```{r}
pilot_region_map <- file.path(app_dir, "results", "pilot", "figures", "kmeans_regions_map.png")
smoke_region_map <- file.path(app_dir, "results", "smoke", "figures", "kmeans_regions_map.png")
region_map <- if (file.exists(pilot_region_map)) pilot_region_map else smoke_region_map
if (file.exists(region_map)) knitr::include_graphics(region_map)
```

## Synthetic Incidence

```{r}
pilot_incidence_map <- file.path(app_dir, "results", "pilot", "figures", "synthetic_incidence_map.png")
smoke_incidence_map <- file.path(app_dir, "results", "smoke", "figures", "synthetic_incidence_map.png")
incidence_map <- if (file.exists(pilot_incidence_map)) pilot_incidence_map else smoke_incidence_map
if (file.exists(incidence_map)) knitr::include_graphics(incidence_map)
```

## Design Performance

```{r}
if (nrow(summary_results) > 0) {
  summary_results |>
    mutate(
      design_short_name = factor(design_short_name, levels = APPLICATION_DESIGN_DISPLAY_ORDER),
      design_group = factor(design_group, levels = c("Blocking", "Stratified", "Saturation"))
    ) |>
    group_by(profile, design_id, design_short_name, design_group) |>
    summarise(
      mean_mse = mean(mse, na.rm = TRUE),
      mean_bias = mean(bias, na.rm = TRUE),
      mean_coverage = mean(coverage, na.rm = TRUE),
      mean_fail_rate = mean(fail_rate, na.rm = TRUE),
      .groups = "drop"
    ) |>
    arrange(profile, design_group, design_short_name) |>
    kable(digits = 4)
}
```

```{r}
if (nrow(summary_results) > 0) {
  plot_results <- summary_results |>
    mutate(
      design_short_name = factor(design_short_name, levels = APPLICATION_DESIGN_DISPLAY_ORDER),
      design_group = factor(design_group, levels = c("Blocking", "Stratified", "Saturation"))
    )

  ggplot(plot_results, aes(x = design_short_name, y = mse, fill = design_group)) +
    geom_boxplot() +
    coord_flip() +
    facet_wrap(~ profile, scales = "free_x") +
    scale_fill_manual(values = c("Blocking" = "#D55E00", "Stratified" = "#0072B2", "Saturation" = "#009E73")) +
    labs(x = NULL, y = "MSE", fill = "Design group", title = "Smoke/Pilot MSE by Design") +
    theme_minimal(base_size = 11)
}
```

## Pilot Ranking

```{r}
if (nrow(summary_results) > 0 && "pilot" %in% summary_results$profile) {
  summary_results |>
    filter(profile == "pilot") |>
    group_by(design_id, design_short_name, design_group) |>
    summarise(
      mean_mse = mean(mse, na.rm = TRUE),
      mean_bias = mean(bias, na.rm = TRUE),
      mean_coverage = mean(coverage, na.rm = TRUE),
      .groups = "drop"
    ) |>
    arrange(mean_mse) |>
    kable(digits = 4)
}
```

## Deferred Full Run

The full profile remains reserved for later execution:

- `tau = c(0.8, 1.0, 1.5, 2.0, 3.0)`
- `gamma = c(0.5, 0.6, 0.7, 0.8)`
- `rho = c(0, 0.01, 0.20, 0.50)`
- Queen neighbors only
- `spillover_type = "both"`
- 25 design resamples and 10 outcome resamples
- 160,000 MLE fits total
