---
title: "SpillSpatialDepSim — Unified Analysis Report"
author: "Andrew Walther"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 10, fig.height = 6, dpi = 120)

# Detect script directory for relative paths
script_dir <- tryCatch(
  dirname(knitr::current_input(dir = TRUE)),
  error = function(e) getwd()
)

source(file.path(script_dir, "03_analysis_functions.R"))
results_dir <- file.path(dirname(dirname(script_dir)), "results")
```

# Overview

This report presents results from the SpillSpatialDepSim unified simulation.
It covers all three grid sizes (2×4, 3×3, 3×4) and all 48 parameter scenarios
in a single document, replacing the inline-only output of
`SimEstimateAnalysisAll.Rmd` and `SimEstimateAnalysisMeans.Rmd`.

**Research question:** Does block-stratified treatment assignment produce more
precise estimates of intervention effects than random assignment, in the presence
of spillover effects and spatial autocorrelation?

**Key parameters:**

| Parameter | Symbol | Values |
|-----------|--------|--------|
| Intervention effect | beta | 1.0 (true) |
| Spillover effect    | psi  | 0.5, 0.6, 0.7, 0.8 |
| Spatial autocorrelation | rho | 0.00, 0.01 |
| Spillover type | — | TrtNoSpill (case 1), TrtSpill (case 2) |
| Grid sizes | — | 2×4 (70 combos), 3×3 (126 combos), 3×4 (924 combos) |

```{r load-data}
results <- load_unified_results(results_dir)
cat(sprintf("Loaded %d rows from sim_results_unified.rds\n", nrow(results)))
cat(sprintf("Grids: %s\n", paste(unique(results$grid), collapse = ", ")))
cat(sprintf("Parameters: %s\n", paste(unique(results$param), collapse = ", ")))
```

---

# Intervention Effect (beta)

## MSE Distributions by Grid

### 2×4 Grid

```{r mse-box-2x4-beta-nospill, fig.cap="MSE distribution, 2x4 grid, TrtNoSpill"}
plot_mse_boxplot(results, param_nm = "beta", grid_nm = "2x4", spill = FALSE)
```

```{r mse-box-2x4-beta-spill, fig.cap="MSE distribution, 2x4 grid, TrtSpill"}
plot_mse_boxplot(results, param_nm = "beta", grid_nm = "2x4", spill = TRUE)
```

### 3×3 Grid

```{r mse-box-3x3-beta-nospill}
plot_mse_boxplot(results, param_nm = "beta", grid_nm = "3x3", spill = FALSE)
```

```{r mse-box-3x3-beta-spill}
plot_mse_boxplot(results, param_nm = "beta", grid_nm = "3x3", spill = TRUE)
```

### 3×4 Grid

```{r mse-box-3x4-beta-nospill}
plot_mse_boxplot(results, param_nm = "beta", grid_nm = "3x4", spill = FALSE)
```

```{r mse-box-3x4-beta-spill}
plot_mse_boxplot(results, param_nm = "beta", grid_nm = "3x4", spill = TRUE)
```

## All Grids Side-by-Side

```{r mse-all-grids-beta-nospill, fig.width=12}
plot_mse_all_grids(results, param_nm = "beta", spill = FALSE)
```

```{r mse-all-grids-beta-spill, fig.width=12}
plot_mse_all_grids(results, param_nm = "beta", spill = TRUE)
```

## Mean MSE by Assignment Method

```{r mse-means-2x4-beta, fig.height=8}
plot_mse_means(results, param_nm = "beta", grid_nm = "2x4")
```

```{r mse-means-3x3-beta, fig.height=8}
plot_mse_means(results, param_nm = "beta", grid_nm = "3x3")
```

```{r mse-means-3x4-beta, fig.height=8}
plot_mse_means(results, param_nm = "beta", grid_nm = "3x4")
```

---

# Spillover Effect (psi)

## MSE Distributions

```{r mse-all-grids-psi-nospill, fig.width=12}
plot_mse_all_grids(results, param_nm = "psi", spill = FALSE)
```

```{r mse-all-grids-psi-spill, fig.width=12}
plot_mse_all_grids(results, param_nm = "psi", spill = TRUE)
```

---

# Baseline (alpha) and Spatial Autocorrelation (rho)

```{r mse-all-grids-alpha, fig.width=12}
plot_mse_all_grids(results, param_nm = "alpha")
```

```{r mse-all-grids-rho, fig.width=12}
plot_mse_all_grids(results, param_nm = "rho")
```

---

# Optimal Treatment Combinations

Minimum-MSE treatment combination for each scenario (parameter = beta).

```{r optimal-combos}
opt <- get_optimal_combos(results, param_nm = "beta")
knitr::kable(opt,
             caption = "Minimum-MSE treatment combination per scenario (beta)",
             digits  = 4)
```

Proportion of optimal combos that are block-stratified assignments:

```{r optimal-prop-block}
cat(sprintf("%.1f%% of optimal combos are block-stratified assignments\n",
            100 * mean(opt$is_block)))
```

---

# Random vs. Block Stratification Summary

```{r comparison-table}
comp <- table_mse_comparison(results, param_nm = "beta")
knitr::kable(comp,
             caption = "Mean and median MSE by assignment method — beta",
             digits  = 4)
```

---

# Session Information

```{r session-info, echo=TRUE}
sessionInfo()
```
